### 2015-09-09 RMS/submission.tex
add outlines & part of Sect RTMaude

% This is LLNCS.DOC the documentation file of
% the LaTeX2e class from Springer-Verlag
% for Lecture Notes in Computer Science, version 2.4
\documentclass{llncs}
\usepackage{alltt}
\usepackage{amsmath}
%\usepackage{llncsdoc}
%
\begin{document}
%\thispagestyle{empty}
%\begin{flushleft}
%\end{flushleft}

\title{Formal Analysis of Rate-Monotonic Scheduling Implementation via Real-Time Maude}
\author{Jiaxiang Liu\inst{1,2}}
\institute{School of Software, Tsinghua University, Beijing, China
  \and \'Ecole Polytechnique, Palaiseau, France}
\maketitle
\thispagestyle{empty}

\section{Introduction}

\section{Real-Time Maude}

Real-Time Maude is a language and tool that extends Maude to support
the formal specification and analysis of real-time systems.

\subsection{Specification}

A Real-Time Maude module specifies a \emph{real-time rewrite theory}
$(\Sigma, E\cup A , IR, TR)$, where:

\begin{itemize}
\item $\Sigma$ is an algebraic \emph{signature}, that is, a set of
  declarations of \emph{sorts}, \emph{subsorts} and \emph{function
    symbols}.

\item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
  theory}, with $E$ a set of possibly conditional equations, and $A$ a
  set of equational axioms such as associativiy, commutativity and
  identity.  $(\Sigma, E\cup A)$ specifies the system's state space as
  an algebraic data type, and includes a built-in specification of a
  sort \verb|Time|.

\item $IR$ is a set of \emph{labeled conditional rewrite rules}
  specifying the system's local transitions, each of which has the
  form $[l]~:~t\rightarrow t'\mbox{ \textbf{if}
  }\bigwedge^n_{j=1}cond_j$, where each $cond_j$ is an equality
  $u_j=v_j$, and $l$ is a \emph{label}. Such a rule specifies an
  \emph{instantaneous transition} from an instance of $t$ to the
  corresponding instance of $t'$, \emph{provided} the conditions hold.

\item $TR$ is a set of \emph{tick rules} $[l]~:~\{t\}\rightarrow\{t'\}
  \mbox{ \textbf{in time} }\tau\mbox{ \textbf{if} }cond$ that advance
  time in the \emph{entire} state $t$ by $\tau$ time units.
\end{itemize}

A class declaration $\texttt{class }C\texttt{ |
}att_1\texttt{:}s_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}s_n$
declares a class $C$ with attributes $att_1$ to $att_n$ of sorts $s_1$
to $s_n$. An \emph{object} of class $C$ in a given state is
represented as a term $\texttt{< } O\texttt{:} C \texttt{ | }
att_1\texttt{:}val_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}val_n\texttt{
  >}$ of sort \verb|Object|, where $O$, of sort \verb|Oid|, is the object's
\emph{identifier}, and where $val_1$ to $val_n$ are the current values of the
attributes $att_1$ to $att_n$. A \emph{subclass} inherits all the attributes
and rules of its superclasses.

\subsection{Formal Analysis}
In this

\section{Rate-Monotonic Scheduling Algorithm and the Implementation}

\section{Formalizing the RMS Implementation}

\section{Formal Analysis}
\subsection{Properties}
\subsection{Completeness of the Analysis}

\section{Related Work}

\section{Conclusion}

\end{document}

### 2015-09-09 RMS/submission.tex
finish Sect. RTMaude

@@
 represented as a term $\texttt{< } O\texttt{:} C \texttt{ | }
-att_1\texttt{:}val_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}val_n\texttt{
-  >}$ of sort \verb|Object|, where $O$, of sort \verb|Oid|, is the object's
-\emph{identifier}, and where $val_1$ to $val_n$ are the current values of the
-attributes $att_1$ to $att_n$. A \emph{subclass} inherits all the attributes
-and rules of its superclasses.
+att_1\texttt{:}val_1\texttt{,} \ldots
+\texttt{,}att_n\texttt{:}val_n\texttt{ >}$ of sort \verb|Object|,
+where $O$, of sort \verb|Oid|, is the object's \emph{identifier}, and
+where $val_1$ to $val_n$ are the current values of the attributes
+$att_1$ to $att_n$. A \emph{subclass} inherits all the attributes and
+rules of its superclasses.
 
 \subsection{Formal Analysis}
-In this
+In this paper, we only consider Real-Time Maude's \emph{linear
+  temporal logic model checker}, which analyzes whether \emph{each}
+behavior satisfies a temporal logic formula. \emph{State propositions}
+are terms of sort \verb|Prop|, and their symantics is defined by
+equations $\texttt{ceq } statePattern \texttt{ |= } prop \texttt{ = }
+b \texttt{ if } cond$, with $b$ a term of sort \verb|Bool|, stating
+that $prop$ evaluates to $b$ in states that are instances of
+$statePattern$ when the condition $cond$ holds. These equations
+together define $prop$ to hold in all states $t$ where $t \texttt{ |=
+} prop$ evaluates to \verb|true|. A temporal logic \emph{formula} is
+constructed by state propositions and temporal logic operators such as
+\verb|True|, \verb|False|, \verb|~|(negation), \verb|/\|, \verb|\/|,
+\verb|->|(implication), \verb|[]|(``always''),
+\verb|<>|(``eventually'') and \verb|U|(``until''). Real-Time Maude
+provides both \emph{unbounded} and \emph{time-bounded} LTL model
+checking. The time-bounded model checking command
+\begin{alltt}
+  (mc \(t\) |=t \(formula\) in time <= \(timeLimit\) .)
+\end{alltt}
+checks whether the temporal logic formula holds in all behaviors up to
+duration $timeLimit$ starting from the initial state $t$.
 

### 2015-09-10 RMS/submission.tex
add part of Sect. 3.1

@@
 
+\subsection{Formulation of the Standard Setting}
+The frequently used setting of the RMS algorithm for analysis
+considers a task set consisting only of $n$ periodic tasks
+$\tau_1,\ldots,\tau_n$. Task $\tau_i$ has a period $T_i$ and a
+computation time $C_i$. First jobs of all tasks are assumed to be
+instantiated simultaneously.  This means that jobs corresponding to
+task $\tau_i$ are initiated at times $kT_i, k\ge 0$. The job initiated
+at time $kT_i$ has $(k+1)T_i$ as its deadline, the initiation time of
+the next job. The RMS algorithm chooses the labeling such that $T_1\le
+T_2\le \ldots \le T_n$. Consequently, $\tau_i$ receives priority
+$i$. The following assumptions are made:
+
+(A1) Computation time $C_i$ for each task $\tau_i$ is constant and
+does not vary with time.
+
+(A2) Tasks are independent, such that they are ready to run at their
+initiation times and can be preempted instantly (ignoring all
+blocking).
+
+(A3) All overhead, such as task swapping times, is ignored.
+
 \section{Formalizing the RMS Implementation}

### 2015-09-11 RMS/submission.tex
introduce pseudo-code

@@
 \usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 %\usepackage{llncsdoc}
-%
+
+\newcommand{\hide}[1]{\ignorespaces}
+
 \begin{document}
@@
 instantiated simultaneously. This means that jobs corresponding to
-task $\tau_i$ are initiated at times $kT_i, k\ge 0$. The job initiated
-at time $kT_i$ has $(k+1)T_i$ as its deadline, the initiation time of
+task $\tau_i$ are initiated at times $kT_i, k\ge 0$. Deadlines consist
+of runability constraints only, that is, the job initiated at time
+$kT_i$ has $(k+1)T_i$ as its deadline, which is the initiation time of
 the next job. The RMS algorithm chooses the labeling such that $T_1\le
@@
 
+In this paper, our application of the RMS algorithm meets the
+assumption~(A2), while we would try to relax (A1) and (A3) in our
+analysis model.
+
+\subsection{The Implementation of RMS}
+The algorithm of the RMS is straightforward, and it is easy to
+implement it in pratical systems. However, the way to implement it is
+not unique. Our target implementation to analyze is from a realistic
+avionic operating system. Interrupts triggered by the clock would come
+every $T$, which we call \emph{interrupt cycle}. When an interrupt
+request comes, if the system is interruptable, i.e. the interrupt
+switch is enabled, the funtion $schedule()$ will be called; otherwise
+$schedule()$ will be called once the interrupt switch becomes enable.
+The pseudo code of $schedule()$ is shown as
+Algorithm~\ref{a:schedule}, where $taskList$ is the list of periodic
+tasks, which are needed to be scheduled, and assumed ordered
+descendingly by priorities, and where both variables $taskList$ and
+$timer$ are global. In this implementation, the period $T_i$ of each
+task is a multiple of $T$, and the tasks are independent, meeting the
+assumption~(A2).
+
+\begin{algorithm}
+  \caption{The C-Like Pseudo Code of $schedule()$}
+  \label{a:schedule}
+  \begin{algorithmic}[1]
+\Function{$schedule$}{$ $}{}
+  \State \Call{$int\_o\!f\!\!f$}{$ $}; \Comment{to disable interrupts}
+  \State \Call{$updateStatus$}{$taskList$};
+  \State $timer = timer + 1$;
+  \State $p = taskList$;
+  \While{$p$} 
+    \If{$p\rightarrow status == \textit{INTERRUPT}$}
+      \State \Return;
+    \ElsIf{$p\rightarrow status == \textit{READY}$}      
+      \State $p\rightarrow status = \textit{RUNNING}$;
+      \State \Call{$int\_on$}{$ $}; \Comment{to enable interrupts}
+      \State $p\rightarrow function()$; \Comment{to run the task}
+      \State \Call{$int\_o\!f\!\!f$}{$ $};
+      \State $p\rightarrow status = \textit{DORMANT}$;
+    \EndIf
+    \State $p = p\rightarrow next$;
+  \EndWhile
+\EndFunction
+\Function{$updateStatus$}{$p$}
+  \While{$p$}
+    \If{$p\rightarrow status == \textit{RUNNING}$}
+      \State $p\rightarrow status = \textit{INTERRUPT}$;
+    \EndIf
+    \If{$timer~\%~(p\rightarrow period) == 0$} \Comment{the task should be initiated}
+      \If{$p\rightarrow status == \textit{DORMANT}$} 
+        \State $p\rightarrow status = \textit{READY}$;
+      \Else \Comment{the status is \textit{READY} or \textit{INTERRUPT}}
+	\State \Call{$reportTaskError$}{$p$}; \Comment{the task misses its deadline}
+      \EndIf
+    \EndIf
+    \State $p = p\rightarrow next$;
+  \EndWhile
+\EndFunction
+  \end{algorithmic}
+\end{algorithm}
+
 \section{Formalizing the RMS Implementation}

### 2015-09-12 RMS/submission.tex
modify Sect. 3

@@
 \section{Real-Time Maude}
-
 Real-Time Maude is a language and tool that extends Maude to support
@@
 \subsection{Specification}
-
 A Real-Time Maude module specifies a \emph{real-time rewrite theory}
 $(\Sigma, E\cup A , IR, TR)$, where:
-
 \begin{itemize}
@@
     symbols}.
-
 \item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
@@
   sort \verb|Time|.
-
 \item $IR$ is a set of \emph{labeled conditional rewrite rules}
@@
   corresponding instance of $t'$, \emph{provided} the conditions hold.
-
 \item $TR$ is a set of \emph{tick rules} $[l]~:~\{t\}\rightarrow\{t'\}
@@
 implement it in pratical systems. However, the way to implement it is
-not unique. Our target implementation to analyze is from a realistic
-avionic operating system. Interrupts triggered by the clock would come
-every $T$, which we call \emph{interrupt cycle}. When an interrupt
-request comes, if the system is interruptable, i.e. the interrupt
-switch is enabled, the funtion $schedule()$ will be called; otherwise
-$schedule()$ will be called once the interrupt switch becomes enable.
-The pseudo code of $schedule()$ is shown as
-Algorithm~\ref{a:schedule}, where $taskList$ is the list of periodic
-tasks, which are needed to be scheduled, and assumed ordered
-descendingly by priorities, and where both variables $taskList$ and
-$timer$ are global. In this implementation, the period $T_i$ of each
-task is a multiple of $T$, and the tasks are independent, meeting the
+not unique. Our target implementation to analyze is part of a
+realistic avionic operating system from our industrial
+partner. Interrupts triggered by the clock would come every $T$, which
+we call \emph{interrupt cycle}. When an interrupt request comes, if
+the system is interruptable, i.e. the interrupt mask is cleared, the
+funtion $schedule()$ will be called; otherwise $schedule()$ will be
+called once the interrupt mask becomes cleared.  The pseudocode of
+$schedule()$ is shown as Algorithm~\ref{a:schedule}, where $taskList$
+is the list of periodic tasks, which are needed to be scheduled, and
+assumed ordered descendingly by priorities, and where both variables
+$taskList$ and $timer$ are global. In this implementation, there is
+only one kind of interrupt, the period $T_i$ of each task is a
+multiple of $T$, and the tasks are independent, meeting the
 assumption~(A2).
@@
 \begin{algorithm}
-  \caption{The C-Like Pseudo Code of $schedule()$}
+  \caption{The C-Like Pseudocode of $schedule()$}
   \label{a:schedule}
@@
       \State \Call{$int\_on$}{$ $}; \Comment{to enable interrupts}
-      \State $p\rightarrow function()$; \Comment{to run the task}
+      \State $p\rightarrow function()$; \Comment{to run the task} \label{l:function}
       \State \Call{$int\_o\!f\!\!f$}{$ $};
@@
 
+The function $updateStatus()$ updates status of all tasks in the list:
+if the task is running when the interrupt is handled, it becomes
+interrupted\footnote{Note that the status \textit{INTERRUPT} indicates
+  the task is interrupted for the moment, or was interrupted before
+  but is not finished running yet.}; the task, which is at its
+initiated time, would be set to be ready if its previous corresponding
+job is finished, or produce an error otherwise. Notice that
+$schedule()$ is called only when the periodic interrupt is handled. It
+can be also interrupted while running some task (Line~\ref{l:function}
+in Algorithm~\ref{a:schedule}), such that the running of $schedule()$
+can be nested.
+
 \section{Formalizing the RMS Implementation}

### 2015-09-26 RMS/submission.tex
writting section 4.5

@@
 
-(A3) All overhead, such as task swapping times, is ignored.
+(A3) All overhead, such as task switching times, is ignored.
 
-In this paper, our application of the RMS algorithm meets the
-assumption~(A2), while we would try to relax (A1) and (A3) in our
-analysis model.
+In this paper, we consider an implementation instead of the RMS
+algorithm itself, thus the model would be more complicated than this
+ideal formulation.  Assumptions~(A1) and (A3) will be relaxed to shape a more
+realisitc analysis model, as shown below.
 
@@
 the system is interruptable, i.e. the interrupt mask is cleared, the
-funtion $schedule()$ will be called; otherwise $schedule()$ will be
-called once the interrupt mask becomes cleared.  The pseudocode of
-$schedule()$ is shown as Algorithm~\ref{a:schedule}, where $taskList$
-is the list of periodic tasks, which are needed to be scheduled, and
-assumed ordered descendingly by priorities, and where both variables
-$taskList$ and $timer$ are global. In this implementation, there is
-only one kind of interrupt, the period $T_i$ of each task is a
-multiple of $T$, and the tasks are independent, meeting the
-assumption~(A2).
+function $schedule()$ will be called; otherwise the handler function
+$schedule()$ will be pending until the interrupt mask becomes cleared.
+The pseudocode of $schedule()$ is shown as Algorithm~\ref{a:schedule},
+where $taskList$ is the list of periodic tasks, which are needed to be
+scheduled, and assumed ordered descendingly by priorities, and where
+both variables $taskList$ and $timer$ are global. In this
+implementation, there is only one kind of interrupt, the period $T_i$
+of each task is a multiple of $T$, and the tasks are independent,
+meeting assumption~(A2).
 
@@
   \State \Call{$updateStatus$}{$taskList$};
-  \State $timer = timer + 1$;
+  \State $timer = timer + 1$; \label{l:timer}
   \State $p = taskList$;
@@
   \While{$p$}
-    \If{$p\rightarrow status == \textit{RUNNING}$}
+    \If{$p\rightarrow status == \textit{RUNNING}$} \label{l:startupdate}
       \State $p\rightarrow status = \textit{INTERRUPT}$;
@@
       \EndIf
-    \EndIf
+    \EndIf \label{l:endupdate}
     \State $p = p\rightarrow next$;
@@
 \section{Formalizing the RMS Implementation}
+Based on the code, we model the implementation under the following
+assumptions:
+
+(A1') Computation time $C_i$ for each task $\tau_i$ is not constant,
+varying randomly between minimum $C^{min}_i$ and maximum $C^{max}_i$.
+
+(A2) Tasks are independent, such that they are ready to run at their
+initiation times and can be preempted instanly.
+
+(A3') The times for scheduling and task switching should be
+considered, while other overhead is ignored.
+
+These assumptions make our model different with the standard
+formulation. For instance, due to the interrupt masking and
+consideration of scheduling overhead, jobs corresponding to task
+$\tau_i$ could not be initiated at exactly $kT_i$, but a bit later.
+Note that (A2) says jobs are ready to run at their initiation times,
+however, they cannot run at their initiation times, because scheduling
+takes time.
+
+\subsection{Some Basic Data Types}
+In our model, tasks are identified with their indexes of sort
+\verb|Nat| in the $taskList$. We define a sort \verb|MaybeNat|
+wrapping \verb|Nat|s to refer to some task, with \emph{constructor}
+\verb|some| followed by a \verb|Nat| $n$ indicating the task with
+index $n$, and \verb|none| for no task:
+\begin{verbatim}
+  op none : -> MaybeNat [ctor] .
+  op some_ : Nat -> MaybeNat [ctor] .
+\end{verbatim}
+
+A sort \verb|Stack| is introduced to simulate the stack of the system,
+storing the tasks that are being interrupted, and equipped with
+operations \verb|push|, \verb|pop| and \verb|peek| on it.
+\begin{verbatim}
+  op bottom : -> Stack [ctor] .
+  op _#_ : Nat Stack -> Stack [ctor] .
+\end{verbatim}
+
+We also need a sort \verb|Interval| denoting the interval, within
+which the computation time of a task varies, and a sort \verb|Counter|
+to represent how long some task has run and how long it should run.
+\begin{verbatim}
+  op [_,_] : Time Time -> Interval [ctor] .
+  op [_/_] : Time Interval -> Counter [ctor] .
+\end{verbatim}
+
+At last, to make our model checkable by \emph{untimed model-checking},
+it is reasonable to reset the global variable $timer$ when it reaches
+an upperbound while increasing (see Line~\ref{l:timer} in
+Algorithm~\ref{a:schedule}) in the model. Then $timer$ is of sort
+\verb|Timer| and the upperbound would be the least common multiple of
+the periods of all tasks.
+\begin{verbatim}
+  op [_/_] : Nat NzNat -> Timer [ctor] .
+\end{verbatim}
+
+\subsection{Modeling the System States}
+Abstracting from some details, the running system could be considered
+as consisting of several parts: the tasks which are scheduled, the
+scheduler itself, the hardware including registers and stacks, and the
+interrupt source. The scheduler, i.e. the function $schedule()$, has
+only the variable $timer$ to be interesting, thus it can be described
+by a single variable. We will present the modeling of the other parts
+one by one.
+
+\subsubsection{Tasks}
+In this paper, since we are trying to analyze the implementation of
+the scheduler, each task will be abstracted from its functionality and
+treated as a \verb|Counter|. As mentioned above, times for scheduling
+and task switching will be also considered in the model. They are just
+seen as two system tasks. Every task is modeled as an object instance
+of some subclass of the base class \verb|Task|:
+\begin{verbatim}
+  class Task | cnt : Counter .
+  op error : -> Object [ctor] .
+\end{verbatim}
+The attribute \verb|cnt| denotes the computation time of the task,
+while \verb|error| is an object indicating some task which misses its
+deadline.
+
+A periodic task, which is needed to be scheduled, is an object
+instance of the subclass \verb|PTask| with additional attributes
+\verb|priority|, \verb|period| and \verb|status|:
+\begin{verbatim}
+  class PTask | priority : Nat, period : NzNat, status : Status .
+  subclass PTask < Task .
+\end{verbatim}
+where \verb|Status| is a sort with four constant constructors, just as
+in the implementation:
+\begin{verbatim}
+  ops RUNNING INTERRUPT READY DORMANT : -> Status [ctor] .
+\end{verbatim}
+The list of periodic tasks, the variable $taskList$ in the
+implementation, is modeled as an instance of the sort \verb|TaskList|,
+which is a list of \verb|PTask|s\footnote{Following the Maude
+  convention, variables would be written in capital letters.}:
+\begin{verbatim}
+  op null : -> TaskList [ctor] .
+  op _::_ : Object TaskList ~> TaskList [ctor] .
+  mb (< O:Oid : PTask |> :: L:TaskList) : TaskList .
+  mb (error :: L:TaskList) : TaskList .
+\end{verbatim}
+As mentioned already, periodic tasks would be identified by their
+indexes in the list.
+
+On the other hand, a system task is an object instance of the subclass
+\verb|SysTask| of \verb|Task| with no extra attributes:
+\begin{verbatim}
+  class SysTask .            subclass SysTask < Task .
+\end{verbatim}
+Different from periodic tasks, system tasks would be organized in a
+multiset of sort \verb|SysTasks|, and identified by their \verb|Oid|s.
+We abstract here from the detailed definitions thanks to the
+similarity.
+
+\subsubsection{Hardware} Our model considers two parts of hardware relating
+to the interrupt handling inside the system, the registers and the
+stack.
+
+The set of registers is modeled as an object instance of the class
+\verb|Regs|, with attributes \verb|pc| denoting the program counter,
+\verb|mask| for the interrupt masking flag and \verb|ir| for the
+interrupt request flag.
+\begin{verbatim}
+  class Regs | pc : TaskID, mask : Bool, ir : Bool .
+\end{verbatim}
+where the sort \verb|TaskID| is a supersort of \verb|MaybeNat| and
+\verb|Oid|, referring to some task.
+\begin{verbatim}
+  subsorts MaybeNat Oid < TaskID .
+\end{verbatim}
+
+Some operations, such as \verb|getPc|, \verb|setMask| and so on, are
+also defined on the class \verb|Regs|.
+
+Then the hardware is naturally described by the sort \verb|Hardware|:
+\begin{verbatim}
+  op [_;_] : Object Stack ~> Hardware [ctor] .
+  mb ([ < O:Oid : Regs |> ; S:Stack ]) : Hardware .
+\end{verbatim}
+
+\subsubsection{Interrupt Source}
+The interrupt source is modeled in our model as an object of class \verb|IntSrc|,
+with attribute \verb|cycle| denoting the interrupt cycle:
+\begin{verbatim}
+  class IntSrc | val : Time, cycle : Time .
+\end{verbatim}
+
+\subsubsection{System}
+The system in the model is just a composition of the parts introduced
+above, with a sort \verb|System|\footnote{Some variable declarations
+  are not shown for simplicity.}:
+\begin{verbatim}
+  op _____ : 
+       TaskList Timer SysTasks Hardware Object ~> System [ctor] .
+  mb (L T STS HW < O:Oid : IntSrc |>) : System .
+\end{verbatim}
+
+\subsection{Interrupt Requesting}
+Interrupt requests are performed by the source exactly every cycle
+$T$, when the attribute \verb|val| decreases to \verb|zero| while time
+advances. This is modeled by the following instanous conditional rule
+applied on \verb|System|:
+\begin{verbatim}
+  crl [interrupt-request] :
+    (L T STS HW ISRC) => (L T STS (HW).intReq reset(ISRC))
+    if (ISRC).timeout .
+\end{verbatim}
+where the operator \verb|_.timeout| examines whether the attribute
+\verb|val| equals to \verb|zero|, and \verb|_.intReq| sets the
+\verb|ir| flag indicating there is an interrupt request to be handled:
+\begin{verbatim}
+  op _.intReq : Hardware -> Hardware .
+  eq [ REGS ; S ].intReq = [ (REGS).setIr ; S ] .
+\end{verbatim}
+Then the request will wait to be handled, which is explained in
+Section~\ref{ss:inthandling}.
+
+\subsection{Task Initiation}
+Periodic tasks are initiated sequently by exactly the function
+$updateStatus()$ in Algorithm~\ref{a:schedule}, which is modeled by
+the recursive operation as below:
+\begin{verbatim}
+  op updateStatus_with_ : TaskList Timer -> TaskList . 
+  eq updateStatus null with TIMER = null .
+  eq updateStatus (TASK :: L) with TIMER
+       = (update TASK with TIMER) :: (updateStatus L with TIMER) .
+\end{verbatim}
+with \verb|TIMER| the current value of the global variable $timer$,
+and \verb|update_with_| updating the status of individual task
+(Lines~\ref{l:startupdate}-\ref{l:endupdate} in
+Algorithm~\ref{a:schedule})
+\begin{verbatim}
+  op update_with_ : Object Timer ~> Object .
+  ceq update < O : PTask | period : T, status : ST > with TIMER
+        = if ST == DORMANT then < O : PTask | status : READY >
+          else error fi
+      if TIMER rem T == 0 .
+  eq update < O : PTask | status : ST > with TIMER
+       = if ST == RUNNING then < O : PTask | status : INTERRUPT >
+         else < O : PTask |> fi [owise] .
+\end{verbatim}
+In the case where \verb|TIMER|($timer$) can be divided by the task's
+period, i.e. the task should be initiated, if the status is
+\verb|DORMANT|, it should be ready to run; otherwise it means the
+previous job of the task is not finished, thus it misses its deadline,
+producing an \verb|error|. In the other case where the tasks should
+not be initiated, the status of the task changes only if it is
+\verb|RUNNING|. We can easily see \verb|updateStatus_with_| behaves
+the same as $updateStatus()$.
+
+\subsection{Interrupt Handling}
+\label{ss:inthandling}
+When an interrupt request comes, it may not be ``seen'' immediately by
+the system. It requires the \verb|mask| flag to be cleared. Once the
+request is seen, it is handled by performing two stages: the interrupt
+mechanism of the hardware (such as clearing \verb|ir|, pushing context
+into stack and so on) and running the $schedule()$ function. This is
+modeled by the following instanous rewrite rule:
+\begin{verbatim}
+  crl [interrupt-handle] :
+    SYSTEM => ((SYSTEM).interrupt).startScheduling
+    if (SYSTEM).existInt .
+\end{verbatim}
+where \verb|_.existInt| checks whether \verb|mask| is cleared
+\emph{and} \verb|ir| is set. The operation \verb|_.interrupt| models
+the interrupt mechanism performed by the hardware and does four
+things: (i)clearing the \verb|ir| flag, which means the request has
+been handled; (ii)pushing the current \verb|pc| value into the stack,
+storing the interrupted context; (iii)assigning \verb|scheduling| of
+sort \verb|Oid| to \verb|pc|, which indicates that $schedule()$ is
+running; and (iv)setting the \verb|mask| flag, to mask the coming
+interrupt requests.
+
+It is worth pointing out that \emph{scheduling} in our model does not
+refer to the stage in which $schedule()$ is running. We use it to
+refer to the stage scheduling the first should-be-run periodic task,
+i.e.  the code strictly before Line~\ref{l:function} in
+Algorithm~\ref{a:schedule}. Therefore,
+\begin{definition}
+  The \emph{scheduling time} talked about in this paper consists of
+  the time for switching from a running task to the function
+  $schedule()$ when handling interrupts, the time spent by
+  $schedule()$ finding and setting the \emph{first} should-be-run
+  periodic task, and the time for switching from $schedule()$ to that
+  first should-be-run task.
+\end{definition}
+Similarly, \emph{switching} in our model refers to the stage finding
+out the next should-be-run periodic task when one is finished.
+\begin{definition}
+  The \emph{switching time} in this paper consists of the time for
+  switching from a finished task back into $schedule()$, the time
+  spent by $schedule()$ finding and setting the \emph{next}
+  should-be-run periodic task, and the time for switching from
+  $schedule()$ to that next should-be-run task.
+\end{definition}
+
+\subsection{Timed Behaviours of the System}
 

### 2015-09-26 RMS/submission.tex
finish section 4.5

@@
   \State \Call{$int\_o\!f\!\!f$}{$ $}; \Comment{to disable interrupts}
-  \State \Call{$updateStatus$}{$taskList$};
-  \State $timer = timer + 1$; \label{l:timer}
+  \State \Call{$updateStatus$}{$taskList$}; \label{l:updatestatus}
+  \State $timer = timer + 1$; \label{l:timer} \label{l:inc}
   \State $p = taskList$;
-  \While{$p$} 
+  \While{$p$} \label{l:startrun1st}
     \If{$p\rightarrow status == \textit{INTERRUPT}$}
@@
       \State $p\rightarrow status = \textit{RUNNING}$;
-      \State \Call{$int\_on$}{$ $}; \Comment{to enable interrupts}
+      \State \Call{$int\_on$}{$ $}; \Comment{to enable interrupts} \label{l:endrun1st}
       \State $p\rightarrow function()$; \Comment{to run the task} \label{l:function}
@@
 We also need a sort \verb|Interval| denoting the interval, within
-which the computation time of a task varies, and a sort \verb|Counter|
-to represent how long some task has run and how long it should run.
+which the computation time of a task varies and which we call
+\emph{possible finishing interval}, and a sort \verb|Counter| to
+represent the time some task has been running and the corresponding
+possible finishing interval.
 \begin{verbatim}
@@
 
-\subsection{Interrupt Handling}
+\subsection{Interrupt Handling and Task Scheduling}
 \label{ss:inthandling}
@@
 running; and (iv)setting the \verb|mask| flag, to mask the coming
-interrupt requests.
+interrupt requests. As for \verb|_.startScheduling|, it performs
+updating the status of $taskList$ and increasing $timer$ by $1$,
+corresponding to Line~\ref{l:updatestatus} and \ref{l:inc} in
+Algorithm~\ref{a:schedule}.
+\begin{verbatim}
+  op _.startScheduling : System -> System .
+  eq (L T STS HW ISRC).startScheduling 
+       = ((updateStatus L with T) inc(T) STS HW ISRC) .
+\end{verbatim}
 
-It is worth pointing out that \emph{scheduling} in our model does not
-refer to the stage in which $schedule()$ is running. We use it to
-refer to the stage scheduling the first should-be-run periodic task,
-i.e.  the code strictly before Line~\ref{l:function} in
+It is worth pointing out here that \emph{scheduling} in our model does
+not refer to the stage in which $schedule()$ is running. We use it to
+refer to, for simplicity, the stage scheduling the first should-be-run
+periodic task, i.e.  the code strictly before Line~\ref{l:function} in
 Algorithm~\ref{a:schedule}. Therefore,
@@
 
+With our terminology, when the running time of the system task
+\verb|scheduling| reaches its possible finishing interval, the
+following rule may apply to finish the scheduling stage:
+\begin{verbatim}
+  crl [scheduling-finish] :
+    (L T STS HW ISRC) => (SYSTEM).finishScheduling
+    if SYSTEM := (L T STS HW ISRC) 
+       /\ (SYSTEM).running == scheduling 
+       /\ scheduling mayFinish?in STS .
+\end{verbatim}
+where operation \verb|_.running| returns the current \verb|pc| value
+of the system and \verb|_mayFinish?in_| checks if the running time of
+the task reaches its possible finishing interval:
+\begin{verbatim}
+  op _mayFinish?in_ : Oid SysTasks ~> Bool .
+  eq O mayFinish?in [ < O : SysTask | cnt : C > REST ] 
+       = C mayFinish? .
+  op _mayFinish? : Counter -> Bool .
+  eq [ R / [ MIN , MAX ] ] mayFinish?
+       = if R lt MIN then false else true fi .
+\end{verbatim}
+And the operation \verb|_.finishScheduling| performs the remaining
+instructions, which are left by \verb|_.startScheduling|, in the
+scheduling stage: finding the first should-be-run periodic task and
+setting it to run (Line~\ref{l:startrun1st}-\ref{l:endrun1st} in
+Algorithm~\ref{a:schedule}).
+\begin{verbatim}
+  op _.finishScheduling : System -> System .
+  eq (L T STS HW ISRC).finishScheduling
+       = (L T (finish scheduling in STS) HW ISRC).run1stTask .
+\end{verbatim}
+where \verb|finish_in_| resets the counter of task \verb|scheduling|,
+and \verb|_.run1stTask| models
+Line~\ref{l:startrun1st}-\ref{l:endrun1st} in
+Algorithm~\ref{a:schedule}, searching the task with highest priority
+that has status \verb|INTERRUPT| or \verb|READY| then performing an
+\emph{interrupt return} or letting it run respectively.
+
+Similar to \verb|scheduling|, the \verb|switching| stage starts when
+the running time of the current running periodic task reaches its
+possible finishing interval and finishes when its own running time
+does so, with the two following similar rules:
+\begin{verbatim}
+  crl [task-finish] :
+    (L T STS HW ISRC) => (SYSTEM).startSwitching
+    if SYSTEM := (L T STS HW ISRC)
+       /\ some N := (SYSTEM).running
+       /\ some N mayFinish?in L .
+  crl [switching-finish] :
+    (L T STS HW ISRC) => (SYSTEM).finishSwitching
+    if SYSTEM := (L T STS HW ISRC)
+       /\ (SYSTEM).running == switching
+       /\ switching mayFinish?in STS .
+\end{verbatim}
+
 \subsection{Timed Behaviours of the System}

### 2015-10-01 RMS/submission.tex
finishing section 4

@@
 \section{Introduction}
-
-\section{Real-Time Maude}
-Real-Time Maude is a language and tool that extends Maude to support
-the formal specification and analysis of real-time systems.
-
-\subsection{Specification}
-A Real-Time Maude module specifies a \emph{real-time rewrite theory}
-$(\Sigma, E\cup A , IR, TR)$, where:
-\begin{itemize}
-\item $\Sigma$ is an algebraic \emph{signature}, that is, a set of
-  declarations of \emph{sorts}, \emph{subsorts} and \emph{function
-    symbols}.
-\item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
-  theory}, with $E$ a set of possibly conditional equations, and $A$ a
-  set of equational axioms such as associativiy, commutativity and
-  identity.  $(\Sigma, E\cup A)$ specifies the system's state space as
-  an algebraic data type, and includes a built-in specification of a
-  sort \verb|Time|.
-\item $IR$ is a set of \emph{labeled conditional rewrite rules}
-  specifying the system's local transitions, each of which has the
-  form $[l]~:~t\rightarrow t'\mbox{ \textbf{if}
-  }\bigwedge^n_{j=1}cond_j$, where each $cond_j$ is an equality
-  $u_j=v_j$, and $l$ is a \emph{label}. Such a rule specifies an
-  \emph{instantaneous transition} from an instance of $t$ to the
-  corresponding instance of $t'$, \emph{provided} the conditions hold.
-\item $TR$ is a set of \emph{tick rules} $[l]~:~\{t\}\rightarrow\{t'\}
-  \mbox{ \textbf{in time} }\tau\mbox{ \textbf{if} }cond$ that advance
-  time in the \emph{entire} state $t$ by $\tau$ time units.
-\end{itemize}
-
-A class declaration $\texttt{class }C\texttt{ |
-}att_1\texttt{:}s_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}s_n$
-declares a class $C$ with attributes $att_1$ to $att_n$ of sorts $s_1$
-to $s_n$. An \emph{object} of class $C$ in a given state is
-represented as a term $\texttt{< } O\texttt{:} C \texttt{ | }
-att_1\texttt{:}val_1\texttt{,} \ldots
-\texttt{,}att_n\texttt{:}val_n\texttt{ >}$ of sort \verb|Object|,
-where $O$, of sort \verb|Oid|, is the object's \emph{identifier}, and
-where $val_1$ to $val_n$ are the current values of the attributes
-$att_1$ to $att_n$. A \emph{subclass} inherits all the attributes and
-rules of its superclasses.
-
-\subsection{Formal Analysis}
-In this paper, we only consider Real-Time Maude's \emph{linear
-  temporal logic model checker}, which analyzes whether \emph{each}
-behavior satisfies a temporal logic formula. \emph{State propositions}
-are terms of sort \verb|Prop|, and their symantics is defined by
-equations $\texttt{ceq } statePattern \texttt{ |= } prop \texttt{ = }
-b \texttt{ if } cond$, with $b$ a term of sort \verb|Bool|, stating
-that $prop$ evaluates to $b$ in states that are instances of
-$statePattern$ when the condition $cond$ holds. These equations
-together define $prop$ to hold in all states $t$ where $t \texttt{ |=
-} prop$ evaluates to \verb|true|. A temporal logic \emph{formula} is
-constructed by state propositions and temporal logic operators such as
-\verb|True|, \verb|False|, \verb|~|(negation), \verb|/\|, \verb|\/|,
-\verb|->|(implication), \verb|[]|(``always''),
-\verb|<>|(``eventually'') and \verb|U|(``until''). Real-Time Maude
-provides both \emph{unbounded} and \emph{time-bounded} LTL model
-checking. The time-bounded model checking command
-\begin{alltt}
-  (mc \(t\) |=t \(formula\) in time <= \(timeLimit\) .)
-\end{alltt}
-checks whether the temporal logic formula holds in all behaviors up to
-duration $timeLimit$ starting from the initial state $t$.
 
@@
 can be nested.
+
+\section{Real-Time Maude}
+Real-Time Maude is a language and tool that extends Maude to support
+the formal specification and analysis of real-time systems.
+
+\subsection{Specification}
+A Real-Time Maude module specifies a \emph{real-time rewrite theory}
+$(\Sigma, E\cup A , IR, TR)$, where:
+\begin{itemize}
+\item $\Sigma$ is an algebraic \emph{signature}, that is, a set of
+  declarations of \emph{sorts}, \emph{subsorts} and \emph{function
+    symbols}.
+\item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
+  theory}, with $E$ a set of possibly conditional equations, and $A$ a
+  set of equational axioms such as associativiy, commutativity and
+  identity.  $(\Sigma, E\cup A)$ specifies the system's state space as
+  an algebraic data type, and includes a built-in specification of a
+  sort \verb|Time|.
+\item $IR$ is a set of \emph{labeled conditional rewrite rules}
+  specifying the system's local transitions, each of which has the
+  form $[l]~:~t\rightarrow t'\mbox{ \textbf{if}
+  }\bigwedge^n_{j=1}cond_j$, where each $cond_j$ is an equality
+  $u_j=v_j$, and $l$ is a \emph{label}. Such a rule specifies an
+  \emph{instaneous transition} from an instance of $t$ to the
+  corresponding instance of $t'$, \emph{provided} the conditions hold.
+\item $TR$ is a set of \emph{tick rules} $[l]~:~\{t\}\rightarrow\{t'\}
+  \mbox{ \textbf{in time} }\tau\mbox{ \textbf{if} }cond$ that advance
+  time in the \emph{entire} state $t$ by $\tau$ time units.
+\end{itemize}
+
+A class declaration $\texttt{class }C\texttt{ |
+}att_1\texttt{:}s_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}s_n$
+declares a class $C$ with attributes $att_1$ to $att_n$ of sorts $s_1$
+to $s_n$. An \emph{object} of class $C$ in a given state is
+represented as a term $\texttt{< } O\texttt{:} C \texttt{ | }
+att_1\texttt{:}val_1\texttt{,} \ldots
+\texttt{,}att_n\texttt{:}val_n\texttt{ >}$ of sort \verb|Object|,
+where $O$, of sort \verb|Oid|, is the object's \emph{identifier}, and
+where $val_1$ to $val_n$ are the current values of the attributes
+$att_1$ to $att_n$. A \emph{subclass} inherits all the attributes and
+rules of its superclasses.
+
+\subsection{Formal Analysis}
+In this paper, we only consider Real-Time Maude's \emph{linear
+  temporal logic model checker}, which analyzes whether \emph{each}
+behavior satisfies a temporal logic formula. \emph{State propositions}
+are terms of sort \verb|Prop|, and their symantics is defined by
+equations $\texttt{ceq } statePattern \texttt{ |= } prop \texttt{ = }
+b \texttt{ if } cond$, with $b$ a term of sort \verb|Bool|, stating
+that $prop$ evaluates to $b$ in states that are instances of
+$statePattern$ when the condition $cond$ holds. These equations
+together define $prop$ to hold in all states $t$ where $t \texttt{ |=
+} prop$ evaluates to \verb|true|. A temporal logic \emph{formula} is
+constructed by state propositions and temporal logic operators such as
+\verb|True|, \verb|False|, \verb|~|(negation), \verb|/\|, \verb|\/|,
+\verb|->|(implication), \verb|[]|(``always''),
+\verb|<>|(``eventually'') and \verb|U|(``until''). Real-Time Maude
+provides both \emph{unbounded} and \emph{time-bounded} LTL model
+checking. The time-bounded model checking command
+\begin{alltt}
+  (mc \(t\) |=t \(formula\) in time <= \(timeLimit\) .)
+\end{alltt}
+checks whether the temporal logic formula holds in all behaviors up to
+duration $timeLimit$ starting from the initial state $t$.
 
@@
 $T$, when the attribute \verb|val| decreases to \verb|zero| while time
-advances. This is modeled by the following instanous conditional rule
+advances. This is modeled by the following instaneous conditional rule
 applied on \verb|System|:
@@
 into stack and so on) and running the $schedule()$ function. This is
-modeled by the following instanous rewrite rule:
+modeled by the following instaneous rewrite rule:
 \begin{verbatim}
@@
 \subsection{Timed Behaviours of the System}
+\emph{Timed behaviours} of the system consist of two parts, the
+running of tasks, including both periodic ones and system ones, and
+the running of interrupt source. These are all modeled as the
+following one conventional tick rule:
+\begin{verbatim}
+  crl [tick]:
+    {SYSTEM} => {delta(SYSTEM, R)} in time R 
+    if R le mte(SYSTEM) [nonexec] .
+\end{verbatim}
+where \verb|delta| defines the effects of time elapse on the system,
+and \verb|mte| denotes the maximum amount of time allowed to elapse
+from the current state until an instaneous transition \emph{must} be
+performed. Notice that the variable $R$ is \emph{continuous} with
+respect to the specific time domain\footnote{Real-Time Maude contains
+  built-in modules to define the time domain to be natural numbers and
+  rational numbers, specifying \emph{discrete} time domains and
+  \emph{dense} time domains respectively.}  that we choose to
+instantiate the model on, which is different from timed automata that
+discretize dense time by defining ``clock region''.
+
+Time affects the system by advancing both the running task, whose $ID$
+is loaded at \verb|pc|, and the interrupt source simultaneously,
+increasing their \verb|cnt| and \verb|val| respectively:
+\begin{verbatim}
+  ceq delta((L T STS HW ISRC), R)
+        = ((deltaTask(ID, L, R) T STS HW (deltaIS(ISRC, R)))
+      if ID := (HW).getPc /\ ID :: MaybeNat .
+\end{verbatim}
+We ease the reading by not showing the case where $ID$ is of sort
+\verb|Oid|, due to similarity. At that case, \verb|deltaTask| applies
+on \verb|STS| instead of \verb|L|.
+
+The maximum amount of time allowed to elapse depends on three aspects:
+the time remained to finish the running task, either periodic one or
+system one, the time remained to request an interrupt, and whether or
+not there exists a non-masked interrupt request for the moment:
+\begin{verbatim}
+  ceq mte(L T STS HW ISRC)
+        = minimum( mteTask(ID, L),
+                   minimum( mteIS(ISRC), mteIr(HW)))
+      if ID := (HW).getPc /\ ID :: MaybeNat .
+\end{verbatim}
+where \verb|mteIr| will return \verb|zero| if there exists a
+non-masked interrupt request in the system, or \verb|INF| which
+represents \emph{infinity} otherwise. Again we do not show the case
+where $ID$ is of sort \verb|Oid|, which is very similar. We should
+point out that \verb|mteTask| computes the time remained to reach the
+maximum of the possible finishing interval of the task, since it is
+the time until which a ``finish'' transition \emph{must} happen.
 

### 2015-10-02 RMS/submission.tex
writing section verification

@@
 
-\section{Formal Analysis}
-\subsection{Properties}
+\section{Formal Verification}
+Although Real-Time Maude provides many useful commands and tools to
+analyze a model, such as, \verb|rewrite| to execute the model,
+\verb|search| to search some reachable state(s) satisfying given
+properties from the initial state, the Maude Inductive Theorem Prover
+(ITP) to interactively prove properties written in \emph{membership
+  equational logic}, and so on, we concentrate in this paper on using
+the model checking tool to verify the desired properties of our model.
+
+In this section, we analyze our model of the RMS implementation under
+several different scenarios, containing both realistic and
+experimental ones.
+
+The main objective is to verify the schedubility of a given set of
+periodic tasks. Therefore we define an atomic proposition
+\verb|taskTimeout| to hold if there exists an \verb|error| appearing
+in the $taskList$ of the current state:
+\begin{verbatim}
+  op taskTimeout : -> Prop [ctor] .
+  eq {L T STS HW ISRC} |= taskTimeout = containError(L) .
+\end{verbatim}
+
+\subsection{Properties Formalism}
+
 \subsection{Completeness of the Analysis}

### 2015-10-07 RMS/submission.tex
finish writing the experiment results

@@
 \usepackage{algpseudocode}
+\usepackage{enumerate}
+\usepackage{epic}
+\usepackage{pstricks}
 %\usepackage{llncsdoc}
@@
 In this section, we analyze our model of the RMS implementation under
-several different scenarios, containing both realistic and
-experimental ones.
+several different scenarios, including both realistic and experimental
+ones. Notice that from any (reasonable) given initial state, the
+number of reachable states is finite, thanks to the upperbound given
+to the $timer$, which provides the potential for applying the untimed
+model-checker.
 
-The main objective is to verify the schedubility of a given set of
+\subsection{Properties Verified}
+The main objective is to verify the schedulability of a given set of
 periodic tasks. Therefore we define an atomic proposition
@@
 \end{verbatim}
+where \verb|containError| returns \verb|true| if there is an object
+\verb|error| existing in $L$. Then our desired
+property--schedulability--can be formalized as the temporal logic
+formula \verb|[](~taskTimeout)|. As the property is not
+\emph{clocked}, given an initial state \verb|init|, the following
+untimed model-checking command returns \verb|true| if our desired
+schedulability property holds \emph{with no time limit}; otherwise 
+a trace showing a counterexample is provided.
+\begin{verbatim}
+  (mc init |=u [](~taskTimeout) .)
+\end{verbatim}
 
-\subsection{Properties Formalism}
+The other objective is to verify the correctness of the
+implementation, in the sense that the periodic tasks are scheduled
+exactly with respect to their priorities. The atomic proposition
+\verb|scheduleCorrectly| is defined to hold if the running periodic
+task is the one requested to be run and with the highest priority:
+\begin{verbatim}
+  op scheduleCorrectly : -> Prop [ctor] .
+  ceq {L T STS HW ISRC} |= scheduleCorrectly 
+        = (not containError(L))
+          and (if ID :: MaybeNat then shouldRun(ID, L)
+               else true fi)
+      if ID := (HW).getPc .
+\end{verbatim}
+where \verb|shouldRun(ID, L)| returns \verb|true| if the task
+identified by \verb|ID|, probably \verb|none|, is the one possessing
+the highest priority among those whose status is \verb|READY|,
+\verb|RUNNING| or \verb|INTERRUPT|. Note that \verb|scheduleCorrectly|
+requires no \verb|error| popping up, since our defined correctness
+property makes no sense in the implementation once some task misses
+its deadline. The correctness property is formalized as the temporal
+logic formula \verb|[]scheduleCorrectly|, and can be verified by the
+following untimed model-checking command provided an initial state
+\verb|init|, which returning \verb|true| indicates the correctness
+property holds with no time limit.
+\begin{verbatim}
+  (mc init |=u []scheduleCorrectly .)
+\end{verbatim}
+
+\subsection{Scenarios}
+We use the following setting for our verification, which is from the 
+statistics provided by our industrial partner:
+\begin{itemize}
+\item The interrupt cycle is $5ms$.
+\item The scheduling time ranges from $5{\mu}s$ to $9{\mu}s$, and the
+switching time ranges from $2{\mu}s$ to $4{\mu}s$.
+\item The initial state is with empty stack, empty \verb|pc|, cleared 
+\verb|mask| and cleared \verb|ir|.
+\end{itemize}
+
+We have analyzed our model/implementation in ten different scenarios,
+including both realistic ones provided by our industrial partner and
+experimental ones designed by ourselves, four of them are described
+below:
+\begin{itemize}
+\item Scenario (i) with two tasks: one having period $5ms$ and
+  possible finishing interval $[2.4ms, 3ms]$, and the other having
+  period $25ms$ and possible finishing interval $[6.1ms, 7ms]$.
+\item Scenario (ii) with two tasks: one having period $5ms$ and
+  possible finishing interval $[1.8ms, 2ms]$, and the other having
+  period $25ms$ and possible finishing interval $[2.1ms, 2.3ms]$.
+\item Scenario (iii) with three tasks: the first having period $5ms$
+  and possible finishing interval $[2.5ms, 2.7ms]$, the second having
+  period $10ms$ and possible finishing interval $[1.5ms, 2ms]$, and
+  the third having period $25ms$ and possible finishing interval
+  $[2.6ms, 3ms]$.
+\item Scenario (iv) with three tasks: the first having period $5ms$
+  and possible finishing interval $[2.2ms, 2.5ms]$, the second having
+  period $10ms$ and possible finishing interval $[1.4ms, 1.5ms]$, and
+  the third having period $15ms$ and possible finishing interval
+  $[4.3ms, 4.5ms]$.
+\end{itemize}
+
+Choosing the \emph{maximal time sampling strategy}, the results of the
+model checking show that both the schedulability and the correctness
+properties hold in Scenarios (i-iii), but not in Scenario (iv). For
+Scenario (iv), one counterexample of the schedulability is pictured in
+Figure~\ref{f:counterexample}, where the third task (task$2$) misses
+its deadline at the time $15ms$ that is marked by the tiny red
+triangle. And the correctness fails in Scenario (iv) because of the
+failure of schedulability.
+
+\begin{figure}[h]
+\begin{center}
+\begin{picture}(300,110)(0,-10)
+\thicklines
+\put(0,0){\vector(1,0){320}}
+\put(305,5){time(${\mu}s$)}
+\thinlines
+\put(0,0){\line(0,1){110}}
+\put(-25,97){task$0$}
+\put(-25,77){task$1$}
+\put(-25,57){task$2$}
+\put(-44,37){scheduling}
+\put(-40,17){switching}
+\put(-2,-8){$0$}
+
+\dashline[30]{3}(0,100)(250,100)
+\dashline[30]{3}(0,80)(280,80)
+\dashline[30]{3}(0,60)(300,60)
+\dashline[30]{3}(0,40)(210,40)
+\dashline[30]{3}(0,20)(285,20)
+
+\dashline[30]{3}(10,-10)(10,100)
+\thicklines
+\textcolor{red}{\put(0,40){\line(1,0){10}}}
+\put(8,-18){$9$}
+
+\thinlines
+\dashline[30]{3}(50,0)(50,100)
+\thicklines
+\textcolor{blue}{\put(10,100){\line(1,0){40}}}
+\put(35,-8){$2509$}
+
+\thinlines
+\dashline[30]{3}(55,-10)(55,80)
+\thicklines
+\textcolor{red}{\put(50,20){\line(1,0){5}}}
+\put(46,-18){$2513$}
+
+\thinlines
+\dashline[30]{3}(80,0)(80,80)
+\thicklines
+\textcolor{blue}{\put(55,80){\line(1,0){25}}}
+\put(65,-8){$4013$}
+
+\thinlines
+\dashline[30]{3}(85,-10)(85,60)
+\thicklines
+\textcolor{red}{\put(80,20){\line(1,0){5}}}
+\put(76,-18){$4017$}
+
+\thinlines
+\dashline[30]{3}(100,0)(100,60)
+\thicklines
+\textcolor{blue}{\put(85,60){\line(1,0){15}}}
+\put(90,-8){$5000$}
+
+\thinlines
+\dashline[30]{3}(110,-10)(110,100)
+\thicklines
+\textcolor{red}{\put(100,40){\line(1,0){10}}}
+\put(101,-18){$5009$}
+
+\thinlines
+\dashline[30]{3}(150,0)(150,100)
+\thicklines
+\textcolor{blue}{\put(110,100){\line(1,0){40}}}
+\put(135,-8){$7509$}
+
+\thinlines
+\dashline[30]{3}(155,-10)(155,60)
+\thicklines
+\textcolor{red}{\put(150,20){\line(1,0){5}}}
+\put(146,-18){$7513$}
+
+\thinlines
+\dashline[30]{3}(200,0)(200,60)
+\thicklines
+\textcolor{blue}{\put(155,60){\line(1,0){45}}}
+\put(185,-8){$10000$}
+
+\thinlines
+\dashline[30]{3}(210,-10)(210,100)
+\thicklines
+\textcolor{red}{\put(200,40){\line(1,0){10}}}
+\put(198,-18){$10009$}
+
+\thinlines
+\dashline[30]{3}(250,0)(250,100)
+\thicklines
+\textcolor{blue}{\put(210,100){\line(1,0){40}}}
+\put(230,-8){$12509$}
+
+\thinlines
+\dashline[30]{3}(255,-10)(255,80)
+\thicklines
+\textcolor{red}{\put(250,20){\line(1,0){5}}}
+\put(243,-18){$12513$}
+
+\thinlines
+\dashline[30]{3}(280,0)(280,80)
+\thicklines
+\textcolor{blue}{\put(255,80){\line(1,0){25}}}
+\put(260,-8){$14013$}
+
+\thinlines
+\dashline[30]{3}(285,-10)(285,60)
+\thicklines
+\textcolor{red}{\put(280,20){\line(1,0){5}}}
+\put(272,-18){$14017$}
+
+\thinlines
+\dashline[30]{3}(300,0)(300,60)
+\thicklines
+\textcolor{blue}{\put(285,60){\line(1,0){15}}}
+\put(289,-8){$15000$}
+
+\textcolor{red}{\put(300,60){\vector(-1,0){0}}}
+
+\end{picture}
+\end{center}
+\caption{An Counterexample of Scenario (iv).}
+\label{f:counterexample}
+\end{figure}
 

### 2015-10-08 RMS/submission.tex
finish completeness

@@
 \usepackage{amssymb}
+\usepackage{mathabx}
 \usepackage{algorithm}
@@
 A Real-Time Maude module specifies a \emph{real-time rewrite theory}
-$(\Sigma, E\cup A , IR, TR)$, where:
+${\cal R} = (\Sigma, E\cup A , IR, TR)$, where:
 \begin{itemize}
@@
 \subsection{Scenarios}
+\label{ss:results}
 We use the following setting for our verification, which is from the 
@@
 
-Choosing the \emph{maximal time sampling strategy}, the results of the
-model checking show that both the schedulability and the correctness
+Instantiating our model on dense time domain and choosing the
+\emph{maximal time sampling strategy}, the results of the model
+checking show that both the schedulability and the correctness
 properties hold in Scenarios (i-iii), but not in Scenario (iv). For
@@
 
-\subsection{Completeness of the Analysis}
+\subsection{Soundness and Completeness of the Analysis}
+We call an analysis method \emph{sound} if any counterexample found
+using such a method is a real counterexample of the question, and
+\emph{complete} if the fact that no counterexample can be found using
+such a method implies no counterexample exist for the question in
+analysis. The soundness of our results is easy to check, simply by
+examining the counterexamples found. But this is not the case for
+completeness, since we choose instantiating our model on dense time
+domain to make it more real but giving rise to an infinite state space
+which is unfeasible to exhaust. In general, completeness of untimed
+model checking cannot be achieved for any systems, any time sampling
+stategies and any properties. However, \"Olveczky and Meseguer proved
+the completeness of untimed temporal logic model checking, under the
+maximal time sampling strategy, for a large class of real-time
+systems:
+\begin{theorem}
+\label{t:completeness}
+Given a \emph{time-robust} real-time rewrite theory $\cal R$, a set
+$P$ of \emph{tick-stabilizing} atomic propositions, an LTL formula
+$\Phi$ (excluding the \emph{next} operator $\bigcirc$) whose atomic
+propositions are contained in $P$. The untimed temporal logic model
+checking verifying $\Phi$ is \emph{complete} under the maximal time
+sampling stategy.
+\end{theorem}
+
+To apply Theorem~\ref{t:completeness} on our analysis to show the
+completeness, we only need to prove time-robustness of our model and
+tick-stabilization of our defined atomic propositions,
+\verb|taskTimeout| and \verb|scheduleCorrectly|. The latter is quite
+trivial, while the former requires little adjustments to the model,
+which collapse the possible finishing interval for some periodic task
+into a single value that should be assigned to the possible maximum
+computation time. Then we can apply Lemma~\ref{l:timerobustness} to
+prove the time-robustness of our (adjusted) model.
+\begin{lemma}
+\label{l:timerobustness}
+An object-oriented specification $\cal R$, with a conventional tick
+rule, is \emph{time-robust} if the following conditions are satisfied
+for all appropriate \emph{ground} terms $t$ and $r,r'$:
+
+\noindent
+(i) $mte(\delta(t,r))=mte(t)\dotdiv r$, for all $r\le mte(t)$;
+
+\noindent
+(ii) $\delta(t,0)=t$;
+
+\noindent
+(iii) $\delta(\delta(t,r),r')=\delta(t,r+r')$, for $r+r'\le mte(t)$;
+
+\noindent
+(iv) $mte(\sigma(l))=0$ for each ground instance $\sigma(l)$ of a
+left-hand side of an instantaneous rewrite rule.
+\end{lemma}
+
+We achieve the same verification results for the adjusted model as for
+the original one: schedulability and correctness hold in Scenarios
+(i-iii) but fail in Scenario~(iv). The only thing remained to show the
+completeness of our results is to prove the reasonability of the
+adjustments, that is, if a set of tasks (including system ones) is
+schedulable when the computation time of some task $\tau_i$ in it
+equals to $C_i^{max}$, then when some jobs of $\tau_i$ become possible
+to finish in time $r\le C_i^{max}$, the set of tasks remains still
+schedulable. This is done by proving Lemma~\ref{l:max} and considering
+\verb|scheduling| and \verb|switching| as having same and higher
+priority than all periodic tasks.
+\begin{lemma}
+\label{l:max}
+Assume the time $r_s$ at which a job of $\tau_i$ starts running is
+fixed. The time $r_f$, at which this job finishes, reaches its maximum
+if all job instances of tasks $\tau$'s, the priorities of which are
+higher than or equal to that of $\tau_i$, running between $r_s$ and
+$r_f$ finish in their maximum possible computation time.
+\end{lemma}
 

### 2015-10-09 RMS/submission.tex
adding bib file, finishing introduction.

@@
 \section{Introduction}
+Periodic task scheduling is one of the most studied topics within the
+field of real-time systems, due to the large number of control systems
+that require cyclic activities. A set of periodic tasks is said to be
+\emph{schedulable} with respect to some scheduling algorithm if all
+jobs meet their deadlines. \emph{Rate-Monotonic Scheduling}
+(\emph{RMS}) algorithm is a \emph{fixed} priority scheduling algorithm
+for preemptive hard real-time environments proposed by Liu and
+Layland~\cite{DBLP:journals/jacm/LiuL73} in 1973, which assigns
+priorities to jobs according to the periods of the corresponding
+tasks: the smaller the period, the higher the priority. As it is easy
+to implement and is proved to be the \emph{optimal} fixed priority
+scheduling algorithm~\cite{DBLP:journals/jacm/LiuL73}, in the sense
+that any set of tasks that is schedulable under \emph{some} fixed
+priority scheduling algorithm is also schedulable with respect to RMS
+algorithm, RMS is widely used in different kinds of real-time
+applications, some of which are even safety-critical, such as trains,
+avionics and so on.
+
+Liu and Layland also gave a sufficient condition for the
+schedulability of a set of $n$ tasks scheduled by RMS algorithm
+in~\cite{DBLP:journals/jacm/LiuL73}:
+$\displaystyle\Sigma^n_{i=1}C_i/T_i \le n(2^{1/n}-1)$, where $C_i$ and
+$T_i$ are the computation time and the period of task $\tau_i$
+respectively. Two main directions on RMS have been explored since
+then. One is to relax the assumptions on the original RMS model, for
+instance, to allow aperiodic
+tasks~\cite{DBLP:conf/rtss/LehoczkySS87,DBLP:journals/rts/SpruntSL89,DBLP:conf/rtss/LehoczkyR92,DBLP:journals/tc/StrosniderLS95},
+to generalize it to be
+\emph{deadline-monotonic}~\cite{DBLP:journals/pe/LeungW82,audsley1993deadline},
+to allow resource sharing among tasks~\cite{DBLP:journals/tc/ShaRL90},
+to extend it on
+multiprocessors~\cite{dhall1978real,DBLP:journals/rts/LopezGDG03,DBLP:journals/tpds/LopezDG04,DBLP:journals/tc/BaruahG03},
+to enhance
+fault-tolerance~\cite{DBLP:journals/rts/OhS94,DBLP:journals/rts/GhoshMMS98,DBLP:journals/tpds/BertossiMR99}
+and so on, making RMS algorithm applicable on more systems. The other
+direction is to generate better schedulablity test conditions for the
+algorithm and its
+extensions~\cite{DBLP:conf/rtss/LehoczkySD89,DBLP:conf/rtss/KuoM91,DBLP:journals/tc/BiniBB03,DBLP:journals/rts/LopezGDG03,DBLP:journals/tc/BaruahG03,gardner1999}. The
+RMS algorithm is of such practical importance that we certainly cannot
+exhaust all the results in literatures here.
+
+On the other hand, an increasing number of efforts to apply formal
+methods, such as model checking and theorem proving, are made to
+analyze safety-critical systems for the past few
+years~\cite{DBLP:journals/iandc/MeseguerR13,DBLP:journals/cacm/Leroy09,DBLP:conf/sosp/KleinEHACDEEKNSTW09}. However,
+as far as we know, few~\cite{DBLP:conf/iceccs/CuiDT14,TianD2011} are
+made to analyze the RMS algorithm, none for implementations of RMS.
+
+In this paper, we use \emph{Real-Time Maude}, a \emph{rewriting}-based
+modeling language and analyzing tool for real-time systems, to model a
+realistic implementation of RMS algorithm and then verify some desired
+properties on the built model. The model we built based on the
+realistic implementation extends the original ideal one proposed
+in~\cite{DBLP:journals/jacm/LiuL73}, by allowing computation time of
+tasks to be non-constant, and by considering overheads and other
+realistic aspects.
+
+The rest of this paper is organized as follows: Section~\ref{s:rms}
+introduces the standard setting of the RMS algorithm proposed
+in~\cite{DBLP:journals/jacm/LiuL73} and our considering realistic
+implementation. Section~\ref{s:rtmaude} gives a background to
+Real-Time Maude. Section~\ref{s:formalism} presents how we model the
+RMS implementation using Real-Time Maude. Then
+Section~\ref{s:verification} explains how to verify the desired
+properties and to analyze the results. Related work is discussed in
+Section~\ref{s:relate} before concluding in
+Section~\ref{s:conclusion}.
 
 \section{Rate-Monotonic Scheduling Algorithm and the Implementation}
-
+\label{s:rms}
 \subsection{Formulation of the Standard Setting}
@@
 \section{Real-Time Maude}
+\label{s:rtmaude}
 Real-Time Maude is a language and tool that extends Maude to support
@@
 \section{Formalizing the RMS Implementation}
+\label{s:formalism}
 Based on the code, we model the implementation under the following
@@
 \section{Formal Verification}
+\label{s:verification}
 Although Real-Time Maude provides many useful commands and tools to
@@
 \section{Related Work}
+\label{s:relate}
 
 \section{Conclusion}
+\label{s:conclusion}
 
+\bibliographystyle{splncs03}
+\bibliography{submission}
 \end{document}

### 2015-10-10 RMS/submission.tex
first completed version

@@
 RMS algorithm is of such practical importance that we certainly cannot
-exhaust all the results in literatures here.
+exhaust all the results in the literature here.
 
@@
 \label{s:relate}
+In this section we discuss our results with related work in two
+directions.
+
+Considering schedulability test, Liu and Layland gave
+in~\cite{DBLP:journals/jacm/LiuL73} the famous sufficient condition
+that a set of periodic tasks is schedulable with respect to RMS if
+$\displaystyle \Sigma^n_{i=1} C_i/T_i \le n(2^{1/n}-1)$ holds, where
+$C_i$ and $T_i$ are the computation time and the period of task
+$\tau_i$ respectively. Then in~\cite{DBLP:journals/tc/BiniBB03}, a
+more sufficient condition, known as \emph{Hyperbolic Bound}, which has
+the same complexity as Liu and Layland's one, was proposed by Bini et
+al. On the other hand, necessary and sufficient conditions for
+schedulability were derived independently
+in~\cite{DBLP:journals/rts/SpruntSL89} and~\cite{audsley1993deadline},
+requiring more sophisticated analysis on the task set. Nevertheless,
+these results take no overhead into account, being not as realistic as
+ours. Katcher et al. did consider overhead in their schedulability
+analysis under several models based on different kinds of popular
+implementations~\cite{DBLP:journals/tse/KatcherAS93}. But as we
+mentioned at the very beginning, the ways to implement the RMS
+algorithm are countless, hence their analysis could not be applied on
+our target implementation. Furthermore, comparing with those
+theoretical analysis, our method by formal modeling and verification
+has a great advantage that if our schedulability test answers ``no'',
+it returns at the same time a real counterexample, which is able to
+guide our engineer to adjust the design.
+
+\cite{DBLP:conf/iceccs/CuiDT14} and~\cite{TianD2011} also made use of
+model checking to analyze the RMS algorithm along the same line with
+different languages and tools. They only considered the ideal setting
+as in~\cite{DBLP:journals/jacm/LiuL73}, but not an implementation
+which contains much more details. Our model of the implementation
+easily degenerates to a model of the RMS algorithm, if we let the time
+for scheduling and switching be zero and let the possible finishing
+interval of each task be a single value.
+
+Finally, Maude and Real-Time Maude have been successfully applied on
+large numbers of applications~\cite{DBLP:journals/jlp/Meseguer12},
+especially on communication protocols, real-time and cyber-physical
+systems. But few results are achieved on scheduling problems. RMS is
+investigated using Real-Time Maude for the first time.
 
@@
 \label{s:conclusion}
+We have formally modeled a realistic implementation of RMS algorithm,
+obtained from our industrial partner, using Real-Time Maude, a
+modeling language based on rewriting logic. By taking into acount the
+overhead of scheduling and switching, assuming the possible
+computation time for each task may not be constant, we believe that
+our model has enough details to be analyzed for the behaviours of the
+real system. Two important properties--schedulability and
+correctness--are verified by model checking on the model, under
+several given scenarios. We also prove at last the soundness and
+completeness of our analysis.
 
-\bibliographystyle{splncs03}
-\bibliography{submission}
+\bibliographystyle{splncs03} \bibliography{submission}
 \end{document}

### 2015-10-17 RMS/submission.tex
restruct section 2 and 3, modify a little until section 2.2.

@@
 
-\title{Formal Analysis of Rate-Monotonic Scheduling Implementation via Real-Time Maude}
+\title{Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude}
 \author{Jiaxiang Liu\inst{1,2}}
@@
 \section{Introduction}
-Periodic task scheduling is one of the most studied topics within the
-field of real-time systems, due to the large number of control systems
-that require cyclic activities. A set of periodic tasks is said to be
-\emph{schedulable} with respect to some scheduling algorithm if all
-jobs meet their deadlines. \emph{Rate-Monotonic Scheduling}
-(\emph{RMS}) algorithm is a \emph{fixed} priority scheduling algorithm
-for preemptive hard real-time environments proposed by Liu and
-Layland~\cite{DBLP:journals/jacm/LiuL73} in 1973, which assigns
-priorities to jobs according to the periods of the corresponding
-tasks: the smaller the period, the higher the priority. As it is easy
-to implement and is proved to be the \emph{optimal} fixed priority
-scheduling algorithm~\cite{DBLP:journals/jacm/LiuL73}, in the sense
-that any set of tasks that is schedulable under \emph{some} fixed
-priority scheduling algorithm is also schedulable with respect to RMS
-algorithm, RMS is widely used in different kinds of real-time
-applications, some of which are even safety-critical, such as trains,
-avionics and so on.
-
-Liu and Layland also gave a sufficient condition for the
-schedulability of a set of $n$ tasks scheduled by RMS algorithm
-in~\cite{DBLP:journals/jacm/LiuL73}:
-$\displaystyle\Sigma^n_{i=1}C_i/T_i \le n(2^{1/n}-1)$, where $C_i$ and
-$T_i$ are the computation time and the period of task $\tau_i$
-respectively. Two main directions on RMS have been explored since
-then. One is to relax the assumptions on the original RMS model, for
-instance, to allow aperiodic
-tasks~\cite{DBLP:conf/rtss/LehoczkySS87,DBLP:journals/rts/SpruntSL89,DBLP:conf/rtss/LehoczkyR92,DBLP:journals/tc/StrosniderLS95},
-to generalize it to be
-\emph{deadline-monotonic}~\cite{DBLP:journals/pe/LeungW82,audsley1993deadline},
-to allow resource sharing among tasks~\cite{DBLP:journals/tc/ShaRL90},
-to extend it on
-multiprocessors~\cite{dhall1978real,DBLP:journals/rts/LopezGDG03,DBLP:journals/tpds/LopezDG04,DBLP:journals/tc/BaruahG03},
-to enhance
-fault-tolerance~\cite{DBLP:journals/rts/OhS94,DBLP:journals/rts/GhoshMMS98,DBLP:journals/tpds/BertossiMR99}
-and so on, making RMS algorithm applicable on more systems. The other
-direction is to generate better schedulablity test conditions for the
-algorithm and its
+Periodic task scheduling is one of the most important topics within
+the field of real-time systems, due to the large number of control
+systems that require cyclic activities~\cite{buttazzo2011hard}. A set
+of periodic tasks is said to be \emph{schedulable} with respect to
+some scheduling algorithm if all jobs meet their
+deadlines. \emph{Rate-Monotonic Scheduling} (\emph{RMS}) is a
+\emph{fixed} priority scheduling algorithm for preemptive hard
+real-time environments proposed by Liu and
+Layland~\cite{DBLP:journals/jacm/LiuL73}, which assigns priorities to
+jobs according to the periods of the corresponding tasks: the smaller
+period, the higher priority. It is proved to be the \emph{optimal}
+fixed priority scheduling algorithm~\cite{DBLP:journals/jacm/LiuL73},
+in the sense that any set of tasks, which is schedulable under
+\emph{some} fixed priority scheduling algorithm, is also schedulable
+with respect to RMS. It is widely used in safety-critical real-time
+applications, such as trains and avionics, thanks to its optimality
+and easiness to implement.
+
+Liu and Layland~\cite{DBLP:journals/jacm/LiuL73} gave a sufficient
+condition for the schedulability of a set of $n$ tasks scheduled by
+RMS: $\displaystyle\Sigma^n_{i=1}C_i/T_i \le n(2^{1/n}-1)$, where
+$C_i$ and $T_i$ are the computation time and the period of task
+$\tau_i$, respectively. Two main directions on RMS have been explored
+since then. One is to relax the assumptions on the original RMS model,
+making it applicable on more systems.  For instance,
+\cite{DBLP:conf/rtss/LehoczkySS87,DBLP:journals/rts/SpruntSL89,DBLP:conf/rtss/LehoczkyR92,DBLP:journals/tc/StrosniderLS95}
+allow aperiodic tasks in the scheduling,
+\cite{DBLP:journals/pe/LeungW82,audsley1993deadline} generalize RMS to
+be \emph{deadline-monotonic}, \cite{DBLP:journals/tc/ShaRL90} allows
+resource sharing among tasks,
+\cite{dhall1978real,DBLP:journals/rts/LopezGDG03,DBLP:journals/tpds/LopezDG04,DBLP:journals/tc/BaruahG03}
+extend RMS on multiprocessors, and
+\cite{DBLP:journals/rts/OhS94,DBLP:journals/rts/GhoshMMS98,DBLP:journals/tpds/BertossiMR99}
+enhance fault-tolerance. The other direction is to generate better
+schedulablity test conditions for the algorithm and its
 extensions~\cite{DBLP:conf/rtss/LehoczkySD89,DBLP:conf/rtss/KuoM91,DBLP:journals/tc/BiniBB03,DBLP:journals/rts/LopezGDG03,DBLP:journals/tc/BaruahG03,gardner1999}. The
-RMS algorithm is of such practical importance that we certainly cannot
-exhaust all the results in the literature here.
-
-On the other hand, an increasing number of efforts to apply formal
-methods, such as model checking and theorem proving, are made to
-analyze safety-critical systems for the past few
+RMS algorithm is no doubt of practical importance.
+
+Extensive effort to apply formal methods, such as model checking and
+theorem proving, has been made to analyze safety-critical systems for
+the past few
 years~\cite{DBLP:journals/iandc/MeseguerR13,DBLP:journals/cacm/Leroy09,DBLP:conf/sosp/KleinEHACDEEKNSTW09}. However,
-as far as we know, few~\cite{DBLP:conf/iceccs/CuiDT14,TianD2011} are
-made to analyze the RMS algorithm, none for implementations of RMS.
+as far as we know, few~\cite{DBLP:conf/iceccs/CuiDT14,TianD2011}
+attempt to analyze the RMS algorithm, while no work for
+implementations of RMS is found.
 
@@
 realistic implementation of RMS algorithm and then verify some desired
-properties on the built model. The model we built based on the
-realistic implementation extends the original ideal one proposed
+properties on the built model. Based on a realistic implementation,
+our model extends the original ideal one proposed
 in~\cite{DBLP:journals/jacm/LiuL73}, by allowing computation time of
 tasks to be non-constant, and by considering overheads and other
-realistic aspects.
-
-The rest of this paper is organized as follows: Section~\ref{s:rms}
+details of the enviroments.
+
+The rest of this paper is organized as follows. Section~\ref{s:background}
 introduces the standard setting of the RMS algorithm proposed
-in~\cite{DBLP:journals/jacm/LiuL73} and our considering realistic
-implementation. Section~\ref{s:rtmaude} gives a background to
+in~\cite{DBLP:journals/jacm/LiuL73} and our
+implementation. Section~\ref{s:imp} gives a background to
 Real-Time Maude. Section~\ref{s:formalism} presents how we model the
@@
 properties and to analyze the results. Related work is discussed in
-Section~\ref{s:relate} before concluding in
+Section~\ref{s:relate}. We conclude the paper in
 Section~\ref{s:conclusion}.
 
-\section{Rate-Monotonic Scheduling Algorithm and the Implementation}
-\label{s:rms}
-\subsection{Formulation of the Standard Setting}
-The frequently used setting of the RMS algorithm for analysis
-considers a task set consisting only of $n$ periodic tasks
+\section{Background}
+\label{s:background}
+
+\subsection{Rate-Monotonic Scheduling Algorithm}
+\label{ss:rms}
+%\subsection{Formulation of the Standard Setting}
+A task set consists of \emph{only} $n$ periodic tasks
 $\tau_1,\ldots,\tau_n$. Task $\tau_i$ has a period $T_i$ and a
 computation time $C_i$. First jobs of all tasks are assumed to be
-instantiated simultaneously. This means that jobs corresponding to
-task $\tau_i$ are initiated at times $kT_i, k\ge 0$. Deadlines consist
-of runability constraints only, that is, the job initiated at time
-$kT_i$ has $(k+1)T_i$ as its deadline, which is the initiation time of
-the next job. The RMS algorithm chooses the labeling such that $T_1\le
-T_2\le \ldots \le T_n$. Consequently, $\tau_i$ receives priority
-$i$. The following assumptions are made:
+initiated simultaneously. This means that jobs corresponding to task
+$\tau_i$ are initiated at times $kT_i$ with integers $k\ge
+0$. Deadlines consist of runability constraints only: the job
+initiated at time $kT_i$ has $(k+1)T_i$ as its deadline, which is the
+initiation time of the next job. The RMS algorithm chooses the
+labeling such that $T_1\le T_2\le \ldots \le T_n$. Consequently,
+$\tau_i$ receives priority $i$, assuming smaller numbers have higher
+priorities. The following assumptions are made:
 
@@
 
-In this paper, we consider an implementation instead of the RMS
-algorithm itself, thus the model would be more complicated than this
-ideal formulation.  Assumptions~(A1) and (A3) will be relaxed to shape a more
-realisitc analysis model, as shown below.
-
-\subsection{The Implementation of RMS}
+However in this paper, we consider an implementation instead of the
+RMS algorithm itself, thus the model would be more complicated than
+this ideal setting.  Assumptions~(A1) and (A3) will be relaxed later
+to obtain a more realisitc analysis model.
+
+\subsection{Real-Time Maude}
+Based on \emph{rewriting logic}, \emph{Real-Time Maude} is a language
+and tool that extends \emph{Maude} to support the formal specification
+and analysis of real-time
+systems~\cite{DBLP:journals/lisp/OlveczkyM07}.
+
+\subsubsection{Specification}
+Real-Time Maude models a system using \emph{modules}. A module
+specifies a \emph{real-time rewrite theory} ${\cal R} = (\Sigma, E\cup
+A , IR, TR)$, where:
+\begin{itemize}
+\item $\Sigma$ is an algebraic \emph{signature}, that is, a set of
+  declarations of \emph{sorts}, \emph{subsorts} and \emph{function
+    symbols}.
+\item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
+  theory}, with $E$ a set of possibly conditional equations, and $A$ a
+  set of equational axioms such as associativiy, commutativity and
+  identity.  $(\Sigma, E\cup A)$ models the system's ``static'' states
+  as an algebraic data type, and includes a built-in specification of
+  a sort \verb|Time|.
+\item $IR$ is a set of \emph{labeled conditional rewrite rules}
+  specifying the system's local transitions. Each rule has the form
+  $[l]~:~t\rightarrow t'\mbox{ \textbf{if} }\bigwedge^n_{j=1}cond_j$,
+  where each $cond_j$ is an equality $u_j=v_j$ and $l$ is a
+  \emph{label}. Such a rule specifies an \emph{instaneous transition}
+  from an instance of $t$ to the corresponding instance of $t'$,
+  \emph{provided} the conditions hold.
+\item $TR$ is a set of \emph{tick rules} $[l]~:~\{t\}\rightarrow\{t'\}
+  \mbox{ \textbf{in time} }r\mbox{ \textbf{if} }cond$ that specify
+  \emph{timed transitions} advancing time in the \emph{entire} state
+  $t$ by $r$ time units. $IR$ and $TR$ together model the ``dynamic''
+  behaviors of the system.
+\end{itemize}
+
+Real-Time Maude supports \emph{object-oriented} style specifications.
+A class declaration $\texttt{class }C\texttt{ |
+}att_1\texttt{:}s_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}s_n$
+declares a class $C$ with attributes $att_1$ to $att_n$ of sorts $s_1$
+to $s_n$. An \emph{object} of class $C$ in a given state is
+represented as a term $\texttt{< } O\texttt{:} C \texttt{ | }
+att_1\texttt{:}val_1\texttt{,} \ldots
+\texttt{,}att_n\texttt{:}val_n\texttt{ >}$ of sort \verb|Object|,
+where $O$, of sort \verb|Oid|, is the object's \emph{identifier}, and
+where $val_1$ to $val_n$ are the current values of the attributes
+$att_1$ to $att_n$. A \emph{subclass} inherits all the attributes and
+rules of its superclasses.
+
+\subsubsection{Formal Analysis}
+In this paper, we only consider Real-Time Maude's \emph{linear
+  temporal logic model checker}, which analyzes whether \emph{each}
+behavior satisfies a temporal logic formula. \emph{State propositions}
+are terms of sort \verb|Prop|, and their symantics is defined by
+equations $\texttt{ceq } statePattern \texttt{ |= } prop \texttt{ = }
+b \texttt{ if } cond$, with $b$ a term of sort \verb|Bool|, stating
+that $prop$ evaluates to $b$ in states that are instances of
+$statePattern$ when the condition $cond$ holds. These equations
+together define $prop$ to hold in all states $t$ where $t \texttt{ |=
+} prop$ evaluates to \verb|true|. A temporal logic \emph{formula} is
+constructed by state propositions and temporal logic operators such as
+\verb|True|, \verb|False|, \verb|~|(negation), \verb|/\|, \verb|\/|,
+\verb|->|(implication), \verb|[]|(``always''),
+\verb|<>|(``eventually'') and \verb|U|(``until''). Real-Time Maude
+provides both \emph{unbounded} and \emph{time-bounded} LTL model
+checking. The time-bounded model checking command
+\begin{alltt}
+  (mc \(t\) |=t \(formula\) in time <= \(timeLimit\) .)
+\end{alltt}
+checks whether the temporal logic formula holds in all behaviors up to
+duration $timeLimit$ starting from the initial state $t$.
+
+\section{The Implementation of RMS}
+\label{s:imp}
 The algorithm of the RMS is straightforward, and it is easy to
@@
 
-\section{Real-Time Maude}
-\label{s:rtmaude}
-Real-Time Maude is a language and tool that extends Maude to support
-the formal specification and analysis of real-time systems.
-
-\subsection{Specification}
-A Real-Time Maude module specifies a \emph{real-time rewrite theory}
-${\cal R} = (\Sigma, E\cup A , IR, TR)$, where:
-\begin{itemize}
-\item $\Sigma$ is an algebraic \emph{signature}, that is, a set of
-  declarations of \emph{sorts}, \emph{subsorts} and \emph{function
-    symbols}.
-\item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
-  theory}, with $E$ a set of possibly conditional equations, and $A$ a
-  set of equational axioms such as associativiy, commutativity and
-  identity.  $(\Sigma, E\cup A)$ specifies the system's state space as
-  an algebraic data type, and includes a built-in specification of a
-  sort \verb|Time|.
-\item $IR$ is a set of \emph{labeled conditional rewrite rules}
-  specifying the system's local transitions, each of which has the
-  form $[l]~:~t\rightarrow t'\mbox{ \textbf{if}
-  }\bigwedge^n_{j=1}cond_j$, where each $cond_j$ is an equality
-  $u_j=v_j$, and $l$ is a \emph{label}. Such a rule specifies an
-  \emph{instaneous transition} from an instance of $t$ to the
-  corresponding instance of $t'$, \emph{provided} the conditions hold.
-\item $TR$ is a set of \emph{tick rules} $[l]~:~\{t\}\rightarrow\{t'\}
-  \mbox{ \textbf{in time} }\tau\mbox{ \textbf{if} }cond$ that advance
-  time in the \emph{entire} state $t$ by $\tau$ time units.
-\end{itemize}
-
-A class declaration $\texttt{class }C\texttt{ |
-}att_1\texttt{:}s_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}s_n$
-declares a class $C$ with attributes $att_1$ to $att_n$ of sorts $s_1$
-to $s_n$. An \emph{object} of class $C$ in a given state is
-represented as a term $\texttt{< } O\texttt{:} C \texttt{ | }
-att_1\texttt{:}val_1\texttt{,} \ldots
-\texttt{,}att_n\texttt{:}val_n\texttt{ >}$ of sort \verb|Object|,
-where $O$, of sort \verb|Oid|, is the object's \emph{identifier}, and
-where $val_1$ to $val_n$ are the current values of the attributes
-$att_1$ to $att_n$. A \emph{subclass} inherits all the attributes and
-rules of its superclasses.
-
-\subsection{Formal Analysis}
-In this paper, we only consider Real-Time Maude's \emph{linear
-  temporal logic model checker}, which analyzes whether \emph{each}
-behavior satisfies a temporal logic formula. \emph{State propositions}
-are terms of sort \verb|Prop|, and their symantics is defined by
-equations $\texttt{ceq } statePattern \texttt{ |= } prop \texttt{ = }
-b \texttt{ if } cond$, with $b$ a term of sort \verb|Bool|, stating
-that $prop$ evaluates to $b$ in states that are instances of
-$statePattern$ when the condition $cond$ holds. These equations
-together define $prop$ to hold in all states $t$ where $t \texttt{ |=
-} prop$ evaluates to \verb|true|. A temporal logic \emph{formula} is
-constructed by state propositions and temporal logic operators such as
-\verb|True|, \verb|False|, \verb|~|(negation), \verb|/\|, \verb|\/|,
-\verb|->|(implication), \verb|[]|(``always''),
-\verb|<>|(``eventually'') and \verb|U|(``until''). Real-Time Maude
-provides both \emph{unbounded} and \emph{time-bounded} LTL model
-checking. The time-bounded model checking command
-\begin{alltt}
-  (mc \(t\) |=t \(formula\) in time <= \(timeLimit\) .)
-\end{alltt}
-checks whether the temporal logic formula holds in all behaviors up to
-duration $timeLimit$ starting from the initial state $t$.
-
 \section{Formalizing the RMS Implementation}

### 2015-10-22 RMS/submission.tex
finish modifying with Prof. Song's comments

@@
 \newcommand{\hide}[1]{\ignorespaces}
+\newcommand{\jx}[1]{{\bf Jiaxiang: }#1{ \bf End}}
 
@@
 RMS: $\displaystyle\Sigma^n_{i=1}C_i/T_i \le n(2^{1/n}-1)$, where
-$C_i$ and $T_i$ are the computation time and the period of task
-$\tau_i$, respectively. Two main directions on RMS have been explored
-since then. One is to relax the assumptions on the original RMS model,
-making it applicable on more systems.  For instance,
+$C_i$ and $T_i$ are the \emph{computation (time) requirement} and the
+period of task $\tau_i$, respectively. Two main directions on RMS have
+been explored since then. One is to relax the assumptions on the
+original RMS model, making it applicable on more systems.  For
+instance,
 \cite{DBLP:conf/rtss/LehoczkySS87,DBLP:journals/rts/SpruntSL89,DBLP:conf/rtss/LehoczkyR92,DBLP:journals/tc/StrosniderLS95}
@@
 our model extends the original ideal one proposed
-in~\cite{DBLP:journals/jacm/LiuL73}, by allowing computation time of
-tasks to be non-constant, and by considering overheads and other
-details of the enviroments.
+in~\cite{DBLP:journals/jacm/LiuL73}, by allowing computation
+requirements of tasks to be non-constant, and by considering overhead
+and other details of the enviroments.
 
@@
 $\tau_1,\ldots,\tau_n$. Task $\tau_i$ has a period $T_i$ and a
-computation time $C_i$. First jobs of all tasks are assumed to be
-initiated simultaneously. This means that jobs corresponding to task
-$\tau_i$ are initiated at times $kT_i$ with integers $k\ge
+computation requirement $C_i$. First jobs of all tasks are assumed to
+be initiated simultaneously. This means that jobs corresponding to
+task $\tau_i$ are initiated at times $kT_i$ with integers $k\ge
 0$. Deadlines consist of runability constraints only: the job
@@
 
-(A1) Computation time $C_i$ for each task $\tau_i$ is constant and
-does not vary with time.
+(A1) Computation requirement $C_i$ for each task $\tau_i$ is constant
+and does not vary with time.
 
@@
   declarations of \emph{sorts}, \emph{subsorts} and \emph{function
-    symbols}.
+    symbols}. The function symbols are allowed to be mixfix.
 \item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
-  theory}, with $E$ a set of possibly conditional equations, and $A$ a
-  set of equational axioms such as associativiy, commutativity and
-  identity.  $(\Sigma, E\cup A)$ models the system's ``static'' states
-  as an algebraic data type, and includes a built-in specification of
-  a sort \verb|Time|.
+  theory}, with $E$ a set of conditional equations on $\Sigma$, and
+  $A$ a set of equational axioms such as associativiy, commutativity
+  and identity.  $(\Sigma, E\cup A)$ models the system's ``static''
+  states as an algebraic data type, and includes a built-in
+  specification of a sort \verb|Time|.
 \item $IR$ is a set of \emph{labeled conditional rewrite rules}
@@
   where each $cond_j$ is an equality $u_j=v_j$ and $l$ is a
-  \emph{label}. Such a rule specifies an \emph{instaneous transition}
-  from an instance of $t$ to the corresponding instance of $t'$,
-  \emph{provided} the conditions hold.
-\item $TR$ is a set of \emph{tick rules} $[l]~:~\{t\}\rightarrow\{t'\}
-  \mbox{ \textbf{in time} }r\mbox{ \textbf{if} }cond$ that specify
-  \emph{timed transitions} advancing time in the \emph{entire} state
-  $t$ by $r$ time units. $IR$ and $TR$ together model the ``dynamic''
-  behaviors of the system.
+  \emph{label}. Such a rule specifies an \emph{instaneous transition},
+  without consuming time, from an instance of $t$ to the corresponding
+  instance of $t'$, \emph{provided} the conditions hold.
+\item $TR$ is a set of (\emph{labeled}) \emph{tick rules}
+  $[l]~:~\{t\}\rightarrow\{t'\} \mbox{ \textbf{in time} }r\mbox{
+  \textbf{if} }cond$ that specify \emph{timed transitions} advancing
+  time in the \emph{entire} state $t$ by $r$ time units. $IR$ and $TR$
+  together model the ``dynamic'' behaviors of the system.
 \end{itemize}
 
-Real-Time Maude supports \emph{object-oriented} style specifications.
-A class declaration $\texttt{class }C\texttt{ |
+Real-Time Maude supports specifications in \emph{object-oriented}
+style.  A class declaration $\texttt{class }C\texttt{ |
 }att_1\texttt{:}s_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}s_n$
-declares a class $C$ with attributes $att_1$ to $att_n$ of sorts $s_1$
-to $s_n$. An \emph{object} of class $C$ in a given state is
-represented as a term $\texttt{< } O\texttt{:} C \texttt{ | }
+defines a class $C$ with attributes $att_1$ to $att_n$ of sorts $s_1$
+to $s_n$, respectively. An \emph{object} of class $C$ is represented
+as a term $\texttt{< } O\texttt{:} C \texttt{ | }
 att_1\texttt{:}val_1\texttt{,} \ldots
@@
 where $O$, of sort \verb|Oid|, is the object's \emph{identifier}, and
-where $val_1$ to $val_n$ are the current values of the attributes
-$att_1$ to $att_n$. A \emph{subclass} inherits all the attributes and
-rules of its superclasses.
+$val_1$ to $val_n$ are the values of the attributes $att_1$ to
+$att_n$. A \emph{subclass} inherits all the attributes and rules of
+its superclasses.
 
 \subsubsection{Formal Analysis}
+Real-Time Maude provides many useful commands and tools to analyze a
+model. For example, \verb|rewrite| allows to execute the model,
+symbolically; given an initial state, \verb|search| is used to search
+reachable states satisfying the desired properties; the Maude's
+\emph{Inductive Theorem Prover} (ITP) can be applied to interactively
+prove properties written in \emph{membership equational logic}.
+
 In this paper, we only consider Real-Time Maude's \emph{linear
@@
 behavior satisfies a temporal logic formula. \emph{State propositions}
-are terms of sort \verb|Prop|, and their symantics is defined by
-equations $\texttt{ceq } statePattern \texttt{ |= } prop \texttt{ = }
-b \texttt{ if } cond$, with $b$ a term of sort \verb|Bool|, stating
-that $prop$ evaluates to $b$ in states that are instances of
-$statePattern$ when the condition $cond$ holds. These equations
-together define $prop$ to hold in all states $t$ where $t \texttt{ |=
-} prop$ evaluates to \verb|true|. A temporal logic \emph{formula} is
-constructed by state propositions and temporal logic operators such as
-\verb|True|, \verb|False|, \verb|~|(negation), \verb|/\|, \verb|\/|,
-\verb|->|(implication), \verb|[]|(``always''),
+are terms of sort \verb|Prop|. Their symantics is defined by equations
+of the form $\texttt{ceq } statePattern \texttt{ |= } prop \texttt{ =
+} b \texttt{ if } cond$, with $b$ a term of sort \verb|Bool|, stating
+that $prop$ evaluates to $b$ in states which are instances of
+$statePattern$ provided the condition $cond$ holds. These equations
+together define $prop$ to hold in all states $t$ that make $t \texttt{
+  |= } prop$ evaluate to \verb|true|. A temporal logic \emph{formula}
+is constructed by state propositions and temporal logic operators such
+as \verb|True|, \verb|False|, \verb|~|(negation), \verb|/\|,
+\verb|\/|, \verb|->|(implication), \verb|[]|(``always''),
 \verb|<>|(``eventually'') and \verb|U|(``until''). Real-Time Maude
-provides both \emph{unbounded} and \emph{time-bounded} LTL model
-checking. The time-bounded model checking command
+supports both \emph{timed} and \emph{untimed} LTL model checking. The
+untimed model checking command
 \begin{alltt}
-  (mc \(t\) |=t \(formula\) in time <= \(timeLimit\) .)
+  (mc \(t\) |=u \(formula\) .)
 \end{alltt}
-checks whether the temporal logic formula holds in all behaviors up to
-duration $timeLimit$ starting from the initial state $t$.
+checks whether the temporal logic $formula$ holds in all behaviors
+starting from the initial state $t$, \emph{with no time limit}.
 
@@
 \label{s:imp}
-The algorithm of the RMS is straightforward, and it is easy to
-implement it in pratical systems. However, the way to implement it is
-not unique. Our target implementation to analyze is part of a
-realistic avionic operating system from our industrial
-partner. Interrupts triggered by the clock would come every $T$, which
-we call \emph{interrupt cycle}. When an interrupt request comes, if
-the system is interruptable, i.e. the interrupt mask is cleared, the
-function $schedule()$ will be called; otherwise the handler function
-$schedule()$ will be pending until the interrupt mask becomes cleared.
-The pseudocode of $schedule()$ is shown as Algorithm~\ref{a:schedule},
-where $taskList$ is the list of periodic tasks, which are needed to be
-scheduled, and assumed ordered descendingly by priorities, and where
-both variables $taskList$ and $timer$ are global. In this
-implementation, there is only one kind of interrupt, the period $T_i$
-of each task is a multiple of $T$, and the tasks are independent,
-meeting assumption~(A2).
+The implementation is in a realistic avionic operating system.
+Interrupts triggered by the clock would come every $T$, which we call
+\emph{interrupt cycle}. When an interrupt request occurs, if the
+system is interruptable, i.e. the interrupt mask is cleared, the
+handler function $schedule()$ will be invoked; otherwise $schedule()$
+will be pending until the interrupt mask becomes cleared.  The
+implementation is shown as $schedule()$ in Algorithm~\ref{a:schedule},
+where $taskList$ is the list of periodic tasks to be scheduled. We assume that 
+the list is ordered descendingly by priorities, and both variables
+$taskList$ and $timer$ are global. In this implementation, there is
+only one kind of interrupt, the period $T_i$ of each task is a
+multiple of $T$, and the tasks are independent, meeting
+assumption~(A2).
 
@@
 \Function{$schedule$}{$ $}{}
-  \State \Call{$int\_o\!f\!\!f$}{$ $}; \Comment{to disable interrupts}
+  \State \Call{$int\_o\!f\!\!f$}{$ $}; \Comment{to disable interrupts} \label{l:1stline}
   \State \Call{$updateStatus$}{$taskList$}; \label{l:updatestatus}
@@
       \State \Call{$int\_on$}{$ $}; \Comment{to enable interrupts} \label{l:endrun1st}
-      \State $p\rightarrow function()$; \Comment{to run the task} \label{l:function}
+      \State $p\rightarrow function()$; \Comment{to execute the task} \label{l:function}
       \State \Call{$int\_o\!f\!\!f$}{$ $};
@@
     \If{$timer~\%~(p\rightarrow period) == 0$} \Comment{the task should be initiated}
-      \If{$p\rightarrow status == \textit{DORMANT}$} 
+      \If{$p\rightarrow status == \textit{DORMANT}$} \Comment{the previous job finishes} 
         \State $p\rightarrow status = \textit{READY}$;
@@
 
-The function $updateStatus()$ updates status of all tasks in the list:
-if the task is running when the interrupt is handled, it becomes
-interrupted\footnote{Note that the status \textit{INTERRUPT} indicates
-  the task is interrupted for the moment, or was interrupted before
-  but is not finished running yet.}; the task, which is at its
-initiated time, would be set to be ready if its previous corresponding
-job is finished, or produce an error otherwise. Notice that
-$schedule()$ is called only when the periodic interrupt is handled. It
-can be also interrupted while running some task (Line~\ref{l:function}
-in Algorithm~\ref{a:schedule}), such that the running of $schedule()$
-can be nested.
-
-\section{Formalizing the RMS Implementation}
+In Algorithm~\ref{a:schedule}, the handler function $scheduler()$
+first updates status of all tasks in $taskList$ via function
+$updateStatus()$. Then it scans the list to execute the ready tasks
+one by one, or to do a return when encountering an interrupted task.
+The function $updateStatus()$ updates each task in two stages:
+firstly, if the task is running, it becomes interrupted\footnote{Note
+  that the status \textit{INTERRUPT} indicates the task is interrupted
+  for the moment, or was interrupted before but its execution is not
+  finished yet.}; secondly for the task at its initiation time, if its
+previous job is finished, it would be set to be ready, otherwise it
+produces an error. Notice that $schedule()$ is invoked only when the
+periodic interrupt is handled. Its running cannot be interrupted when
+it is updating status of tasks or finding the next task to be
+executed, however, it can be interrupted while executing some task
+(Line~\ref{l:function}). This allows the running of $schedule()$ to be
+nested.
+
+In the rest of this paper, we use \emph{scheduling} to refer to the
+stage, from the moment when a pending interrupt request is detected,
+to the moment when the first should-be-run periodic task starts
+executing, i.e. Line~\ref{l:function} in
+Algorithm~\ref{a:schedule}. Therefore, \emph{scheduling time} mainly
+consists of three parts: (i) the time for switching context from the
+running task, possibly none, to $schedule()$ when handling interrupt
+requests, (ii) the time spent by $schedule()$ finding and setting the
+\emph{first} should-be-run periodic task
+(Lines~\ref{l:1stline}-\ref{l:endrun1st} in
+Algorithm~\ref{a:schedule}), and (iii) the time for switching context
+from $schedule()$ to that first should-be-run task. \emph{Switching}
+refers to the stage, from the moment when a periodic task completes
+its execution, to the moment when the next should-be-run periodic task
+starts executing. \emph{Switching time} thus also consists of three
+parts: (i) the time for switching context from the finished task back
+to $schedule()$, (ii) the time spent by $schedule()$ finding and
+setting the \emph{next} should-be-run periodic task, and (iii) the
+time for switching context from $schedule()$ to that next
+should-be-run task.
+
+\section{Formal Model of the Implementation}
 \label{s:formalism}
-Based on the code, we model the implementation under the following
-assumptions:
-
-(A1') Computation time $C_i$ for each task $\tau_i$ is not constant,
-varying randomly between minimum $C^{min}_i$ and maximum $C^{max}_i$.
+We model the implementation under the following assumptions:
+
+(A1') Computation requirement $C_i$ for each task $\tau_i$ is not
+constant. It varies randomly between minimum $C^{min}_i$ and maximum
+$C^{max}_i$, i.e. within an interval $[C^{min}_i, C^{max}_i]$.
 
@@
 
-(A3') The times for scheduling and task switching should be
-considered, while other overhead is ignored.
-
-These assumptions make our model different with the standard
-formulation. For instance, due to the interrupt masking and
-consideration of scheduling overhead, jobs corresponding to task
-$\tau_i$ could not be initiated at exactly $kT_i$, but a bit later.
-Note that (A2) says jobs are ready to run at their initiation times,
-however, they cannot run at their initiation times, because scheduling
-takes time.
-
-\subsection{Some Basic Data Types}
+(A3') Scheduling time and switching time are considered, while other
+overhead is ignored.
+
+These assumptions make our model different from the standard one. For
+instance, if an interrupt request occurs while switching is performed,
+jobs corresponding to task $\tau_i$ could not be initiated at exactly
+$kT_i$. They should wait until switching is finished and the interrupt
+mask is cleared. Note that (A2) says that jobs are ready to run at
+their initiation times, however, no one can start running at exactly
+its initiation time, because scheduling takes time.
+
+\jx{TODO. A figure is needed here to demostrate the scheduling under
+  the three assumptions above.}
+
+In this section, we introduce first how we model the states--the
+static aspect--of the system using algebraic data types, then how we
+specify the essential behaviors--the dynamic aspect--using rewrite
+rules.
+
+\subsection{Basic Data Types}
 In our model, tasks are identified with their indexes of sort
@@
 \subsection{Modeling the System States}
-Abstracting from some details, the running system could be considered
-as consisting of several parts: the tasks which are scheduled, the
-scheduler itself, the hardware including registers and stacks, and the
-interrupt source. The scheduler, i.e. the function $schedule()$, has
-only the variable $timer$ to be interesting, thus it can be described
-by a single variable. We will present the modeling of the other parts
-one by one.
+The running system can be considered as consisting of several parts:
+the tasks which are scheduled, the scheduler itself, the hardware
+including registers and stacks, and the interrupt source. The
+scheduler, i.e. the function $schedule()$, can be described by a
+single variable $timer$. We present the models of the other parts one
+by one.
 
 \subsubsection{Tasks}
-In this paper, since we are trying to analyze the implementation of
-the scheduler, each task will be abstracted from its functionality and
-treated as a \verb|Counter|. As mentioned above, times for scheduling
-and task switching will be also considered in the model. They are just
-seen as two system tasks. Every task is modeled as an object instance
-of some subclass of the base class \verb|Task|:
+Each task is abstracted from its functionality as a \verb|Counter|.
+Overhead for scheduling and switching is considered in the model. They
+are treated as two system tasks. Every task is modeled as an object
+instance of some subclass of the base class \verb|Task|:
 \begin{verbatim}
@@
 \end{verbatim}
-As mentioned already, periodic tasks would be identified by their
-indexes in the list.
+Periodic tasks are identified by their indexes in the list.
 
@@
 \end{verbatim}
-Different from periodic tasks, system tasks would be organized in a
+Different from periodic tasks, system tasks are organized in a
 multiset of sort \verb|SysTasks|, and identified by their \verb|Oid|s.
-We abstract here from the detailed definitions thanks to the
-similarity.
-
-\subsubsection{Hardware} Our model considers two parts of hardware relating
-to the interrupt handling inside the system, the registers and the
-stack.
+%We abstract here from the detailed definitions thanks to the
+%similarity.
+
+\subsubsection{Hardware}
+Our model considers two parts of hardware related to the interrupt
+handling inside the system: the registers and the stack.
 
@@
 \verb|mask| for the interrupt masking flag and \verb|ir| for the
-interrupt request flag.
+interrupt request flag, respectively.
 \begin{verbatim}
@@
 \end{verbatim}
-
-Some operations, such as \verb|getPc|, \verb|setMask| and so on, are
-also defined on the class \verb|Regs|.
+Some operations, such as \verb|getPc| and \verb|setMask|, are defined
+on the class \verb|Regs|.
 
@@
 \subsubsection{Interrupt Source}
-The interrupt source is modeled in our model as an object of class \verb|IntSrc|,
-with attribute \verb|cycle| denoting the interrupt cycle:
+The interrupt source is modeled as an object of class \verb|IntSrc|,
+with attributes \verb|cycle| denoting the interrupt cycle $T$, and
+\verb|val| for the value which will decrease from $T$ to $0$ while
+time advances:
 \begin{verbatim}
@@
 \subsubsection{System}
-The system in the model is just a composition of the parts introduced
-above, with a sort \verb|System|\footnote{Some variable declarations
-  are not shown for simplicity.}:
+The entire system in the model is a composition of the parts
+introduced above, with a sort \verb|System|\footnote{Some variable
+  declarations are not shown for simplicity.}:
 \begin{verbatim}
@@
 
-\subsection{Interrupt Requesting}
+\subsection{Interrupt Requests}
 Interrupt requests are performed by the source exactly every cycle
-$T$, when the attribute \verb|val| decreases to \verb|zero| while time
-advances. This is modeled by the following instaneous conditional rule
-applied on \verb|System|:
+$T$, when the attribute \verb|val| decreases to \verb|zero|. The
+requesting is an instaneous action, and thus is modeled by the
+following instaneous conditional rule applied on \verb|System|:
 \begin{verbatim}
@@
 where the operator \verb|_.timeout| examines whether the attribute
-\verb|val| equals to \verb|zero|, and \verb|_.intReq| sets the
-\verb|ir| flag indicating there is an interrupt request to be handled:
+\verb|val| equals \verb|zero|, and \verb|_.intReq| sets the \verb|ir|
+flag indicating there is an interrupt request to be handled:
 \begin{verbatim}
@@
 \subsection{Task Initiation}
-Periodic tasks are initiated sequently by exactly the function
+Periodic tasks are initiated sequentially by the function
 $updateStatus()$ in Algorithm~\ref{a:schedule}, which is modeled by
@@
 not be initiated, the status of the task changes only if it is
-\verb|RUNNING|. We can easily see \verb|updateStatus_with_| behaves
-the same as $updateStatus()$.
+\verb|RUNNING|. We can see that \verb|updateStatus_with_| behaves the
+same as $updateStatus()$.
 
@@
 \label{ss:inthandling}
-When an interrupt request comes, it may not be ``seen'' immediately by
-the system. It requires the \verb|mask| flag to be cleared. Once the
-request is seen, it is handled by performing two stages: the interrupt
-mechanism of the hardware (such as clearing \verb|ir|, pushing context
-into stack and so on) and running the $schedule()$ function. This is
-modeled by the following instaneous rewrite rule:
+When an interrupt request occurs, it may not be detected immediately
+by the system. It requires the \verb|mask| flag to be cleared. Once
+the request is detected, it is handled by two steps: the interrupt
+handling mechanism of the hardware (such as clearing \verb|ir|,
+pushing context into stack and so on) and to call the $schedule()$
+function. This is modeled by the following instaneous rewrite rule:
 \begin{verbatim}
@@
 \emph{and} \verb|ir| is set. The operation \verb|_.interrupt| models
-the interrupt mechanism performed by the hardware and does four
-things: (i)clearing the \verb|ir| flag, which means the request has
-been handled; (ii)pushing the current \verb|pc| value into the stack,
-storing the interrupted context; (iii)assigning \verb|scheduling| of
-sort \verb|Oid| to \verb|pc|, which indicates that $schedule()$ is
-running; and (iv)setting the \verb|mask| flag, to mask the coming
-interrupt requests. As for \verb|_.startScheduling|, it performs
-updating the status of $taskList$ and increasing $timer$ by $1$,
-corresponding to Line~\ref{l:updatestatus} and \ref{l:inc} in
+the interrupt handling mechanism performed by the hardware and does
+four things: (i) clearing the \verb|ir| flag, which means the request
+has been handled; (ii) pushing the current \verb|pc| value into the
+stack, storing the interrupted context; (iii) assigning
+\verb|scheduling| of sort \verb|Oid| to \verb|pc|, which indicates
+that $schedule()$ is running; and (iv) setting the \verb|mask| flag,
+to mask the coming interrupt requests. As for
+\verb|_.startScheduling|, it performs updating the status of
+$taskList$ and increasing $timer$ by $1$, corresponding to
+Lines~\ref{l:updatestatus} and \ref{l:inc} in
 Algorithm~\ref{a:schedule}.
@@
 \end{verbatim}
-
-It is worth pointing out here that \emph{scheduling} in our model does
-not refer to the stage in which $schedule()$ is running. We use it to
-refer to, for simplicity, the stage scheduling the first should-be-run
-periodic task, i.e.  the code strictly before Line~\ref{l:function} in
-Algorithm~\ref{a:schedule}. Therefore,
-\begin{definition}
-  The \emph{scheduling time} talked about in this paper consists of
-  the time for switching from a running task to the function
-  $schedule()$ when handling interrupts, the time spent by
-  $schedule()$ finding and setting the \emph{first} should-be-run
-  periodic task, and the time for switching from $schedule()$ to that
-  first should-be-run task.
-\end{definition}
-Similarly, \emph{switching} in our model refers to the stage finding
-out the next should-be-run periodic task when one is finished.
-\begin{definition}
-  The \emph{switching time} in this paper consists of the time for
-  switching from a finished task back into $schedule()$, the time
-  spent by $schedule()$ finding and setting the \emph{next}
-  should-be-run periodic task, and the time for switching from
-  $schedule()$ to that next should-be-run task.
-\end{definition}
 
@@
 scheduling stage: finding the first should-be-run periodic task and
-setting it to run (Line~\ref{l:startrun1st}-\ref{l:endrun1st} in
+setting it to run (Lines~\ref{l:startrun1st}-\ref{l:endrun1st} in
 Algorithm~\ref{a:schedule}).
@@
 and \verb|_.run1stTask| models
-Line~\ref{l:startrun1st}-\ref{l:endrun1st} in
+Lines~\ref{l:startrun1st}-\ref{l:endrun1st} in
 Algorithm~\ref{a:schedule}, searching the task with highest priority
 that has status \verb|INTERRUPT| or \verb|READY| then performing an
-\emph{interrupt return} or letting it run respectively.
+\emph{interrupt return} or letting it run, respectively.
 
@@
 
-\subsection{Timed Behaviours of the System}
-\emph{Timed behaviours} of the system consist of two parts, the
-running of tasks, including both periodic ones and system ones, and
-the running of interrupt source. These are all modeled as the
-following one conventional tick rule:
+\subsection{Timed Behaviors of the System}
+\emph{Timed behaviors} of the system consist of two parts: the
+execution of tasks and the execution of the interrupt source. Both are
+modeled into the following one ``standard'' tick
+rule~\cite{DBLP:journals/entcs/OlveczkyM07a}:
 \begin{verbatim}
@@
 where \verb|delta| defines the effects of time elapse on the system,
-and \verb|mte| denotes the maximum amount of time allowed to elapse
-from the current state until an instaneous transition \emph{must} be
-performed. Notice that the variable $R$ is \emph{continuous} with
-respect to the specific time domain\footnote{Real-Time Maude contains
-  built-in modules to define the time domain to be natural numbers and
-  rational numbers, specifying \emph{discrete} time domains and
-  \emph{dense} time domains respectively.}  that we choose to
-instantiate the model on, which is different from timed automata that
-discretize dense time by defining ``clock region''.
-
-Time affects the system by advancing both the running task, whose $ID$
-is loaded at \verb|pc|, and the interrupt source simultaneously,
-increasing their \verb|cnt| and \verb|val| respectively:
+and \verb|mte| denotes the \emph{m}aximum amount of \emph{t}ime
+allowed to \emph{e}lapse from the current state until an instaneous
+transition \emph{must} be performed. Notice that the variable $R$ is
+\emph{continuous} with respect to the specific time
+domain\footnote{Real-Time Maude contains built-in modules to define
+  the time domain to be natural numbers and rational numbers,
+  specifying \emph{discrete} time domains and \emph{dense} time
+  domains respectively.}  that we choose to instantiate the model on,
+which is different from timed automata that discretize dense time by
+defining ``clock region''.
+
+Time affects the system by advancing both the running task whose $ID$
+is loaded at \verb|pc| and the interrupt source simultaneously.  While
+time elapses, \verb|cnt| of the former increases and \verb|val| of the
+latter decreases, respetively.
 \begin{verbatim}
@@
 \end{verbatim}
-We ease the reading by not showing the case where $ID$ is of sort
-\verb|Oid|, due to similarity. At that case, \verb|deltaTask| applies
-on \verb|STS| instead of \verb|L|.
-
-The maximum amount of time allowed to elapse depends on three aspects:
-the time remained to finish the running task, either periodic one or
-system one, the time remained to request an interrupt, and whether or
-not there exists a non-masked interrupt request for the moment:
+We omit details for the case where \verb|ID| is of sort \verb|Oid| due
+to similarity. In that case, \verb|deltaTask| applies on \verb|STS|
+instead of \verb|L|.
+
+\verb|mte|, the maximum amount of time allowed to elapse, depends on
+when the next instaneous action must perform. Therefore, it is decided
+by three arguments: the remaining time to finish the running task, the
+remaining time to request the next interrupt, and whether or not there
+exists an interrupt request detected for the moment:
 \begin{verbatim}
@@
 represents \emph{infinity} otherwise. Again we do not show the case
-where $ID$ is of sort \verb|Oid|, which is very similar. We should
-point out that \verb|mteTask| computes the time remained to reach the
-maximum of the possible finishing interval of the task, since it is
-the time until which a ``finish'' transition \emph{must} happen.
+where \verb|ID| is of sort \verb|Oid|, which is very similar. We
+should point out that \verb|mteTask| computes the remaining time to
+reach the maximum of the possible finishing interval of the task,
+since it is the time at which a complete transition \emph{must}
+happen.
 
@@
 \label{s:verification}
-Although Real-Time Maude provides many useful commands and tools to
-analyze a model, such as, \verb|rewrite| to execute the model,
-\verb|search| to search some reachable state(s) satisfying given
-properties from the initial state, the Maude Inductive Theorem Prover
-(ITP) to interactively prove properties written in \emph{membership
-  equational logic}, and so on, we concentrate in this paper on using
-the model checking tool to verify the desired properties of our model.
-
-In this section, we analyze our model of the RMS implementation under
-several different scenarios, including both realistic and experimental
-ones. Notice that from any (reasonable) given initial state, the
-number of reachable states is finite, thanks to the upperbound given
-to the $timer$, which provides the potential for applying the untimed
-model-checker.
-
-\subsection{Properties Verified}
+In this section, we analyze our model of the RMS implementation within
+different realistic scenarios.  Notice that from any (reasonable)
+given initial state, the number of reachable states is finite, but may
+be unknown, thanks to the upper bound given to the $timer$, which
+provides the potential for applying the untimed model checker.
+
+\subsection{Properties}
 The main objective is to verify the schedulability of a given set of
-periodic tasks. Therefore we define an atomic proposition
+periodic tasks. Therefore, we define an atomic proposition
 \verb|taskTimeout| to hold if there exists an \verb|error| appearing
@@
 property--schedulability--can be formalized as the temporal logic
-formula \verb|[](~taskTimeout)|. As the property is not
+formula: \verb|[](~taskTimeout)|. As the property is not
 \emph{clocked}, given an initial state \verb|init|, the following
 untimed model-checking command returns \verb|true| if our desired
-schedulability property holds \emph{with no time limit}; otherwise 
-a trace showing a counterexample is provided.
+schedulability property holds \emph{with no time limit}; otherwise a
+trace showing a counterexample is provided.
 \begin{verbatim}
@@
 
-The other objective is to verify the correctness of the
-implementation, in the sense that the periodic tasks are scheduled
-exactly with respect to their priorities. The atomic proposition
+Another objective is to verify the correctness of the implementation,
+in the sense that the periodic tasks are scheduled exactly with
+respect to their priorities. The atomic proposition
 \verb|scheduleCorrectly| is defined to hold if the running periodic
-task is the one requested to be run and with the highest priority:
+task is the one requested to be run with the highest priority:
 \begin{verbatim}
@@
 
-\subsection{Soundness and Completeness of the Analysis}
-We call an analysis method \emph{sound} if any counterexample found
+\subsection{Evaluation}
+%\subsection{Soundness and Completeness of the Analysis}
+We now show our results are both \emph{sound} and \emph{complete} in
+this section.
+
+An analysis method is called \emph{sound} if any counterexample found
 using such a method is a real counterexample of the question, and
 \emph{complete} if the fact that no counterexample can be found using
-such a method implies no counterexample exist for the question in
+such a method implies no counterexample exists for the question in
 analysis. The soundness of our results is easy to check, simply by
-examining the counterexamples found. But this is not the case for
-completeness, since we choose instantiating our model on dense time
-domain to make it more real but giving rise to an infinite state space
-which is unfeasible to exhaust. In general, completeness of untimed
-model checking cannot be achieved for any systems, any time sampling
-stategies and any properties. However, \"Olveczky and Meseguer proved
-the completeness of untimed temporal logic model checking, under the
-maximal time sampling strategy, for a large class of real-time
-systems:
-\begin{theorem}
+examining the counterexamples found. For instance, the counterexample
+shown in Figure~\ref{f:counterexample} is a real counterexample,
+implying that the result of Scenario~(iv) is sound. But this is not
+the case for completeness, since we choose instantiating our model on
+dense time domain to make it more real but giving rise to an infinite
+state space which is unfeasible to exhaust.
+
+In general, completeness of untimed model checking cannot be achieved
+for any systems, any time sampling stategies and any
+properties. However, \"Olveczky and Meseguer proved the completeness
+of untimed temporal logic model checking, under the maximal time
+sampling strategy, for a large class of real-time
+systems~\cite{DBLP:journals/entcs/OlveczkyM07a}:
+\begin{theorem}[\cite{DBLP:journals/entcs/OlveczkyM07a}]
 \label{t:completeness}
@@
 checking verifying $\Phi$ is \emph{complete} under the maximal time
-sampling stategy.
+sampling strategy.
 \end{theorem}
 
+In order to prove the completeness of our verification, we need little
+adjustments to our model.  For each task $\tau_i$, we collapse its
+computation requirement $[C_i^{min},C_i^{max}]$ into the single value
+$C_i^{max}$.  That is, in the adjusted model, we use the maximum time
+that is possible to be required to complete the task, as in the
+standard setting. The adjustment is reasonable for verifying our
+properties, since the schedulability and correctness of the adjusted
+model imply the schedulability and correctness of our original
+model. In particular, this is because we can prove that, if a set of
+tasks (including system ones) is schedulable when the computation
+requirement of some task $\tau_i$ equals $C_i^{max}$, then the set
+remains still schedulable when some jobs of $\tau_i$ become possible
+to terminate in time $r\le C_i^{max}$. This statement is done by
+proving Lemma~\ref{l:max}, and considering \verb|scheduling| and
+\verb|switching| as tasks with same priority, which is higher than all
+periodic tasks.
+\begin{lemma}
+\label{l:max}
+Assume $r_s, r_f$ are the times at which a job of $\tau_i$ starts and
+completes its execution, respectively. Let $S_i$ be the set of tasks,
+which have priorities higher than $\tau_i$ or equal to it. Assumed
+$r_s$ is fixed, $r_f$ reaches its maximum, if all job instances of
+each task $\tau_j\in S_i$, which execute between $r_s$ and $r_f$, are
+completed in time $C_j^{max}$.
+\end{lemma}
+
+We achieve the same verification results in the adjusted model as in
+our original one: schedulability and correctness hold in
+Scenarios~(i-iii)\footnote{In fact, positive results in the original
+  model imply positive results in the adjusted one, since the set of
+  behaviors of the adjusted model is a subset of those of the
+  original.} but fail in Scenario~(iv).  The adjusted model is
+time-robust and our defined atomic propositions--\verb|taskTimeout|
+and \verb|scheduleCorrectly|--are tick-stabilizing, hence our analysis
+using untimed model checking on the adjusted model is complete by
+Theorem~\ref{t:completeness}. Therefore, the results shown in
+Section~\ref{ss:results} for our original model are complete.
+
+\hide{
 To apply Theorem~\ref{t:completeness} on our analysis to show the
@@
 \end{lemma}
+}
 

### 2015-10-22 RMS/submission.tex
temporary commit

@@
 jobs according to the periods of the corresponding tasks: the smaller
-period, the higher priority. It is proved to be the \emph{optimal}
+period, the higher priority. RMS is proved to be the \emph{optimal}
 fixed priority scheduling algorithm~\cite{DBLP:journals/jacm/LiuL73},
@@
 modeling language and analyzing tool for real-time systems, to model a
-realistic implementation of RMS algorithm and then verify some desired
+realistic implementation of RMS and then verify some desired
 properties on the built model. Based on a realistic implementation,
-our model extends the original ideal one proposed
+our model extends the standard one proposed
 in~\cite{DBLP:journals/jacm/LiuL73}, by allowing computation
@@
 
-The rest of this paper is organized as follows. Section~\ref{s:background}
-introduces the standard setting of the RMS algorithm proposed
-in~\cite{DBLP:journals/jacm/LiuL73} and our
-implementation. Section~\ref{s:imp} gives a background to
-Real-Time Maude. Section~\ref{s:formalism} presents how we model the
-RMS implementation using Real-Time Maude. Then
-Section~\ref{s:verification} explains how to verify the desired
-properties and to analyze the results. Related work is discussed in
-Section~\ref{s:relate}. We conclude the paper in
+The rest of this paper is organized as
+follows. Section~\ref{s:background} gives some background of the RMS
+algorithm and Real-Time Maude.  Section~\ref{s:imp} presents the RMS
+implementation that we model and analyze.  Section~\ref{s:formalism}
+introduces how we model the RMS implementation using Real-Time
+Maude. Then Section~\ref{s:verification} explains how to verify the
+desired properties and to evaluate the results. Related work is
+discussed in Section~\ref{s:relate}. We conclude the paper in
 Section~\ref{s:conclusion}.
@@
 A task set consists of \emph{only} $n$ periodic tasks
-$\tau_1,\ldots,\tau_n$. Task $\tau_i$ has a period $T_i$ and a
+$\tau_1,\ldots,\tau_n$. Each task $\tau_i$ has a period $T_i$ and a
 computation requirement $C_i$. First jobs of all tasks are assumed to
@@
 RMS algorithm itself, thus the model would be more complicated than
-this ideal setting.  Assumptions~(A1) and (A3) will be relaxed later
-to obtain a more realisitc analysis model.
+this standard, ideal setting.  Assumptions~(A1) and (A3) will be
+relaxed later to obtain a more realistic analysis model.
 
@@
 \subsubsection{Specification}
-Real-Time Maude models a system using \emph{modules}. A module
-specifies a \emph{real-time rewrite theory} ${\cal R} = (\Sigma, E\cup
-A , IR, TR)$, where:
+Real-Time Maude models systems as \emph{modules}. A module specifies a
+\emph{real-time rewrite theory} ${\cal R} = (\Sigma, E\cup A , IR,
+TR)$, where:
 \begin{itemize}
@@
   theory}, with $E$ a set of conditional equations on $\Sigma$, and
-  $A$ a set of equational axioms such as associativiy, commutativity
+  $A$ a set of equational axioms such as associativity, commutativity
   and identity.  $(\Sigma, E\cup A)$ models the system's ``static''
@@
 The implementation is in a realistic avionic operating system.
-Interrupts triggered by the clock would come every $T$, which we call
+Interrupts would be triggered by the clock every $T$, which we call
 \emph{interrupt cycle}. When an interrupt request occurs, if the
@@
 implementation is shown as $schedule()$ in Algorithm~\ref{a:schedule},
-where $taskList$ is the list of periodic tasks to be scheduled. We assume that 
-the list is ordered descendingly by priorities, and both variables
-$taskList$ and $timer$ are global. In this implementation, there is
-only one kind of interrupt, the period $T_i$ of each task is a
-multiple of $T$, and the tasks are independent, meeting
+where $taskList$ is the list of periodic tasks to be scheduled. We
+assume that the list is ordered descendingly by priorities, and both
+variables $taskList$ and $timer$ are global. In this implementation,
+there is only one kind of interrupt, the period $T_i$ of each task is
+a multiple of $T$, and the tasks are independent, meeting
 assumption~(A2).
@@
 first updates status of all tasks in $taskList$ via function
-$updateStatus()$. Then it scans the list to execute the ready tasks
-one by one, or to do a return when encountering an interrupted task.
-The function $updateStatus()$ updates each task in two stages:
-firstly, if the task is running, it becomes interrupted\footnote{Note
-  that the status \textit{INTERRUPT} indicates the task is interrupted
-  for the moment, or was interrupted before but its execution is not
-  finished yet.}; secondly for the task at its initiation time, if its
-previous job is finished, it would be set to be ready, otherwise it
-produces an error. Notice that $schedule()$ is invoked only when the
-periodic interrupt is handled. Its running cannot be interrupted when
-it is updating status of tasks or finding the next task to be
-executed, however, it can be interrupted while executing some task
-(Line~\ref{l:function}). This allows the running of $schedule()$ to be
-nested.
+$updateStatus()$. Then it traverses the list to execute the ready
+tasks one by one, or to do a return when encountering an
+interrupted\footnote{Note that the status \textit{INTERRUPT} indicates
+  the task is interrupted for the moment, or was interrupted before
+  but its execution is not complete yet.} task. The function
+$updateStatus()$ updates each task in two steps: firstly, if the task
+is running, it becomes interrupted; secondly for the task at its
+initiation time, if its previous job is complete, it would be set to
+be ready, otherwise it misses its deadline, producing an error. Notice
+that $schedule()$ is invoked only when the periodic interrupt is
+handled. Its execution cannot be interrupted when it is updating
+status of tasks or finding the next task to execute, however, it can
+be interrupted while executing some task (Line~\ref{l:function}). This
+allows the execution of $schedule()$ to be nested.
 
@@
 consists of three parts: (i) the time for switching context from the
-running task, possibly none, to $schedule()$ when handling interrupt
-requests, (ii) the time spent by $schedule()$ finding and setting the
-\emph{first} should-be-run periodic task
+running task, possibly none, to $schedule()$ when an interrupt request
+is handled, (ii) the time spent by $schedule()$ finding and setting
+the \emph{first} should-be-run periodic task
 (Lines~\ref{l:1stline}-\ref{l:endrun1st} in
@@
 instance, if an interrupt request occurs while switching is performed,
-jobs corresponding to task $\tau_i$ could not be initiated at exactly
-$kT_i$. They should wait until switching is finished and the interrupt
+jobs corresponding to task $\tau_i$ may not be initiated at exactly
+$kT_i$. They should wait until switching finishes and the interrupt
 mask is cleared. Note that (A2) says that jobs are ready to run at
@@
 
-\jx{TODO. A figure is needed here to demostrate the scheduling under
+\jx{TODO. A figure is needed here to demonstrate the scheduling under
   the three assumptions above.}
@@
 specify the essential behaviors--the dynamic aspect--using rewrite
-rules.
+rules. In particular, modeling of instaneous behaviors would be
+explained in Sections~\ref{ss:ir}, \ref{ss:init}
+and~\ref{ss:inthandling}, followed by timed behaviors in
+Section~\ref{ss:timedbehavior}.
 
 \subsection{Basic Data Types}
-In our model, tasks are identified with their indexes of sort
-\verb|Nat| in the $taskList$. We define a sort \verb|MaybeNat|
-wrapping \verb|Nat|s to refer to some task, with \emph{constructor}
-\verb|some| followed by a \verb|Nat| $n$ indicating the task with
-index $n$, and \verb|none| for no task:
+In our model, tasks are identified by their indexes of sort \verb|Nat|
+in the $taskList$. We define a sort \verb|MaybeNat| wrapping
+\verb|Nat|s to refer to some task, with \emph{constructor} \verb|some|
+followed by a \verb|Nat| $n$ indicating the task indexed $n$, and
+\verb|none| for no task:
 \begin{verbatim}
@@
 
-We also need a sort \verb|Interval| denoting the interval, within
-which the computation time of a task varies and which we call
-\emph{possible finishing interval}, and a sort \verb|Counter| to
+We also need a sort \verb|Interval|
+to denote computation requirements of tasks, 
+and a sort \jx{} \verb|Counter| to
 represent the time some task has been running and the corresponding
@@
 \subsection{Interrupt Requests}
+\label{ss:ir}
 Interrupt requests are performed by the source exactly every cycle
@@
 \subsection{Task Initiation}
+\label{ss:init}
 Periodic tasks are initiated sequentially by the function
@@
 \subsection{Timed Behaviors of the System}
+\label{ss:timedbehavior}
 \emph{Timed behaviors} of the system consist of two parts: the

### 2015-10-22 RMS/submission.tex
finish polishing for the moment, lacking figures demonstrate scheduling

@@
 \subsection{Real-Time Maude}
-Based on \emph{rewriting logic}, \emph{Real-Time Maude} is a language
-and tool that extends \emph{Maude} to support the formal specification
-and analysis of real-time
-systems~\cite{DBLP:journals/lisp/OlveczkyM07}.
+Based on \emph{rewriting logic}~\cite{DBLP:journals/jlp/Meseguer12},
+\emph{Real-Time Maude} is a language and tool that extends
+\emph{Maude} to support the formal specification and analysis of
+real-time systems~\cite{DBLP:journals/lisp/OlveczkyM07}.
 
@@
   where each $cond_j$ is an equality $u_j=v_j$ and $l$ is a
-  \emph{label}. Such a rule specifies an \emph{instaneous transition},
-  without consuming time, from an instance of $t$ to the corresponding
-  instance of $t'$, \emph{provided} the conditions hold.
+  \emph{label}. Such a rule specifies an \emph{instantaneous
+    transition}, without consuming time, from an instance of $t$ to
+  the corresponding instance of $t'$, \emph{provided} the conditions
+  hold.
 \item $TR$ is a set of (\emph{labeled}) \emph{tick rules}
@@
 
-Real-Time Maude supports specifications in \emph{object-oriented}
+In rewriting logic, rewrite rules are applied non-deterministically,
+that is, when several rules can be applied on a given $t$, any of them
+may be chosen. Hence non-deterministic behaviors can be modeled
+naturally in Real-Time Maude.
+
+Real-Time Maude also supports specifications in \emph{object-oriented}
 style.  A class declaration $\texttt{class }C\texttt{ |
@@
 \verb|<>|(``eventually'') and \verb|U|(``until''). Real-Time Maude
-supports both \emph{timed} and \emph{untimed} LTL model checking. The
+supports both \emph{timed} and \emph{untimed LTL model checking}. The
 untimed model checking command
@@
 specify the essential behaviors--the dynamic aspect--using rewrite
-rules. In particular, modeling of instaneous behaviors would be
+rules. In particular, modeling of instantaneous behaviors would be
 explained in Sections~\ref{ss:ir}, \ref{ss:init}
@@
 
-We also need a sort \verb|Interval|
-to denote computation requirements of tasks, 
-and a sort \jx{} \verb|Counter| to
-represent the time some task has been running and the corresponding
-possible finishing interval.
+We also need a sort \verb|Interval| to denote computation requirements
+of tasks, and a sort \verb|Counter| to record execution of tasks.  We
+call \emph{execution time} the time how long a task has been executing
+for. A \verb|Counter| records the execution time and the computation
+requirement of a task.
 \begin{verbatim}
@@
 
-At last, to make our model checkable by \emph{untimed model-checking},
-it is reasonable to reset the global variable $timer$ when it reaches
-an upperbound while increasing (see Line~\ref{l:timer} in
+\hide{
+At last, to make our model checkable by untimed model checking, it is
+reasonable to reset the global variable $timer$ when it reaches an
+upperbound while increasing (see Line~\ref{l:timer} in
 Algorithm~\ref{a:schedule}) in the model. Then $timer$ is of sort
 \verb|Timer| and the upperbound would be the least common multiple of
-the periods of all tasks.
+the periods of all tasks.}
+
+The global variable $timer$ is reset when it reaches an upper bound
+while increasing, which is not shown in detail in
+Algorithm~\ref{a:schedule} but is reasonable. The upper bound is the
+least common multiple of the periods of all tasks. A sort \verb|Timer|
+is defined:
 \begin{verbatim}
@@
 \subsection{Modeling the System States}
-The running system can be considered as consisting of several parts:
-the tasks which are scheduled, the scheduler itself, the hardware
-including registers and stacks, and the interrupt source. The
-scheduler, i.e. the function $schedule()$, can be described by a
-single variable $timer$. We present the models of the other parts one
-by one.
+The system can be considered as consisting of several parts: the tasks
+which are scheduled, the scheduler itself, the hardware including
+registers and stacks, and the interrupt source. The scheduler,
+i.e. the function $schedule()$, can be described by a single variable
+$timer$. We present the models of the other parts one by one.
 
@@
 Each task is abstracted from its functionality as a \verb|Counter|.
-Overhead for scheduling and switching is considered in the model. They
+Overhead for scheduling and switching is considered in our model. They
 are treated as two system tasks. Every task is modeled as an object
@@
 \end{verbatim}
-The attribute \verb|cnt| denotes the computation time of the task,
-while \verb|error| is an object indicating some task which misses its
+where \verb|error| is an object indicating some task that misses its
 deadline.
@@
 \end{verbatim}
-where \verb|Status| is a sort with four constant constructors, just as
+where \verb|Status| is a sort with four constant constructors, same as
 in the implementation:
@@
 Our model considers two parts of hardware related to the interrupt
-handling inside the system: the registers and the stack.
+handling mechanism: the registers and the stack.
 
@@
 \subsubsection{System}
-The entire system in the model is a composition of the parts
+The entire system in our model is a composition of the parts
 introduced above, with a sort \verb|System|\footnote{Some variable
@@
 $T$, when the attribute \verb|val| decreases to \verb|zero|. The
-requesting is an instaneous action, and thus is modeled by the
-following instaneous conditional rule applied on \verb|System|:
+requesting is an instantaneous action, thus is modeled by the
+following instantaneous conditional rule applied on \verb|System|:
 \begin{verbatim}
@@
 \end{verbatim}
-where the operator \verb|_.timeout| examines whether the attribute
+where the function \verb|_.timeout| examines whether the attribute
 \verb|val| equals \verb|zero|, and \verb|_.intReq| sets the \verb|ir|
-flag indicating there is an interrupt request to be handled:
+flag indicating there exists an interrupt request to be handled:
 \begin{verbatim}
@@
 Periodic tasks are initiated sequentially by the function
-$updateStatus()$ in Algorithm~\ref{a:schedule}, which is modeled by
-the recursive operation as below:
+$updateStatus()$ in Algorithm~\ref{a:schedule}, which is treated as an
+instantaneous action in our model. It is modeled by the recursive
+function as below:
 \begin{verbatim}
@@
 with \verb|TIMER| the current value of the global variable $timer$,
-and \verb|update_with_| updating the status of individual task
-(Lines~\ref{l:startupdate}-\ref{l:endupdate} in
-Algorithm~\ref{a:schedule})
+and function \verb|update_with_| updating the status of individual
+task (Lines~\ref{l:startupdate}-\ref{l:endupdate} in
+Algorithm~\ref{a:schedule}):
 \begin{verbatim}
@@
 \end{verbatim}
-In the case where \verb|TIMER|($timer$) can be divided by the task's
-period, i.e. the task should be initiated, if the status is
-\verb|DORMANT|, it should be ready to run; otherwise it means the
-previous job of the task is not finished, thus it misses its deadline,
-producing an \verb|error|. In the other case where the tasks should
-not be initiated, the status of the task changes only if it is
-\verb|RUNNING|. We can see that \verb|updateStatus_with_| behaves the
-same as $updateStatus()$.
+Given a task, if \verb|TIMER|($timer$) can be divided by its period,
+this task should be initiated.  In the case where the task should be
+initiated, it is set to be \verb|READY| if its \verb|status| is
+\verb|DORMANT|; otherwise that means the previous job of this task is
+not complete, hence it misses its deadline, producing an
+\verb|error|. In the other case where the task should not be
+initiated, its \verb|status| changes only if it is \verb|RUNNING|.
+
+We can see that \verb|updateStatus_with_| behaves the same as
+$updateStatus()$.
 
@@
 handling mechanism of the hardware (such as clearing \verb|ir|,
-pushing context into stack and so on) and to call the $schedule()$
-function. This is modeled by the following instaneous rewrite rule:
+pushing context into stack and so on), and to invoke the $schedule()$
+function. This behavior is modeled by the following instantaneous
+rewrite rule:
 \begin{verbatim}
@@
 where \verb|_.existInt| checks whether \verb|mask| is cleared
-\emph{and} \verb|ir| is set. The operation \verb|_.interrupt| models
+\emph{and} \verb|ir| is set. The function \verb|_.interrupt| models
 the interrupt handling mechanism performed by the hardware and does
@@
 \verb|scheduling| of sort \verb|Oid| to \verb|pc|, which indicates
-that $schedule()$ is running; and (iv) setting the \verb|mask| flag,
-to mask the coming interrupt requests. As for
-\verb|_.startScheduling|, it performs updating the status of
-$taskList$ and increasing $timer$ by $1$, corresponding to
-Lines~\ref{l:updatestatus} and \ref{l:inc} in
-Algorithm~\ref{a:schedule}.
+that the system is scheduling; and (iv) setting the \verb|mask| flag,
+to mask coming interrupt requests.
+
+Unlike periodic tasks, even though the scheduling stage is modeled by
+a \verb|Counter|, its functionality is too important to be abandoned.
+We divide the behaviors of scheduling into three parts.  The first
+part contains its timed behaviors. This part is modeled by regarding
+scheduling as a system task of sort \verb|SysTask|. Modeling timed
+behaviors of tasks is explained in Section~\ref{ss:timedbehavior}.
+The other two parts together define its functionality. The second part
+corresponds to Lines~\ref{l:updatestatus}-\ref{l:inc} in
+Algorithm~\ref{a:schedule}. It performs updating the status of
+$taskList$ and increasing $timer$ by $1$. This part is modeled by
+function \verb|_.startScheduling| which applies instantaneously at the
+beginning of scheduling, as shown in rule \verb|interrupt-handle|:
 \begin{verbatim}
@@
 \end{verbatim}
-
-With our terminology, when the running time of the system task
-\verb|scheduling| reaches its possible finishing interval, the
-following rule may apply to finish the scheduling stage:
+The third part corresponds to
+Lines~\ref{l:startrun1st}-\ref{l:endrun1st}, finding the first
+should-be-run periodic task and setting it to execute. It is modeled
+by function \verb|_.finishScheduling|, which applies instantaneously
+at the end of scheduling:
+\begin{verbatim}
+  op _.finishScheduling : System -> System .
+  eq (L T STS HW ISRC).finishScheduling
+       = (L T (finish scheduling in STS) HW ISRC).run1stTask .
+\end{verbatim}
+where \verb|finish_in_| resets the counter of task \verb|scheduling|,
+and \verb|_.run1stTask| models
+Lines~\ref{l:startrun1st}-\ref{l:endrun1st} in
+Algorithm~\ref{a:schedule}, searching the task with highest priority
+that has status \verb|INTERRUPT| or \verb|READY| then performing an
+\emph{interrupt return} or executing it, respectively.
+
+When the execution time of the system task \verb|scheduling| reaches
+its computation requirement, the scheduling stage may finish. We model
+this instantaneous action with the following rule:
 \begin{verbatim}
@@
 \end{verbatim}
-where operation \verb|_.running| returns the current \verb|pc| value
-of the system and \verb|_mayFinish?in_| checks if the running time of
-the task reaches its possible finishing interval:
+where function \verb|_.running| returns the current \verb|pc| value of
+the system, and \verb|_mayFinish?in_| checks whether the execution
+time of the task reaches its computation requirement.
+\hide{
 \begin{verbatim}
@@
        = if R lt MIN then false else true fi .
-\end{verbatim}
-And the operation \verb|_.finishScheduling| performs the remaining
-instructions, which are left by \verb|_.startScheduling|, in the
-scheduling stage: finding the first should-be-run periodic task and
-setting it to run (Lines~\ref{l:startrun1st}-\ref{l:endrun1st} in
-Algorithm~\ref{a:schedule}).
-\begin{verbatim}
-  op _.finishScheduling : System -> System .
-  eq (L T STS HW ISRC).finishScheduling
-       = (L T (finish scheduling in STS) HW ISRC).run1stTask .
-\end{verbatim}
-where \verb|finish_in_| resets the counter of task \verb|scheduling|,
-and \verb|_.run1stTask| models
-Lines~\ref{l:startrun1st}-\ref{l:endrun1st} in
-Algorithm~\ref{a:schedule}, searching the task with highest priority
-that has status \verb|INTERRUPT| or \verb|READY| then performing an
-\emph{interrupt return} or letting it run, respectively.
-
-Similar to \verb|scheduling|, the \verb|switching| stage starts when
-the running time of the current running periodic task reaches its
-possible finishing interval and finishes when its own running time
-does so, with the two following similar rules:
+\end{verbatim}}
+
+Similar to scheduling, the switching stage is divided into timed
+behaviors of \verb|switching| and its functionality. \verb|switching|
+starts when the execution time of the running periodic task reaches
+its computation requirement, and finishes when its own execution time
+does so. Two similar instantaneous rules are defined:
 \begin{verbatim}
@@
 execution of tasks and the execution of the interrupt source. Both are
-modeled into the following one ``standard'' tick
+modeled together by the following single ``standard'' tick
 rule~\cite{DBLP:journals/entcs/OlveczkyM07a}:
@@
 and \verb|mte| denotes the \emph{m}aximum amount of \emph{t}ime
-allowed to \emph{e}lapse from the current state until an instaneous
-transition \emph{must} be performed. Notice that the variable $R$ is
-\emph{continuous} with respect to the specific time
-domain\footnote{Real-Time Maude contains built-in modules to define
-  the time domain to be natural numbers and rational numbers,
-  specifying \emph{discrete} time domains and \emph{dense} time
-  domains respectively.}  that we choose to instantiate the model on,
-which is different from timed automata that discretize dense time by
-defining ``clock region''.
+allowed to \emph{e}lapse from the current state until an instantaneous
+transition \emph{must} be performed. In fact, the core to model timed
+behaviors is to define functions \verb|delta| and \verb|mte|. Notice
+that the variable $R$ is \emph{continuous} with respect to the
+specific time domain\footnote{Real-Time Maude contains built-in
+  modules to define the time domain to be natural numbers and rational
+  numbers, specifying \emph{discrete} time domains and \emph{dense}
+  time domains, respectively.}  that we choose to instantiate our
+model on, which is different from timed automata that discretize dense
+time by defining ``clock region''.
 
@@
 time elapses, \verb|cnt| of the former increases and \verb|val| of the
-latter decreases, respetively.
+latter decreases, respectively:
 \begin{verbatim}
@@
 \verb|mte|, the maximum amount of time allowed to elapse, depends on
-when the next instaneous action must perform. Therefore, it is decided
-by three arguments: the remaining time to finish the running task, the
-remaining time to request the next interrupt, and whether or not there
-exists an interrupt request detected for the moment:
+when the next instantaneous action must perform. Therefore, it is
+decided by three arguments: the remaining time to finish the running
+task, the remaining time to request the next interrupt, and whether or
+not there exists an interrupt request detected for the moment:
 \begin{verbatim}
@@
 \end{verbatim}
-where \verb|mteIr| will return \verb|zero| if there exists a
-non-masked interrupt request in the system, or \verb|INF| which
-represents \emph{infinity} otherwise. Again we do not show the case
-where \verb|ID| is of sort \verb|Oid|, which is very similar. We
-should point out that \verb|mteTask| computes the remaining time to
-reach the maximum of the possible finishing interval of the task,
-since it is the time at which a complete transition \emph{must}
-happen.
+where \verb|mteIr| returns \verb|zero| if there exists an interrupt
+request detected in the system, or \verb|INF| which represents
+\emph{infinity} otherwise. Again we do not show the case where
+\verb|ID| is of sort \verb|Oid|, which is very similar. We should
+point out that \verb|mteTask| computes the remaining time to reach the
+maximum of the computation requirement of the task, since that is the
+time at which a \verb|task-finish| transition \emph{must} happen.
 
@@
 given initial state, the number of reachable states is finite, but may
-be unknown, thanks to the upper bound given to the $timer$, which
-provides the potential for applying the untimed model checker.
+be unknown, thanks to the upper bound given to $timer$, which provides
+the potential for applying the untimed model checker.
 
@@
 The main objective is to verify the schedulability of a given set of
-periodic tasks. Therefore, we define an atomic proposition
+periodic tasks. To this end, we define an atomic proposition
 \verb|taskTimeout| to hold if there exists an \verb|error| appearing
@@
 \emph{clocked}, given an initial state \verb|init|, the following
-untimed model-checking command returns \verb|true| if our desired
-schedulability property holds \emph{with no time limit}; otherwise a
-trace showing a counterexample is provided.
+untimed model checking command returns \verb|true| if the
+schedulability property holds with no time limit; otherwise a trace
+showing a counterexample is provided:
 \begin{verbatim}
@@
 respect to their priorities. The atomic proposition
-\verb|scheduleCorrectly| is defined to hold if the running periodic
-task is the one requested to be run with the highest priority:
+\verb|scheduleCorrectly| is hence defined to hold if the running
+periodic task is the one requested to be executed with the highest
+priority:
 \begin{verbatim}
@@
 its deadline. The correctness property is formalized as the temporal
-logic formula \verb|[]scheduleCorrectly|, and can be verified by the
-following untimed model-checking command provided an initial state
-\verb|init|, which returning \verb|true| indicates the correctness
-property holds with no time limit.
+logic formula: \verb|[]scheduleCorrectly|, and can be verified by the
+following untimed model checking command provided an initial state
+\verb|init|:
 \begin{verbatim}
@@
 \item Scenario (i) with two tasks: one having period $5ms$ and
-  possible finishing interval $[2.4ms, 3ms]$, and the other having
-  period $25ms$ and possible finishing interval $[6.1ms, 7ms]$.
+  computation requirement $[2.4ms, 3ms]$, and the other having period
+  $25ms$ and computation requirement $[6.1ms, 7ms]$.
 \item Scenario (ii) with two tasks: one having period $5ms$ and
-  possible finishing interval $[1.8ms, 2ms]$, and the other having
-  period $25ms$ and possible finishing interval $[2.1ms, 2.3ms]$.
+  computation requirement $[1.8ms, 2ms]$, and the other having period
+  $25ms$ and computation requirement $[2.1ms, 2.3ms]$.
 \item Scenario (iii) with three tasks: the first having period $5ms$
-  and possible finishing interval $[2.5ms, 2.7ms]$, the second having
-  period $10ms$ and possible finishing interval $[1.5ms, 2ms]$, and
-  the third having period $25ms$ and possible finishing interval
-  $[2.6ms, 3ms]$.
+  and computation requirement $[2.5ms, 2.7ms]$, the second having
+  period $10ms$ and computation requirement $[1.5ms, 2ms]$, and the
+  third having period $25ms$ and computation requirement $[2.6ms,
+    3ms]$.
 \item Scenario (iv) with three tasks: the first having period $5ms$
-  and possible finishing interval $[2.2ms, 2.5ms]$, the second having
-  period $10ms$ and possible finishing interval $[1.4ms, 1.5ms]$, and
-  the third having period $15ms$ and possible finishing interval
-  $[4.3ms, 4.5ms]$.
+  and computation requirement $[2.2ms, 2.5ms]$, the second having
+  period $10ms$ and computation requirement $[1.4ms, 1.5ms]$, and the
+  third having period $15ms$ and computation requirement $[4.3ms,
+    4.5ms]$.
 \end{itemize}
@@
 \label{s:relate}
-In this section we discuss our results with related work in two
-directions.
-
-Considering schedulability test, Liu and Layland gave
-in~\cite{DBLP:journals/jacm/LiuL73} the famous sufficient condition
-that a set of periodic tasks is schedulable with respect to RMS if
-$\displaystyle \Sigma^n_{i=1} C_i/T_i \le n(2^{1/n}-1)$ holds, where
-$C_i$ and $T_i$ are the computation time and the period of task
-$\tau_i$ respectively. Then in~\cite{DBLP:journals/tc/BiniBB03}, a
-more sufficient condition, known as \emph{Hyperbolic Bound}, which has
-the same complexity as Liu and Layland's one, was proposed by Bini et
-al. On the other hand, necessary and sufficient conditions for
-schedulability were derived independently
-in~\cite{DBLP:journals/rts/SpruntSL89} and~\cite{audsley1993deadline},
-requiring more sophisticated analysis on the task set. Nevertheless,
-these results take no overhead into account, being not as realistic as
-ours. Katcher et al. did consider overhead in their schedulability
-analysis under several models based on different kinds of popular
-implementations~\cite{DBLP:journals/tse/KatcherAS93}. But as we
-mentioned at the very beginning, the ways to implement the RMS
-algorithm are countless, hence their analysis could not be applied on
-our target implementation. Furthermore, comparing with those
-theoretical analysis, our method by formal modeling and verification
-has a great advantage that if our schedulability test answers ``no'',
-it returns at the same time a real counterexample, which is able to
-guide our engineer to adjust the design.
+\jx{This section should be adjusted w.r.t. the journal which it is
+  submitted to.}
+
+In this section we discuss our results with related
+work in three directions.
+
+Considering schedulability test, Liu and
+Layland~\cite{DBLP:journals/jacm/LiuL73} gave the famous sufficient
+condition that a set of periodic tasks is schedulable with respect to
+RMS if $\displaystyle \Sigma^n_{i=1} C_i/T_i \le n(2^{1/n}-1)$
+holds. Then a more sufficient condition, known as \emph{Hyperbolic
+  Bound}, which has the same complexity as Liu and Layland's one, was
+proposed in~\cite{DBLP:journals/tc/BiniBB03}. On the other hand,
+necessary and sufficient conditions for schedulability were derived
+independently in~\cite{DBLP:journals/rts/SpruntSL89}
+and~\cite{audsley1993deadline}, requiring more sophisticated analysis
+on the task set. Nevertheless, all these results take no overhead into
+account, being not as realistic as ours. Katcher et al. did consider
+overhead in their schedulability analysis, under several models based
+on different kinds of popular
+implementations~\cite{DBLP:journals/tse/KatcherAS93}.  However, our
+target implementation is not in their scope.  Furthermore, compared
+with those theoretical analysis, our method using formal modeling and
+verification has a great advantage that if our schedulability test
+answers ``no'', it returns at the same time a real counterexample,
+which is able to guide our engineer to adjust the design.
 
 \cite{DBLP:conf/iceccs/CuiDT14} and~\cite{TianD2011} also made use of
-model checking to analyze the RMS algorithm along the same line with
-different languages and tools. They only considered the ideal setting
-as in~\cite{DBLP:journals/jacm/LiuL73}, but not an implementation
-which contains much more details. Our model of the implementation
-easily degenerates to a model of the RMS algorithm, if we let the time
-for scheduling and switching be zero and let the possible finishing
-interval of each task be a single value.
+model checking to analyze the RMS algorithm along the same line but
+with different languages and tools. They considered only the ideal
+setting as in~\cite{DBLP:journals/jacm/LiuL73}, but not an
+implementation which contains much more details. Our model of the
+implementation easily degenerates to a model of the RMS algorithm, if
+we let the times for scheduling and switching be zero and let the
+computation requirement of each task be a single value.
 
@@
 \label{s:conclusion}
-We have formally modeled a realistic implementation of RMS algorithm,
-obtained from our industrial partner, using Real-Time Maude, a
-modeling language based on rewriting logic. By taking into acount the
-overhead of scheduling and switching, assuming the possible
-computation time for each task may not be constant, we believe that
-our model has enough details to be analyzed for the behaviours of the
-real system. Two important properties--schedulability and
-correctness--are verified by model checking on the model, under
-several given scenarios. We also prove at last the soundness and
-completeness of our analysis.
+We have formally modeled a realistic implementation of RMS algorithm
+using Real-Time Maude, a modeling language based on rewriting
+logic. By taking into acount the overhead of scheduling and switching,
+assuming that the computation requirement for each task may not be
+constant, we believe that our model contains enough details to be
+analyzed for the behaviors of the real system. Two important
+properties--schedulability and correctness--are verified by model
+checking on our model, within several given scenarios. We also prove
+at last the soundness and completeness of our results.
 

### 2015-10-24 RMS/submission.tex
fixed some typos

@@
 requirements of tasks to be non-constant, and by considering overhead
-and other details of the enviroments.
+and other details of the environments.
 
@@
 task $\tau_i$ are initiated at times $kT_i$ with integers $k\ge
-0$. Deadlines consist of runability constraints only: the job
+0$. Deadlines consist of runnability constraints only: the job
 initiated at time $kT_i$ has $(k+1)T_i$ as its deadline, which is the
@@
 behavior satisfies a temporal logic formula. \emph{State propositions}
-are terms of sort \verb|Prop|. Their symantics is defined by equations
+are terms of sort \verb|Prop|. Their semantics is defined by equations
 of the form $\texttt{ceq } statePattern \texttt{ |= } prop \texttt{ =
@@
 
-\section{Formal Model of the Implementation}
+\section{Formal Modeling of the Implementation}
 \label{s:formalism}
@@
 (A2) Tasks are independent, such that they are ready to run at their
-initiation times and can be preempted instanly.
+initiation times and can be preempted instantly.
 
@@
 In general, completeness of untimed model checking cannot be achieved
-for any systems, any time sampling stategies and any
+for any systems, any time sampling strategies and any
 properties. However, \"Olveczky and Meseguer proved the completeness

### 2015-10-27 RMS/submission.tex
fixed some typos
changed to ieee style

@@
-% This is LLNCS.DOC the documentation file of
-% the LaTeX2e class from Springer-Verlag
-% for Lecture Notes in Computer Science, version 2.4
-\documentclass{llncs}
+%% bare_jrnl_compsoc.tex
+%% V1.4a
+%% 2014/09/17
+%% by Michael Shell
+%% See:
+%% http://www.michaelshell.org/
+%% for current contact information.
+%%
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.8a or later) with an IEEE
+%% Computer Society journal paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
+%% and
+%% http://www.ieee.org/
+
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE! 
+%% User assumes all risk.
+%% In no event shall IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%
+%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
+%%                    bare_conf.tex, bare_jrnl.tex, bare_conf_compsoc.tex,
+%%                    bare_jrnl_compsoc.tex, bare_jrnl_transmag.tex
+%%*************************************************************************
+
+% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
+% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
+% *** with production work. IEEE's font choices and paper sizes can       ***
+% *** trigger bugs that do not appear when using other class files.       ***                          ***
+% The testflow support page is at:
+% http://www.michaelshell.org/tex/testflow/
+
+\documentclass[10pt,journal,compsoc]{IEEEtran}
+%
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[10pt,journal,compsoc]{../sty/IEEEtran}
+
+% Some very useful LaTeX packages include:
+% (uncomment the ones you want to load)
+
+% *** MISC UTILITY PACKAGES ***
+%
+%\usepackage{ifpdf}
+% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
+% compilation based on whether the output is pdf or dvi.
+% usage:
+% \ifpdf
+%   % pdf code
+% \else
+%   % dvi code
+% \fi
+% The latest version of ifpdf.sty can be obtained from:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
+% Also, note that IEEEtran.cls V1.7 and later provides a builtin
+% \ifCLASSINFOpdf conditional that works the same way.
+% When switching from latex to pdflatex and vice-versa, the compiler may
+% have to be run twice to clear warning/error messages.
+
+% *** CITATION PACKAGES ***
+%
+\ifCLASSOPTIONcompsoc
+  % IEEE Computer Society needs nocompress option
+  % requires cite.sty v4.0 or later (November 2003)
+  \usepackage[nocompress,noadjust]{cite}
+\else
+  % normal IEEE
+  \usepackage[noadjust]{cite}
+\fi
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off
+% such as if a citation ever needs to be enclosed in parenthesis.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 5.0 (2009-03-20) and later if using hyperref.sty.
+% The latest version can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
+% The documentation is contained in the cite.sty file itself.
+%
+% Note that some packages require special options to format as the Computer
+% Society requires. In particular, Computer Society  papers do not use
+% compressed citation ranges as is done in typical IEEE papers
+% (e.g., [1]-[4]). Instead, they list every citation separately in order
+% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
+% package with the nocompress option which is supported by cite.sty v4.0
+% and later. Note also the use of a CLASSOPTION conditional provided by
+% IEEEtran.cls V1.7 and later.
+
+% *** GRAPHICS RELATED PACKAGES ***
+%
+\ifCLASSINFOpdf
+  % \usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  % \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.eps}
+\fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation
+% can be obtained at: 
+% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found at:
+% http://www.ctan.org/tex-archive/info/epslatex/
+%
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
+%
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
+
+% *** MATH PACKAGES ***
+%
+\usepackage[cmex10]{amsmath}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics. If using
+% it, be sure to load this package with the cmex10 option to ensure that
+% only type 1 fonts will utilized at all point sizes. Without this option,
+% it is possible that some math symbols, particularly those within
+% footnotes, will be rendered in bitmap form which will result in a
+% document that can not be IEEE Xplore compliant!
+%
+% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+%\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
+
+% *** SPECIALIZED LIST PACKAGES ***
+%
+%\usepackage{algorithmic}
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
+% There is also a support site at:
+% http://algorithms.berlios.de/index.html
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
+
+\usepackage{algpseudocode}
+
+% *** ALIGNMENT PACKAGES ***
+%
+%\usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/required/tools/
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+% *** SUBFIGURE PACKAGES ***
+\ifCLASSOPTIONcompsoc
+  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
+\else
+  \usepackage[caption=false,font=footnotesize]{subfig}
+\fi
+% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
+% for subfigure.sty, the latter of which is no longer maintained and is
+% incompatible with some LaTeX packages including fixltx2e. However,
+% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
+% which will override IEEEtran.cls' handling of captions and this will result
+% in non-IEEE style figure/table captions. To prevent this problem, be sure
+% and invoke subfig.sty's "caption=false" package option (available since
+% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
+% handling of captions.
+% Note that the Computer Society format requires a sans serif font rather
+% than the serif font used in traditional IEEE formatting and thus the need
+% to invoke different subfig.sty package options depending on whether
+% compsoc mode has been enabled.
+%
+% The latest version and documentation of subfig.sty can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure. The latest version and documentation can be found at:
+% http://www.ctan.org/tex-archive/macros/latex/base/
+
+%\usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
+% Do not use the stfloats baselinefloat ability as IEEE does not allow
+% \baselineskip to stretch. Authors submitting work to the IEEE should note
+% that IEEE rarely uses double column equations and that authors should try
+% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
+% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
+% such ways.
+% Do not attempt to use stfloats with fixltx2e as they are incompatible.
+% Instead, use Morten Hogholm'a dblfloatfix which combines the features
+% of both fixltx2e and stfloats:
+%
+\usepackage{dblfloatfix}
+% The latest version can be found at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/
+
+%\ifCLASSOPTIONcaptionsoff
+%  \usepackage[nomarkers]{endfloat}
+% \let\MYoriglatexcaption\caption
+% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
+%\fi
+% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
+% Axel Sommerfeldt. This package may be useful when used in conjunction with 
+% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
+% submissions have lists of figures/tables at the end of the paper and that
+% figures/tables without any captions are placed on a page by themselves at
+% the end of the document. If needed, the draftcls IEEEtran class option or
+% \CLASSINPUTbaselinestretch interface can be used to increase the line
+% spacing as well. Be sure and use the nomarkers option of endfloat to
+% prevent endfloat from "marking" where the figures would have been placed
+% in the text. The two hack lines of code above are a slight modification of
+% that suggested by in the endfloat docs (section 8.4.1) to ensure that
+% the full captions always appear in the list of figures/tables - even if
+% the user used the short optional argument of \caption[]{}.
+% IEEE papers do not typically make use of \caption[]'s optional argument,
+% so this should not be an issue. A similar trick can be used to disable
+% captions of packages such as subfig.sty that lack options to turn off
+% the subcaptions:
+% For subfig.sty:
+% \let\MYorigsubfloat\subfloat
+% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
+% However, the above trick will not work if both optional arguments of
+% the \subfloat command are used. Furthermore, there needs to be a
+% description of each subfigure *somewhere* and endfloat does not add
+% subfigure captions to its list of figures. Thus, the best approach is to
+% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
+% and instead reference/explain all the subfigures within the main caption.
+% The latest version of endfloat.sty and its documentation can obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
+%
+% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
+% later in the document, say, to conditionally put the References on a 
+% page by themselves.
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
+%\usepackage{url}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
+% Basically, \url{my_url_here}.
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
 \usepackage{alltt}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{mathabx}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-\usepackage{enumerate}
 \usepackage{epic}
 \usepackage{pstricks}
-%\usepackage{llncsdoc}
-
 \newcommand{\hide}[1]{\ignorespaces}
 \newcommand{\jx}[1]{{\bf Jiaxiang: }#1{ \bf End}}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}[theorem]{Lemma}
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
 
 \begin{document}
-%\thispagestyle{empty}
-%\begin{flushleft}
-%\end{flushleft}
-
+%
+% paper title
+% Titles are generally capitalized except for words such as a, an, and, as,
+% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
+% not capitalized unless they are the first or last word of the title.
+% Linebreaks \\ can be used within to get better formatting as desired.
+% Do not put math or special symbols in the title.
 \title{Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude}
-\author{Jiaxiang Liu\inst{1,2}}
-\institute{School of Software, Tsinghua University, Beijing, China
-  \and \'Ecole Polytechnique, Palaiseau, France}
+%
+%
+% author names and IEEE memberships
+% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
+% a structure at a ~ so this keeps an author's name from being broken across
+% two lines.
+% use \thanks{} to gain access to the first footnote area
+% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
+% was not built to handle multiple paragraphs
+%
+%
+%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
+% lists the Computer Society journals use for "first footnote" author
+% affiliations. Use \IEEEcompsocthanksitem which works much like \item
+% for each affiliation group. When not in compsoc mode,
+% \IEEEcompsocitemizethanks becomes like \thanks and
+% \IEEEcompsocthanksitem becomes a line break with idention. This
+% facilitates dual compilation, although admittedly the differences in the
+% desired content of \author between the different types of papers makes a
+% one-size-fits-all approach a daunting prospect. For instance, compsoc 
+% journal papers have the author affiliations above the "Manuscript
+% received ..."  text while in non-compsoc journals this is reversed. Sigh.
+
+\author{Jiaxiang~Liu% <-this % stops a space
+\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem J. Liu is with the School of 
+Software, Tsinghua University, China and LIX, \'Ecole Polytechnique, France\protect\\
+E-mail: jiaxiang.liu@hotmail.com}% <-this % stops an unwanted space
+}
+%\thanks{Manuscript received April 19, 2005; revised September 17, 2014.}}
+
+% note the % following the last \IEEEmembership and also \thanks - 
+% these prevent an unwanted space from occurring between the last author name
+% and the end of the author line. i.e., if you had this:
+% 
+% \author{....lastname \thanks{...} \thanks{...} }
+%                     ^------------^------------^----Do not want these spaces!
+%
+% a space would be appended to the last name and could cause every name on that
+% line to be shifted left slightly. This is one of those "LaTeX things". For
+% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
+% "AB" then you have to do: "\textbf{A}\textbf{B}"
+% \thanks is no different in this regard, so shield the last } of each \thanks
+% that ends a line with a % and do not let a space in before the next \thanks.
+% Spaces after \IEEEmembership other than the last one are OK (and needed) as
+% you are supposed to have spaces between the names. For what it is worth,
+% this is a minor point as most people would not even notice if the said evil
+% space somehow managed to creep in.
+
+% The paper headers
+\markboth{IEEE Transaction on xxx,~Vol.~$x$, No.~$x$, xx~$x$}%
+{Liu \MakeLowercase{\textit{et al.}}: Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude}
+% The only time the second header will appear is for the odd numbered pages
+% after the title page when using the twoside option.
+% 
+% *** Note that you probably will NOT want to include the author's ***
+% *** name in the headers of peer review papers.                   ***
+% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
+% you desire.
+
+% The publisher's ID mark at the bottom of the page is less important with
+% Computer Society journal papers as those publications place the marks
+% outside of the main text columns and, therefore, unlike regular IEEE
+% journals, the available text space is not reduced by their presence.
+% If you want to put a publisher's ID mark on the page you can do it like
+% this:
+%\IEEEpubid{0000--0000/00\$00.00~\copyright~2014 IEEE}
+% or like this to get the Computer Society new two part style.
+%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2014 IEEE}%
+%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
+% Remember, if you use this you must call \IEEEpubidadjcol in the second
+% column for its text to clear the IEEEpubid mark (Computer Society jorunal
+% papers don't need this extra clearance.)
+
+% use for special paper notices
+%\IEEEspecialpapernotice{(Invited Paper)}
+
+% for Computer Society papers, we must declare the abstract and index terms
+% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
+% command as these need to go into the title area created by \maketitle.
+% As a general rule, do not put math, special symbols or citations
+% in the abstract or keywords.
+\IEEEtitleabstractindextext{%
+\begin{abstract}
+The abstract goes here. TODO.
+\end{abstract}
+
+% Note that keywords are not normally used for peerreview papers.
+\begin{IEEEkeywords}
+Computer Society, IEEEtran, journal, \LaTeX, paper, template. TODO.
+\end{IEEEkeywords}}
+
+% make the title area
 \maketitle
-\thispagestyle{empty}
-
-\section{Introduction}
-Periodic task scheduling is one of the most important topics within
-the field of real-time systems, due to the large number of control
-systems that require cyclic activities~\cite{buttazzo2011hard}. A set
-of periodic tasks is said to be \emph{schedulable} with respect to
-some scheduling algorithm if all jobs meet their
-deadlines. \emph{Rate-Monotonic Scheduling} (\emph{RMS}) is a
-\emph{fixed} priority scheduling algorithm for preemptive hard
-real-time environments proposed by Liu and
+
+% To allow for easy dual compilation without having to reenter the
+% abstract/keywords data, the \IEEEtitleabstractindextext text will
+% not be used in maketitle, but will appear (i.e., to be "transported")
+% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
+% or transmag modes are not selected <OR> if conference mode is selected 
+% - because all conference papers position the abstract like regular
+% papers do.
+\IEEEdisplaynontitleabstractindextext
+% \IEEEdisplaynontitleabstractindextext has no effect when using
+% compsoc or transmag under a non-conference mode.
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
+
+\IEEEraisesectionheading{\section{Introduction}\label{s:introduction}}
+% Computer Society journal (but not conference!) papers do something unusual
+% with the very first section heading (almost always called "Introduction").
+% They place it ABOVE the main text! IEEEtran.cls does not automatically do
+% this for you, but you can achieve this effect with the provided
+% \IEEEraisesectionheading{} command. Note the need to keep any \label that
+% is to refer to the section immediately after \section in the above as
+% \IEEEraisesectionheading puts \section within a raised box.
+
+% The very first letter is a 2 line initial drop letter followed
+% by the rest of the first word in caps (small caps for compsoc).
+% 
+% form to use if the first word consists of a single letter:
+% \IEEEPARstart{A}{demo} file is ....
+% 
+% form to use if you need the single drop letter followed by
+% normal text (unknown if ever used by IEEE):
+% \IEEEPARstart{A}{}demo file is ....
+% 
+% Some journals put the first two words in caps:
+% \IEEEPARstart{T}{his demo} file is ....
+% 
+% Here we have the typical use of a "T" for an initial drop letter
+% and "HIS" in caps to complete the first word.
+\IEEEPARstart{P}{eriodic} task scheduling is one of the most important
+topics within the field of real-time systems, due to the large number
+of control systems that require cyclic
+activities~\cite{buttazzo2011hard}. A set of periodic tasks is said to
+be \emph{schedulable} with respect to some scheduling algorithm if all
+jobs meet their deadlines. \emph{Rate-Monotonic Scheduling}
+(\emph{RMS}) is a \emph{fixed} priority scheduling algorithm for
+preemptive hard real-time environments proposed by Liu and
 Layland~\cite{DBLP:journals/jacm/LiuL73}, which assigns priorities to
@@
 where $taskList$ is the list of periodic tasks to be scheduled. We
-assume that the list is ordered descendingly by priorities, and both
+assume that the list is descending order of priority, and both
 variables $taskList$ and $timer$ are global. In this implementation,
@@
 
-\begin{algorithm}
-  \caption{The C-Like Pseudocode of $schedule()$}
-  \label{a:schedule}
+\begin{figure}[!t]
+\hrule\vspace{1mm}
   \begin{algorithmic}[1]
@@
   \end{algorithmic}
-\end{algorithm}
+\hrule
+  \caption{The C-Like Pseudocode of $schedule()$}
+  \label{a:schedule}
+\end{figure}
 
@@
   op [_,_] : Time Time -> Interval [ctor] .  
-  op [_/_] : Time Interval -> Counter [ctor] .
+  op [_/_] : Time Interval 
+               -> Counter [ctor] .
 \end{verbatim}
@@
 \begin{verbatim}
-  class PTask | priority : Nat, period : NzNat, status : Status .
+  class PTask | priority : Nat, 
+                period : NzNat, 
+                status : Status .
   subclass PTask < Task .
@@
 \begin{verbatim}
-  ops RUNNING INTERRUPT READY DORMANT : -> Status [ctor] .
+  ops RUNNING INTERRUPT READY DORMANT 
+        : -> Status [ctor] .
 \end{verbatim}
@@
   op null : -> TaskList [ctor] .
-  op _::_ : Object TaskList ~> TaskList [ctor] .
-  mb (< O:Oid : PTask |> :: L:TaskList) : TaskList .
+  op _::_ : Object TaskList 
+              ~> TaskList [ctor] .
+  mb (< O:Oid : PTask |> :: L:TaskList) 
+       : TaskList .
   mb (error :: L:TaskList) : TaskList .
@@
 \begin{verbatim}
-  class SysTask .            subclass SysTask < Task .
+  class SysTask .            
+  subclass SysTask < Task .
 \end{verbatim}
@@
 \begin{verbatim}
-  class Regs | pc : TaskID, mask : Bool, ir : Bool .
+  class Regs | pc : TaskID, 
+               mask : Bool, ir : Bool .
 \end{verbatim}
@@
 \begin{verbatim}
-  op [_;_] : Object Stack ~> Hardware [ctor] .
-  mb ([ < O:Oid : Regs |> ; S:Stack ]) : Hardware .
+  op [_;_] : Object Stack 
+               ~> Hardware [ctor] .
+  mb ([ < O:Oid : Regs |> ; S:Stack ]) 
+       : Hardware .
 \end{verbatim}
@@
 \begin{verbatim}
-  op _____ : 
-       TaskList Timer SysTasks Hardware Object ~> System [ctor] .
-  mb (L T STS HW < O:Oid : IntSrc |>) : System .
+  op _____ : TaskList Timer 
+             SysTasks Hardware Object 
+               ~> System [ctor] .
+  mb (L T STS HW < O:Oid : IntSrc |>) 
+       : System .
 \end{verbatim}
@@
   crl [interrupt-request] :
-    (L T STS HW ISRC) => (L T STS (HW).intReq reset(ISRC))
+    (L T STS HW ISRC) 
+    => (L T STS (HW).intReq reset(ISRC))
     if (ISRC).timeout .
@@
   op _.intReq : Hardware -> Hardware .
-  eq [ REGS ; S ].intReq = [ (REGS).setIr ; S ] .
+  eq [ REGS ; S ].intReq 
+     = [ (REGS).setIr ; S ] .
 \end{verbatim}
@@
 \begin{verbatim}
-  op updateStatus_with_ : TaskList Timer -> TaskList . 
+  op updateStatus_with_ : TaskList Timer 
+                            -> TaskList . 
   eq updateStatus null with TIMER = null .
   eq updateStatus (TASK :: L) with TIMER
-       = (update TASK with TIMER) :: (updateStatus L with TIMER) .
+       = (update TASK with TIMER) 
+         :: (updateStatus L with TIMER) .
 \end{verbatim}
@@
   op update_with_ : Object Timer ~> Object .
-  ceq update < O : PTask | period : T, status : ST > with TIMER
-        = if ST == DORMANT then < O : PTask | status : READY >
+  ceq update < O : PTask | period : T, 
+                           status : ST > 
+        with TIMER
+      = if ST == DORMANT 
+        then < O : PTask | status : READY >
         else error fi
       if TIMER rem T == 0 .
-  eq update < O : PTask | status : ST > with TIMER
-       = if ST == RUNNING then < O : PTask | status : INTERRUPT >
+  eq update < O : PTask | status : ST > 
+       with TIMER
+     = if ST == RUNNING 
+       then < O : PTask | status 
+                            : INTERRUPT >
        else < O : PTask |> fi [owise] .
@@
   crl [interrupt-handle] :
-    SYSTEM => ((SYSTEM).interrupt).startScheduling
+    SYSTEM 
+    => ((SYSTEM).interrupt).startScheduling
     if (SYSTEM).existInt .
@@
   eq (L T STS HW ISRC).startScheduling 
-       = ((updateStatus L with T) inc(T) STS HW ISRC) .
+     = ((updateStatus L with T) 
+        inc(T) STS HW ISRC) .
 \end{verbatim}
@@
   eq (L T STS HW ISRC).finishScheduling
-       = (L T (finish scheduling in STS) HW ISRC).run1stTask .
+     = (L T (finish scheduling in STS) 
+        HW ISRC).run1stTask .
 \end{verbatim}
@@
   crl [scheduling-finish] :
-    (L T STS HW ISRC) => (SYSTEM).finishScheduling
+    (L T STS HW ISRC) 
+    => (SYSTEM).finishScheduling
     if SYSTEM := (L T STS HW ISRC) 
@@
   crl [task-finish] :
-    (L T STS HW ISRC) => (SYSTEM).startSwitching
+    (L T STS HW ISRC) 
+    => (SYSTEM).startSwitching
     if SYSTEM := (L T STS HW ISRC)
@@
   crl [switching-finish] :
-    (L T STS HW ISRC) => (SYSTEM).finishSwitching
+    (L T STS HW ISRC) 
+    => (SYSTEM).finishSwitching
     if SYSTEM := (L T STS HW ISRC)
@@
   ceq delta((L T STS HW ISRC), R)
-        = ((deltaTask(ID, L, R) T STS HW (deltaIS(ISRC, R)))
-      if ID := (HW).getPc /\ ID :: MaybeNat .
+      = ((deltaTask(ID, L, R) 
+         T STS HW (deltaIS(ISRC, R)))
+      if ID := (HW).getPc 
+         /\ ID :: MaybeNat .
 \end{verbatim}
@@
       = minimum( mteTask(ID, L),
-                   minimum( mteIS(ISRC), mteIr(HW)))
-      if ID := (HW).getPc /\ ID :: MaybeNat .
+                 minimum( mteIS(ISRC), 
+                          mteIr(HW)))
+      if ID := (HW).getPc 
+         /\ ID :: MaybeNat .
 \end{verbatim}
@@
   op taskTimeout : -> Prop [ctor] .
-  eq {L T STS HW ISRC} |= taskTimeout = containError(L) .
+  eq {L T STS HW ISRC} |= taskTimeout 
+     = containError(L) .
 \end{verbatim}
@@
       = (not containError(L))
-          and (if ID :: MaybeNat then shouldRun(ID, L)
+        and (if ID :: MaybeNat 
+             then shouldRun(ID, L)
              else true fi)
@@
 
-\begin{figure}[h]
-\begin{center}
-\begin{picture}(300,110)(0,-10)
+\begin{figure*}[!t]
+\centering
+\begin{picture}(300,120)(0,-10)
 \thicklines
@@
 \put(-25,57){task$2$}
-\put(-44,37){scheduling}
-\put(-40,17){switching}
+\put(-50,37){scheduling}
+\put(-45,17){switching}
 \put(-2,-8){$0$}
@@
 \end{picture}
-\end{center}
 \caption{An Counterexample of Scenario (iv).}
 \label{f:counterexample}
-\end{figure}
+\end{figure*}
 
@@
 
-\bibliographystyle{splncs03} \bibliography{submission}
+\hide{
+% use section* for acknowledgment
+\ifCLASSOPTIONcompsoc
+  % The Computer Society usually uses the plural form
+  \section*{Acknowledgments}
+\else
+  % regular IEEE prefers the singular form
+  \section*{Acknowledgment}
+\fi
+
+The authors would like to thank...
+}
+
+% Can use something like this to put references on a page
+% by themselves when using endfloat and the captionsoff option.
+\ifCLASSOPTIONcaptionsoff
+  \newpage
+\fi
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+\bibliography{IEEEabrv,submission}
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+
+% biography section
+% 
+% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+% needed around the contents of the optional argument to biography to prevent
+% the LaTeX parser from getting confused when it sees the complicated
+% \includegraphics command within an optional argument. (You could create
+% your own custom macro containing the \includegraphics command to make things
+% simpler here.)
+%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
+% or if you just want to reserve a space for a photo:
+
+\begin{IEEEbiography}{Jiaxiang Liu}
+Biography text here.
+\end{IEEEbiography}
+
+\hide{
+% if you will not have a photo at all:
+\begin{IEEEbiographynophoto}{John Doe}
+Biography text here.
+\end{IEEEbiographynophoto}
+
+% insert where needed to balance the two columns on the last page with
+% biographies
+%\newpage
+
+\begin{IEEEbiographynophoto}{Jane Doe}
+Biography text here.
+\end{IEEEbiographynophoto}
+}
+
+% You can push biographies down or up by placing
+% a \vfill before or after them. The appropriate
+% use of \vfill depends on what kind of text is
+% on the last page and whether or not the columns
+% are being equalized.
+
+%\vfill
+
+% Can be used to pull up biographies so that the bottom of the last one
+% is flush with the other column.
+%\enlargethispage{-5in}
+
+% that's all folks
 \end{document}

### 2015-11-04 RMS/submission.tex
drawed part of counterexample figure

@@
-%% bare_jrnl_compsoc.tex
-%% V1.4a
-%% 2014/09/17
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8a or later) with an IEEE
-%% Computer Society journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_conf_compsoc.tex,
-%%                    bare_jrnl_compsoc.tex, bare_jrnl_transmag.tex
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices and paper sizes can       ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
 \documentclass[10pt,journal,compsoc]{IEEEtran}
@@
 \usepackage{pstricks}
+\usepackage{tikz}
 \newcommand{\hide}[1]{\ignorespaces}
@@
 
-\author{Jiaxiang~Liu% <-this % stops a space
-\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem J. Liu is with the School of 
-Software, Tsinghua University, China and LIX, \'Ecole Polytechnique, France\protect\\
-E-mail: jiaxiang.liu@hotmail.com}% <-this % stops an unwanted space
+\author{Jiaxiang~Liu,
+        Min~Zhou,
+        Xiaoyu~Song,
+        Ming~Gu,
+        and~Jiaguang~Sun% <-this % stops a space
+\IEEEcompsocitemizethanks{%
+\IEEEcompsocthanksitem J. Liu is with the School of Software, Tsinghua
+University, Beijing 100084, China, and also with LIX, \'Ecole
+Polytechnique, Palaiseau 91120, France.\protect\\ E-mail:
+jiaxiang.liu@hotmail.com
+\IEEEcompsocthanksitem M. Zhou, M. Gu and J. Sun are with the School
+of Software, Tsinghua University, Beijing 100084, China.
+\IEEEcompsocthanksitem X. Song is with the Department of Electrical \&
+Computer Engineering, Portland State University, Portland, OR
+97207-0751, USA.}% <-this % stops an unwanted space
 }
@@
 will be pending until the interrupt mask becomes cleared.  The
-implementation is shown as $schedule()$ in Algorithm~\ref{a:schedule},
+implementation is shown as $schedule()$ in Figure~\ref{a:schedule},
 where $taskList$ is the list of periodic tasks to be scheduled. We
@@
 
-In Algorithm~\ref{a:schedule}, the handler function $scheduler()$
+In Figure~\ref{a:schedule}, the handler function $scheduler()$
 first updates status of all tasks in $taskList$ via function
@@
 executing, i.e. Line~\ref{l:function} in
-Algorithm~\ref{a:schedule}. Therefore, \emph{scheduling time} mainly
+Figure~\ref{a:schedule}. Therefore, \emph{scheduling time} mainly
 consists of three parts: (i) the time for switching context from the
@@
 (Lines~\ref{l:1stline}-\ref{l:endrun1st} in
-Algorithm~\ref{a:schedule}), and (iii) the time for switching context
+Figure~\ref{a:schedule}), and (iii) the time for switching context
 from $schedule()$ to that first should-be-run task. \emph{Switching}
@@
 upperbound while increasing (see Line~\ref{l:timer} in
-Algorithm~\ref{a:schedule}) in the model. Then $timer$ is of sort
+Figure~\ref{a:schedule}) in the model. Then $timer$ is of sort
 \verb|Timer| and the upperbound would be the least common multiple of
@@
 while increasing, which is not shown in detail in
-Algorithm~\ref{a:schedule} but is reasonable. The upper bound is the
+Figure~\ref{a:schedule} but is reasonable. The upper bound is the
 least common multiple of the periods of all tasks. A sort \verb|Timer|
@@
 Periodic tasks are initiated sequentially by the function
-$updateStatus()$ in Algorithm~\ref{a:schedule}, which is treated as an
+$updateStatus()$ in Figure~\ref{a:schedule}, which is treated as an
 instantaneous action in our model. It is modeled by the recursive
@@
 task (Lines~\ref{l:startupdate}-\ref{l:endupdate} in
-Algorithm~\ref{a:schedule}):
+Figure~\ref{a:schedule}):
 \begin{verbatim}
@@
 corresponds to Lines~\ref{l:updatestatus}-\ref{l:inc} in
-Algorithm~\ref{a:schedule}. It performs updating the status of
+Figure~\ref{a:schedule}. It performs updating the status of
 $taskList$ and increasing $timer$ by $1$. This part is modeled by
@@
 Lines~\ref{l:startrun1st}-\ref{l:endrun1st} in
-Algorithm~\ref{a:schedule}, searching the task with highest priority
+Figure~\ref{a:schedule}, searching the task with highest priority
 that has status \verb|INTERRUPT| or \verb|READY| then performing an
@@
 \item The interrupt cycle is $5ms$.
-\item The scheduling time ranges from $5{\mu}s$ to $9{\mu}s$, and the
-switching time ranges from $2{\mu}s$ to $4{\mu}s$.
+\item The scheduling time ranges from $15{\mu}s$ to $38{\mu}s$, and the
+switching time ranges from $10{\mu}s$ to $20{\mu}s$.
+\hide{\item The scheduling time ranges from $5{\mu}s$ to $9{\mu}s$, and the
+switching time ranges from $2{\mu}s$ to $4{\mu}s$.}
 \item The initial state is with empty stack, empty \verb|pc|, cleared 
@@
 \label{f:counterexample}
+\end{figure*}
+
+\begin{figure*}[!t]
+\centering
+\begin{tikzpicture}[
+    % styles
+    system task/.style={fill=gray!70,draw=gray},
+    periodic task/.style={fill=gray!70!black,draw=gray!50!black},
+    task line/.style={gray!30,very thin},
+    time line/.style={gray!50,very thin,dashed}]
+
+  \foreach \x in {0.5,1.2,...,3.3}
+    \draw[task line] (0,\x) -- (15.7,\x);
+  \draw[->,thick] (0,0) -- (16,0);
+  \draw[thin] (0,0) -- (0,3.8);
+
+  \draw[time line] (0.5,3.3) -- (0.5,0);
+  \draw[time line] (2.5,3.3) -- (2.5,0);
+  \filldraw[system task] (0,1.2) rectangle +(0.5,0.2);
+  \filldraw[periodic task] (0.5,3.3) rectangle +(2,0.2);
+  \filldraw[system task] (2.5,0.5) rectangle +(0.25,0.2);
+  \filldraw[periodic task] (2.75,2.6) rectangle +(1.25,0.2);
+  \filldraw[system task] (4,0.5) rectangle +(0.25,0.2);
+  \filldraw[periodic task] (4.25,1.9) rectangle +(0.75,0.2);
+
+  \filldraw[system task] (5,1.2) rectangle +(0.5,0.2);
+  \filldraw[periodic task] (5.5,3.3) rectangle +(2,0.2);
+  \filldraw[system task] (7.5,0.5) rectangle +(0.25,0.2);
+  \filldraw[periodic task] (7.75,1.9) rectangle +(2.25,0.2);
+
+  \filldraw[system task] (10,1.2) rectangle +(0.5,0.2);
+  \filldraw[periodic task] (10.5,3.3) rectangle +(2,0.2);
+  \filldraw[system task] (12.5,0.5) rectangle +(0.25,0.2);
+  \filldraw[periodic task] (12.75,2.6) rectangle +(1.25,0.2);
+  \filldraw[system task] (14,0.5) rectangle +(0.25,0.2);
+  \filldraw[periodic task] (14.25,1.9) rectangle +(0.75,0.2);
+\end{tikzpicture}
+\caption{An Counterexample of Scenario (iv).}
+\label{f:tikz}
 \end{figure*}
@@
 
+\hide{
+
 \begin{IEEEbiography}{Jiaxiang Liu}
@@
 
-\hide{
 % if you will not have a photo at all:

### 2015-11-05 RMS/submission.tex
finished the figure of counterexample

@@
 \usepackage{alltt}
-\usepackage{epic}
-\usepackage{pstricks}
+%\usepackage{epic}
+%\usepackage{pstricks}
 \usepackage{tikz}
+\usetikzlibrary{arrows.meta}
 \newcommand{\hide}[1]{\ignorespaces}
@@
 
+\hide{
 \begin{figure*}[!t]
@@
 \end{figure*}
+}
 
@@
 \centering
-\begin{tikzpicture}[
+\begin{tikzpicture}[font=\small,
     % styles
@@
     task line/.style={gray!30,very thin},
-    time line/.style={gray!50,very thin,dashed}]
-
+    time line/.style={gray!50,very thin,dashed},
+    short line/.style={gray!50,very thin,dashed},
+    init/.style={{Triangle[fill=white,scale=1.3]}-},
+    complete/.style={{Triangle[scale=1.3]}-}]
+
+  % grid
   \foreach \x in {0.5,1.2,...,3.3}
     \draw[task line] (0,\x) -- (15.7,\x);
-  \draw[->,thick] (0,0) -- (16,0);
+
+  % time indicator
+  \draw (0,0) node [below] {$0$};
+  \draw[time line] (0.5,3.3) -- (0.5,0);
+  \draw (0.5,-0.35) node [below] {$38$} [short line] -- +(0,0.35);
+  \draw (0.5,-3pt) -- (0.5,3pt);
+  \draw[time line] (2.5,3.3) -- (2.5,0);
+  \draw (2.3,0) node [below] {$2538$};
+  \draw (2.5,0) -- (2.5,3pt);
+  \draw[time line] (2.75,2.6) -- (2.75,0);
+  \draw (2.75,-0.35) node [below] {$2558$} [short line] -- +(0,0.35);
+  \draw (2.75,-3pt) -- (2.75,3pt);
+  \draw[time line] (4,2.6) -- (4,0);
+  \draw (3.8,0) node [below] {$4058$};
+  \draw (4,0) -- (4,3pt);
+  \draw[time line] (4.25,1.9) -- (4.25,0);
+  \draw (4.25,-0.35) node [below] {$4078$} [short line] -- +(0,0.35);
+  \draw (4.25,-3pt) -- (4.25,3pt);
+
+  \draw[time line] (5,3.3) -- (5,0);
+  \draw (5,0) node [below] {$5000$};
+  \draw (5,0) -- (5,3pt);
+  \draw[time line] (5.5,3.3) -- (5.5,0);
+  \draw (5.5,-0.35) node [below] {$5038$} [short line] -- +(0,0.35);
+  \draw (5.5,-3pt) -- (5.5,3pt);
+  \draw[time line] (7.5,3.3) -- (7.5,0);
+  \draw (7.3,0) node [below] {$7538$};
+  \draw (7.5,0) -- (7.5,3pt);
+  \draw[time line] (7.75,1.9) -- (7.75,0);
+  \draw (7.75,-0.35) node [below] {$7558$} [short line] -- +(0,0.35);
+  \draw (7.75,-3pt) -- (7.75,3pt);
+
+  \draw[time line] (10,3.3) -- (10,0);
+  \draw (9.9,0) node [below] {$10000$};
+  \draw (10,0) -- (10,3pt);
+  \draw[time line] (10.5,3.3) -- (10.5,0);
+  \draw (10.5,-0.35) node [below] {$10038$} [short line] -- +(0,0.35);
+  \draw (10.5,-3pt) -- (10.5,3pt);
+  \draw[time line] (12.5,3.3) -- (12.5,0);
+  \draw (12.2,0) node [below] {$12538$};
+  \draw (12.5,0) -- (12.5,3pt);
+  \draw[time line] (12.75,2.6) -- (12.75,0);
+  \draw (12.75,-0.35) node [below] {$12558$} [short line] -- +(0,0.35);
+  \draw (12.75,-3pt) -- (12.75,3pt);
+  \draw[time line] (14,2.6) -- (14,0);
+  \draw (13.7,0) node [below] {$14058$};
+  \draw (14,0) -- (14,3pt);
+  \draw[time line] (14.25,1.9) -- (14.25,0);
+  \draw (14.25,-0.35) node [below] {$14078$} [short line] -- +(0,0.35);
+  \draw (14.25,-3pt) -- (14.25,3pt);
+  \draw[time line] (15,1.9) -- (15,0);
+  \draw (15,0) node [below] {$15000$};
+  \draw (15,0) -- (15,3pt);
+
+  % axes
+  \draw[->,thick] (0,0) -- (15.7,0) node [above] {time(${\mu}s$)};
   \draw[thin] (0,0) -- (0,3.8);
 
-  \draw[time line] (0.5,3.3) -- (0.5,0);
-  \draw[time line] (2.5,3.3) -- (2.5,0);
+  % tips of tasks
+  \draw (0,0.6) node [left] {switching};
+  \draw (0,1.3) node [left] {scheduling};
+  \draw (0,2) node [left] {task$2$};
+  \draw (0,2.7) node [left] {task$1$};
+  \draw (0,3.4) node [left] {task$0$};
+
+  % tasks
   \filldraw[system task] (0,1.2) rectangle +(0.5,0.2);
@@
   \filldraw[periodic task] (14.25,1.9) rectangle +(0.75,0.2);
+
+  % initiation of tasks
+  \foreach \x in {0,5,10}
+    \draw [init] (\x,3.3) -- +(0,-0.1);
+  \foreach \x in {0,10}
+    \draw [init] (\x,2.6) -- +(0,-0.1);  
+  \foreach \x in {0,15}
+    \draw [init] (\x,1.9) -- +(0,-0.1);
+
+  % completion of tasks
+  \draw [complete] (2.5,3.5) -- +(0,0.1);
+  \draw [complete] (4,2.8) -- +(0,0.1);
+  \draw [complete] (7.5,3.5) -- +(0,0.1);
+  \draw [complete] (12.5,3.5) -- +(0,0.1);
+  \draw [complete] (14,2.8) -- +(0,0.1);
+
+  % text
+  \draw[{Stealth}-,thick] (15,2.2) -- +(0,1.5)
+    node [above] {\emph{Misses Deadline!}};
+
+  % legend
+  \begin{scope}[xshift = -1.2cm]  
+    \draw [fill=gray!25,draw=gray!50,dashed] (1.5,4) rectangle +(8,1);
+    \draw (1.5,4.5) node [above right] {LEGEND};
+    \draw [init] (2,4.4) -- +(0,-0.1);
+    \draw (2.2,4.55) node [below right] {: Initiation of Tasks};
+    \draw [complete] (6,4.2) -- +(0,0.1);
+    \draw (6.2,4.55) node [below right] {: Completion of Tasks};
+  \end{scope}
+
 \end{tikzpicture}

### 2015-11-05 RMS/submission.tex
changed to non-compsoc style, and modified until introducing real-time maude

@@
-\documentclass[10pt,journal,compsoc]{IEEEtran}
+\documentclass[10pt,journal]{IEEEtran}
 %
@@
 
+\hide{
 \author{Jiaxiang~Liu,
@@
 % space somehow managed to creep in.
+}
 
@@
 \begin{IEEEkeywords}
-Computer Society, IEEEtran, journal, \LaTeX, paper, template. TODO.
-\end{IEEEkeywords}}
+  Real-time systems, scheduling, embedded systems, modeling, formal
+  verification, rewriting logic.
+\end{IEEEkeywords}
+}
 
@@
 
-\IEEEraisesectionheading{\section{Introduction}\label{s:introduction}}
+%\IEEEraisesectionheading{\section{Introduction}\label{s:introduction}}
+\section{Introduction}\label{s:introduction}
 % Computer Society journal (but not conference!) papers do something unusual
@@
 with respect to RMS. It is widely used in safety-critical real-time
-applications, such as trains and avionics, thanks to its optimality
+applications, such as vehicles and avionics, thanks to its optimality
 and easiness to implement.
@@
 
-Extensive effort to apply formal methods, such as model checking and
-theorem proving, has been made to analyze safety-critical systems for
-the past few
-years~\cite{DBLP:journals/iandc/MeseguerR13,DBLP:journals/cacm/Leroy09,DBLP:conf/sosp/KleinEHACDEEKNSTW09}. However,
+It is also crucial to ensure the reliability of the implementation of
+RMS when it serves in a safety-critical system. When analyzing a
+realistic implementation instead of the algorithm, theoretical results
+may be no more applicable. For instance, switching overhead may lead
+to unschedulability even if the task set satisfies the schedulability
+condition derived from algorithm analysis. Extensive effort to apply
+formal methods, such as model checking and theorem proving, has been
+made to analyze safety-critical systems for the past few
+years~\cite{DBLP:journals/tie/MiyawakiMSYV05,DBLP:journals/iandc/MeseguerR13,DBLP:journals/cacm/Leroy09,DBLP:conf/sosp/KleinEHACDEEKNSTW09}. However,
 as far as we know, few~\cite{DBLP:conf/iceccs/CuiDT14,TianD2011}
@@
 In this paper, we use \emph{Real-Time Maude}, a \emph{rewriting}-based
-modeling language and analyzing tool for real-time systems, to model a
-realistic implementation of RMS and then verify some desired
-properties on the built model. Based on a realistic implementation,
-our model extends the standard one proposed
+formal modeling language and analyzing tool for real-time systems, to
+model a realistic implementation of RMS, which serves as a simplified
+operating system within an avionic control system, and then verify
+several desired properties. Based on a realistic implementation, our
+model extends the standard RMS model proposed
 in~\cite{DBLP:journals/jacm/LiuL73}, by allowing computation
 requirements of tasks to be non-constant, and by considering overhead
-and other details of the environments.
+and other details of the hardware platform.
 
 The rest of this paper is organized as
-follows. Section~\ref{s:background} gives some background of the RMS
-algorithm and Real-Time Maude.  Section~\ref{s:imp} presents the RMS
-implementation that we model and analyze.  Section~\ref{s:formalism}
-introduces how we model the RMS implementation using Real-Time
-Maude. Then Section~\ref{s:verification} explains how to verify the
-desired properties and to evaluate the results. Related work is
-discussed in Section~\ref{s:relate}. We conclude the paper in
+follows. Section~\ref{s:background} gives some background of both the
+RMS algorithm and Real-Time Maude.  Section~\ref{s:imp} presents the
+RMS implementation that we model and analyze.
+Section~\ref{s:formalism} introduces how we model the RMS
+implementation using Real-Time Maude. Then
+Section~\ref{s:verification} explains how to verify the desired
+properties and to evaluate the results. Related work is discussed in
+Section~\ref{s:relate}. We conclude the paper in
 Section~\ref{s:conclusion}.
@@
 computation requirement $C_i$. First jobs of all tasks are assumed to
-be initiated simultaneously. This means that jobs corresponding to
-task $\tau_i$ are initiated at times $kT_i$ with integers $k\ge
-0$. Deadlines consist of runnability constraints only: the job
-initiated at time $kT_i$ has $(k+1)T_i$ as its deadline, which is the
-initiation time of the next job. The RMS algorithm chooses the
-labeling such that $T_1\le T_2\le \ldots \le T_n$. Consequently,
-$\tau_i$ receives priority $i$, assuming smaller numbers have higher
-priorities. The following assumptions are made:
-
-(A1) Computation requirement $C_i$ for each task $\tau_i$ is constant
+be initiated at time $0$ simultaneously.  Deadlines consist of
+runnability constraints only: the deadline of a job corresponding to
+$\tau_i$ is the initiation time of the next job corresponding to
+$\tau_i$.  The RMS algorithm chooses the labeling such that $T_1\le
+T_2\le \ldots \le T_n$. Consequently, $\tau_i$ receives priority $i$,
+assuming smaller numbers have higher priorities. The following
+assumptions are made:
+
+(A1) Jobs corresponding to task $\tau_i$ are initiated exactly at
+times $kT_i$ with integers $k\ge 0$.
+
+(A2) Computation requirement $C_i$ for each task $\tau_i$ is constant
 and does not vary with time.
 
-(A2) Tasks are independent, such that they are ready to run at their
+(A3) Tasks are independent, such that they are ready to run at their
 initiation times and can be preempted instantly (ignoring all
@@
 
-(A3) All overhead, such as task switching times, is ignored.
+(A4) All overhead, such as task switching times, is ignored.
 
@@
 RMS algorithm itself, thus the model would be more complicated than
-this standard, ideal setting.  Assumptions~(A1) and (A3) will be
-relaxed later to obtain a more realistic analysis model.
+this standard, ideal setting. Assumption~(A1) will be modified because
+of the interrupt masking mechanism, while (A2) and (A4) are relaxed to
+obtain a more realistic analysis model.
 
 \subsection{Real-Time Maude}
-Based on \emph{rewriting logic}~\cite{DBLP:journals/jlp/Meseguer12},
-\emph{Real-Time Maude} is a language and tool that extends
-\emph{Maude} to support the formal specification and analysis of
-real-time systems~\cite{DBLP:journals/lisp/OlveczkyM07}.
+\emph{Real-Time Maude}~\cite{DBLP:journals/lisp/OlveczkyM07} is an
+extension of \emph{Maude}~\cite{DBLP:journals/tcs/ClavelDELMMQ02}
+which is a language and tool based on \emph{rewriting
+  logic}~\cite{DBLP:journals/jlp/Meseguer12}.  It supports formal
+specification and analysis of real-time systems.
 
@@
 \item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
-  theory}, with $E$ a set of conditional equations on $\Sigma$, and
-  $A$ a set of equational axioms such as associativity, commutativity
-  and identity.  $(\Sigma, E\cup A)$ models the system's ``static''
-  states as an algebraic data type, and includes a built-in
-  specification of a sort \verb|Time|.
+  theory}, with $E$ a set of conditional \emph{equations} and
+  \emph{memberships} on $\Sigma$, and $A$ a set of equational axioms
+  such as associativity, commutativity and identity.  $(\Sigma, E\cup
+  A)$ models the system's ``static'' states as an algebraic data type,
+  and is equipped with a built-in specification of a sort \verb|Time|.
 \item $IR$ is a set of \emph{labeled conditional rewrite rules}
   specifying the system's local transitions. Each rule has the form
-  $[l]~:~t\rightarrow t'\mbox{ \textbf{if} }\bigwedge^n_{j=1}cond_j$,
+  $[l]~:~s\rightarrow s'\mbox{ \textbf{if} }\bigwedge^n_{j=1}cond_j$,
   where each $cond_j$ is an equality $u_j=v_j$ and $l$ is a
   \emph{label}. Such a rule specifies an \emph{instantaneous
-    transition}, without consuming time, from an instance of $t$ to
-  the corresponding instance of $t'$, \emph{provided} the conditions
+    transition}, without consuming time, from an instance of $s$ to
+  the corresponding instance of $s'$, \emph{provided} the conditions
   hold.
-\item $TR$ is a set of (\emph{labeled}) \emph{tick rules}
-  $[l]~:~\{t\}\rightarrow\{t'\} \mbox{ \textbf{in time} }r\mbox{
-  \textbf{if} }cond$ that specify \emph{timed transitions} advancing
-  time in the \emph{entire} state $t$ by $r$ time units. $IR$ and $TR$
-  together model the ``dynamic'' behaviors of the system.
+\item $TR$ is a set of (\emph{labeled}) \emph{tick rules} of the form
+  $[l]~:~\{s\}\rightarrow\{s'\} \mbox{ \textbf{in time} }t\mbox{
+  \textbf{if} }cond$ that specify \emph{timed transitions}, which
+  advances time in the \emph{entire} state $s$ by $t$ time units. $IR$
+  and $TR$ together model the ``dynamic'' behaviors of the system.
 \end{itemize}

### 2015-11-06 RMS/submission.tex
polished until first part of Section.Modeling.

@@
 
-It is also crucial to ensure the reliability of the implementation of
-RMS when it serves in a safety-critical system. When analyzing a
-realistic implementation instead of the algorithm, theoretical results
-may be no more applicable. For instance, switching overhead may lead
-to unschedulability even if the task set satisfies the schedulability
-condition derived from algorithm analysis. Extensive effort to apply
+It is even more crucial to ensure the reliability of an implementation
+instead of the algorithm, when RMS serves in a safety-critical
+system. When analyzing a realistic implementation, theoretical results
+may be no more applicable. For instance, even though the conditions
+derived from algorithm analysis are satisfied, schedulability can be
+broken by overhead in the system, or by the interrupt masking
+mechanism which may delay interrupt handling. On the other hand,
+correctness of the implementation with respect to the algorithm is
+difficult to be verified by the traditional methods such as testing
+and simulation, since they are incomplete. Extensive effort to apply
 formal methods, such as model checking and theorem proving, has been
@@
 
-However in this paper, we consider an implementation instead of the
-RMS algorithm itself, thus the model would be more complicated than
-this standard, ideal setting. Assumption~(A1) will be modified because
-of the interrupt masking mechanism, while (A2) and (A4) are relaxed to
-obtain a more realistic analysis model.
+A simple example showing this algorithm is depicted in
+Figure~\ref{sf:rmsalg}. However in this paper, we consider an
+implementation instead of the RMS algorithm itself, thus the model
+would be more complicated than this standard, ideal
+setting. Assumption~(A1) will be modified because of the interrupt
+masking mechanism, while (A2) and (A4) are relaxed to obtain a more
+realistic analysis model.
 
@@
 In rewriting logic, rewrite rules are applied non-deterministically,
-that is, when several rules can be applied on a given $t$, any of them
+that is, when several rules can be applied on a given $s$, any of them
 may be chosen. Hence non-deterministic behaviors can be modeled
-naturally in Real-Time Maude.
-
-Real-Time Maude also supports specifications in \emph{object-oriented}
-style.  A class declaration $\texttt{class }C\texttt{ |
+naturally in Real-Time Maude.  Real-Time Maude also supports
+specifications in \emph{object-oriented} style.  A class declaration
+$\texttt{class }C\texttt{ |
 }att_1\texttt{:}s_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}s_n$
@@
 where $O$, of sort \verb|Oid|, is the object's \emph{identifier}, and
-$val_1$ to $val_n$ are the values of the attributes $att_1$ to
-$att_n$. A \emph{subclass} inherits all the attributes and rules of
-its superclasses.
+$val_i$ is the value of the attribute $att_i$ with $i\in [1,n]$. A
+\emph{subclass} inherits all the attributes and rules of its
+superclasses.
 
@@
 Real-Time Maude provides many useful commands and tools to analyze a
-model. For example, \verb|rewrite| allows to execute the model,
+given model. For example, \verb|rewrite| allows to execute the model,
 symbolically; given an initial state, \verb|search| is used to search
@@
 
-In this paper, we only consider Real-Time Maude's \emph{linear
-  temporal logic model checker}, which analyzes whether \emph{each}
-behavior satisfies a temporal logic formula. \emph{State propositions}
-are terms of sort \verb|Prop|. Their semantics is defined by equations
-of the form $\texttt{ceq } statePattern \texttt{ |= } prop \texttt{ =
-} b \texttt{ if } cond$, with $b$ a term of sort \verb|Bool|, stating
-that $prop$ evaluates to $b$ in states which are instances of
-$statePattern$ provided the condition $cond$ holds. These equations
-together define $prop$ to hold in all states $t$ that make $t \texttt{
-  |= } prop$ evaluate to \verb|true|. A temporal logic \emph{formula}
-is constructed by state propositions and temporal logic operators such
-as \verb|True|, \verb|False|, \verb|~|(negation), \verb|/\|,
-\verb|\/|, \verb|->|(implication), \verb|[]|(``always''),
-\verb|<>|(``eventually'') and \verb|U|(``until''). Real-Time Maude
-supports both \emph{timed} and \emph{untimed LTL model checking}. The
-untimed model checking command
+In this paper, we only consider Real-Time Maude's \emph{Linear
+  Temporal Logic (LTL) model checker}, which analyzes whether
+\emph{each} behavior satisfies a temporal logic formula. \emph{State
+  propositions} are defined as terms of sort \verb|Prop|. Their
+semantics is defined by conditional equations of the form $\texttt{ceq
+} statePattern \texttt{ |= } prop \texttt{ = } b \texttt{ if } cond$,
+with $b$ a term of sort \verb|Bool|, stating that $prop$ evaluates to
+$b$ in states which are instances of $statePattern$ provided the
+condition $cond$ holds. These equations together define $prop$ to hold
+in all states $s$ that make $s \texttt{ |= } prop$ evaluate to
+\verb|true|. A temporal logic \emph{formula} is constructed by state
+propositions and temporal logic operators such as \verb|True|,
+\verb|False|, \verb|~|(negation), \verb|/\|, \verb|\/|,
+\verb|->|(implication), \verb|[]|(``always'') and
+\verb|U|(``until''). Real-Time Maude supports both \emph{timed} and
+\emph{untimed LTL model checking}. The untimed model checking command
 \begin{alltt}
-  (mc \(t\) |=u \(formula\) .)
+  (mc \(s\) |=u \(formula\) .)
 \end{alltt}
 checks whether the temporal logic $formula$ holds in all behaviors
-starting from the initial state $t$, \emph{with no time limit}.
+starting from the initial state $s$, \emph{with no time limit}.
 
@@
 \label{s:imp}
-The implementation is in a realistic avionic operating system.
-Interrupts would be triggered by the clock every $T$, which we call
-\emph{interrupt cycle}. When an interrupt request occurs, if the
-system is interruptable, i.e. the interrupt mask is cleared, the
-handler function $schedule()$ will be invoked; otherwise $schedule()$
-will be pending until the interrupt mask becomes cleared.  The
-implementation is shown as $schedule()$ in Figure~\ref{a:schedule},
-where $taskList$ is the list of periodic tasks to be scheduled. We
-assume that the list is descending order of priority, and both
-variables $taskList$ and $timer$ are global. In this implementation,
-there is only one kind of interrupt, the period $T_i$ of each task is
-a multiple of $T$, and the tasks are independent, meeting
-assumption~(A2).
+The implementation is in a realistic avionic control system.
+Interrupts would be triggered by, and only by, the clock every $T$,
+which we call \emph{interrupt cycle}. When an interrupt request
+occurs, if the system is interruptable, i.e. the interrupt masking bit
+is cleared, the handler function $schedule()$ will be invoked;
+otherwise $schedule()$ will be pending until the interrupt masking bit
+becomes cleared.  The implementation is shown as $schedule()$ in
+Figure~\ref{a:schedule}, where $taskList$ is the list of periodic
+tasks to be scheduled. We assume that the list is in descending order
+of priority, and both variables $taskList$ and $timer$ are global. In
+this implementation, there is only one kind of interrupt, the period
+$T_i$ of each task is a multiple of $T$, and the tasks are
+independent, meeting assumption~(A3).
 
@@
     \If{$p\rightarrow status == \textit{INTERRUPT}$}
-      \State \Return;
+      \State \Return; \label{l:return}
     \ElsIf{$p\rightarrow status == \textit{READY}$}      
@@
 
-In Figure~\ref{a:schedule}, the handler function $scheduler()$
-first updates status of all tasks in $taskList$ via function
-$updateStatus()$. Then it traverses the list to execute the ready
-tasks one by one, or to do a return when encountering an
-interrupted\footnote{Note that the status \textit{INTERRUPT} indicates
-  the task is interrupted for the moment, or was interrupted before
-  but its execution is not complete yet.} task. The function
-$updateStatus()$ updates each task in two steps: firstly, if the task
-is running, it becomes interrupted; secondly for the task at its
-initiation time, if its previous job is complete, it would be set to
-be ready, otherwise it misses its deadline, producing an error. Notice
-that $schedule()$ is invoked only when the periodic interrupt is
-handled. Its execution cannot be interrupted when it is updating
+In Figure~\ref{a:schedule}, the handler function $scheduler()$ first
+updates status of all tasks in $taskList$ via function
+$updateStatus()$. This updating actually initiates tasks which should
+be scheduled in the current interrupt cycle. Then $scheduler()$
+traverses the list to execute the ready tasks one by one, or to do a
+return when encountering an interrupted\footnote{Note that the status
+  \textit{INTERRUPT} indicates the task is interrupted for the moment,
+  or was interrupted before but its execution is not complete yet.}
+task. As for the function $updateStatus()$, it updates each task in
+two steps: firstly, if the task is running, it becomes interrupted;
+secondly for the task at its initiation time, if its previous job is
+complete, it would be set to be ready, otherwise it misses its
+deadline, producing an error. Notice that $schedule()$ is invoked only
+when the interrupt request is handled, not when the interrupt is
+disabled (the interrupt masking bit is set). Due to the interrupt
+masking bit, its execution cannot be interrupted when it is updating
 status of tasks or finding the next task to execute, however, it can
@@
 
-In the rest of this paper, we use \emph{scheduling} to refer to the
-stage, from the moment when a pending interrupt request is detected,
-to the moment when the first should-be-run periodic task starts
-executing, i.e. Line~\ref{l:function} in
+For simplicity, in the rest of this paper, we use \emph{scheduling} to
+refer to the stage, from the moment when a pending interrupt request
+is detected, to the moment when the first should-be-run periodic task
+starts executing, i.e. Line~\ref{l:return} or~\ref{l:function} in
 Figure~\ref{a:schedule}. Therefore, \emph{scheduling time} mainly
@@
 the \emph{first} should-be-run periodic task
-(Lines~\ref{l:1stline}-\ref{l:endrun1st} in
-Figure~\ref{a:schedule}), and (iii) the time for switching context
-from $schedule()$ to that first should-be-run task. \emph{Switching}
-refers to the stage, from the moment when a periodic task completes
-its execution, to the moment when the next should-be-run periodic task
-starts executing. \emph{Switching time} thus also consists of three
-parts: (i) the time for switching context from the finished task back
-to $schedule()$, (ii) the time spent by $schedule()$ finding and
-setting the \emph{next} should-be-run periodic task, and (iii) the
-time for switching context from $schedule()$ to that next
-should-be-run task.
+(Lines~\ref{l:1stline}-\ref{l:endrun1st} in Figure~\ref{a:schedule}),
+and (iii) the time for switching context from $schedule()$ to that
+task. \emph{Switching} refers to the stage, from the moment when a
+periodic task completes its execution, to the moment when the next
+should-be-run periodic task starts executing. \emph{Switching time}
+thus also consists of three parts: (i) the time for switching context
+from the complete task back to $schedule()$, (ii) the time spent by
+$schedule()$ finding and setting the \emph{next} should-be-run
+periodic task, and (iii) the time for switching context from
+$schedule()$ to that task.
 
@@
 \label{s:formalism}
-We model the implementation under the following assumptions:
-
-(A1') Computation requirement $C_i$ for each task $\tau_i$ is not
+Considering some technical details of the platform, such as interrupt
+masking mechanism, we model the implementation under the following
+assumptions:
+
+(A1') Jobs corresponding to task $\tau_i$ are initiated at the
+beginning of scheduling that handles the requests triggered at times
+$kT_i$ with integers $k\ge 0$.
+
+(A2') Computation requirement $C_i$ for each task $\tau_i$ is not
 constant. It varies randomly between minimum $C^{min}_i$ and maximum
@@
 
-(A2) Tasks are independent, such that they are ready to run at their
+(A3) Tasks are independent, such that they are ready to run at their
 initiation times and can be preempted instantly.
 
-(A3') Scheduling time and switching time are considered, while other
+(A4') Scheduling time and switching time are considered, while other
 overhead is ignored.
@@
 These assumptions make our model different from the standard one. For
-instance, if an interrupt request occurs while switching is performed,
-jobs corresponding to task $\tau_i$ may not be initiated at exactly
-$kT_i$. They should wait until switching finishes and the interrupt
-mask is cleared. Note that (A2) says that jobs are ready to run at
-their initiation times, however, no one can start running at exactly
-its initiation time, because scheduling takes time.
-
-\jx{TODO. A figure is needed here to demonstrate the scheduling under
-  the three assumptions above.}
+instance, with assumption~(A1'), an interrupt request that occurs
+while switching is performed will be pending, such that jobs of task
+$\tau_i$ cannot initiate at $kT_i$. They should wait until switching
+finishes and the interrupt masking bit is cleared, which is different
+from~(A1). Note that (A3) says that jobs are ready to run at their
+initiation times, however, no one can start running at exactly its
+initiation time, because scheduling takes time. Under these
+assumptions, an example for showing the execution of tasks scheduled
+by the implementation is depicted in Figure~\ref{sf:rmsimp}. Note that
+the second job of $\tau_1$ is initiated at time $5.5$ instead of $5$,
+because switching is performed and the interrupt masking bit is set at
+time $5$.
+
+\begin{figure}[!t]
+\centering
+\subfloat[RMS Algorithm]{
+  \begin{tikzpicture}[font=\small,scale=1.25,
+    % styles
+    system task/.style={fill=gray!70,draw=gray},
+    periodic task/.style={fill=gray!70!black,draw=gray!50!black},
+    task line/.style={gray!30,very thin},
+    time line/.style={gray!50,very thin,dashed},
+    short line/.style={gray!50,very thin,dashed},
+    init/.style={{Triangle[fill=white,scale=1.1]}-},
+    complete/.style={{Triangle[scale=1.1]}-}]
+
+  % legend
+  \begin{scope}[xshift=-2cm]  
+    \draw [fill=gray!25,draw=gray!50,dashed] (1.5,2.3) rectangle +(4,-1);
+    \draw (1.5,2.3) node [below right] {LEGEND};
+    \draw [init] (2,1.85) -- +(0,-0.01);
+    \draw (2.1,2) node [below right] {: Initiation of Tasks};
+    \draw [complete] (2,1.42) -- +(0,0.1);
+    \draw (2.1,1.7) node [below right] {: Completion of Tasks};
+  \end{scope}
+
+    % grid
+    \foreach \x in {0.3,0.7}
+      \draw[task line] (0,\x) -- (5.2,\x);
+
+    % axes
+    \draw[->,thick] (0,0) node [below] {$0$} -- (5.3,0) node [above] {time};
+    \draw[thin] (0,0) -- (0,1);
+
+    % time indicator
+    \draw [time line] (1.5,0.7) -- (1.5,0);
+    \draw (1.5,0) node [below] {$3$} -- +(0,2pt);
+    \draw [time line] (2.5,0.7) -- (2.5,0);
+    \draw (2.5,0) node [below] {$5$} -- +(0,2pt);
+    \draw [time line] (4,0.7) -- (4,0);
+    \draw (4,0) node [below] {$8$} -- +(0,2pt);
+    \draw [time line] (4.5,0.3) -- (4.5,0);
+    \draw (4.5,0) node [below] {$9$} -- +(0,2pt);
+    \draw [time line] (5,0.7) -- (5,0);
+    \draw (5,0) node [below] {$10$} -- +(0,2pt);
+
+    % tasks
+    \draw [periodic task] (0,0.7) rectangle +(1.5,0.14);
+    \draw [periodic task] (1.5,0.3) rectangle +(1,0.14);
+    \draw [periodic task] (2.5,0.7) rectangle +(1.5,0.14);
+    \draw [periodic task] (4,0.3) rectangle +(0.5,0.14);
+
+    % text
+    \draw (0,0.75) node [left] {$\tau_1$};
+    \draw (0,0.35) node [left] {$\tau_2$};
+    \path (0,0.75) node [left,text opacity=0] {scheduling};
+    \path (0,0.35) node [left,text opacity=0] {switching};
+
+    % initiation of tasks
+    \foreach \x in {0,2.5,5}
+      \draw [init] (\x,0.7) -- +(0,-0.01);
+    \foreach \x in {0,5}
+      \draw [init] (\x,0.3) -- +(0,-0.01);
+
+    % completion of tasks
+    \draw [complete] (1.5,0.84) -- +(0,0.01);
+    \draw [complete] (4,0.84) -- +(0,0.01);
+    \draw [complete] (4.5,0.44) -- +(0,0.01);
+  \end{tikzpicture}
+\label{sf:rmsalg}}\\
+\subfloat[RMS Implementation]{
+  \begin{tikzpicture}[font=\small,scale=1.25,
+    % styles
+    system task/.style={fill=gray!70,draw=gray},
+    periodic task/.style={fill=gray!70!black,draw=gray!50!black},
+    task line/.style={gray!30,very thin},
+    time line/.style={gray!50,very thin,dashed},
+    short line/.style={gray!50,very thin,dashed},
+    init/.style={{Triangle[fill=white,scale=1.1]}-},
+    complete/.style={{Triangle[scale=1.1]}-}]
+
+    % grid
+    \foreach \x in {0.3,0.7,1.1,1.5}
+      \draw[task line] (0,\x) -- (5.2,\x);
+
+    % axes
+    \draw[->,thick] (0,0) node [below] {$0$} -- (5.3,0) node [above] {time};
+    \draw[thin] (0,0) -- (0,1.8);
+
+    % time indicator
+    \draw [time line] (0.5,1.5) -- (0.5,0);
+    \draw (0.5,0) node [below] {$1$} -- +(0,2pt);
+    \draw [time line] (1.25,1.5) -- (1.25,0);
+    \draw (1.25,0) node [below] {$2.5$} -- +(0,2pt);
+    \draw [time line] (1.75,1.1) -- (1.75,0);
+    \draw (1.75,0) node [below] {$3.5$} -- +(0,2pt);
+    \draw [time line] (2.25,1.1) -- (2.25,0);
+    \draw (2.25,0) node [below] {$4.5$} -- +(0,2pt);
+    \draw [time line] (2.75,1.5) -- (2.75,0);
+    \draw (2.75,0) node [below] {$5.5$} -- +(0,2pt);
+    \draw [time line] (3.25,1.5) -- (3.25,0);
+    \draw (3.25,0) node [below] {$6.5$} -- +(0,2pt);
+    \draw [time line] (4.25,1.5) -- (4.25,0);
+    \draw (4.25,0) node [below] {$8.5$} -- +(0,2pt);
+    \draw [time line] (4.75,0.3) -- (4.75,0);
+    \draw (4.75,0) -- +(0,2pt);
+    \draw (4.65,0) node [below] {$9.5$};
+    \draw [time line] (5,1.5) -- (5,0);
+    \draw (5,0) node [below] {$10$} -- +(0,2pt);
+
+    % tasks
+    \draw [system task] (0,0.7) rectangle +(0.5,0.14);
+    \draw [periodic task] (0.5,1.5) rectangle +(0.75,0.14);
+    \draw [system task] (1.25,0.3) rectangle +(0.5,0.14);
+    \draw [periodic task] (1.75,1.1) rectangle +(0.5,0.14);
+    \draw [system task] (2.25,0.3) rectangle +(0.5,0.14);
+    \draw [system task] (2.75,0.7) rectangle +(0.5,0.14);
+    \draw [periodic task] (3.25,1.5) rectangle +(1,0.14);
+    \draw [system task] (4.25,0.3) rectangle +(0.5,0.14);
+
+    % text
+    \draw (0,1.55) node [left] {$\tau_1$};
+    \draw (0,1.15) node [left] {$\tau_2$};
+    \draw (0,0.75) node [left] {scheduling};
+    \draw (0,0.35) node [left] {switching};
+
+    % initiation of tasks
+    \foreach \x in {0,2.75,5}
+      \draw [init] (\x,1.5) -- +(0,-0.01);
+    \foreach \x in {0,5}
+      \draw [init] (\x,1.1) -- +(0,-0.01);
+
+    % completion of tasks
+    \draw [complete] (1.25,1.64) -- +(0,0.01);
+    \draw [complete] (2.25,1.24) -- +(0,0.01);
+    \draw [complete] (4.25,1.64) -- +(0,0.01);
+  \end{tikzpicture}
+\label{sf:rmsimp}}
+\caption{A task set scheduled under RMS algorithm and the
+  implementation, respectively. $T=T_1=5$, $T_2=10$.  In
+  Figure~\ref{sf:rmsalg}, with assumption~(A2), $C_1=3$, $C_2=3$. In
+  Figure~\ref{sf:rmsimp}, with assumption~(A2'), $C_1\in [1,3]$ and
+  $C_2\in [1,3]$, assuming both scheduling time and switching time are
+  $1$.}
+\label{f:example}
+\end{figure}
 

### 2015-11-06 RMS/submission.tex
almost final version, to be sent to Prof.Song.

@@
 \newtheorem{theorem}{Theorem}
-\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{lemma}{Lemma}
 
@@
 \begin{abstract}
-The abstract goes here. TODO.
+Rate-Monotonic Scheduling (RMS) is one of the most important real-time
+scheduling algorithms. There are large numbers of results about RMS,
+especially on its schedulability. However, these theoretical results
+contain not enough details to be used directly to investigate a
+realistic RMS implementation. On the other hand, the correctness of
+such an implementation is of the same importance. In this paper, we
+analyze a realistic RMS implementation by formal modeling using
+Real-Time Maude, a language and tool based on rewriting
+logic. Overhead and some details of the hardware are taken into
+account in the model. We verify the schedulability and the correctness
+of the implementation within several scenarios, using model checking
+tool built in Real-Time Maude. The soundness and the completeness of
+our results are proved in the end.
 \end{abstract}
@@
 derived from algorithm analysis are satisfied, schedulability can be
-broken by overhead in the system, or by the interrupt masking
-mechanism which may delay interrupt handling. On the other hand,
-correctness of the implementation with respect to the algorithm is
-difficult to be verified by the traditional methods such as testing
-and simulation, since they are incomplete. Extensive effort to apply
-formal methods, such as model checking and theorem proving, has been
-made to analyze safety-critical systems for the past few
+broken by overhead in the system, or by the interrupt mask mechanism
+which may delay interrupt handling. On the other hand, correctness of
+the implementation with respect to the algorithm is difficult to be
+verified by the traditional methods such as testing and simulation due
+to their incompleteness. Extensive effort to apply formal methods,
+such as model checking and theorem proving, has been made to analyze
+safety-critical systems for the past few
 years~\cite{DBLP:journals/tie/MiyawakiMSYV05,DBLP:journals/iandc/MeseguerR13,DBLP:journals/cacm/Leroy09,DBLP:conf/sosp/KleinEHACDEEKNSTW09}. However,
@@
 setting. Assumption~(A1) will be modified because of the interrupt
-masking mechanism, while (A2) and (A4) are relaxed to obtain a more
+mask mechanism, while (A2) and (A4) are relaxed to obtain a more
 realistic analysis model.
@@
 which we call \emph{interrupt cycle}. When an interrupt request
-occurs, if the system is interruptable, i.e. the interrupt masking bit
+occurs, if the system is interruptable, i.e. the interrupt mask bit
 is cleared, the handler function $schedule()$ will be invoked;
-otherwise $schedule()$ will be pending until the interrupt masking bit
+otherwise $schedule()$ will be pending until the interrupt mask bit
 becomes cleared.  The implementation is shown as $schedule()$ in
@@
 
-In Figure~\ref{a:schedule}, the handler function $scheduler()$ first
+In Figure~\ref{a:schedule}, the handler function $schedule()$ first
 updates status of all tasks in $taskList$ via function
 $updateStatus()$. This updating actually initiates tasks which should
-be scheduled in the current interrupt cycle. Then $scheduler()$
+be scheduled in the current interrupt cycle. Then $schedule()$
 traverses the list to execute the ready tasks one by one, or to do a
@@
 when the interrupt request is handled, not when the interrupt is
-disabled (the interrupt masking bit is set). Due to the interrupt
-masking bit, its execution cannot be interrupted when it is updating
+disabled (the interrupt mask bit is set). Due to the interrupt
+mask bit, its execution cannot be interrupted when it is updating
 status of tasks or finding the next task to execute, however, it can
@@
 Considering some technical details of the platform, such as interrupt
-masking mechanism, we model the implementation under the following
+mask mechanism, we model the implementation under the following
 assumptions:
@@
 $\tau_i$ cannot initiate at $kT_i$. They should wait until switching
-finishes and the interrupt masking bit is cleared, which is different
+finishes and the interrupt mask bit is cleared, which is different
 from~(A1). Note that (A3) says that jobs are ready to run at their
@@
 the second job of $\tau_1$ is initiated at time $5.5$ instead of $5$,
-because switching is performed and the interrupt masking bit is set at
+because switching is performed and the interrupt mask bit is set at
 time $5$.
@@
 specify the essential behaviors--the dynamic aspect--using rewrite
-rules. In particular, modeling of instantaneous behaviors would be
-explained in Sections~\ref{ss:ir}, \ref{ss:init}
-and~\ref{ss:inthandling}, followed by timed behaviors in
+rules. In particular, modeling of \emph{instantaneous behaviors} would
+be explained in Sections~\ref{ss:ir}, \ref{ss:init}
+and~\ref{ss:inthandling}, followed by \emph{timed behaviors} in
 Section~\ref{ss:timedbehavior}.
@@
 
-A sort \verb|Stack| is introduced to simulate the stack of the system,
+A sort \verb|Stack| is introduced to model the stack of the system,
 storing the tasks that are being interrupted, and equipped with
@@
 
-A periodic task, which is needed to be scheduled, is an object
-instance of the subclass \verb|PTask| with additional attributes
+A periodic task, which needs to be scheduled, is an object instance of
+the subclass \verb|PTask| of \verb|Task| with additional attributes
 \verb|priority|, \verb|period| and \verb|status|:
@@
 \verb|Regs|, with attributes \verb|pc| denoting the program counter,
-\verb|mask| for the interrupt masking flag and \verb|ir| for the
-interrupt request flag, respectively.
+\verb|mask| for the interrupt mask bit and \verb|ir| for the interrupt
+request bit, respectively.
 \begin{verbatim}
@@
 
-Then the hardware is naturally described by the sort \verb|Hardware|:
+Then the hardware is described by the sort \verb|Hardware|:
 \begin{verbatim}
@@
 The entire system in our model is a composition of the parts
-introduced above, with a sort \verb|System|\footnote{Some variable
+introduced above, of a sort \verb|System|\footnote{Some variable
   declarations are not shown for simplicity.}:
@@
 \verb|val| equals \verb|zero|, and \verb|_.intReq| sets the \verb|ir|
-flag indicating there exists an interrupt request to be handled:
+bit indicating there exists an interrupt request to be handled:
 \begin{verbatim}
@@
 \begin{verbatim}
-  op update_with_ : Object Timer ~> Object .
+ op update_with_ : Object Timer 
+                     ~> Object .
  ceq update < O : PTask | period : T, 
@@
 When an interrupt request occurs, it may not be detected immediately
-by the system. It requires the \verb|mask| flag to be cleared. Once
-the request is detected, it is handled by two steps: the interrupt
+by the system. It requires the \verb|mask| bit to be cleared. Once the
+request is detected, it is handled in two steps: the interrupt
 handling mechanism of the hardware (such as clearing \verb|ir|,
@@
 the interrupt handling mechanism performed by the hardware and does
-four things: (i) clearing the \verb|ir| flag, which means the request
+four things: (i) clearing the \verb|ir| bit, which means the request
 has been handled; (ii) pushing the current \verb|pc| value into the
@@
 \verb|scheduling| of sort \verb|Oid| to \verb|pc|, which indicates
-that the system is scheduling; and (iv) setting the \verb|mask| flag,
+that the system is scheduling; and (iv) setting the \verb|mask| bit,
 to mask coming interrupt requests.
@@
 corresponds to Lines~\ref{l:updatestatus}-\ref{l:inc} in
-Figure~\ref{a:schedule}. It performs updating the status of
-$taskList$ and increasing $timer$ by $1$. This part is modeled by
-function \verb|_.startScheduling| which applies instantaneously at the
+Figure~\ref{a:schedule}. It updates the status of $taskList$ and
+increases $timer$ by $1$. This part is modeled by function
+\verb|_.startScheduling| which applies instantaneously at the
 beginning of scheduling, as shown in rule \verb|interrupt-handle|:
@@
 its computation requirement, and finishes when its own execution time
-does so. Two similar instantaneous rules are defined:
+does so. Two similar instantaneous rules are defined to model the
+functionality of switching:
 \begin{verbatim}
@@
 \label{ss:timedbehavior}
-\emph{Timed behaviors} of the system consist of two parts: the
-execution of tasks and the execution of the interrupt source. Both are
-modeled together by the following single ``standard'' tick
+Timed behaviors of the system consist of two parts: the execution of
+tasks and the execution of the interrupt source. Both are modeled
+together by the following single ``standard'' tick
 rule~\cite{DBLP:journals/entcs/OlveczkyM07a}:
@@
  crl [tick]:
-    {SYSTEM} => {delta(SYSTEM, R)} in time R 
+   {SYSTEM} 
+   => {delta(SYSTEM, R)} in time R 
    if R le mte(SYSTEM) [nonexec] .
@@
 behaviors is to define functions \verb|delta| and \verb|mte|. Notice
-that the variable $R$ is \emph{continuous} with respect to the
+that the variable \verb|R| is \emph{continuous} with respect to the
 specific time domain\footnote{Real-Time Maude contains built-in
@@
 when the next instantaneous action must perform. Therefore, it is
-decided by three arguments: the remaining time to finish the running
+decided by three arguments: the remaining time to complete the running
 task, the remaining time to request the next interrupt, and whether or
@@
 \subsection{Properties}
-The main objective is to verify the schedulability of a given set of
-periodic tasks. To this end, we define an atomic proposition
-\verb|taskTimeout| to hold if there exists an \verb|error| appearing
-in the $taskList$ of the current state:
+We consider two properties in this paper: schedulability and
+correctness. By schedulability, we examine whether a given task set is
+schedulable by the implementation. By correctness, we verify whether
+the implementation schedules periodic tasks exactly with respect to
+their priorities and periods.
+
+To verify the schedulability of a given set of periodic tasks, we
+define an atomic proposition \verb|taskTimeout| to hold if there
+exists an \verb|error| appearing in $taskList$ of the current state:
 \begin{verbatim}
@@
 where \verb|containError| returns \verb|true| if there is an object
-\verb|error| existing in $L$. Then our desired
+\verb|error| existing in \verb|L|. Then our desired
 property--schedulability--can be formalized as the temporal logic
@@
 
-Another objective is to verify the correctness of the implementation,
-in the sense that the periodic tasks are scheduled exactly with
-respect to their priorities. The atomic proposition
-\verb|scheduleCorrectly| is hence defined to hold if the running
-periodic task is the one requested to be executed with the highest
-priority:
-\begin{verbatim}
-  op scheduleCorrectly : -> Prop [ctor] .
-  ceq {L T STS HW ISRC} |= scheduleCorrectly 
-      = (not containError(L))
-        and (if ID :: MaybeNat 
+Another objective is to verify the correctness of the implementation.
+The atomic proposition \verb|correct| is hence defined to hold if the
+running periodic task is the one requested to be executed with the
+highest priority:
+\begin{verbatim}
+ op correct : -> Prop [ctor] .
+ ceq {L T STS HW ISRC} |= correct
+     = if ID :: MaybeNat 
        then shouldRun(ID, L)
-             else true fi)
+       else true fi
      if ID := (HW).getPc .
@@
 the highest priority among those whose status is \verb|READY|,
-\verb|RUNNING| or \verb|INTERRUPT|. Note that \verb|scheduleCorrectly|
-requires no \verb|error| popping up, since our defined correctness
-property makes no sense in the implementation once some task misses
-its deadline. The correctness property is formalized as the temporal
-logic formula: \verb|[]scheduleCorrectly|, and can be verified by the
-following untimed model checking command provided an initial state
+\verb|RUNNING| or \verb|INTERRUPT|. Note that in this paper, we do not
+care the behaviors after some task misses its deadline. Therefore, the
+correctness property is formalized by the temporal logic formula:
+\verb|([]correct) \/ (correct U taskTimeout)|, and can be verified by
+the following untimed model checking command provided an initial state
 \verb|init|:
 \begin{verbatim}
-  (mc init |=u []scheduleCorrectly .)
+ (mc init |=u (correct U taskTimeout) 
+              \/ ([]correct) .)
 \end{verbatim}
@@
 \begin{itemize}
-\item The interrupt cycle is $5ms$.
+\item The interrupt cycle $T$ is $5ms$.
 \item The scheduling time ranges from $15{\mu}s$ to $38{\mu}s$, and the
@@
 below:
+\begin{itemize}
+\item Scenario~(i) with two tasks $\tau_1$ and $\tau_2$: $T_1=5ms$,
+  $C_1\in [2.4ms, 3ms]$, $T_2=25ms$ and $C_2\in [6.1ms, 7ms]$.
+\item Scenario~(ii) with two tasks $\tau_1$ and $\tau_2$: $T_1=5ms$,
+  $C_1\in [1.8ms, 2ms]$, $T_2=25ms$ and $C_2\in [2.1ms, 2.3ms]$.
+\item Scenario~(iii) with three tasks $\tau_1$, $\tau_2$ and $\tau_3$:
+  $T_1=5ms$, $C_1\in [2.5ms, 2.7ms]$, $T_2=10ms$, $C_2\in [1.5ms,
+  2ms]$, $T_3=25ms$ and $C_3\in [2.6ms, 3ms]$.
+\item Scenario~(iv) with three tasks $\tau_1$, $\tau_2$ and $\tau_3$:
+  $T_1=5ms$, $C_1\in [2.2ms, 2.5ms]$, $T_2=10ms$, $C_2\in [1.4ms,
+  1.5ms]$, $T_3=15ms$ and $C_3\in [4.3ms, 4.5ms]$.
+\end{itemize}
+
+\hide{
 \begin{itemize}
@@
 \end{itemize}
+}
 
@@
 \emph{maximal time sampling strategy}, the results of the model
-checking show that both the schedulability and the correctness
-properties hold in Scenarios (i-iii), but not in Scenario (iv). For
-Scenario (iv), one counterexample of the schedulability is pictured in
-Figure~\ref{f:counterexample}, where the third task (task$2$) misses
-its deadline at the time $15ms$ that is marked by the tiny red
-triangle. And the correctness fails in Scenario (iv) because of the
-failure of schedulability.
+checking show that the correctness property holds in all scenarios. As
+to the schedulability property, it holds in Scenarios~(i-iii), but not
+in Scenario~(iv).  One counterexample of the schedulability for
+Scenario~(iv), returned by the model checking command, is pictured in
+Figure~\ref{f:counterexample}, where the third task $\tau_3$ misses
+its deadline at the time $15ms$.
 
@@
   \draw (0,1.3) node [left] {scheduling};
-  \draw (0,2) node [left] {task$2$};
-  \draw (0,2.7) node [left] {task$1$};
-  \draw (0,3.4) node [left] {task$0$};
+  \draw (0,2) node [left] {$\tau_3$};
+  \draw (0,2.7) node [left] {$\tau_2$};
+  \draw (0,3.4) node [left] {$\tau_1$};
 
@@
 \end{tikzpicture}
-\caption{An Counterexample of Scenario (iv).}
-\label{f:tikz}
+\caption{An counterexample of schedulablity in Scenario~(iv). Each job
+  of each task executes for the maximum of its computation
+  requirement. The first job of $\tau_3$ misses its deadline at time
+  $15ms$, which is the initiation time for the second job of
+  $\tau_3$.}
+\label{f:counterexample}
 \end{figure*}
@@
 shown in Figure~\ref{f:counterexample} is a real counterexample,
-implying that the result of Scenario~(iv) is sound. But this is not
-the case for completeness, since we choose instantiating our model on
-dense time domain to make it more real but giving rise to an infinite
-state space which is unfeasible to exhaust.
+implying that the result for schedulability of Scenario~(iv) is
+sound. But this is not the case for completeness, since we choose
+instantiating our model on dense time domain to make it more real but
+giving rise to an infinite state space which is unfeasible to exhaust.
 
@@
 model imply the schedulability and correctness of our original
-model. In particular, this is because we can prove that, if a set of
-tasks (including system ones) is schedulable when the computation
-requirement of some task $\tau_i$ equals $C_i^{max}$, then the set
-remains still schedulable when some jobs of $\tau_i$ become possible
-to terminate in time $r\le C_i^{max}$. This statement is done by
-proving Lemma~\ref{l:max}, and considering \verb|scheduling| and
-\verb|switching| as tasks with same priority, which is higher than all
-periodic tasks.
+model. In particular, this is because we can prove the followings.
 \begin{lemma}
 \label{l:max}
-Assume $r_s, r_f$ are the times at which a job of $\tau_i$ starts and
+Assume $t_s, t_f$ are the times at which a job of $\tau_i$ starts and
 completes its execution, respectively. Let $S_i$ be the set of tasks,
-which have priorities higher than $\tau_i$ or equal to it. Assumed
-$r_s$ is fixed, $r_f$ reaches its maximum, if all job instances of
-each task $\tau_j\in S_i$, which execute between $r_s$ and $r_f$, are
-completed in time $C_j^{max}$.
+which have priorities higher than $\tau_i$ or equal to it, including
+the system tasks scheduling and switching. Assumed $t_s$ is fixed,
+$t_f$ reaches its maximum, if all job instances of each task
+$\tau_j\in S_i$, which execute between $t_s$ and $t_f$, are completed
+in time $C_j^{max}$.
 \end{lemma}
+\begin{IEEEproof} 
+Note that each job instance that executes between $t_s$ and $t_f$
+corresponds to some task in $S_i$. Assume the number of job instances
+of task $\tau_j\in S_i$ is $m_j$, and they execute for time
+$C_j^1,C_j^2,\ldots,C_j^{m_j}$ respectively to complete. We have
+$m_i=1$. Then assume the number of interrupts between $t_s$ and $t_f$
+is $m_{int}$, the corresponding $m_{int}$ scheduling stages take time
+$C_{sch}^1,\ldots,C_{sch}^{m_{int}}$, respectively. By our definition
+of switching, the number of switching stages between $t_s$ and $t_f$
+is $M_{swi}=\Sigma_{k=1}^{i-1}m_k$, we assuming they execute for
+$C_{swi}^1,\ldots,C_{swi}^{M_{swi}}$ to complete. It follows that
+$t_f-t_s=\Sigma_{j=1}^i\Sigma_{k=1}^{m_j}C_j^k+\Sigma_{k=1}^{m_{int}}C_{sch}^k+\Sigma_{k=1}^{M_{swi}}C_{swi}^k$. Along
+the timeline, when $C_j^k$, $C_{sch}^k$ or $C_{swi}^k$ increases,
+$m_j$, $m_{int}$ and/or $M_{swi}$ may increase as well. Therefore,
+$t_f$ reaches its maximum when $C_j^k$, $C_{sch}^k$ and $C_{swi}^k$
+reach their maximum, hence the statement.
+\end{IEEEproof}
+\begin{theorem}
+\label{th:max}
+Given a set of tasks that is schedulable when the computation
+requirement of each task $\tau_i$ equals $C_i^{max}$, this set remains
+still schedulable when some job instances of some $\tau_i$ become
+possible to terminate in time $t\le C_i^{max}$.
+\end{theorem}
+\begin{IEEEproof}
+By investigating the effects on the completion time of some job
+instance when reducing other job instances' computation requirements,
+and using Lemma~\ref{l:max}.
+\end{IEEEproof}
 
 We achieve the same verification results in the adjusted model as in
-our original one: schedulability and correctness hold in
-Scenarios~(i-iii)\footnote{In fact, positive results in the original
-  model imply positive results in the adjusted one, since the set of
-  behaviors of the adjusted model is a subset of those of the
-  original.} but fail in Scenario~(iv).  The adjusted model is
-time-robust and our defined atomic propositions--\verb|taskTimeout|
-and \verb|scheduleCorrectly|--are tick-stabilizing, hence our analysis
-using untimed model checking on the adjusted model is complete by
-Theorem~\ref{t:completeness}. Therefore, the results shown in
-Section~\ref{ss:results} for our original model are complete.
+our original one: while correctness holds within all scenarios,
+schedulability holds only in Scenarios~(i-iii)\footnote{In fact,
+  positive results in the original model imply positive results in the
+  adjusted one, since the set of behaviors of the adjusted model is a
+  subset of those of the original.} but fail in Scenario~(iv). Since
+the adjusted model is time-robust and our defined atomic
+propositions--\verb|taskTimeout| and \verb|correct|--are
+tick-stabilizing, our analysis using untimed model checking on the
+adjusted model is complete by Theorem~\ref{t:completeness}. Therefore
+by Theorem~\ref{th:max}, the results shown in Section~\ref{ss:results}
+for our original model are complete.
 
@@
 \label{s:relate}
-\jx{This section should be adjusted w.r.t. the journal which it is
-  submitted to.}
-
 In this section we discuss our results with related
@@
 setting as in~\cite{DBLP:journals/jacm/LiuL73}, but not an
-implementation which contains much more details. Our model of the
-implementation easily degenerates to a model of the RMS algorithm, if
-we let the times for scheduling and switching be zero and let the
-computation requirement of each task be a single value.
+implementation which contains much more complex details. Our model of
+the implementation easily degenerates to a model of the RMS algorithm,
+if we let the times for scheduling and switching be zero and let the
+computation requirement of each task collapse to a single value.
 
@@
 \label{s:conclusion}
-We have formally modeled a realistic implementation of RMS algorithm
-using Real-Time Maude, a modeling language based on rewriting
-logic. By taking into acount the overhead of scheduling and switching,
-assuming that the computation requirement for each task may not be
-constant, we believe that our model contains enough details to be
-analyzed for the behaviors of the real system. Two important
-properties--schedulability and correctness--are verified by model
-checking on our model, within several given scenarios. We also prove
-at last the soundness and completeness of our results.
+We have formally modeled a realistic implementation of RMS using
+Real-Time Maude, a modeling language based on rewriting logic. By
+taking into acount the overhead of scheduling and switching, assuming
+that the computation requirement for each task may not be constant,
+and modeling some mechanism of the hardware, we believe that our model
+contains enough details to be analyzed for the behaviors of the real
+system. Two important properties--schedulability and correctness--are
+verified by model checking on our model, within several given
+scenarios. We also prove at last the soundness and completeness of our
+results.
 

### 2015-11-07 RMS/submission.tex
polished a bit wrt remarks from Prof. Song.

@@
 Rate-Monotonic Scheduling (RMS) is one of the most important real-time
-scheduling algorithms. There are large numbers of results about RMS,
-especially on its schedulability. However, these theoretical results
-contain not enough details to be used directly to investigate a
-realistic RMS implementation. On the other hand, the correctness of
-such an implementation is of the same importance. In this paper, we
-analyze a realistic RMS implementation by formal modeling using
-Real-Time Maude, a language and tool based on rewriting
+scheduling used in industry. There are a large number of results about
+RMS, especially on its schedulability. However, the theoretical
+results do not contain enough details to be used directly for an
+industrial RMS implementation. On the other hand, the correctness of
+such an implementation is of the crucial importance. In this paper, we
+analyze a realistic RMS implementation by using Real-Time Maude, a
+formal modeling language and analysis tool based on rewriting
 logic. Overhead and some details of the hardware are taken into
-account in the model. We verify the schedulability and the correctness
-of the implementation within several scenarios, using model checking
-tool built in Real-Time Maude. The soundness and the completeness of
-our results are proved in the end.
+account in the model. We validate the schedulability and the
+correctness of the implementation within key scenarios. The soundness
+and the completeness of our approach are substantiated.
 \end{abstract}
@@
 \IEEEPARstart{P}{eriodic} task scheduling is one of the most important
-topics within the field of real-time systems, due to the large number
-of control systems that require cyclic
-activities~\cite{buttazzo2011hard}. A set of periodic tasks is said to
-be \emph{schedulable} with respect to some scheduling algorithm if all
-jobs meet their deadlines. \emph{Rate-Monotonic Scheduling}
-(\emph{RMS}) is a \emph{fixed} priority scheduling algorithm for
-preemptive hard real-time environments proposed by Liu and
+topics within the field of industrial real-time systems.
+%due to the large number of control systems that require cyclic activities~\cite{buttazzo2011hard}. 
+A set of periodic tasks is said to be \emph{schedulable} with respect
+to some scheduling algorithm if all jobs meet their
+deadlines. \emph{Rate-Monotonic Scheduling} (\emph{RMS}) is a
+\emph{fixed} priority scheduling algorithm for preemptive hard
+real-time environments proposed by Liu and
 Layland~\cite{DBLP:journals/jacm/LiuL73}, which assigns priorities to
@@
 \end{picture}
-\caption{An Counterexample of Scenario (iv).}
+\caption{A Counterexample of Scenario (iv).}
 \label{f:counterexample}
@@
 \end{tikzpicture}
-\caption{An counterexample of schedulablity in Scenario~(iv). Each job
+\caption{A counterexample of schedulablity in Scenario~(iv). Each job
   of each task executes for the maximum of its computation
@@
 that the computation requirement for each task may not be constant,
-and modeling some mechanism of the hardware, we believe that our model
-contains enough details to be analyzed for the behaviors of the real
-system. Two important properties--schedulability and correctness--are
-verified by model checking on our model, within several given
-scenarios. We also prove at last the soundness and completeness of our
+and modeling some mechanism of the hardware, our model contains
+sufficient details to be analyzed for the behaviors of real
+systems. Two important properties--schedulability and correctness--are
+verified by model checking on our model, within several key
+scenarios. We demonstrate the soundness and completeness of our
 results.

### 2015-11-07 RMS/submission.tex
A new version using single value as computation requirement

@@
 jobs according to the periods of the corresponding tasks: the smaller
-period, the higher priority. RMS is proved to be the \emph{optimal}
+period, the higher priority. RMS is proven to be the \emph{optimal}
 fixed priority scheduling algorithm~\cite{DBLP:journals/jacm/LiuL73},
@@
 enhance fault-tolerance. The other direction is to generate better
-schedulablity test conditions for the algorithm and its
+schedulability test conditions for the algorithm and its
 extensions~\cite{DBLP:conf/rtss/LehoczkySD89,DBLP:conf/rtss/KuoM91,DBLP:journals/tc/BiniBB03,DBLP:journals/rts/LopezGDG03,DBLP:journals/tc/BaruahG03,gardner1999}. The
@@
 In this paper, we use \emph{Real-Time Maude}, a \emph{rewriting}-based
-formal modeling language and analyzing tool for real-time systems, to
+formal modeling language and analysis tool for real-time systems, to
 model a realistic implementation of RMS, which serves as a simplified
@@
 model extends the standard RMS model proposed
-in~\cite{DBLP:journals/jacm/LiuL73}, by allowing computation
-requirements of tasks to be non-constant, and by considering overhead
-and other details of the hardware platform.
+in~\cite{DBLP:journals/jacm/LiuL73}, by considering overhead and other
+details of the hardware platform.
 
@@
 
-(A4) All overhead, such as task switching times, is ignored.
+(A4) All overhead, such as task switching time, is ignored.
 
@@
 setting. Assumption~(A1) will be modified because of the interrupt
-mask mechanism, while (A2) and (A4) are relaxed to obtain a more
-realistic analysis model.
+mask mechanism, while (A4) is relaxed to obtain a more realistic
+analysis model.
 
 \subsection{Real-Time Maude}
-\emph{Real-Time Maude}~\cite{DBLP:journals/lisp/OlveczkyM07} is an
-extension of \emph{Maude}~\cite{DBLP:journals/tcs/ClavelDELMMQ02}
-which is a language and tool based on \emph{rewriting
+Real-Time Maude~\cite{DBLP:journals/lisp/OlveczkyM07} is an extension
+of \emph{Maude}~\cite{DBLP:journals/tcs/ClavelDELMMQ02} which is a
+language and tool based on \emph{rewriting
   logic}~\cite{DBLP:journals/jlp/Meseguer12}.  It supports formal
@@
 \begin{alltt}
-  (mc \(s\) |=u \(formula\) .)
+  (mc \(s\) |=u \(\Phi\) .)
 \end{alltt}
-checks whether the temporal logic $formula$ holds in all behaviors
-starting from the initial state $s$, \emph{with no time limit}.
+checks whether the temporal logic formula $\Phi$ holds in all
+behaviors starting from the initial state $s$, \emph{with no time
+  limit}.
 
@@
 \label{s:imp}
-The implementation is in a realistic avionic control system.
+The implementation is in an industrial avionic control system.
 Interrupts would be triggered by, and only by, the clock every $T$,
 which we call \emph{interrupt cycle}. When an interrupt request
-occurs, if the system is interruptable, i.e. the interrupt mask bit
-is cleared, the handler function $schedule()$ will be invoked;
-otherwise $schedule()$ will be pending until the interrupt mask bit
-becomes cleared.  The implementation is shown as $schedule()$ in
+occurs, if the system is interruptable, i.e. the interrupt mask bit is
+cleared, the handler function $schedule()$ will be invoked; otherwise
+$schedule()$ will be pending until the interrupt mask bit becomes
+cleared.  The implementation is shown as $schedule()$ in
 Figure~\ref{a:schedule}, where $taskList$ is the list of periodic
@@
 updates status of all tasks in $taskList$ via function
-$updateStatus()$. This updating actually initiates tasks which should
+$updateStatus()$. This updating actually initiates tasks that should
 be scheduled in the current interrupt cycle. Then $schedule()$
@@
 secondly for the task at its initiation time, if its previous job is
-complete, it would be set to be ready, otherwise it misses its
-deadline, producing an error. Notice that $schedule()$ is invoked only
-when the interrupt request is handled, not when the interrupt is
-disabled (the interrupt mask bit is set). Due to the interrupt
-mask bit, its execution cannot be interrupted when it is updating
-status of tasks or finding the next task to execute, however, it can
-be interrupted while executing some task (Line~\ref{l:function}). This
-allows the execution of $schedule()$ to be nested.
+complete, it would be set ready, otherwise it misses its deadline,
+producing an error. Notice that $schedule()$ is invoked only when the
+interrupt request is handled, not when the interrupt is disabled (the
+interrupt mask bit is set). Due to the interrupt mask bit, its
+execution cannot be interrupted when it is updating status of tasks or
+searching the next task to execute, however, it can be interrupted while
+executing some task (Line~\ref{l:function}). This allows the execution
+of $schedule()$ to be nested.
 
@@
 running task, possibly none, to $schedule()$ when an interrupt request
-is handled, (ii) the time spent by $schedule()$ finding and setting
+is handled, (ii) the time spent by $schedule()$ searching and setting
 the \emph{first} should-be-run periodic task
@@
 from the complete task back to $schedule()$, (ii) the time spent by
-$schedule()$ finding and setting the \emph{next} should-be-run
+$schedule()$ searching and setting the \emph{next} should-be-run
 periodic task, and (iii) the time for switching context from
@@
 
-(A2') Computation requirement $C_i$ for each task $\tau_i$ is not
-constant. It varies randomly between minimum $C^{min}_i$ and maximum
-$C^{max}_i$, i.e. within an interval $[C^{min}_i, C^{max}_i]$.
+(A2) Computation requirement $C_i$ for each task $\tau_i$ is constant
+and does not vary with time.
 
@@
 instance, with assumption~(A1'), an interrupt request that occurs
-while switching is performed will be pending, such that jobs of task
-$\tau_i$ cannot initiate at $kT_i$. They should wait until switching
-finishes and the interrupt mask bit is cleared, which is different
+during switching will be pending, such that jobs of task $\tau_i$
+cannot initiate at $kT_i$. They should wait until switching finishes
+and the interrupt mask bit is cleared, which is different
 from~(A1). Note that (A3) says that jobs are ready to run at their
@@
 initiation time, because scheduling takes time. Under these
-assumptions, an example for showing the execution of tasks scheduled
-by the implementation is depicted in Figure~\ref{sf:rmsimp}. Note that
-the second job of $\tau_1$ is initiated at time $5.5$ instead of $5$,
-because switching is performed and the interrupt mask bit is set at
-time $5$.
+assumptions, an example showing the execution of tasks scheduled by
+the implementation is depicted in Figure~\ref{sf:rmsimp}. Note that
+the second job instance of $\tau_1$ is initiated at time $11$ instead
+of $10$, because switching is performed and the interrupt mask bit is
+set at time $10$.
 
@@
     % time indicator
-    \draw [time line] (1.5,0.7) -- (1.5,0);
-    \draw (1.5,0) node [below] {$3$} -- +(0,2pt);
+    \draw [time line] (0.75,0.7) -- (0.75,0);
+    \draw (0.75,0) node [below] {$3$} -- +(0,2pt);
+    \draw [time line] (1.25,0.3) -- (1.25,0);
+    \draw (1.25,0) node [below] {$5$} -- +(0,2pt);
     \draw [time line] (2.5,0.7) -- (2.5,0);
-    \draw (2.5,0) node [below] {$5$} -- +(0,2pt);
-    \draw [time line] (4,0.7) -- (4,0);
-    \draw (4,0) node [below] {$8$} -- +(0,2pt);
-    \draw [time line] (4.5,0.3) -- (4.5,0);
-    \draw (4.5,0) node [below] {$9$} -- +(0,2pt);
+    \draw (2.5,0) node [below] {$10$} -- +(0,2pt);
+    \draw [time line] (3.25,0.7) -- (3.25,0);
+    \draw (3.25,0) node [below] {$13$} -- +(0,2pt);
+
     \draw [time line] (5,0.7) -- (5,0);
-    \draw (5,0) node [below] {$10$} -- +(0,2pt);
+    \draw (5,0) node [below] {$20$} -- +(0,2pt);
 
     % tasks
-    \draw [periodic task] (0,0.7) rectangle +(1.5,0.14);
-    \draw [periodic task] (1.5,0.3) rectangle +(1,0.14);
-    \draw [periodic task] (2.5,0.7) rectangle +(1.5,0.14);
-    \draw [periodic task] (4,0.3) rectangle +(0.5,0.14);
+    \draw [periodic task] (0,0.7) rectangle +(0.75,0.14);
+    \draw [periodic task] (0.75,0.3) rectangle +(0.5,0.14);
+    \draw [periodic task] (2.5,0.7) rectangle +(0.75,0.14);
 
@@
     % completion of tasks
-    \draw [complete] (1.5,0.84) -- +(0,0.01);
-    \draw [complete] (4,0.84) -- +(0,0.01);
-    \draw [complete] (4.5,0.44) -- +(0,0.01);
+    \draw [complete] (0.75,0.84) -- +(0,0.01);
+    \draw [complete] (3.25,0.84) -- +(0,0.01);
+    \draw [complete] (1.25,0.44) -- +(0,0.01);
   \end{tikzpicture}
@@
     \draw [time line] (0.5,1.5) -- (0.5,0);
-    \draw (0.5,0) node [below] {$1$} -- +(0,2pt);
+    \draw (0.5,0) node [below] {$2$} -- +(0,2pt);
     \draw [time line] (1.25,1.5) -- (1.25,0);
-    \draw (1.25,0) node [below] {$2.5$} -- +(0,2pt);
+    \draw (1.25,0) node [below] {$5$} -- +(0,2pt);
     \draw [time line] (1.75,1.1) -- (1.75,0);
-    \draw (1.75,0) node [below] {$3.5$} -- +(0,2pt);
+    \draw (1.75,0) node [below] {$7$} -- +(0,2pt);
     \draw [time line] (2.25,1.1) -- (2.25,0);
-    \draw (2.25,0) node [below] {$4.5$} -- +(0,2pt);
+    \draw (2.25,0) node [below] {$9$} -- +(0,2pt);
     \draw [time line] (2.75,1.5) -- (2.75,0);
-    \draw (2.75,0) node [below] {$5.5$} -- +(0,2pt);
+    \draw (2.75,0) node [below] {$11$} -- +(0,2pt);
     \draw [time line] (3.25,1.5) -- (3.25,0);
-    \draw (3.25,0) node [below] {$6.5$} -- +(0,2pt);
-    \draw [time line] (4.25,1.5) -- (4.25,0);
-    \draw (4.25,0) node [below] {$8.5$} -- +(0,2pt);
-    \draw [time line] (4.75,0.3) -- (4.75,0);
-    \draw (4.75,0) -- +(0,2pt);
-    \draw (4.65,0) node [below] {$9.5$};
+    \draw (3.25,0) node [below] {$13$} -- +(0,2pt);
+    \draw [time line] (4,1.5) -- (4,0);
+    \draw (4,0) node [below] {$16$} -- +(0,2pt);
+    \draw [time line] (4.5,0.3) -- (4.5,0);
+    \draw (4.5,0) -- +(0,2pt);
+    \draw (4.5,0) node [below] {$18$};
     \draw [time line] (5,1.5) -- (5,0);
-    \draw (5,0) node [below] {$10$} -- +(0,2pt);
+    \draw (5,0) node [below] {$20$} -- +(0,2pt);
 
@@
     \draw [system task] (2.75,0.7) rectangle +(0.5,0.14);
-    \draw [periodic task] (3.25,1.5) rectangle +(1,0.14);
-    \draw [system task] (4.25,0.3) rectangle +(0.5,0.14);
+    \draw [periodic task] (3.25,1.5) rectangle +(0.75,0.14);
+    \draw [system task] (4,0.3) rectangle +(0.5,0.14);
 
@@
     \draw [complete] (2.25,1.24) -- +(0,0.01);
-    \draw [complete] (4.25,1.64) -- +(0,0.01);
+    \draw [complete] (4,1.64) -- +(0,0.01);
   \end{tikzpicture}
 \label{sf:rmsimp}}
-\caption{A task set scheduled under RMS algorithm and the
-  implementation, respectively. $T=T_1=5$, $T_2=10$.  In
-  Figure~\ref{sf:rmsalg}, with assumption~(A2), $C_1=3$, $C_2=3$. In
-  Figure~\ref{sf:rmsimp}, with assumption~(A2'), $C_1\in [1,3]$ and
-  $C_2\in [1,3]$, assuming both scheduling time and switching time are
-  $1$.}
+\caption{A set of $2$ periodic tasks scheduled under RMS algorithm and
+  the implementation, respectively. $T=T_1=10$, $T_2=20$, $C_1=3$,
+  $C_2=2$. In Figure~\ref{sf:rmsimp}, we assume both scheduling time
+  and switching time are $2$.}
 \label{f:example}
@@
 
-We also need a sort \verb|Interval| to denote computation requirements
-of tasks, and a sort \verb|Counter| to record execution of tasks.  We
-call \emph{execution time} the time how long a task has been executing
+We also need
+%a sort \verb|Interval| to denote computation requirements of tasks, and 
+a sort \verb|Counter| to record the execution of tasks.  We call
+\emph{execution time} the time how long a task has been executing
 for. A \verb|Counter| records the execution time and the computation
@@
 \begin{verbatim}
- op [_,_] : Time Time -> Interval [ctor] .  
- op [_/_] : Time Interval 
-              -> Counter [ctor] .
+ op [_/_] : Time Time -> Counter [ctor] .
 \end{verbatim}
@@
 \begin{verbatim}
- class SysTask .            
+ class SysTask | .            
  subclass SysTask < Task .
@@
 this task should be initiated.  In the case where the task should be
-initiated, it is set to be \verb|READY| if its \verb|status| is
+initiated, it is set \verb|READY| if its \verb|status| is
 \verb|DORMANT|; otherwise that means the previous job of this task is
@@
 When an interrupt request occurs, it may not be detected immediately
-by the system. It requires the \verb|mask| bit to be cleared. Once the
+by the system. It requires the bit \verb|mask| to be cleared. Once the
 request is detected, it is handled in two steps: the interrupt
 handling mechanism of the hardware (such as clearing \verb|ir|,
-pushing context into stack and so on), and to invoke the $schedule()$
-function. This behavior is modeled by the following instantaneous
+pushing context into stack and so on), and to invoke the function
+$schedule()$. This behavior is modeled by the following instantaneous
 rewrite rule:
@@
 the interrupt handling mechanism performed by the hardware and does
-four things: (i) clearing the \verb|ir| bit, which means the request
+four things: (i) clearing the bit \verb|ir|, which means the request
 has been handled; (ii) pushing the current \verb|pc| value into the
@@
 \verb|scheduling| of sort \verb|Oid| to \verb|pc|, which indicates
-that the system is scheduling; and (iv) setting the \verb|mask| bit,
+that the system is scheduling; and (iv) setting the bit \verb|mask|,
 to mask coming interrupt requests.
@@
 The third part corresponds to
-Lines~\ref{l:startrun1st}-\ref{l:endrun1st}, finding the first
+Lines~\ref{l:startrun1st}-\ref{l:endrun1st}, searching the first
 should-be-run periodic task and setting it to execute. It is modeled
@@
       /\ (SYSTEM).running == scheduling 
-      /\ scheduling mayFinish?in STS .
+      /\ scheduling isComplete?in STS .
 \end{verbatim}
 where function \verb|_.running| returns the current \verb|pc| value of
-the system, and \verb|_mayFinish?in_| checks whether the execution
+the system, and \verb|_isComplete?in_| checks whether the execution
 time of the task reaches its computation requirement.  
@@
       /\ some N := (SYSTEM).running
-      /\ some N mayFinish?in L .
+      /\ some N isComplete?in L .
  crl [switching-finish] :
@@
       /\ (SYSTEM).running == switching
-      /\ switching mayFinish?in STS .
+      /\ switching isComplete?in STS .
 \end{verbatim}
@@
 \emph{infinity} otherwise. Again we do not show the case where
-\verb|ID| is of sort \verb|Oid|, which is very similar. We should
+\verb|ID| is of sort \verb|Oid|, which is very similar. 
+\hide{
+We should
 point out that \verb|mteTask| computes the remaining time to reach the
@@
 time at which a \verb|task-finish| transition \emph{must} happen.
+}
 
@@
 define an atomic proposition \verb|taskTimeout| to hold if there
-exists an \verb|error| appearing in $taskList$ of the current state:
+exists an \verb|error| appearing in $taskList$ of the current state,
+that is, some task misses its deadline:
 \begin{verbatim}
@@
 \item The interrupt cycle $T$ is $5ms$.
-\item The scheduling time ranges from $15{\mu}s$ to $38{\mu}s$, and the
-switching time ranges from $10{\mu}s$ to $20{\mu}s$.
-\hide{\item The scheduling time ranges from $5{\mu}s$ to $9{\mu}s$, and the
-switching time ranges from $2{\mu}s$ to $4{\mu}s$.}
+\item The scheduling time is $38{\mu}s$ and the switching time is
+  $20{\mu}s$.  
+\hide{\item The scheduling time ranges from $5{\mu}s$
+  to $9{\mu}s$, and the switching time ranges from $2{\mu}s$ to
+  $4{\mu}s$.}
 \item The initial state is with empty stack, empty \verb|pc|, cleared 
@@
 \item Scenario~(i) with two tasks $\tau_1$ and $\tau_2$: $T_1=5ms$,
-  $C_1\in [2.4ms, 3ms]$, $T_2=25ms$ and $C_2\in [6.1ms, 7ms]$.
+  $C_1=3ms$, $T_2=25ms$ and $C_2=7ms$.
 \item Scenario~(ii) with two tasks $\tau_1$ and $\tau_2$: $T_1=5ms$,
-  $C_1\in [1.8ms, 2ms]$, $T_2=25ms$ and $C_2\in [2.1ms, 2.3ms]$.
+  $C_1=2ms$, $T_2=25ms$ and $C_2=2.3ms$.
 \item Scenario~(iii) with three tasks $\tau_1$, $\tau_2$ and $\tau_3$:
-  $T_1=5ms$, $C_1\in [2.5ms, 2.7ms]$, $T_2=10ms$, $C_2\in [1.5ms,
-  2ms]$, $T_3=25ms$ and $C_3\in [2.6ms, 3ms]$.
+  $T_1=5ms$, $C_1=2.7ms$, $T_2=10ms$, $C_2=2ms$, $T_3=25ms$ and
+  $C_3=3ms$.
 \item Scenario~(iv) with three tasks $\tau_1$, $\tau_2$ and $\tau_3$:
-  $T_1=5ms$, $C_1\in [2.2ms, 2.5ms]$, $T_2=10ms$, $C_2\in [1.4ms,
-  1.5ms]$, $T_3=15ms$ and $C_3\in [4.3ms, 4.5ms]$.
+  $T_1=5ms$, $C_1=2.5ms$, $T_2=10ms$, $C_2=1.5ms$, $T_3=15ms$ and
+$C_3=4.5ms$.
 \end{itemize}
@@
 checking show that the correctness property holds in all scenarios. As
-to the schedulability property, it holds in Scenarios~(i-iii), but not
-in Scenario~(iv).  One counterexample of the schedulability for
+to the schedulability property, it holds in Scenarios~(i-iii), but
+fails in Scenario~(iv).  One counterexample of the schedulability for
 Scenario~(iv), returned by the model checking command, is pictured in
@@
 \end{tikzpicture}
-\caption{A counterexample of schedulablity in Scenario~(iv). Each job
-  of each task executes for the maximum of its computation
-  requirement. The first job of $\tau_3$ misses its deadline at time
-  $15ms$, which is the initiation time for the second job of
-  $\tau_3$.}
+\caption{A counterexample of schedulablity in Scenario~(iv). The first
+  job instance of $\tau_3$ misses its deadline at time $15ms$, which
+  is the initiation time for the second job instance of $\tau_3$.}
 \label{f:counterexample}
@@
 %\subsection{Soundness and Completeness of the Analysis}
-We now show our results are both \emph{sound} and \emph{complete} in
-this section.
+We now show in this section that our results are both sound and
+complete.
 
@@
 such a method implies no counterexample exists for the question in
-analysis. The soundness of our results is easy to check, simply by
+analysis. The soundness of our results is trivial to check, simply by
 examining the counterexamples found. For instance, the counterexample
@@
 Given a \emph{time-robust} real-time rewrite theory $\cal R$, a set
-$P$ of \emph{tick-stabilizing} atomic propositions, an LTL formula
+$AP$ of \emph{tick-stabilizing} atomic propositions, an LTL formula
 $\Phi$ (excluding the \emph{next} operator $\bigcirc$) whose atomic
-propositions are contained in $P$. The untimed temporal logic model
+propositions are contained in $AP$. The untimed temporal logic model
 checking verifying $\Phi$ is \emph{complete} under the maximal time
@@
 
+Therefore, we achieve the following theorem, showing that the results
+in Section~\ref{ss:results} are complete.
+\begin{theorem} 
+Our approach using untimed model checking to verify the schedulability
+and the correctness of our model is complete.
+\end{theorem}
+\begin{IEEEproof}
+By showing that our model is time-robust and that the two defined
+atomic propositions--\verb|taskTimeout| and \verb|correct|--are
+tick-stabilizing, then using Theorem~\ref{t:completeness}.
+\end{IEEEproof}
+
+\hide{
 In order to prove the completeness of our verification, we need little
@@
 for our original model are complete.
+}
 
@@
 target implementation is not in their scope.  Furthermore, compared
-with those theoretical analysis, our method using formal modeling and
-verification has a great advantage that if our schedulability test
+with those theoretical analyses, our approach based on formal modeling
+and verification has a great advantage that if our schedulability test
 answers ``no'', it returns at the same time a real counterexample,
@@
 with different languages and tools. They considered only the ideal
-setting as in~\cite{DBLP:journals/jacm/LiuL73}, but not an
+setting as in~\cite{DBLP:journals/jacm/LiuL73}, instead of an
 implementation which contains much more complex details. Our model of
 the implementation easily degenerates to a model of the RMS algorithm,
-if we let the times for scheduling and switching be zero and let the
-computation requirement of each task collapse to a single value.
+if we let the times for scheduling and switching be zero.
 
@@
 Real-Time Maude, a modeling language based on rewriting logic. By
-taking into acount the overhead of scheduling and switching, assuming
-that the computation requirement for each task may not be constant,
-and modeling some mechanism of the hardware, our model contains
-sufficient details to be analyzed for the behaviors of real
-systems. Two important properties--schedulability and correctness--are
-verified by model checking on our model, within several key
-scenarios. We demonstrate the soundness and completeness of our
-results.
+taking into acount the overhead of scheduling and switching, and by
+modeling some mechanism of the hardware, our model contains sufficient
+details to be analyzed for the behaviors of real systems. Two
+important properties--schedulability and correctness--are verified by
+model checking on our model, within several key scenarios. We
+demonstrate the soundness and completeness of our results.
 

### 2015-11-07 RMS/submission.tex
spell check

@@
 which we call \emph{interrupt cycle}. When an interrupt request
-occurs, if the system is interruptable, i.e. the interrupt mask bit is
+occurs, if the system is interruptible, i.e. the interrupt mask bit is
 cleared, the handler function $schedule()$ will be invoked; otherwise
@@
 \hrule
-  \caption{The C-Like Pseudocode of $schedule()$}
+  \caption{The C-Like Pseudo-code of $schedule()$}
   \label{a:schedule}
@@
 reasonable to reset the global variable $timer$ when it reaches an
-upperbound while increasing (see Line~\ref{l:timer} in
+upper bound while increasing (see Line~\ref{l:timer} in
 Figure~\ref{a:schedule}) in the model. Then $timer$ is of sort
-\verb|Timer| and the upperbound would be the least common multiple of
+\verb|Timer| and the upper bound would be the least common multiple of
 the periods of all tasks.}
@@
 \end{tikzpicture}
-\caption{A counterexample of schedulablity in Scenario~(iv). The first
+\caption{A counterexample of schedulability in Scenario~(iv). The first
   job instance of $\tau_3$ misses its deadline at time $15ms$, which
@@
 holds. Then a more sufficient condition, known as \emph{Hyperbolic
-  Bound}, which has the same complexity as Liu and Layland's one, was
+  Bound}, which has the same complexity as Liu and Layland's, was
 proposed in~\cite{DBLP:journals/tc/BiniBB03}. On the other hand,
@@
 Real-Time Maude, a modeling language based on rewriting logic. By
-taking into acount the overhead of scheduling and switching, and by
+taking into account the overhead of scheduling and switching, and by
 modeling some mechanism of the hardware, our model contains sufficient

### 2016-02-24 RMS/corrections.tex
create the correction file to answer the answers from reviewers in the major revision of TIE

--- 2015-11-07 RMS/submission.tex
@@
 \usepackage{alltt}
-%\usepackage{epic}
-%\usepackage{pstricks}
 \usepackage{tikz}
 \usetikzlibrary{arrows.meta}
+\usepackage{multicol}
 \newcommand{\hide}[1]{\ignorespaces}
@@
 \newtheorem{lemma}{Lemma}
+
+% Define the fontsize in environment {verbatim}
+\makeatletter
+\def\verbatim{\small\@verbatim \frenchspacing\@vobeyspaces \@xverbatim}
+%\def\verbatim@font{\small\ttfamily}
+\makeatother
 
@@
 % Do not put math or special symbols in the title.
-\title{Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude}
+\title{Corrections to Manuscript No. 15-TIE-3480}
 %
@@
 % The paper headers
-\markboth{IEEE Transaction on xxx,~Vol.~$x$, No.~$x$, xx~$x$}%
-{Liu \MakeLowercase{\textit{et al.}}: Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude}
 % The only time the second header will appear is for the odd numbered pages
@@
 % in the abstract or keywords.
-\IEEEtitleabstractindextext{%
-\begin{abstract}
-Rate-Monotonic Scheduling (RMS) is one of the most important real-time
-scheduling used in industry. There are a large number of results about
-RMS, especially on its schedulability. However, the theoretical
-results do not contain enough details to be used directly for an
-industrial RMS implementation. On the other hand, the correctness of
-such an implementation is of the crucial importance. In this paper, we
-analyze a realistic RMS implementation by using Real-Time Maude, a
-formal modeling language and analysis tool based on rewriting
-logic. Overhead and some details of the hardware are taken into
-account in the model. We validate the schedulability and the
-correctness of the implementation within key scenarios. The soundness
-and the completeness of our approach are substantiated.
-\end{abstract}
-
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-  Real-time systems, scheduling, embedded systems, modeling, formal
-  verification, rewriting logic.
-\end{IEEEkeywords}
-}
 
 % make the title area
-\maketitle
+%\maketitle
 
@@
 % papers do.
-\IEEEdisplaynontitleabstractindextext
+%\IEEEdisplaynontitleabstractindextext
 % \IEEEdisplaynontitleabstractindextext has no effect when using
@@
 % creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-%\IEEEraisesectionheading{\section{Introduction}\label{s:introduction}}
-\section{Introduction}\label{s:introduction}
-% Computer Society journal (but not conference!) papers do something unusual
-% with the very first section heading (almost always called "Introduction").
-% They place it ABOVE the main text! IEEEtran.cls does not automatically do
-% this for you, but you can achieve this effect with the provided
-% \IEEEraisesectionheading{} command. Note the need to keep any \label that
-% is to refer to the section immediately after \section in the above as
-% \IEEEraisesectionheading puts \section within a raised box.
-
-% The very first letter is a 2 line initial drop letter followed
-% by the rest of the first word in caps (small caps for compsoc).
-% 
-% form to use if the first word consists of a single letter:
-% \IEEEPARstart{A}{demo} file is ....
-% 
-% form to use if you need the single drop letter followed by
-% normal text (unknown if ever used by IEEE):
-% \IEEEPARstart{A}{}demo file is ....
-% 
-% Some journals put the first two words in caps:
-% \IEEEPARstart{T}{his demo} file is ....
-% 
-% Here we have the typical use of a "T" for an initial drop letter
-% and "HIS" in caps to complete the first word.
-\IEEEPARstart{P}{eriodic} task scheduling is one of the most important
-topics within the field of industrial real-time systems.
-%due to the large number of control systems that require cyclic activities~\cite{buttazzo2011hard}. 
-A set of periodic tasks is said to be \emph{schedulable} with respect
-to some scheduling algorithm if all jobs meet their
-deadlines. \emph{Rate-Monotonic Scheduling} (\emph{RMS}) is a
-\emph{fixed} priority scheduling algorithm for preemptive hard
-real-time environments proposed by Liu and
-Layland~\cite{DBLP:journals/jacm/LiuL73}, which assigns priorities to
-jobs according to the periods of the corresponding tasks: the smaller
-period, the higher priority. RMS is proven to be the \emph{optimal}
-fixed priority scheduling algorithm~\cite{DBLP:journals/jacm/LiuL73},
-in the sense that any set of tasks, which is schedulable under
-\emph{some} fixed priority scheduling algorithm, is also schedulable
-with respect to RMS. It is widely used in safety-critical real-time
-applications, such as vehicles and avionics, thanks to its optimality
-and easiness to implement.
-
-Liu and Layland~\cite{DBLP:journals/jacm/LiuL73} gave a sufficient
-condition for the schedulability of a set of $n$ tasks scheduled by
-RMS: $\displaystyle\Sigma^n_{i=1}C_i/T_i \le n(2^{1/n}-1)$, where
-$C_i$ and $T_i$ are the \emph{computation (time) requirement} and the
-period of task $\tau_i$, respectively. Two main directions on RMS have
-been explored since then. One is to relax the assumptions on the
-original RMS model, making it applicable on more systems.  For
-instance,
-\cite{DBLP:conf/rtss/LehoczkySS87,DBLP:journals/rts/SpruntSL89,DBLP:conf/rtss/LehoczkyR92,DBLP:journals/tc/StrosniderLS95}
-allow aperiodic tasks in the scheduling,
-\cite{DBLP:journals/pe/LeungW82,audsley1993deadline} generalize RMS to
-be \emph{deadline-monotonic}, \cite{DBLP:journals/tc/ShaRL90} allows
-resource sharing among tasks,
-\cite{dhall1978real,DBLP:journals/rts/LopezGDG03,DBLP:journals/tpds/LopezDG04,DBLP:journals/tc/BaruahG03}
-extend RMS on multiprocessors, and
-\cite{DBLP:journals/rts/OhS94,DBLP:journals/rts/GhoshMMS98,DBLP:journals/tpds/BertossiMR99}
-enhance fault-tolerance. The other direction is to generate better
-schedulability test conditions for the algorithm and its
-extensions~\cite{DBLP:conf/rtss/LehoczkySD89,DBLP:conf/rtss/KuoM91,DBLP:journals/tc/BiniBB03,DBLP:journals/rts/LopezGDG03,DBLP:journals/tc/BaruahG03,gardner1999}. The
-RMS algorithm is no doubt of practical importance.
-
-It is even more crucial to ensure the reliability of an implementation
-instead of the algorithm, when RMS serves in a safety-critical
-system. When analyzing a realistic implementation, theoretical results
-may be no more applicable. For instance, even though the conditions
-derived from algorithm analysis are satisfied, schedulability can be
-broken by overhead in the system, or by the interrupt mask mechanism
-which may delay interrupt handling. On the other hand, correctness of
-the implementation with respect to the algorithm is difficult to be
-verified by the traditional methods such as testing and simulation due
-to their incompleteness. Extensive effort to apply formal methods,
-such as model checking and theorem proving, has been made to analyze
-safety-critical systems for the past few
-years~\cite{DBLP:journals/tie/MiyawakiMSYV05,DBLP:journals/iandc/MeseguerR13,DBLP:journals/cacm/Leroy09,DBLP:conf/sosp/KleinEHACDEEKNSTW09}. However,
-as far as we know, few~\cite{DBLP:conf/iceccs/CuiDT14,TianD2011}
-attempt to analyze the RMS algorithm, while no work for
-implementations of RMS is found.
-
-In this paper, we use \emph{Real-Time Maude}, a \emph{rewriting}-based
-formal modeling language and analysis tool for real-time systems, to
-model a realistic implementation of RMS, which serves as a simplified
-operating system within an avionic control system, and then verify
-several desired properties. Based on a realistic implementation, our
-model extends the standard RMS model proposed
-in~\cite{DBLP:journals/jacm/LiuL73}, by considering overhead and other
-details of the hardware platform.
-
-The rest of this paper is organized as
-follows. Section~\ref{s:background} gives some background of both the
-RMS algorithm and Real-Time Maude.  Section~\ref{s:imp} presents the
-RMS implementation that we model and analyze.
-Section~\ref{s:formalism} introduces how we model the RMS
-implementation using Real-Time Maude. Then
-Section~\ref{s:verification} explains how to verify the desired
-properties and to evaluate the results. Related work is discussed in
-Section~\ref{s:relate}. We conclude the paper in
-Section~\ref{s:conclusion}.
-
-\section{Background}
-\label{s:background}
-
-\subsection{Rate-Monotonic Scheduling Algorithm}
-\label{ss:rms}
-%\subsection{Formulation of the Standard Setting}
-A task set consists of \emph{only} $n$ periodic tasks
-$\tau_1,\ldots,\tau_n$. Each task $\tau_i$ has a period $T_i$ and a
-computation requirement $C_i$. First jobs of all tasks are assumed to
-be initiated at time $0$ simultaneously.  Deadlines consist of
-runnability constraints only: the deadline of a job corresponding to
-$\tau_i$ is the initiation time of the next job corresponding to
-$\tau_i$.  The RMS algorithm chooses the labeling such that $T_1\le
-T_2\le \ldots \le T_n$. Consequently, $\tau_i$ receives priority $i$,
-assuming smaller numbers have higher priorities. The following
-assumptions are made:
-
-(A1) Jobs corresponding to task $\tau_i$ are initiated exactly at
-times $kT_i$ with integers $k\ge 0$.
-
-(A2) Computation requirement $C_i$ for each task $\tau_i$ is constant
-and does not vary with time.
-
-(A3) Tasks are independent, such that they are ready to run at their
-initiation times and can be preempted instantly (ignoring all
-blocking).
-
-(A4) All overhead, such as task switching time, is ignored.
-
-A simple example showing this algorithm is depicted in
-Figure~\ref{sf:rmsalg}. However in this paper, we consider an
-implementation instead of the RMS algorithm itself, thus the model
-would be more complicated than this standard, ideal
-setting. Assumption~(A1) will be modified because of the interrupt
-mask mechanism, while (A4) is relaxed to obtain a more realistic
-analysis model.
-
-\subsection{Real-Time Maude}
-Real-Time Maude~\cite{DBLP:journals/lisp/OlveczkyM07} is an extension
-of \emph{Maude}~\cite{DBLP:journals/tcs/ClavelDELMMQ02} which is a
-language and tool based on \emph{rewriting
-  logic}~\cite{DBLP:journals/jlp/Meseguer12}.  It supports formal
-specification and analysis of real-time systems.
-
-\subsubsection{Specification}
-Real-Time Maude models systems as \emph{modules}. A module specifies a
-\emph{real-time rewrite theory} ${\cal R} = (\Sigma, E\cup A , IR,
-TR)$, where:
-\begin{itemize}
-\item $\Sigma$ is an algebraic \emph{signature}, that is, a set of
-  declarations of \emph{sorts}, \emph{subsorts} and \emph{function
-    symbols}. The function symbols are allowed to be mixfix.
-\item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
-  theory}, with $E$ a set of conditional \emph{equations} and
-  \emph{memberships} on $\Sigma$, and $A$ a set of equational axioms
-  such as associativity, commutativity and identity.  $(\Sigma, E\cup
-  A)$ models the system's ``static'' states as an algebraic data type,
-  and is equipped with a built-in specification of a sort \verb|Time|.
-\item $IR$ is a set of \emph{labeled conditional rewrite rules}
-  specifying the system's local transitions. Each rule has the form
-  $[l]~:~s\rightarrow s'\mbox{ \textbf{if} }\bigwedge^n_{j=1}cond_j$,
-  where each $cond_j$ is an equality $u_j=v_j$ and $l$ is a
-  \emph{label}. Such a rule specifies an \emph{instantaneous
-    transition}, without consuming time, from an instance of $s$ to
-  the corresponding instance of $s'$, \emph{provided} the conditions
-  hold.
-\item $TR$ is a set of (\emph{labeled}) \emph{tick rules} of the form
-  $[l]~:~\{s\}\rightarrow\{s'\} \mbox{ \textbf{in time} }t\mbox{
-  \textbf{if} }cond$ that specify \emph{timed transitions}, which
-  advances time in the \emph{entire} state $s$ by $t$ time units. $IR$
-  and $TR$ together model the ``dynamic'' behaviors of the system.
-\end{itemize}
-
-In rewriting logic, rewrite rules are applied non-deterministically,
-that is, when several rules can be applied on a given $s$, any of them
-may be chosen. Hence non-deterministic behaviors can be modeled
-naturally in Real-Time Maude.  Real-Time Maude also supports
-specifications in \emph{object-oriented} style.  A class declaration
-$\texttt{class }C\texttt{ |
-}att_1\texttt{:}s_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}s_n$
-defines a class $C$ with attributes $att_1$ to $att_n$ of sorts $s_1$
-to $s_n$, respectively. An \emph{object} of class $C$ is represented
-as a term $\texttt{< } O\texttt{:} C \texttt{ | }
-att_1\texttt{:}val_1\texttt{,} \ldots
-\texttt{,}att_n\texttt{:}val_n\texttt{ >}$ of sort \verb|Object|,
-where $O$, of sort \verb|Oid|, is the object's \emph{identifier}, and
-$val_i$ is the value of the attribute $att_i$ with $i\in [1,n]$. A
-\emph{subclass} inherits all the attributes and rules of its
-superclasses.
-
-\subsubsection{Formal Analysis}
-Real-Time Maude provides many useful commands and tools to analyze a
-given model. For example, \verb|rewrite| allows to execute the model,
-symbolically; given an initial state, \verb|search| is used to search
-reachable states satisfying the desired properties; the Maude's
-\emph{Inductive Theorem Prover} (ITP) can be applied to interactively
-prove properties written in \emph{membership equational logic}.
-
-In this paper, we only consider Real-Time Maude's \emph{Linear
-  Temporal Logic (LTL) model checker}, which analyzes whether
-\emph{each} behavior satisfies a temporal logic formula. \emph{State
-  propositions} are defined as terms of sort \verb|Prop|. Their
-semantics is defined by conditional equations of the form $\texttt{ceq
-} statePattern \texttt{ |= } prop \texttt{ = } b \texttt{ if } cond$,
-with $b$ a term of sort \verb|Bool|, stating that $prop$ evaluates to
-$b$ in states which are instances of $statePattern$ provided the
-condition $cond$ holds. These equations together define $prop$ to hold
-in all states $s$ that make $s \texttt{ |= } prop$ evaluate to
-\verb|true|. A temporal logic \emph{formula} is constructed by state
-propositions and temporal logic operators such as \verb|True|,
-\verb|False|, \verb|~|(negation), \verb|/\|, \verb|\/|,
-\verb|->|(implication), \verb|[]|(``always'') and
-\verb|U|(``until''). Real-Time Maude supports both \emph{timed} and
-\emph{untimed LTL model checking}. The untimed model checking command
-\begin{alltt}
-  (mc \(s\) |=u \(\Phi\) .)
-\end{alltt}
-checks whether the temporal logic formula $\Phi$ holds in all
-behaviors starting from the initial state $s$, \emph{with no time
-  limit}.
-
-\section{The Implementation of RMS}
-\label{s:imp}
-The implementation is in an industrial avionic control system.
-Interrupts would be triggered by, and only by, the clock every $T$,
-which we call \emph{interrupt cycle}. When an interrupt request
-occurs, if the system is interruptable, i.e. the interrupt mask bit is
-cleared, the handler function $schedule()$ will be invoked; otherwise
-$schedule()$ will be pending until the interrupt mask bit becomes
-cleared.  The implementation is shown as $schedule()$ in
-Figure~\ref{a:schedule}, where $taskList$ is the list of periodic
-tasks to be scheduled. We assume that the list is in descending order
-of priority, and both variables $taskList$ and $timer$ are global. In
-this implementation, there is only one kind of interrupt, the period
-$T_i$ of each task is a multiple of $T$, and the tasks are
-independent, meeting assumption~(A3).
-
-\begin{figure}[!t]
-\hrule\vspace{1mm}
-  \begin{algorithmic}[1]
-\Function{$schedule$}{$ $}{}
-  \State \Call{$int\_o\!f\!\!f$}{$ $}; \Comment{to disable interrupts} \label{l:1stline}
-  \State \Call{$updateStatus$}{$taskList$}; \label{l:updatestatus}
-  \State $timer = timer + 1$; \label{l:timer} \label{l:inc}
-  \State $p = taskList$;
-  \While{$p$} \label{l:startrun1st}
-    \If{$p\rightarrow status == \textit{INTERRUPT}$}
-      \State \Return; \label{l:return}
-    \ElsIf{$p\rightarrow status == \textit{READY}$}      
-      \State $p\rightarrow status = \textit{RUNNING}$;
-      \State \Call{$int\_on$}{$ $}; \Comment{to enable interrupts} \label{l:endrun1st}
-      \State $p\rightarrow function()$; \Comment{to execute the task} \label{l:function}
-      \State \Call{$int\_o\!f\!\!f$}{$ $};
-      \State $p\rightarrow status = \textit{DORMANT}$;
-    \EndIf
-    \State $p = p\rightarrow next$;
-  \EndWhile
-\EndFunction
-\Function{$updateStatus$}{$p$}
-  \While{$p$}
-    \If{$p\rightarrow status == \textit{RUNNING}$} \label{l:startupdate}
-      \State $p\rightarrow status = \textit{INTERRUPT}$;
-    \EndIf
-    \If{$timer~\%~(p\rightarrow period) == 0$} \Comment{the task should be initiated}
-      \If{$p\rightarrow status == \textit{DORMANT}$} \Comment{the previous job finishes} 
-        \State $p\rightarrow status = \textit{READY}$;
-      \Else \Comment{the status is \textit{READY} or \textit{INTERRUPT}}
-	\State \Call{$reportTaskError$}{$p$}; \Comment{the task misses its deadline}
-      \EndIf
-    \EndIf \label{l:endupdate}
-    \State $p = p\rightarrow next$;
-  \EndWhile
-\EndFunction
-  \end{algorithmic}
-\hrule
-  \caption{The C-Like Pseudocode of $schedule()$}
-  \label{a:schedule}
-\end{figure}
-
-In Figure~\ref{a:schedule}, the handler function $schedule()$ first
-updates status of all tasks in $taskList$ via function
-$updateStatus()$. This updating actually initiates tasks that should
-be scheduled in the current interrupt cycle. Then $schedule()$
-traverses the list to execute the ready tasks one by one, or to do a
-return when encountering an interrupted\footnote{Note that the status
-  \textit{INTERRUPT} indicates the task is interrupted for the moment,
-  or was interrupted before but its execution is not complete yet.}
-task. As for the function $updateStatus()$, it updates each task in
-two steps: firstly, if the task is running, it becomes interrupted;
-secondly for the task at its initiation time, if its previous job is
-complete, it would be set ready, otherwise it misses its deadline,
-producing an error. Notice that $schedule()$ is invoked only when the
-interrupt request is handled, not when the interrupt is disabled (the
-interrupt mask bit is set). Due to the interrupt mask bit, its
-execution cannot be interrupted when it is updating status of tasks or
-searching the next task to execute, however, it can be interrupted while
-executing some task (Line~\ref{l:function}). This allows the execution
-of $schedule()$ to be nested.
-
-For simplicity, in the rest of this paper, we use \emph{scheduling} to
-refer to the stage, from the moment when a pending interrupt request
-is detected, to the moment when the first should-be-run periodic task
-starts executing, i.e. Line~\ref{l:return} or~\ref{l:function} in
-Figure~\ref{a:schedule}. Therefore, \emph{scheduling time} mainly
-consists of three parts: (i) the time for switching context from the
-running task, possibly none, to $schedule()$ when an interrupt request
-is handled, (ii) the time spent by $schedule()$ searching and setting
-the \emph{first} should-be-run periodic task
-(Lines~\ref{l:1stline}-\ref{l:endrun1st} in Figure~\ref{a:schedule}),
-and (iii) the time for switching context from $schedule()$ to that
-task. \emph{Switching} refers to the stage, from the moment when a
-periodic task completes its execution, to the moment when the next
-should-be-run periodic task starts executing. \emph{Switching time}
-thus also consists of three parts: (i) the time for switching context
-from the complete task back to $schedule()$, (ii) the time spent by
-$schedule()$ searching and setting the \emph{next} should-be-run
-periodic task, and (iii) the time for switching context from
-$schedule()$ to that task.
-
-\section{Formal Modeling of the Implementation}
-\label{s:formalism}
-Considering some technical details of the platform, such as interrupt
-mask mechanism, we model the implementation under the following
-assumptions:
-
-(A1') Jobs corresponding to task $\tau_i$ are initiated at the
-beginning of scheduling that handles the requests triggered at times
-$kT_i$ with integers $k\ge 0$.
-
-(A2) Computation requirement $C_i$ for each task $\tau_i$ is constant
-and does not vary with time.
-
-(A3) Tasks are independent, such that they are ready to run at their
-initiation times and can be preempted instantly.
-
-(A4') Scheduling time and switching time are considered, while other
-overhead is ignored.
-
-These assumptions make our model different from the standard one. For
-instance, with assumption~(A1'), an interrupt request that occurs
-during switching will be pending, such that jobs of task $\tau_i$
-cannot initiate at $kT_i$. They should wait until switching finishes
-and the interrupt mask bit is cleared, which is different
-from~(A1). Note that (A3) says that jobs are ready to run at their
-initiation times, however, no one can start running at exactly its
-initiation time, because scheduling takes time. Under these
-assumptions, an example showing the execution of tasks scheduled by
-the implementation is depicted in Figure~\ref{sf:rmsimp}. Note that
-the second job instance of $\tau_1$ is initiated at time $11$ instead
-of $10$, because switching is performed and the interrupt mask bit is
-set at time $10$.
-
-\begin{figure}[!t]
-\centering
-\subfloat[RMS Algorithm]{
-  \begin{tikzpicture}[font=\small,scale=1.25,
-    % styles
-    system task/.style={fill=gray!70,draw=gray},
-    periodic task/.style={fill=gray!70!black,draw=gray!50!black},
-    task line/.style={gray!30,very thin},
-    time line/.style={gray!50,very thin,dashed},
-    short line/.style={gray!50,very thin,dashed},
-    init/.style={{Triangle[fill=white,scale=1.1]}-},
-    complete/.style={{Triangle[scale=1.1]}-}]
-
-  % legend
-  \begin{scope}[xshift=-2cm]  
-    \draw [fill=gray!25,draw=gray!50,dashed] (1.5,2.3) rectangle +(4,-1);
-    \draw (1.5,2.3) node [below right] {LEGEND};
-    \draw [init] (2,1.85) -- +(0,-0.01);
-    \draw (2.1,2) node [below right] {: Initiation of Tasks};
-    \draw [complete] (2,1.42) -- +(0,0.1);
-    \draw (2.1,1.7) node [below right] {: Completion of Tasks};
-  \end{scope}
-
-    % grid
-    \foreach \x in {0.3,0.7}
-      \draw[task line] (0,\x) -- (5.2,\x);
-
-    % axes
-    \draw[->,thick] (0,0) node [below] {$0$} -- (5.3,0) node [above] {time};
-    \draw[thin] (0,0) -- (0,1);
-
-    % time indicator
-    \draw [time line] (0.75,0.7) -- (0.75,0);
-    \draw (0.75,0) node [below] {$3$} -- +(0,2pt);
-    \draw [time line] (1.25,0.3) -- (1.25,0);
-    \draw (1.25,0) node [below] {$5$} -- +(0,2pt);
-    \draw [time line] (2.5,0.7) -- (2.5,0);
-    \draw (2.5,0) node [below] {$10$} -- +(0,2pt);
-    \draw [time line] (3.25,0.7) -- (3.25,0);
-    \draw (3.25,0) node [below] {$13$} -- +(0,2pt);
-
-    \draw [time line] (5,0.7) -- (5,0);
-    \draw (5,0) node [below] {$20$} -- +(0,2pt);
-
-    % tasks
-    \draw [periodic task] (0,0.7) rectangle +(0.75,0.14);
-    \draw [periodic task] (0.75,0.3) rectangle +(0.5,0.14);
-    \draw [periodic task] (2.5,0.7) rectangle +(0.75,0.14);
-
-    % text
-    \draw (0,0.75) node [left] {$\tau_1$};
-    \draw (0,0.35) node [left] {$\tau_2$};
-    \path (0,0.75) node [left,text opacity=0] {scheduling};
-    \path (0,0.35) node [left,text opacity=0] {switching};
-
-    % initiation of tasks
-    \foreach \x in {0,2.5,5}
-      \draw [init] (\x,0.7) -- +(0,-0.01);
-    \foreach \x in {0,5}
-      \draw [init] (\x,0.3) -- +(0,-0.01);
-
-    % completion of tasks
-    \draw [complete] (0.75,0.84) -- +(0,0.01);
-    \draw [complete] (3.25,0.84) -- +(0,0.01);
-    \draw [complete] (1.25,0.44) -- +(0,0.01);
-  \end{tikzpicture}
-\label{sf:rmsalg}}\\
-\subfloat[RMS Implementation]{
-  \begin{tikzpicture}[font=\small,scale=1.25,
-    % styles
-    system task/.style={fill=gray!70,draw=gray},
-    periodic task/.style={fill=gray!70!black,draw=gray!50!black},
-    task line/.style={gray!30,very thin},
-    time line/.style={gray!50,very thin,dashed},
-    short line/.style={gray!50,very thin,dashed},
-    init/.style={{Triangle[fill=white,scale=1.1]}-},
-    complete/.style={{Triangle[scale=1.1]}-}]
-
-    % grid
-    \foreach \x in {0.3,0.7,1.1,1.5}
-      \draw[task line] (0,\x) -- (5.2,\x);
-
-    % axes
-    \draw[->,thick] (0,0) node [below] {$0$} -- (5.3,0) node [above] {time};
-    \draw[thin] (0,0) -- (0,1.8);
-
-    % time indicator
-    \draw [time line] (0.5,1.5) -- (0.5,0);
-    \draw (0.5,0) node [below] {$2$} -- +(0,2pt);
-    \draw [time line] (1.25,1.5) -- (1.25,0);
-    \draw (1.25,0) node [below] {$5$} -- +(0,2pt);
-    \draw [time line] (1.75,1.1) -- (1.75,0);
-    \draw (1.75,0) node [below] {$7$} -- +(0,2pt);
-    \draw [time line] (2.25,1.1) -- (2.25,0);
-    \draw (2.25,0) node [below] {$9$} -- +(0,2pt);
-    \draw [time line] (2.75,1.5) -- (2.75,0);
-    \draw (2.75,0) node [below] {$11$} -- +(0,2pt);
-    \draw [time line] (3.25,1.5) -- (3.25,0);
-    \draw (3.25,0) node [below] {$13$} -- +(0,2pt);
-    \draw [time line] (4,1.5) -- (4,0);
-    \draw (4,0) node [below] {$16$} -- +(0,2pt);
-    \draw [time line] (4.5,0.3) -- (4.5,0);
-    \draw (4.5,0) -- +(0,2pt);
-    \draw (4.5,0) node [below] {$18$};
-    \draw [time line] (5,1.5) -- (5,0);
-    \draw (5,0) node [below] {$20$} -- +(0,2pt);
-
-    % tasks
-    \draw [system task] (0,0.7) rectangle +(0.5,0.14);
-    \draw [periodic task] (0.5,1.5) rectangle +(0.75,0.14);
-    \draw [system task] (1.25,0.3) rectangle +(0.5,0.14);
-    \draw [periodic task] (1.75,1.1) rectangle +(0.5,0.14);
-    \draw [system task] (2.25,0.3) rectangle +(0.5,0.14);
-    \draw [system task] (2.75,0.7) rectangle +(0.5,0.14);
-    \draw [periodic task] (3.25,1.5) rectangle +(0.75,0.14);
-    \draw [system task] (4,0.3) rectangle +(0.5,0.14);
-
-    % text
-    \draw (0,1.55) node [left] {$\tau_1$};
-    \draw (0,1.15) node [left] {$\tau_2$};
-    \draw (0,0.75) node [left] {scheduling};
-    \draw (0,0.35) node [left] {switching};
-
-    % initiation of tasks
-    \foreach \x in {0,2.75,5}
-      \draw [init] (\x,1.5) -- +(0,-0.01);
-    \foreach \x in {0,5}
-      \draw [init] (\x,1.1) -- +(0,-0.01);
-
-    % completion of tasks
-    \draw [complete] (1.25,1.64) -- +(0,0.01);
-    \draw [complete] (2.25,1.24) -- +(0,0.01);
-    \draw [complete] (4,1.64) -- +(0,0.01);
-  \end{tikzpicture}
-\label{sf:rmsimp}}
-\caption{A set of $2$ periodic tasks scheduled under RMS algorithm and
-  the implementation, respectively. $T=T_1=10$, $T_2=20$, $C_1=3$,
-  $C_2=2$. In Figure~\ref{sf:rmsimp}, we assume both scheduling time
-  and switching time are $2$.}
-\label{f:example}
-\end{figure}
-
-In this section, we introduce first how we model the states--the
-static aspect--of the system using algebraic data types, then how we
-specify the essential behaviors--the dynamic aspect--using rewrite
-rules. In particular, modeling of \emph{instantaneous behaviors} would
-be explained in Sections~\ref{ss:ir}, \ref{ss:init}
-and~\ref{ss:inthandling}, followed by \emph{timed behaviors} in
-Section~\ref{ss:timedbehavior}.
-
-\subsection{Basic Data Types}
-In our model, tasks are identified by their indexes of sort \verb|Nat|
-in the $taskList$. We define a sort \verb|MaybeNat| wrapping
-\verb|Nat|s to refer to some task, with \emph{constructor} \verb|some|
-followed by a \verb|Nat| $n$ indicating the task indexed $n$, and
-\verb|none| for no task:
-\begin{verbatim}
- op none : -> MaybeNat [ctor] .
- op some_ : Nat -> MaybeNat [ctor] .
-\end{verbatim}
-
-A sort \verb|Stack| is introduced to model the stack of the system,
-storing the tasks that are being interrupted, and equipped with
-operations \verb|push|, \verb|pop| and \verb|peek| on it.
-\begin{verbatim}
- op bottom : -> Stack [ctor] .
- op _#_ : Nat Stack -> Stack [ctor] .
-\end{verbatim}
-
-We also need
-%a sort \verb|Interval| to denote computation requirements of tasks, and 
-a sort \verb|Counter| to record the execution of tasks.  We call
-\emph{execution time} the time how long a task has been executing
-for. A \verb|Counter| records the execution time and the computation
-requirement of a task.
-\begin{verbatim}
- op [_/_] : Time Time -> Counter [ctor] .
-\end{verbatim}
-
-\hide{
-At last, to make our model checkable by untimed model checking, it is
-reasonable to reset the global variable $timer$ when it reaches an
-upperbound while increasing (see Line~\ref{l:timer} in
-Figure~\ref{a:schedule}) in the model. Then $timer$ is of sort
-\verb|Timer| and the upperbound would be the least common multiple of
-the periods of all tasks.}
-
-The global variable $timer$ is reset when it reaches an upper bound
-while increasing, which is not shown in detail in
-Figure~\ref{a:schedule} but is reasonable. The upper bound is the
-least common multiple of the periods of all tasks. A sort \verb|Timer|
-is defined:
-\begin{verbatim}
- op [_/_] : Nat NzNat -> Timer [ctor] .
-\end{verbatim}
-
-\subsection{Modeling the System States}
-The system can be considered as consisting of several parts: the tasks
-which are scheduled, the scheduler itself, the hardware including
-registers and stacks, and the interrupt source. The scheduler,
-i.e. the function $schedule()$, can be described by a single variable
-$timer$. We present the models of the other parts one by one.
-
-\subsubsection{Tasks}
-Each task is abstracted from its functionality as a \verb|Counter|.
-Overhead for scheduling and switching is considered in our model. They
-are treated as two system tasks. Every task is modeled as an object
-instance of some subclass of the base class \verb|Task|:
-\begin{verbatim}
- class Task | cnt : Counter .
- op error : -> Object [ctor] .
-\end{verbatim}
-where \verb|error| is an object indicating some task that misses its
-deadline.
-
-A periodic task, which needs to be scheduled, is an object instance of
-the subclass \verb|PTask| of \verb|Task| with additional attributes
-\verb|priority|, \verb|period| and \verb|status|:
-\begin{verbatim}
- class PTask | priority : Nat, 
-               period : NzNat, 
-               status : Status .
- subclass PTask < Task .
-\end{verbatim}
-where \verb|Status| is a sort with four constant constructors, same as
-in the implementation:
-\begin{verbatim}
- ops RUNNING INTERRUPT READY DORMANT 
-       : -> Status [ctor] .
-\end{verbatim}
-The list of periodic tasks, the variable $taskList$ in the
-implementation, is modeled as an instance of the sort \verb|TaskList|,
-which is a list of \verb|PTask|s\footnote{Following the Maude
-  convention, variables would be written in capital letters.}:
-\begin{verbatim}
- op null : -> TaskList [ctor] .
- op _::_ : Object TaskList 
-             ~> TaskList [ctor] .
- mb (< O:Oid : PTask |> :: L:TaskList) 
-      : TaskList .
- mb (error :: L:TaskList) : TaskList .
-\end{verbatim}
-Periodic tasks are identified by their indexes in the list.
-
-On the other hand, a system task is an object instance of the subclass
-\verb|SysTask| of \verb|Task| with no extra attributes:
-\begin{verbatim}
- class SysTask | .            
- subclass SysTask < Task .
-\end{verbatim}
-Different from periodic tasks, system tasks are organized in a
-multiset of sort \verb|SysTasks|, and identified by their \verb|Oid|s.
-%We abstract here from the detailed definitions thanks to the
-%similarity.
-
-\subsubsection{Hardware}
-Our model considers two parts of hardware related to the interrupt
-handling mechanism: the registers and the stack.
-
-The set of registers is modeled as an object instance of the class
-\verb|Regs|, with attributes \verb|pc| denoting the program counter,
-\verb|mask| for the interrupt mask bit and \verb|ir| for the interrupt
-request bit, respectively.
-\begin{verbatim}
- class Regs | pc : TaskID, 
-              mask : Bool, ir : Bool .
-\end{verbatim}
-where the sort \verb|TaskID| is a supersort of \verb|MaybeNat| and
-\verb|Oid|, referring to some task.
-\begin{verbatim}
- subsorts MaybeNat Oid < TaskID .
-\end{verbatim}
-Some operations, such as \verb|getPc| and \verb|setMask|, are defined
-on the class \verb|Regs|.
-
-Then the hardware is described by the sort \verb|Hardware|:
-\begin{verbatim}
- op [_;_] : Object Stack 
-              ~> Hardware [ctor] .
- mb ([ < O:Oid : Regs |> ; S:Stack ]) 
-      : Hardware .
-\end{verbatim}
-
-\subsubsection{Interrupt Source}
-The interrupt source is modeled as an object of class \verb|IntSrc|,
-with attributes \verb|cycle| denoting the interrupt cycle $T$, and
-\verb|val| for the value which will decrease from $T$ to $0$ while
-time advances:
-\begin{verbatim}
- class IntSrc | val : Time, cycle : Time .
-\end{verbatim}
-
-\subsubsection{System}
-The entire system in our model is a composition of the parts
-introduced above, of a sort \verb|System|\footnote{Some variable
-  declarations are not shown for simplicity.}:
-\begin{verbatim}
- op _____ : TaskList Timer 
-            SysTasks Hardware Object 
-              ~> System [ctor] .
- mb (L T STS HW < O:Oid : IntSrc |>) 
-      : System .
-\end{verbatim}
-
-\subsection{Interrupt Requests}
-\label{ss:ir}
-Interrupt requests are performed by the source exactly every cycle
-$T$, when the attribute \verb|val| decreases to \verb|zero|. The
-requesting is an instantaneous action, thus is modeled by the
-following instantaneous conditional rule applied on \verb|System|:
-\begin{verbatim}
- crl [interrupt-request] :
-   (L T STS HW ISRC) 
-   => (L T STS (HW).intReq reset(ISRC))
-   if (ISRC).timeout .
-\end{verbatim}
-where the function \verb|_.timeout| examines whether the attribute
-\verb|val| equals \verb|zero|, and \verb|_.intReq| sets the \verb|ir|
-bit indicating there exists an interrupt request to be handled:
-\begin{verbatim}
- op _.intReq : Hardware -> Hardware .
- eq [ REGS ; S ].intReq 
-    = [ (REGS).setIr ; S ] .
-\end{verbatim}
-Then the request will wait to be handled, which is explained in
-Section~\ref{ss:inthandling}.
-
-\subsection{Task Initiation}
-\label{ss:init}
-Periodic tasks are initiated sequentially by the function
-$updateStatus()$ in Figure~\ref{a:schedule}, which is treated as an
-instantaneous action in our model. It is modeled by the recursive
-function as below:
-\begin{verbatim}
- op updateStatus_with_ : TaskList Timer 
-                           -> TaskList . 
- eq updateStatus null with TIMER = null .
- eq updateStatus (TASK :: L) with TIMER
-    = (update TASK with TIMER) 
-      :: (updateStatus L with TIMER) .
-\end{verbatim}
-with \verb|TIMER| the current value of the global variable $timer$,
-and function \verb|update_with_| updating the status of individual
-task (Lines~\ref{l:startupdate}-\ref{l:endupdate} in
-Figure~\ref{a:schedule}):
-\begin{verbatim}
- op update_with_ : Object Timer 
-                     ~> Object .
- ceq update < O : PTask | period : T, 
-                          status : ST > 
-       with TIMER
-     = if ST == DORMANT 
-       then < O : PTask | status : READY >
-       else error fi
-     if TIMER rem T == 0 .
- eq update < O : PTask | status : ST > 
-      with TIMER
-    = if ST == RUNNING 
-      then < O : PTask | status 
-                           : INTERRUPT >
-      else < O : PTask |> fi [owise] .
-\end{verbatim}
-Given a task, if \verb|TIMER|($timer$) can be divided by its period,
-this task should be initiated.  In the case where the task should be
-initiated, it is set \verb|READY| if its \verb|status| is
-\verb|DORMANT|; otherwise that means the previous job of this task is
-not complete, hence it misses its deadline, producing an
-\verb|error|. In the other case where the task should not be
-initiated, its \verb|status| changes only if it is \verb|RUNNING|.
-
-We can see that \verb|updateStatus_with_| behaves the same as
-$updateStatus()$.
-
-\subsection{Interrupt Handling and Task Scheduling}
-\label{ss:inthandling}
-When an interrupt request occurs, it may not be detected immediately
-by the system. It requires the bit \verb|mask| to be cleared. Once the
-request is detected, it is handled in two steps: the interrupt
-handling mechanism of the hardware (such as clearing \verb|ir|,
-pushing context into stack and so on), and to invoke the function
-$schedule()$. This behavior is modeled by the following instantaneous
-rewrite rule:
-\begin{verbatim}
- crl [interrupt-handle] :
-   SYSTEM 
-   => ((SYSTEM).interrupt).startScheduling
-   if (SYSTEM).existInt .
-\end{verbatim}
-where \verb|_.existInt| checks whether \verb|mask| is cleared
-\emph{and} \verb|ir| is set. The function \verb|_.interrupt| models
-the interrupt handling mechanism performed by the hardware and does
-four things: (i) clearing the bit \verb|ir|, which means the request
-has been handled; (ii) pushing the current \verb|pc| value into the
-stack, storing the interrupted context; (iii) assigning
-\verb|scheduling| of sort \verb|Oid| to \verb|pc|, which indicates
-that the system is scheduling; and (iv) setting the bit \verb|mask|,
-to mask coming interrupt requests.
-
-Unlike periodic tasks, even though the scheduling stage is modeled by
-a \verb|Counter|, its functionality is too important to be abandoned.
-We divide the behaviors of scheduling into three parts.  The first
-part contains its timed behaviors. This part is modeled by regarding
-scheduling as a system task of sort \verb|SysTask|. Modeling timed
-behaviors of tasks is explained in Section~\ref{ss:timedbehavior}.
-The other two parts together define its functionality. The second part
-corresponds to Lines~\ref{l:updatestatus}-\ref{l:inc} in
-Figure~\ref{a:schedule}. It updates the status of $taskList$ and
-increases $timer$ by $1$. This part is modeled by function
-\verb|_.startScheduling| which applies instantaneously at the
-beginning of scheduling, as shown in rule \verb|interrupt-handle|:
-\begin{verbatim}
- op _.startScheduling : System -> System .
- eq (L T STS HW ISRC).startScheduling 
-    = ((updateStatus L with T) 
-       inc(T) STS HW ISRC) .
-\end{verbatim}
-The third part corresponds to
-Lines~\ref{l:startrun1st}-\ref{l:endrun1st}, searching the first
-should-be-run periodic task and setting it to execute. It is modeled
-by function \verb|_.finishScheduling|, which applies instantaneously
-at the end of scheduling:
-\begin{verbatim}
- op _.finishScheduling : System -> System .
- eq (L T STS HW ISRC).finishScheduling
-    = (L T (finish scheduling in STS) 
-       HW ISRC).run1stTask .
-\end{verbatim}
-where \verb|finish_in_| resets the counter of task \verb|scheduling|,
-and \verb|_.run1stTask| models
-Lines~\ref{l:startrun1st}-\ref{l:endrun1st} in
-Figure~\ref{a:schedule}, searching the task with highest priority
-that has status \verb|INTERRUPT| or \verb|READY| then performing an
-\emph{interrupt return} or executing it, respectively.
-
-When the execution time of the system task \verb|scheduling| reaches
-its computation requirement, the scheduling stage may finish. We model
-this instantaneous action with the following rule:
-\begin{verbatim}
- crl [scheduling-finish] :
-   (L T STS HW ISRC) 
-   => (SYSTEM).finishScheduling
-   if SYSTEM := (L T STS HW ISRC) 
-      /\ (SYSTEM).running == scheduling 
-      /\ scheduling isComplete?in STS .
-\end{verbatim}
-where function \verb|_.running| returns the current \verb|pc| value of
-the system, and \verb|_isComplete?in_| checks whether the execution
-time of the task reaches its computation requirement.  
-\hide{
-\begin{verbatim}
-  op _mayFinish?in_ : Oid SysTasks ~> Bool .
-  eq O mayFinish?in [ < O : SysTask | cnt : C > REST ] 
-       = C mayFinish? .
-  op _mayFinish? : Counter -> Bool .
-  eq [ R / [ MIN , MAX ] ] mayFinish?
-       = if R lt MIN then false else true fi .
-\end{verbatim}}
-
-Similar to scheduling, the switching stage is divided into timed
-behaviors of \verb|switching| and its functionality. \verb|switching|
-starts when the execution time of the running periodic task reaches
-its computation requirement, and finishes when its own execution time
-does so. Two similar instantaneous rules are defined to model the
-functionality of switching:
-\begin{verbatim}
- crl [task-finish] :
-   (L T STS HW ISRC) 
-   => (SYSTEM).startSwitching
-   if SYSTEM := (L T STS HW ISRC)
-      /\ some N := (SYSTEM).running
-      /\ some N isComplete?in L .
- crl [switching-finish] :
-   (L T STS HW ISRC) 
-   => (SYSTEM).finishSwitching
-   if SYSTEM := (L T STS HW ISRC)
-      /\ (SYSTEM).running == switching
-      /\ switching isComplete?in STS .
-\end{verbatim}
-
-\subsection{Timed Behaviors of the System}
-\label{ss:timedbehavior}
-Timed behaviors of the system consist of two parts: the execution of
-tasks and the execution of the interrupt source. Both are modeled
-together by the following single ``standard'' tick
-rule~\cite{DBLP:journals/entcs/OlveczkyM07a}:
-\begin{verbatim}
- crl [tick]:
-   {SYSTEM} 
-   => {delta(SYSTEM, R)} in time R 
-   if R le mte(SYSTEM) [nonexec] .
-\end{verbatim}
-where \verb|delta| defines the effects of time elapse on the system,
-and \verb|mte| denotes the \emph{m}aximum amount of \emph{t}ime
-allowed to \emph{e}lapse from the current state until an instantaneous
-transition \emph{must} be performed. In fact, the core to model timed
-behaviors is to define functions \verb|delta| and \verb|mte|. Notice
-that the variable \verb|R| is \emph{continuous} with respect to the
-specific time domain\footnote{Real-Time Maude contains built-in
-  modules to define the time domain to be natural numbers and rational
-  numbers, specifying \emph{discrete} time domains and \emph{dense}
-  time domains, respectively.}  that we choose to instantiate our
-model on, which is different from timed automata that discretize dense
-time by defining ``clock region''.
-
-Time affects the system by advancing both the running task whose $ID$
-is loaded at \verb|pc| and the interrupt source simultaneously.  While
-time elapses, \verb|cnt| of the former increases and \verb|val| of the
-latter decreases, respectively:
-\begin{verbatim}
- ceq delta((L T STS HW ISRC), R)
-     = ((deltaTask(ID, L, R) 
-        T STS HW (deltaIS(ISRC, R)))
-     if ID := (HW).getPc 
-        /\ ID :: MaybeNat .
-\end{verbatim}
-We omit details for the case where \verb|ID| is of sort \verb|Oid| due
-to similarity. In that case, \verb|deltaTask| applies on \verb|STS|
-instead of \verb|L|.
-
-\verb|mte|, the maximum amount of time allowed to elapse, depends on
-when the next instantaneous action must perform. Therefore, it is
-decided by three arguments: the remaining time to complete the running
-task, the remaining time to request the next interrupt, and whether or
-not there exists an interrupt request detected for the moment:
-\begin{verbatim}
- ceq mte(L T STS HW ISRC)
-     = minimum( mteTask(ID, L),
-                minimum( mteIS(ISRC), 
-                         mteIr(HW)))
-     if ID := (HW).getPc 
-        /\ ID :: MaybeNat .
-\end{verbatim}
-where \verb|mteIr| returns \verb|zero| if there exists an interrupt
-request detected in the system, or \verb|INF| which represents
-\emph{infinity} otherwise. Again we do not show the case where
-\verb|ID| is of sort \verb|Oid|, which is very similar. 
-\hide{
-We should
-point out that \verb|mteTask| computes the remaining time to reach the
-maximum of the computation requirement of the task, since that is the
-time at which a \verb|task-finish| transition \emph{must} happen.
-}
-
-\section{Formal Verification}
-\label{s:verification}
-In this section, we analyze our model of the RMS implementation within
-different realistic scenarios.  Notice that from any (reasonable)
-given initial state, the number of reachable states is finite, but may
-be unknown, thanks to the upper bound given to $timer$, which provides
-the potential for applying the untimed model checker.
-
-\subsection{Properties}
-We consider two properties in this paper: schedulability and
-correctness. By schedulability, we examine whether a given task set is
-schedulable by the implementation. By correctness, we verify whether
-the implementation schedules periodic tasks exactly with respect to
-their priorities and periods.
-
-To verify the schedulability of a given set of periodic tasks, we
-define an atomic proposition \verb|taskTimeout| to hold if there
-exists an \verb|error| appearing in $taskList$ of the current state,
-that is, some task misses its deadline:
-\begin{verbatim}
- op taskTimeout : -> Prop [ctor] .
- eq {L T STS HW ISRC} |= taskTimeout 
-    = containError(L) .
-\end{verbatim}
-where \verb|containError| returns \verb|true| if there is an object
-\verb|error| existing in \verb|L|. Then our desired
-property--schedulability--can be formalized as the temporal logic
-formula: \verb|[](~taskTimeout)|. As the property is not
-\emph{clocked}, given an initial state \verb|init|, the following
-untimed model checking command returns \verb|true| if the
-schedulability property holds with no time limit; otherwise a trace
-showing a counterexample is provided:
-\begin{verbatim}
-  (mc init |=u [](~taskTimeout) .)
-\end{verbatim}
-
-Another objective is to verify the correctness of the implementation.
-The atomic proposition \verb|correct| is hence defined to hold if the
-running periodic task is the one requested to be executed with the
-highest priority:
-\begin{verbatim}
- op correct : -> Prop [ctor] .
- ceq {L T STS HW ISRC} |= correct
-     = if ID :: MaybeNat 
-       then shouldRun(ID, L)
-       else true fi
-     if ID := (HW).getPc .
-\end{verbatim}
-where \verb|shouldRun(ID, L)| returns \verb|true| if the task
-identified by \verb|ID|, probably \verb|none|, is the one possessing
-the highest priority among those whose status is \verb|READY|,
-\verb|RUNNING| or \verb|INTERRUPT|. Note that in this paper, we do not
-care the behaviors after some task misses its deadline. Therefore, the
-correctness property is formalized by the temporal logic formula:
-\verb|([]correct) \/ (correct U taskTimeout)|, and can be verified by
-the following untimed model checking command provided an initial state
-\verb|init|:
-\begin{verbatim}
- (mc init |=u (correct U taskTimeout) 
-              \/ ([]correct) .)
-\end{verbatim}
-
-\subsection{Scenarios}
-\label{ss:results}
-We use the following setting for our verification, which is from the 
-statistics provided by our industrial partner:
-\begin{itemize}
-\item The interrupt cycle $T$ is $5ms$.
-\item The scheduling time is $38{\mu}s$ and the switching time is
-  $20{\mu}s$.  
-\hide{\item The scheduling time ranges from $5{\mu}s$
-  to $9{\mu}s$, and the switching time ranges from $2{\mu}s$ to
-  $4{\mu}s$.}
-\item The initial state is with empty stack, empty \verb|pc|, cleared 
-\verb|mask| and cleared \verb|ir|.
-\end{itemize}
-
-We have analyzed our model/implementation in ten different scenarios,
-including both realistic ones provided by our industrial partner and
-experimental ones designed by ourselves, four of them are described
-below:
-\begin{itemize}
-\item Scenario~(i) with two tasks $\tau_1$ and $\tau_2$: $T_1=5ms$,
-  $C_1=3ms$, $T_2=25ms$ and $C_2=7ms$.
-\item Scenario~(ii) with two tasks $\tau_1$ and $\tau_2$: $T_1=5ms$,
-  $C_1=2ms$, $T_2=25ms$ and $C_2=2.3ms$.
-\item Scenario~(iii) with three tasks $\tau_1$, $\tau_2$ and $\tau_3$:
-  $T_1=5ms$, $C_1=2.7ms$, $T_2=10ms$, $C_2=2ms$, $T_3=25ms$ and
-  $C_3=3ms$.
-\item Scenario~(iv) with three tasks $\tau_1$, $\tau_2$ and $\tau_3$:
-  $T_1=5ms$, $C_1=2.5ms$, $T_2=10ms$, $C_2=1.5ms$, $T_3=15ms$ and
-$C_3=4.5ms$.
-\end{itemize}
-
-\hide{
-\begin{itemize}
-\item Scenario (i) with two tasks: one having period $5ms$ and
-  computation requirement $[2.4ms, 3ms]$, and the other having period
-  $25ms$ and computation requirement $[6.1ms, 7ms]$.
-\item Scenario (ii) with two tasks: one having period $5ms$ and
-  computation requirement $[1.8ms, 2ms]$, and the other having period
-  $25ms$ and computation requirement $[2.1ms, 2.3ms]$.
-\item Scenario (iii) with three tasks: the first having period $5ms$
-  and computation requirement $[2.5ms, 2.7ms]$, the second having
-  period $10ms$ and computation requirement $[1.5ms, 2ms]$, and the
-  third having period $25ms$ and computation requirement $[2.6ms,
-    3ms]$.
-\item Scenario (iv) with three tasks: the first having period $5ms$
-  and computation requirement $[2.2ms, 2.5ms]$, the second having
-  period $10ms$ and computation requirement $[1.4ms, 1.5ms]$, and the
-  third having period $15ms$ and computation requirement $[4.3ms,
-    4.5ms]$.
-\end{itemize}
-}
-
-Instantiating our model on dense time domain and choosing the
-\emph{maximal time sampling strategy}, the results of the model
-checking show that the correctness property holds in all scenarios. As
-to the schedulability property, it holds in Scenarios~(i-iii), but
-fails in Scenario~(iv).  One counterexample of the schedulability for
-Scenario~(iv), returned by the model checking command, is pictured in
-Figure~\ref{f:counterexample}, where the third task $\tau_3$ misses
-its deadline at the time $15ms$.
-
-\hide{
-\begin{figure*}[!t]
-\centering
-\begin{picture}(300,120)(0,-10)
-\thicklines
-\put(0,0){\vector(1,0){320}}
-\put(305,5){time(${\mu}s$)}
-\thinlines
-\put(0,0){\line(0,1){110}}
-\put(-25,97){task$0$}
-\put(-25,77){task$1$}
-\put(-25,57){task$2$}
-\put(-50,37){scheduling}
-\put(-45,17){switching}
-\put(-2,-8){$0$}
-
-\dashline[30]{3}(0,100)(250,100)
-\dashline[30]{3}(0,80)(280,80)
-\dashline[30]{3}(0,60)(300,60)
-\dashline[30]{3}(0,40)(210,40)
-\dashline[30]{3}(0,20)(285,20)
-
-\dashline[30]{3}(10,-10)(10,100)
-\thicklines
-\textcolor{red}{\put(0,40){\line(1,0){10}}}
-\put(8,-18){$9$}
-
-\thinlines
-\dashline[30]{3}(50,0)(50,100)
-\thicklines
-\textcolor{blue}{\put(10,100){\line(1,0){40}}}
-\put(35,-8){$2509$}
-
-\thinlines
-\dashline[30]{3}(55,-10)(55,80)
-\thicklines
-\textcolor{red}{\put(50,20){\line(1,0){5}}}
-\put(46,-18){$2513$}
-
-\thinlines
-\dashline[30]{3}(80,0)(80,80)
-\thicklines
-\textcolor{blue}{\put(55,80){\line(1,0){25}}}
-\put(65,-8){$4013$}
-
-\thinlines
-\dashline[30]{3}(85,-10)(85,60)
-\thicklines
-\textcolor{red}{\put(80,20){\line(1,0){5}}}
-\put(76,-18){$4017$}
-
-\thinlines
-\dashline[30]{3}(100,0)(100,60)
-\thicklines
-\textcolor{blue}{\put(85,60){\line(1,0){15}}}
-\put(90,-8){$5000$}
-
-\thinlines
-\dashline[30]{3}(110,-10)(110,100)
-\thicklines
-\textcolor{red}{\put(100,40){\line(1,0){10}}}
-\put(101,-18){$5009$}
-
-\thinlines
-\dashline[30]{3}(150,0)(150,100)
-\thicklines
-\textcolor{blue}{\put(110,100){\line(1,0){40}}}
-\put(135,-8){$7509$}
-
-\thinlines
-\dashline[30]{3}(155,-10)(155,60)
-\thicklines
-\textcolor{red}{\put(150,20){\line(1,0){5}}}
-\put(146,-18){$7513$}
-
-\thinlines
-\dashline[30]{3}(200,0)(200,60)
-\thicklines
-\textcolor{blue}{\put(155,60){\line(1,0){45}}}
-\put(185,-8){$10000$}
-
-\thinlines
-\dashline[30]{3}(210,-10)(210,100)
-\thicklines
-\textcolor{red}{\put(200,40){\line(1,0){10}}}
-\put(198,-18){$10009$}
-
-\thinlines
-\dashline[30]{3}(250,0)(250,100)
-\thicklines
-\textcolor{blue}{\put(210,100){\line(1,0){40}}}
-\put(230,-8){$12509$}
-
-\thinlines
-\dashline[30]{3}(255,-10)(255,80)
-\thicklines
-\textcolor{red}{\put(250,20){\line(1,0){5}}}
-\put(243,-18){$12513$}
-
-\thinlines
-\dashline[30]{3}(280,0)(280,80)
-\thicklines
-\textcolor{blue}{\put(255,80){\line(1,0){25}}}
-\put(260,-8){$14013$}
-
-\thinlines
-\dashline[30]{3}(285,-10)(285,60)
-\thicklines
-\textcolor{red}{\put(280,20){\line(1,0){5}}}
-\put(272,-18){$14017$}
-
-\thinlines
-\dashline[30]{3}(300,0)(300,60)
-\thicklines
-\textcolor{blue}{\put(285,60){\line(1,0){15}}}
-\put(289,-8){$15000$}
-
-\textcolor{red}{\put(300,60){\vector(-1,0){0}}}
-
-\end{picture}
-\caption{A Counterexample of Scenario (iv).}
-\label{f:counterexample}
-\end{figure*}
-}
-
-\begin{figure*}[!t]
-\centering
-\begin{tikzpicture}[font=\small,
-    % styles
-    system task/.style={fill=gray!70,draw=gray},
-    periodic task/.style={fill=gray!70!black,draw=gray!50!black},
-    task line/.style={gray!30,very thin},
-    time line/.style={gray!50,very thin,dashed},
-    short line/.style={gray!50,very thin,dashed},
-    init/.style={{Triangle[fill=white,scale=1.3]}-},
-    complete/.style={{Triangle[scale=1.3]}-}]
-
-  % grid
-  \foreach \x in {0.5,1.2,...,3.3}
-    \draw[task line] (0,\x) -- (15.7,\x);
-
-  % time indicator
-  \draw (0,0) node [below] {$0$};
-  \draw[time line] (0.5,3.3) -- (0.5,0);
-  \draw (0.5,-0.35) node [below] {$38$} [short line] -- +(0,0.35);
-  \draw (0.5,-3pt) -- (0.5,3pt);
-  \draw[time line] (2.5,3.3) -- (2.5,0);
-  \draw (2.3,0) node [below] {$2538$};
-  \draw (2.5,0) -- (2.5,3pt);
-  \draw[time line] (2.75,2.6) -- (2.75,0);
-  \draw (2.75,-0.35) node [below] {$2558$} [short line] -- +(0,0.35);
-  \draw (2.75,-3pt) -- (2.75,3pt);
-  \draw[time line] (4,2.6) -- (4,0);
-  \draw (3.8,0) node [below] {$4058$};
-  \draw (4,0) -- (4,3pt);
-  \draw[time line] (4.25,1.9) -- (4.25,0);
-  \draw (4.25,-0.35) node [below] {$4078$} [short line] -- +(0,0.35);
-  \draw (4.25,-3pt) -- (4.25,3pt);
-
-  \draw[time line] (5,3.3) -- (5,0);
-  \draw (5,0) node [below] {$5000$};
-  \draw (5,0) -- (5,3pt);
-  \draw[time line] (5.5,3.3) -- (5.5,0);
-  \draw (5.5,-0.35) node [below] {$5038$} [short line] -- +(0,0.35);
-  \draw (5.5,-3pt) -- (5.5,3pt);
-  \draw[time line] (7.5,3.3) -- (7.5,0);
-  \draw (7.3,0) node [below] {$7538$};
-  \draw (7.5,0) -- (7.5,3pt);
-  \draw[time line] (7.75,1.9) -- (7.75,0);
-  \draw (7.75,-0.35) node [below] {$7558$} [short line] -- +(0,0.35);
-  \draw (7.75,-3pt) -- (7.75,3pt);
-
-  \draw[time line] (10,3.3) -- (10,0);
-  \draw (9.9,0) node [below] {$10000$};
-  \draw (10,0) -- (10,3pt);
-  \draw[time line] (10.5,3.3) -- (10.5,0);
-  \draw (10.5,-0.35) node [below] {$10038$} [short line] -- +(0,0.35);
-  \draw (10.5,-3pt) -- (10.5,3pt);
-  \draw[time line] (12.5,3.3) -- (12.5,0);
-  \draw (12.2,0) node [below] {$12538$};
-  \draw (12.5,0) -- (12.5,3pt);
-  \draw[time line] (12.75,2.6) -- (12.75,0);
-  \draw (12.75,-0.35) node [below] {$12558$} [short line] -- +(0,0.35);
-  \draw (12.75,-3pt) -- (12.75,3pt);
-  \draw[time line] (14,2.6) -- (14,0);
-  \draw (13.7,0) node [below] {$14058$};
-  \draw (14,0) -- (14,3pt);
-  \draw[time line] (14.25,1.9) -- (14.25,0);
-  \draw (14.25,-0.35) node [below] {$14078$} [short line] -- +(0,0.35);
-  \draw (14.25,-3pt) -- (14.25,3pt);
-  \draw[time line] (15,1.9) -- (15,0);
-  \draw (15,0) node [below] {$15000$};
-  \draw (15,0) -- (15,3pt);
-
-  % axes
-  \draw[->,thick] (0,0) -- (15.7,0) node [above] {time(${\mu}s$)};
-  \draw[thin] (0,0) -- (0,3.8);
-
-  % tips of tasks
-  \draw (0,0.6) node [left] {switching};
-  \draw (0,1.3) node [left] {scheduling};
-  \draw (0,2) node [left] {$\tau_3$};
-  \draw (0,2.7) node [left] {$\tau_2$};
-  \draw (0,3.4) node [left] {$\tau_1$};
-
-  % tasks
-  \filldraw[system task] (0,1.2) rectangle +(0.5,0.2);
-  \filldraw[periodic task] (0.5,3.3) rectangle +(2,0.2);
-  \filldraw[system task] (2.5,0.5) rectangle +(0.25,0.2);
-  \filldraw[periodic task] (2.75,2.6) rectangle +(1.25,0.2);
-  \filldraw[system task] (4,0.5) rectangle +(0.25,0.2);
-  \filldraw[periodic task] (4.25,1.9) rectangle +(0.75,0.2);
-
-  \filldraw[system task] (5,1.2) rectangle +(0.5,0.2);
-  \filldraw[periodic task] (5.5,3.3) rectangle +(2,0.2);
-  \filldraw[system task] (7.5,0.5) rectangle +(0.25,0.2);
-  \filldraw[periodic task] (7.75,1.9) rectangle +(2.25,0.2);
-
-  \filldraw[system task] (10,1.2) rectangle +(0.5,0.2);
-  \filldraw[periodic task] (10.5,3.3) rectangle +(2,0.2);
-  \filldraw[system task] (12.5,0.5) rectangle +(0.25,0.2);
-  \filldraw[periodic task] (12.75,2.6) rectangle +(1.25,0.2);
-  \filldraw[system task] (14,0.5) rectangle +(0.25,0.2);
-  \filldraw[periodic task] (14.25,1.9) rectangle +(0.75,0.2);
-
-  % initiation of tasks
-  \foreach \x in {0,5,10}
-    \draw [init] (\x,3.3) -- +(0,-0.1);
-  \foreach \x in {0,10}
-    \draw [init] (\x,2.6) -- +(0,-0.1);  
-  \foreach \x in {0,15}
-    \draw [init] (\x,1.9) -- +(0,-0.1);
-
-  % completion of tasks
-  \draw [complete] (2.5,3.5) -- +(0,0.1);
-  \draw [complete] (4,2.8) -- +(0,0.1);
-  \draw [complete] (7.5,3.5) -- +(0,0.1);
-  \draw [complete] (12.5,3.5) -- +(0,0.1);
-  \draw [complete] (14,2.8) -- +(0,0.1);
-
-  % text
-  \draw[{Stealth}-,thick] (15,2.2) -- +(0,1.5)
-    node [above] {\emph{Misses Deadline!}};
-
-  % legend
-  \begin{scope}[xshift = -1.2cm]  
-    \draw [fill=gray!25,draw=gray!50,dashed] (1.5,4) rectangle +(8,1);
-    \draw (1.5,4.5) node [above right] {LEGEND};
-    \draw [init] (2,4.4) -- +(0,-0.1);
-    \draw (2.2,4.55) node [below right] {: Initiation of Tasks};
-    \draw [complete] (6,4.2) -- +(0,0.1);
-    \draw (6.2,4.55) node [below right] {: Completion of Tasks};
-  \end{scope}
-
-\end{tikzpicture}
-\caption{A counterexample of schedulablity in Scenario~(iv). The first
-  job instance of $\tau_3$ misses its deadline at time $15ms$, which
-  is the initiation time for the second job instance of $\tau_3$.}
-\label{f:counterexample}
-\end{figure*}
-
-\subsection{Evaluation}
-%\subsection{Soundness and Completeness of the Analysis}
-We now show in this section that our results are both sound and
-complete.
-
-An analysis method is called \emph{sound} if any counterexample found
-using such a method is a real counterexample of the question, and
-\emph{complete} if the fact that no counterexample can be found using
-such a method implies no counterexample exists for the question in
-analysis. The soundness of our results is trivial to check, simply by
-examining the counterexamples found. For instance, the counterexample
-shown in Figure~\ref{f:counterexample} is a real counterexample,
-implying that the result for schedulability of Scenario~(iv) is
-sound. But this is not the case for completeness, since we choose
-instantiating our model on dense time domain to make it more real but
-giving rise to an infinite state space which is unfeasible to exhaust.
-
-In general, completeness of untimed model checking cannot be achieved
-for any systems, any time sampling strategies and any
-properties. However, \"Olveczky and Meseguer proved the completeness
-of untimed temporal logic model checking, under the maximal time
-sampling strategy, for a large class of real-time
-systems~\cite{DBLP:journals/entcs/OlveczkyM07a}:
-\begin{theorem}[\cite{DBLP:journals/entcs/OlveczkyM07a}]
-\label{t:completeness}
-Given a \emph{time-robust} real-time rewrite theory $\cal R$, a set
-$AP$ of \emph{tick-stabilizing} atomic propositions, an LTL formula
-$\Phi$ (excluding the \emph{next} operator $\bigcirc$) whose atomic
-propositions are contained in $AP$. The untimed temporal logic model
-checking verifying $\Phi$ is \emph{complete} under the maximal time
-sampling strategy.
-\end{theorem}
-
-Therefore, we achieve the following theorem, showing that the results
-in Section~\ref{ss:results} are complete.
-\begin{theorem} 
-Our approach using untimed model checking to verify the schedulability
-and the correctness of our model is complete.
-\end{theorem}
-\begin{IEEEproof}
-By showing that our model is time-robust and that the two defined
-atomic propositions--\verb|taskTimeout| and \verb|correct|--are
-tick-stabilizing, then using Theorem~\ref{t:completeness}.
-\end{IEEEproof}
-
-\hide{
-In order to prove the completeness of our verification, we need little
-adjustments to our model.  For each task $\tau_i$, we collapse its
-computation requirement $[C_i^{min},C_i^{max}]$ into the single value
-$C_i^{max}$.  That is, in the adjusted model, we use the maximum time
-that is possible to be required to complete the task, as in the
-standard setting. The adjustment is reasonable for verifying our
-properties, since the schedulability and correctness of the adjusted
-model imply the schedulability and correctness of our original
-model. In particular, this is because we can prove the followings.
-\begin{lemma}
-\label{l:max}
-Assume $t_s, t_f$ are the times at which a job of $\tau_i$ starts and
-completes its execution, respectively. Let $S_i$ be the set of tasks,
-which have priorities higher than $\tau_i$ or equal to it, including
-the system tasks scheduling and switching. Assumed $t_s$ is fixed,
-$t_f$ reaches its maximum, if all job instances of each task
-$\tau_j\in S_i$, which execute between $t_s$ and $t_f$, are completed
-in time $C_j^{max}$.
-\end{lemma}
-\begin{IEEEproof} 
-Note that each job instance that executes between $t_s$ and $t_f$
-corresponds to some task in $S_i$. Assume the number of job instances
-of task $\tau_j\in S_i$ is $m_j$, and they execute for time
-$C_j^1,C_j^2,\ldots,C_j^{m_j}$ respectively to complete. We have
-$m_i=1$. Then assume the number of interrupts between $t_s$ and $t_f$
-is $m_{int}$, the corresponding $m_{int}$ scheduling stages take time
-$C_{sch}^1,\ldots,C_{sch}^{m_{int}}$, respectively. By our definition
-of switching, the number of switching stages between $t_s$ and $t_f$
-is $M_{swi}=\Sigma_{k=1}^{i-1}m_k$, we assuming they execute for
-$C_{swi}^1,\ldots,C_{swi}^{M_{swi}}$ to complete. It follows that
-$t_f-t_s=\Sigma_{j=1}^i\Sigma_{k=1}^{m_j}C_j^k+\Sigma_{k=1}^{m_{int}}C_{sch}^k+\Sigma_{k=1}^{M_{swi}}C_{swi}^k$. Along
-the timeline, when $C_j^k$, $C_{sch}^k$ or $C_{swi}^k$ increases,
-$m_j$, $m_{int}$ and/or $M_{swi}$ may increase as well. Therefore,
-$t_f$ reaches its maximum when $C_j^k$, $C_{sch}^k$ and $C_{swi}^k$
-reach their maximum, hence the statement.
-\end{IEEEproof}
-\begin{theorem}
-\label{th:max}
-Given a set of tasks that is schedulable when the computation
-requirement of each task $\tau_i$ equals $C_i^{max}$, this set remains
-still schedulable when some job instances of some $\tau_i$ become
-possible to terminate in time $t\le C_i^{max}$.
-\end{theorem}
-\begin{IEEEproof}
-By investigating the effects on the completion time of some job
-instance when reducing other job instances' computation requirements,
-and using Lemma~\ref{l:max}.
-\end{IEEEproof}
-
-We achieve the same verification results in the adjusted model as in
-our original one: while correctness holds within all scenarios,
-schedulability holds only in Scenarios~(i-iii)\footnote{In fact,
-  positive results in the original model imply positive results in the
-  adjusted one, since the set of behaviors of the adjusted model is a
-  subset of those of the original.} but fail in Scenario~(iv). Since
-the adjusted model is time-robust and our defined atomic
-propositions--\verb|taskTimeout| and \verb|correct|--are
-tick-stabilizing, our analysis using untimed model checking on the
-adjusted model is complete by Theorem~\ref{t:completeness}. Therefore
-by Theorem~\ref{th:max}, the results shown in Section~\ref{ss:results}
-for our original model are complete.
-}
-
-\hide{
-To apply Theorem~\ref{t:completeness} on our analysis to show the
-completeness, we only need to prove time-robustness of our model and
-tick-stabilization of our defined atomic propositions,
-\verb|taskTimeout| and \verb|scheduleCorrectly|. The latter is quite
-trivial, while the former requires little adjustments to the model,
-which collapse the possible finishing interval for some periodic task
-into a single value that should be assigned to the possible maximum
-computation time. Then we can apply Lemma~\ref{l:timerobustness} to
-prove the time-robustness of our (adjusted) model.
-\begin{lemma}
-\label{l:timerobustness}
-An object-oriented specification $\cal R$, with a conventional tick
-rule, is \emph{time-robust} if the following conditions are satisfied
-for all appropriate \emph{ground} terms $t$ and $r,r'$:
-
-\noindent
-(i) $mte(\delta(t,r))=mte(t)\dotdiv r$, for all $r\le mte(t)$;
-
-\noindent
-(ii) $\delta(t,0)=t$;
-
-\noindent
-(iii) $\delta(\delta(t,r),r')=\delta(t,r+r')$, for $r+r'\le mte(t)$;
-
-\noindent
-(iv) $mte(\sigma(l))=0$ for each ground instance $\sigma(l)$ of a
-left-hand side of an instantaneous rewrite rule.
-\end{lemma}
-
-We achieve the same verification results for the adjusted model as for
-the original one: schedulability and correctness hold in Scenarios
-(i-iii) but fail in Scenario~(iv). The only thing remained to show the
-completeness of our results is to prove the reasonability of the
-adjustments, that is, if a set of tasks (including system ones) is
-schedulable when the computation time of some task $\tau_i$ in it
-equals to $C_i^{max}$, then when some jobs of $\tau_i$ become possible
-to finish in time $r\le C_i^{max}$, the set of tasks remains still
-schedulable. This is done by proving Lemma~\ref{l:max} and considering
-\verb|scheduling| and \verb|switching| as having same and higher
-priority than all periodic tasks.
-\begin{lemma}
-\label{l:max}
-Assume the time $r_s$ at which a job of $\tau_i$ starts running is
-fixed. The time $r_f$, at which this job finishes, reaches its maximum
-if all job instances of tasks $\tau$'s, the priorities of which are
-higher than or equal to that of $\tau_i$, running between $r_s$ and
-$r_f$ finish in their maximum possible computation time.
-\end{lemma}
-}
-
-\section{Related Work}
-\label{s:relate}
-In this section we discuss our results with related
-work in three directions.
-
-Considering schedulability test, Liu and
-Layland~\cite{DBLP:journals/jacm/LiuL73} gave the famous sufficient
-condition that a set of periodic tasks is schedulable with respect to
-RMS if $\displaystyle \Sigma^n_{i=1} C_i/T_i \le n(2^{1/n}-1)$
-holds. Then a more sufficient condition, known as \emph{Hyperbolic
-  Bound}, which has the same complexity as Liu and Layland's one, was
-proposed in~\cite{DBLP:journals/tc/BiniBB03}. On the other hand,
-necessary and sufficient conditions for schedulability were derived
-independently in~\cite{DBLP:journals/rts/SpruntSL89}
-and~\cite{audsley1993deadline}, requiring more sophisticated analysis
-on the task set. Nevertheless, all these results take no overhead into
-account, being not as realistic as ours. Katcher et al. did consider
-overhead in their schedulability analysis, under several models based
-on different kinds of popular
-implementations~\cite{DBLP:journals/tse/KatcherAS93}.  However, our
-target implementation is not in their scope.  Furthermore, compared
-with those theoretical analyses, our approach based on formal modeling
-and verification has a great advantage that if our schedulability test
-answers ``no'', it returns at the same time a real counterexample,
-which is able to guide our engineer to adjust the design.
-
-\cite{DBLP:conf/iceccs/CuiDT14} and~\cite{TianD2011} also made use of
-model checking to analyze the RMS algorithm along the same line but
-with different languages and tools. They considered only the ideal
-setting as in~\cite{DBLP:journals/jacm/LiuL73}, instead of an
-implementation which contains much more complex details. Our model of
-the implementation easily degenerates to a model of the RMS algorithm,
-if we let the times for scheduling and switching be zero.
-
-Finally, Maude and Real-Time Maude have been successfully applied on
-large numbers of applications~\cite{DBLP:journals/jlp/Meseguer12},
-especially on communication protocols, real-time and cyber-physical
-systems. But few results are achieved on scheduling problems. RMS is
-investigated using Real-Time Maude for the first time.
-
-\section{Conclusion}
-\label{s:conclusion}
-We have formally modeled a realistic implementation of RMS using
-Real-Time Maude, a modeling language based on rewriting logic. By
-taking into acount the overhead of scheduling and switching, and by
-modeling some mechanism of the hardware, our model contains sufficient
-details to be analyzed for the behaviors of real systems. Two
-important properties--schedulability and correctness--are verified by
-model checking on our model, within several key scenarios. We
-demonstrate the soundness and completeness of our results.
+%\IEEEpeerreviewmaketitle
+
+\twocolumn[
+  \begin{@twocolumnfalse}
+\maketitle
+
+\begin{center}
+  \begin{tabular}{r l}
+    \hline\hline
+    & \\
+    Manuscript Number: & 15-TIE-3480\\
+    Manuscript Title: & Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation\\
+    & with Real-Time Maude \\
+    Submitted to: & Transactions on Industrial Eletronics \\
+    Manuscript Type: & Regular paper \\
+    & \\
+    \hline\hline
+  \end{tabular}
+  \bigskip
+\end{center}
+
+  \end{@twocolumnfalse}
+]
+
+\section{Answers to the Reviewers}
+\subsection{Reviewer 1}
+Comments to the Author
+
+The paper shows a realistic implementation of a Rate-Monotonic
+Scheduling algorithm using Real-Time Maude (a modeling language based
+on rewriting logic) by taking into account the overhead of scheduling
+and some other details of the hardware platform. The correctness of
+the implementation with respect to the algorithm and the completeness
+of the model are verified by model checking, and validated within
+different realistic scenarios.
+
+On the positive side, this paper presents a solid piece of
+work. Periodic task scheduling is an important (and difficult)
+problem, and the topic of the paper appears to be well suited within
+the field of the industrial real-time systems. Overall the paper is
+well structured, technically accurate, presents the work in a
+comprehensive and reasonable way, and tackles theoretical as well as
+practical aspects. There are two principal contributions of the paper:
+
+1) A novel implementation of the Rate-Monotonic Scheduling algorithm,
+which contains more complex and realistic details instead of the ideal
+setting.
+
+2) Rate-Monotonic Scheduling is investigated using Real-Time Maude for
+the first time, to apply formal methods such as model checking and
+theorem proving to analyze theoretical results, verify desired
+properties, and evaluate results.
+
+On the negative side:
+
+1) The weak point is the lack of evidence of practicality, efficiency
+and scalability. Since there are only small and simplistic scenarios
+to analyze this model, it is difficult to judge the effectiveness of
+the proposed implementation. The key scenarios appear conveniently
+small to allow the implementation fully supports all these examples,
+returning at the same time appropriate counterexamples to guide and
+adjust the design. Is this true for larger examples of "real world"
+applications within the field of industrial real-time systems? How do
+the authors propose to handle very large scenarios? ¿How does it
+behave on typical real-time scheduling problems used in industry? I
+would like to see more complex examples to convince the reader of the
+practicability of the approach on the assumptions given for the model,
+and would probably increase the mentioned benefits. The paper does not
+give any directions to the above problems, and some sentences pointing
+out the difficulties in the implementation of more generic and
+realistic scenarios would be most welcome to understand the real
+contribution of the paper.
+
+2) One of my biggest problems with the theoretical part of this work
+is that the paper is technically solid as far as I can tell, but
+there's not much yet in the way of theorems and results about formal
+properties in Maude. The complete and detailed proof of the Theorem 2
+should be provided somewhere. If the proof of the main results of
+schedulability and correctness of the model is straightforward (as is
+suggested) it seems not necessary to present a complex formalism on
+Real-Time Maude and all the theorems provided are natural consequences
+of Theorem 1. I agree that even non-surprising results need to be
+investigated in the proof of Theorem 2, some sentences pointing out
+the difficulties in the theoretical formalization in Real-Time Maude
+would be most welcome. Please, include (e.g., in an appendix or even
+in a technical report) a detailed proof.
+
+3) Another important point which needs improvement is the description
+of the implementation. I guess other readers might have less
+difficulties with the motivations if they know Maude and the Real-Time
+Maude extension, but if you aim for a more general audience, it might
+not work. Many pages are spent for the description of the formal
+modeling of the implementation and the section is hard to read. I
+highly recommend the authors to thoroughly revise this part of the
+paper to make it easy-to-read. It would be better preferable to have a
+much shorter description of the principal insights for the
+implementation followed by more convincing examples and benchmarks
+with respect to related work to convince the reader of the
+practicability of the approach. You should try to summarize this
+section and to extend the original contribution. From my point of
+view, there is a trade off in this paper between the contributions and
+the presentation of the implementation.
+
+In conclusion, the RMS implementation proposed by the authors by using
+Real-Time Maude is interesting, but not complete (theorems and results
+about the formal modeling and verification of the implementation in
+Maude ought be clearly demonstrated). Moreover, the weak point is the
+lack of evidence for practicality, and the presentation of Section IV
+can be improved. It's not clear at all how this kind of key scenarios
+could actually run in practice in more general real-time
+systems. However, I think that the paper is worthy of publication,
+because is the first time that Rate-Monotonic Scheduling is
+investigated using Real-Time Maude in a (more) realistic
+implementation, providing a solid semantic foundation for formal
+verification. Therefore, I recommend the (weak) acceptance of this
+paper.
+
+Some minor remarks:
+
+- Page 7, Related Work. More comparisons with other approaches based
+on model checking would help to evaluate pros and cons of an
+implementation with Real-Time Maude with respect to different
+languages and tools. The authors should review the comparison with
+[24] and [25] more thoroughly. You should benchmark your approach
+against others.
+
+- Page 8, Conclusions. Where in the paper do you show that the details
+of your "realistic" implementation are "sufficient" for the behaviors
+of all real systems used in the current industry? This should be
+briefly discussed.
+
+\subsection{Reviewer 2}
+Comments to the Author
+
+The paper proposes a new way of modelling Rate Monotonic Scheduling
+(RMS).  The new modelling approach is more accurate than the
+simplified way originally proposed by Liu and Layland, as it also
+models some of the overhead that is present in a real system
+(e.g. scheduling and switching time).  This implies taking some of the
+hardware details into account.  The model, which is based on the
+formal language of Real-Time Maude, can be analyzed using the formal
+verification tools provided by Real-Time Maude.  The paper shows how
+this approach can be used for modelling and analyzing a particular RMS
+implementation.
+
+Up to my knowledge, this is original work. Related papers address
+different aspects and do not take implementation overhead into
+account.
+
+The technique proposed by the paper is of industrial interest because
+it improves the accuracy of analyzing schedulability in RMS
+implementations with respect to the bare application of the theoretic
+schedulability result.
+
+The paper is well written and it looks sound, but I could not check it
+completely.
+
+One of the problems with this paper is that it is not completely
+self-contained.  Some knowledge about Real-Time Maude is necessary in
+order to fully understand it.  I found the short introduction about
+Real-Time Maude (section II.B) not enough for understanding the
+formalism used in the rest of the paper (see details below).
+
+Another concern is that the significance of the paper could be much
+better if the paper addressed the problem of modelling RMS in a more
+general way. Instead, the paper takes the form of a case study, where
+the formal modelling of one specific RMS implementation is presented,
+rather than a general method for modelling and analyzing RMS
+implementations.  Also, the discussion about soundness and
+completeness of the analysis (section V.C) is not fully developed and,
+once again, it refers to the specific model rather than being a
+general result.
+
+As a conclusion, even if the significance of the paper is not as much
+as it could be, I think the paper provides something novel and
+interesting for the readers. Hence, my recommendation is to accept
+this paper provided it is made more self-contained (without assuming
+any reader's knowledge about Maude) and the proof of completeness and
+soundness is fully developed.
+
+Detailed comments
+
+Section II.B \\ In the definition of IR, it is not clear what s and s'
+are. I guess they are states, but the concept of state was not
+introduced. \\ In the definition of a class, the authors should
+specify that a class includes a collection of rules, otherwise this
+fact may be missed.
+
+Section III \\ Page 2 right column, line -24 The implementation is
+shown as schedule() in Figure 1 -> The pseudocode of schedule() is
+shown in Figure 1
+
+Section IV.A \\ I don't understand the meaning of [ctor] in the
+definition of some operations (maybe because I have no specific
+background on Maude). I could not find the explanation of this writing
+in the introduction to Maude. \\ For the stack sort, the authors
+mention operations push, pop and peek, but then you don't write the
+definitions of these operations. Instead, they write the definitions
+of bottom and \#, which are not explained in the text. This part should
+be made clearer. \\ Also, the meaning of NzNat is not explained.
+
+Section V.C \\ In the statement of theorem 1, the definition of
+time-robust real-time rewrite theory is missing. Also, the meaning of
+tick-stabilizing atomic propositions is not defined. \\ This makes the
+section not self-contained. \\ The proof of theorem 2 is missing. The
+authors just indicate how the proof could be developed, but they do
+not develop it. A possibility would be to point to a document where
+this proof has been developed.
+
+\subsection{Reviewer 3}
+Comments to the Author
+
+This paper stuides the implementation of a rate-monotonic scheduling
+with real-time maude, according to my carefully reading of this paper,
+I do not think this paper is qualified for TIE due to the following
+reasons:
+
+1. Rate-monotonic scheduling is a very simple scheduling and has been
+sufficiently invesigated in the field of embedded system, the authors
+claim the innovation of this paper as the implementation using
+real-time maude, however, I cannot see any special point (or
+advantage) when using this real-time maude in modelling RMS.
+
+2. RMS has many different realizatio methods, no comparison is given
+to justify the strong point of real-time maude when applied to RMS.
+
+3. The assumptions given in IV is too rigid, which makes the
+scheduling problem to be investigated by very simple, then what is the
+difficulty?
+
+4. The description in section IV (A-E) is trivial, it can only be
+viewed as a simple application of the rewriting logic.
+
+5. The model checking part is not sufficiently discussed, the authors
+only list the commands but not illustrate the mechanism behind these
+commands.
+
+Based on the above comments, I thinks this paper is only a simple
+application [26] and [27] in RMS, hence I do not recommend this paper.
 
@@
 % http://www.michaelshell.org/tex/ieeetran/bibtex/
-\bibliographystyle{IEEEtran}
+%\bibliographystyle{IEEEtran}
 % argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{IEEEabrv,submission}
+%\bibliography{IEEEabrv,submission}
 %

### 2016-03-20 RMS/submission.tex
modified fontsize in verbatim, shorten the paper within 8 pages.
edited the appendix

@@
 \usepackage{alltt}
-%\usepackage{epic}
-%\usepackage{pstricks}
 \usepackage{tikz}
 \usetikzlibrary{arrows.meta}
+\usepackage{mathabx}
 \newcommand{\hide}[1]{\ignorespaces}
@@
 \newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{definition}[theorem]{Definition}
+
+% Define the fontsize in environment {verbatim}
+\makeatletter
+\def\verbatim{\small\@verbatim \frenchspacing\@vobeyspaces \@xverbatim}
+%\def\verbatim@font{\small\ttfamily}
+\makeatother
 
@@
 \hrule\vspace{1mm}
-  \begin{algorithmic}[1]
+  \begin{algorithmic}[1]\small
 \Function{$schedule$}{$ $}{}
@@
       \Else \Comment{the status is \textit{READY} or \textit{INTERRUPT}}
-  \State \Call{$reportTaskError$}{$p$}; \Comment{the task misses its deadline}
+  \State \Call{$reportTaskError$}{$p$}; \Comment{task misses its deadline}
       \EndIf
@@
 \begin{verbatim}
- class PTask | priority : Nat, 
-               period : NzNat, 
+  class PTask | priority : Nat, period : NzNat, 
                 status : Status .
@@
 \begin{verbatim}
- op [_;_] : Object Stack 
-              ~> Hardware [ctor] .
+  op [_;_] : Object Stack ~> Hardware [ctor] .
   mb ([ < O:Oid : Regs |> ; S:Stack ]) 
@@
                ~> System [ctor] .
- mb (L T STS HW < O:Oid : IntSrc |>) 
-      : System .
+  mb (L T STS HW < O : IntSrc |>) : System .
 \end{verbatim}
@@
 \begin{verbatim}
- op update_with_ : Object Timer 
-                     ~> Object .
+  op update_with_ : Object Timer ~> Object .
   ceq update < O : PTask | period : T, 
@@
      = if ST == RUNNING 
-      then < O : PTask | status 
-                           : INTERRUPT >
+       then < O : PTask | status : INTERRUPT >
        else < O : PTask |> fi [owise] .
@@
 tasks and the execution of the interrupt source. Both are modeled
-together by the following single ``standard'' tick
+together by the following single \emph{standard} tick
 rule~\cite{DBLP:journals/entcs/OlveczkyM07a}:
@@
   crl [tick]:
-   {SYSTEM} 
-   => {delta(SYSTEM, R)} in time R 
+    {SYSTEM} => {delta(SYSTEM, R)} in time R 
     if R le mte(SYSTEM) [nonexec] .
@@
          T STS HW (deltaIS(ISRC, R)))
-     if ID := (HW).getPc 
-        /\ ID :: MaybeNat .
+      if ID := (HW).getPc /\ ID :: MaybeNat .
 \end{verbatim}
@@
                           mteIr(HW)))
-     if ID := (HW).getPc 
-        /\ ID :: MaybeNat .
+      if ID := (HW).getPc /\ ID :: MaybeNat .
 \end{verbatim}
@@
   ceq {L T STS HW ISRC} |= correct
-     = if ID :: MaybeNat 
-       then shouldRun(ID, L)
+      = if ID :: MaybeNat then shouldRun(ID, L)
         else true fi
@@
 \begin{verbatim}
- (mc init |=u (correct U taskTimeout) 
-              \/ ([]correct) .)
+  (mc init |=u ([]correct) 
+               \/ (correct U taskTimeout) .)
 \end{verbatim}
@@
 \end{itemize}
-}
-
-Instantiating our model on dense time domain and choosing the
-\emph{maximal time sampling strategy}, the results of the model
-checking show that the correctness property holds in all scenarios. As
-to the schedulability property, it holds in Scenarios~(i-iii), but
-fails in Scenario~(iv).  One counterexample of the schedulability for
-Scenario~(iv), returned by the model checking command, is pictured in
-Figure~\ref{f:counterexample}, where the third task $\tau_3$ misses
-its deadline at the time $15ms$.
-
-\hide{
-\begin{figure*}[!t]
-\centering
-\begin{picture}(300,120)(0,-10)
-\thicklines
-\put(0,0){\vector(1,0){320}}
-\put(305,5){time(${\mu}s$)}
-\thinlines
-\put(0,0){\line(0,1){110}}
-\put(-25,97){task$0$}
-\put(-25,77){task$1$}
-\put(-25,57){task$2$}
-\put(-50,37){scheduling}
-\put(-45,17){switching}
-\put(-2,-8){$0$}
-
-\dashline[30]{3}(0,100)(250,100)
-\dashline[30]{3}(0,80)(280,80)
-\dashline[30]{3}(0,60)(300,60)
-\dashline[30]{3}(0,40)(210,40)
-\dashline[30]{3}(0,20)(285,20)
-
-\dashline[30]{3}(10,-10)(10,100)
-\thicklines
-\textcolor{red}{\put(0,40){\line(1,0){10}}}
-\put(8,-18){$9$}
-
-\thinlines
-\dashline[30]{3}(50,0)(50,100)
-\thicklines
-\textcolor{blue}{\put(10,100){\line(1,0){40}}}
-\put(35,-8){$2509$}
-
-\thinlines
-\dashline[30]{3}(55,-10)(55,80)
-\thicklines
-\textcolor{red}{\put(50,20){\line(1,0){5}}}
-\put(46,-18){$2513$}
-
-\thinlines
-\dashline[30]{3}(80,0)(80,80)
-\thicklines
-\textcolor{blue}{\put(55,80){\line(1,0){25}}}
-\put(65,-8){$4013$}
-
-\thinlines
-\dashline[30]{3}(85,-10)(85,60)
-\thicklines
-\textcolor{red}{\put(80,20){\line(1,0){5}}}
-\put(76,-18){$4017$}
-
-\thinlines
-\dashline[30]{3}(100,0)(100,60)
-\thicklines
-\textcolor{blue}{\put(85,60){\line(1,0){15}}}
-\put(90,-8){$5000$}
-
-\thinlines
-\dashline[30]{3}(110,-10)(110,100)
-\thicklines
-\textcolor{red}{\put(100,40){\line(1,0){10}}}
-\put(101,-18){$5009$}
-
-\thinlines
-\dashline[30]{3}(150,0)(150,100)
-\thicklines
-\textcolor{blue}{\put(110,100){\line(1,0){40}}}
-\put(135,-8){$7509$}
-
-\thinlines
-\dashline[30]{3}(155,-10)(155,60)
-\thicklines
-\textcolor{red}{\put(150,20){\line(1,0){5}}}
-\put(146,-18){$7513$}
-
-\thinlines
-\dashline[30]{3}(200,0)(200,60)
-\thicklines
-\textcolor{blue}{\put(155,60){\line(1,0){45}}}
-\put(185,-8){$10000$}
-
-\thinlines
-\dashline[30]{3}(210,-10)(210,100)
-\thicklines
-\textcolor{red}{\put(200,40){\line(1,0){10}}}
-\put(198,-18){$10009$}
-
-\thinlines
-\dashline[30]{3}(250,0)(250,100)
-\thicklines
-\textcolor{blue}{\put(210,100){\line(1,0){40}}}
-\put(230,-8){$12509$}
-
-\thinlines
-\dashline[30]{3}(255,-10)(255,80)
-\thicklines
-\textcolor{red}{\put(250,20){\line(1,0){5}}}
-\put(243,-18){$12513$}
-
-\thinlines
-\dashline[30]{3}(280,0)(280,80)
-\thicklines
-\textcolor{blue}{\put(255,80){\line(1,0){25}}}
-\put(260,-8){$14013$}
-
-\thinlines
-\dashline[30]{3}(285,-10)(285,60)
-\thicklines
-\textcolor{red}{\put(280,20){\line(1,0){5}}}
-\put(272,-18){$14017$}
-
-\thinlines
-\dashline[30]{3}(300,0)(300,60)
-\thicklines
-\textcolor{blue}{\put(285,60){\line(1,0){15}}}
-\put(289,-8){$15000$}
-
-\textcolor{red}{\put(300,60){\vector(-1,0){0}}}
-
-\end{picture}
-\caption{A Counterexample of Scenario (iv).}
-\label{f:counterexample}
-\end{figure*}
 }
@@
   \end{scope}
-
 \end{tikzpicture}
@@
 \end{figure*}
+
+Instantiating our model on dense time domain and choosing the
+\emph{maximal time sampling strategy}, the results of the model
+checking show that the correctness property holds in all scenarios. As
+to the schedulability property, it holds in Scenarios~(i-iii), but
+fails in Scenario~(iv).  One counterexample of the schedulability for
+Scenario~(iv), returned by the model checking command, is pictured in
+Figure~\ref{f:counterexample}, where the third task $\tau_3$ misses
+its deadline at the time $15ms$.
+
+\hide{
+\begin{figure*}[!t]
+\centering
+\begin{picture}(300,120)(0,-10)
+\thicklines
+\put(0,0){\vector(1,0){320}}
+\put(305,5){time(${\mu}s$)}
+\thinlines
+\put(0,0){\line(0,1){110}}
+\put(-25,97){task$0$}
+\put(-25,77){task$1$}
+\put(-25,57){task$2$}
+\put(-50,37){scheduling}
+\put(-45,17){switching}
+\put(-2,-8){$0$}
+
+\dashline[30]{3}(0,100)(250,100)
+\dashline[30]{3}(0,80)(280,80)
+\dashline[30]{3}(0,60)(300,60)
+\dashline[30]{3}(0,40)(210,40)
+\dashline[30]{3}(0,20)(285,20)
+
+\dashline[30]{3}(10,-10)(10,100)
+\thicklines
+\textcolor{red}{\put(0,40){\line(1,0){10}}}
+\put(8,-18){$9$}
+
+\thinlines
+\dashline[30]{3}(50,0)(50,100)
+\thicklines
+\textcolor{blue}{\put(10,100){\line(1,0){40}}}
+\put(35,-8){$2509$}
+
+\thinlines
+\dashline[30]{3}(55,-10)(55,80)
+\thicklines
+\textcolor{red}{\put(50,20){\line(1,0){5}}}
+\put(46,-18){$2513$}
+
+\thinlines
+\dashline[30]{3}(80,0)(80,80)
+\thicklines
+\textcolor{blue}{\put(55,80){\line(1,0){25}}}
+\put(65,-8){$4013$}
+
+\thinlines
+\dashline[30]{3}(85,-10)(85,60)
+\thicklines
+\textcolor{red}{\put(80,20){\line(1,0){5}}}
+\put(76,-18){$4017$}
+
+\thinlines
+\dashline[30]{3}(100,0)(100,60)
+\thicklines
+\textcolor{blue}{\put(85,60){\line(1,0){15}}}
+\put(90,-8){$5000$}
+
+\thinlines
+\dashline[30]{3}(110,-10)(110,100)
+\thicklines
+\textcolor{red}{\put(100,40){\line(1,0){10}}}
+\put(101,-18){$5009$}
+
+\thinlines
+\dashline[30]{3}(150,0)(150,100)
+\thicklines
+\textcolor{blue}{\put(110,100){\line(1,0){40}}}
+\put(135,-8){$7509$}
+
+\thinlines
+\dashline[30]{3}(155,-10)(155,60)
+\thicklines
+\textcolor{red}{\put(150,20){\line(1,0){5}}}
+\put(146,-18){$7513$}
+
+\thinlines
+\dashline[30]{3}(200,0)(200,60)
+\thicklines
+\textcolor{blue}{\put(155,60){\line(1,0){45}}}
+\put(185,-8){$10000$}
+
+\thinlines
+\dashline[30]{3}(210,-10)(210,100)
+\thicklines
+\textcolor{red}{\put(200,40){\line(1,0){10}}}
+\put(198,-18){$10009$}
+
+\thinlines
+\dashline[30]{3}(250,0)(250,100)
+\thicklines
+\textcolor{blue}{\put(210,100){\line(1,0){40}}}
+\put(230,-8){$12509$}
+
+\thinlines
+\dashline[30]{3}(255,-10)(255,80)
+\thicklines
+\textcolor{red}{\put(250,20){\line(1,0){5}}}
+\put(243,-18){$12513$}
+
+\thinlines
+\dashline[30]{3}(280,0)(280,80)
+\thicklines
+\textcolor{blue}{\put(255,80){\line(1,0){25}}}
+\put(260,-8){$14013$}
+
+\thinlines
+\dashline[30]{3}(285,-10)(285,60)
+\thicklines
+\textcolor{red}{\put(280,20){\line(1,0){5}}}
+\put(272,-18){$14017$}
+
+\thinlines
+\dashline[30]{3}(300,0)(300,60)
+\thicklines
+\textcolor{blue}{\put(285,60){\line(1,0){15}}}
+\put(289,-8){$15000$}
+
+\textcolor{red}{\put(300,60){\vector(-1,0){0}}}
+
+\end{picture}
+\caption{A Counterexample of Scenario (iv).}
+\label{f:counterexample}
+\end{figure*}
+}
 
@@
 \begin{theorem}
+\label{t:main}
 Our approach using untimed model checking to verify the schedulability
@@
 
+\appendix[Proof of Theorem~\ref{t:main}]
+\setcounter{theorem}{0}
+\renewcommand{\thetheorem}{\thesection.\arabic{theorem}}
+\newcommand{\lrps}[2]{\rightarrow^{#1}_{#2}}
+
+We show here a detailed proof of Theorem~\ref{t:main}.
+
+First we need to introduce some more preliminaries
+from~\cite{DBLP:journals/entcs/OlveczkyM07a}. A term $t$ is called
+\emph{ground} if it contains no variables. For a set $P\subseteq AP$
+of atomic propositions and ground terms $t,t'$, we write $t\simeq_P
+t'$ (or $t\simeq t'$ for simplicity when $P$ is implicit) if $t$ and
+$t'$ satisfy exactly the same set of propositions from $P$.
+
+The following lemma is needed to prove the time-robustness of our
+model:
+\begin{lemma}[\cite{DBLP:journals/entcs/OlveczkyM07a}]
+\label{l:timerobustness}
+Let $\cal R$ be an object-oriented specification with a standard tick
+rule, let the infinity element \verb|INF| be the only element in the
+time domain which is not a normal time value, and let the time domain
+be \emph{linear}. Then $\cal R$ is time-robust if the following
+conditions are satisfied for all appropriate ground terms $t$ and
+$r,r'$:
+
+\noindent
+(i) \verb|mte(delta(|$t$\verb|,|$r$\verb|))| $=$
+\verb|mte(|$t$\verb|) monus |$r$, for all $r\le$
+\verb|mte(|$t$\verb|)|;
+
+\noindent
+(ii) \verb|delta(|$t$\verb|,|$0$\verb|)| $= t$;
+
+\noindent
+(iii) \verb|delta(delta(|$t$\verb|,|$r$\verb|),|$r'$\verb|)| $=$
+\verb|delta(|$t$\verb|,|$r+r'$\verb|)|, for $r+r'\le$
+\verb|mte(|$t$\verb|)|;
+
+\noindent
+(iv) \verb|mte(|$\sigma(l)$\verb|)|$= 0$ for each ground instance
+$\sigma(l)$ of each left-hand side of an instantaneous rewrite rule.
+\end{lemma}
+
+Each one-step rewrite can be categorized and then tick-invariance can
+be defined:
+\begin{definition}[\cite{DBLP:journals/entcs/OlveczkyM07a}]
+A one-step rewrite $t\lrps{r}{1}t'$ using a tick rule and having
+duration $r$ is:\\
+- a \emph{maximal tick step}, written $t\lrps{r}{max}t'$, if there is
+no time value $r'>r$ such that $t\lrps{r'}{1}t''$ for some $t''$; \\
+- an \emph{$\infty$ tick step}, written $t\lrps{r}{\infty}t'$, if
+for each time value $r'>0$, there is a tick rewrite step
+$t\lrps{r'}{1}t''$; and \\
+- a \emph{non-maximal tick step} if there is a maximal tick step
+$t\lrps{r'}{max}t''$ for $r'>r$.
+\end{definition}
+\begin{definition}[\cite{DBLP:journals/entcs/OlveczkyM07a}]
+  A time-robust specification $\cal R$ is \emph{tick-invariant} with
+  respect to a set $P$ of propositions if and only if it is the case
+  that $t\simeq_P t'$ holds for each non-maximal or $\infty$ tick step
+  $t\lrps{r}{}t'$.
+\end{definition}
+
+The following lemma is needed to prove the tick-invariance of our
+defined propositions:
+\begin{lemma}[\cite{DBLP:journals/entcs/OlveczkyM07a}]
+Let $\cal R$ be a time-robust object-oriented specification with a
+standard tick rule, let the infinity element \verb|INF| be the only
+element in the time domain which is not a normal time value, and let
+the time domain be \emph{linear}. Then $\cal R$ is tick-invariant with
+respect to a set $P$ of atomic propositions if \verb|{|$t$\verb|}|
+$\simeq_P$ \verb|{delta(|$t$\verb|,|$r$\verb|)}| for all $t,r$ with
+$r<$ \verb|mte(|$t$\verb|)|.
+\end{lemma}
+
+Now we can present the detailed proof of Theorem~\ref{t:main}:
+\noindent
+\begin{IEEEproof}[Proof of Theorem~\ref{t:main}]
+first
+\end{IEEEproof}
+
 \hide{

### 2016-03-21 RMS/submission.tex
partial editting

@@
   ceq delta((L T STS HW ISRC), R)
-      = ((deltaTask(ID, L, R) 
+      = (deltaTask(ID, L, R) 
          T STS HW (deltaIS(ISRC, R)))
@@
 
-First we need to introduce some more preliminaries
-from~\cite{DBLP:journals/entcs/OlveczkyM07a}. A term $t$ is called
-\emph{ground} if it contains no variables. For a set $P\subseteq AP$
-of atomic propositions and ground terms $t,t'$, we write $t\simeq_P
-t'$ (or $t\simeq t'$ for simplicity when $P$ is implicit) if $t$ and
-$t'$ satisfy exactly the same set of propositions from $P$.
+Some more preliminaries from~\cite{DBLP:journals/entcs/OlveczkyM07a}
+are needed. A term $t$ is called \emph{ground} if it contains no
+variables. For a set $P\subseteq AP$ of atomic propositions and ground
+terms $t,t'$, we write $t\simeq_P t'$ (or $t\simeq t'$ for simplicity
+when $P$ is implicit) if $t$ and $t'$ satisfy exactly the same set of
+propositions from $P$.
 
@@
 $r,r'$:
-
-\noindent
-(i) \verb|mte(delta(|$t$\verb|,|$r$\verb|))| $=$
+\begin{enumerate}
+\item
+[(i)] \verb|mte(delta(|$t$\verb|,|$r$\verb|))| $=$
 \verb|mte(|$t$\verb|) monus |$r$, for all $r\le$
@@
 
-\noindent
-(ii) \verb|delta(|$t$\verb|,|$0$\verb|)| $= t$;
-
-\noindent
-(iii) \verb|delta(delta(|$t$\verb|,|$r$\verb|),|$r'$\verb|)| $=$
+\item
+[(ii)] \verb|delta(|$t$\verb|,|$0$\verb|)| $= t$;
+
+\item
+[(iii)] \verb|delta(delta(|$t$\verb|,|$r$\verb|),|$r'$\verb|)| $=$
 \verb|delta(|$t$\verb|,|$r+r'$\verb|)|, for $r+r'\le$
@@
 
-\noindent
-(iv) \verb|mte(|$\sigma(l)$\verb|)|$= 0$ for each ground instance
+\item
+[(iv)] \verb|mte(|$\sigma(l)$\verb|)|$= 0$ for each ground instance
 $\sigma(l)$ of each left-hand side of an instantaneous rewrite rule.
+\end{enumerate}
 \end{lemma}
@@
 \begin{IEEEproof}[Proof of Theorem~\ref{t:main}]
-first
+We first prove the time-robustness of our model by
+Lemma~\ref{l:timerobustness}.  Instantiated on the built-in dense time
+domain \verb|POSRAT-TIME-DOMAIN-WITH-INF|, our model has \verb|INF| as
+the only element which is not a normal time value. As presented in
+Section~\ref{ss:timedbehavior}, only a single standard tick rule is
+defined. Hence our model is time-robust by
+Lemma~\ref{l:timerobustness} provided conditions (i-iv) hold.
+\begin{enumerate}
+\item[(i)] We must prove \verb|mte(delta(|$s$\verb|,|$r$\verb|))| $=$
+  \verb|mte(|$s$\verb|)| \verb|monus| $r$ for all $r\le$
+  \verb|mte(|$s$\verb|)|, with $s$ being a system state of sort
+  \verb|System|.
+\end{enumerate}
+
 \end{IEEEproof}

### 2016-03-21 RMS/submission.tex
added two auxiliary lemmas

@@
 %
-%\usepackage{array}
+\usepackage{array}
 % Frank Mittelbach's and David Carlisle's array.sty patches and improves
@@
 
+\newcommand{\mteTask}[2]{\texttt{mteTask(}#1\texttt{,}#2\texttt{)}}
+\newcommand{\deltaTask}[3]{\texttt{deltaTask(}#1\texttt{,}#2\texttt{,}#3\texttt{)}}
+\newcommand{\mteIS}[1]{\texttt{mteIS(}#1\texttt{)}}
+\newcommand{\deltaIS}[2]{\texttt{deltaIS(}#1\texttt{,}#2\texttt{)}}
+\newcommand{\IntSrc}[3]{\texttt{<}#1\texttt{:IntSrc|val:}#2\texttt{,cycle:}#3\texttt{>}}
+
+Several auxiliary lemmas are proved:
+\begin{lemma}
+Given $ID$ of sort \verb|MaybeNat| and $L$ of sort \verb|TaskList|,
+\verb|mteTask(|$ID$\verb|,deltaTask(|$ID$\verb|,|$L$\verb|,|$r$\verb|))|
+$=$ \verb|mteTask(|$ID$\verb|,|$L$\verb|)| \verb|monus| $r$ for all
+$r\le$ \verb|mteTask(|$ID$\verb|,|$L$\verb|)|.
+\end{lemma}
+\begin{IEEEproof}
+If $ID=$ \verb|none|, the case is trivial. By definition,
+\verb|mteTask(none,deltaTask(none,|$L$\verb|,|$r$\verb|))| $=$
+\verb|mteTask(none,|$L$\verb|)| $=$ \verb|INF| $=$
+\verb|mteTask(none,|$L$\verb|)| \verb|monus| $r$. Otherwise, $ID=$
+\verb|some| $N$ with $N$ of sort \verb|Nat|. Assume that the
+\verb|cnt| of the $N$th task in $L$ is
+\verb|[|$r_e$\verb|/|$C$\verb|]|. Then by definition,
+\verb|deltaTask(|$ID$\verb|,|$L$\verb|,|$r$\verb|)| $= L'$, where the
+$N$th task in $L'$ has \verb|cnt| value being
+\verb|[|$(r_e+r)$\verb|/|$C$\verb|]|. Hence,
+\begin{IEEEeqnarray*}{Cl}
+  & \mteTask{ID}{\deltaTask{ID}{L}{r}}
+\\  
+= & \mteTask{ID}{L'}
+\\
+= & C~\verb|monus|~(r_e+r) 
+= (C~\verb|monus|~r_e)~\verb|monus|~r 
+\\
+= & \mteTask{ID}{L}~\verb|monus|~r~.
+\end{IEEEeqnarray*}
+\end{IEEEproof}
+\begin{lemma}
+Given $ISRC$ of class \verb|IntSrc| representing an reasonable state
+of interrupt source in our model, \mteIS{\deltaIS{$ISRC$}{$r$}} $=$
+\mteIS{$ISRC$} \verb|monus| $r$ for all $r\le$ \mteIS{$ISRC$}.
+\end{lemma}
+\begin{IEEEproof}
+A reasonable $ISRC$ must be of the form \IntSrc{$O$}{$v$}{$T$} with
+$v\le T$. Thus by definition, 
+\begin{IEEEeqnarray*}{Cl}
+  & \mteIS{\deltaIS{ISRC}{r}}
+\\  
+= & \mteIS{\IntSrc{O}{(v~\texttt{monus}~r)}{T}}
+\\
+= & v~\verb|monus|~r
+= \mteIS{ISRC}~\verb|monus|~r~.
+\end{IEEEeqnarray*}
+\end{IEEEproof}
+
 Now we can present the detailed proof of Theorem~\ref{t:main}:

### 2016-03-22 RMS/submission.tex
proof to condition (ii)

@@
 \newcommand{\IntSrc}[3]{\texttt{<}#1\texttt{:IntSrc|val:}#2\texttt{,cycle:}#3\texttt{>}}
+\newcommand{\mteIr}[1]{\texttt{mteIr(}#1\texttt{)}}
+\newcommand{\mteS}[1]{\texttt{mte(}#1\texttt{)}}
+\newcommand{\deltaS}[2]{\texttt{delta(}#1\texttt{,}#2\texttt{)}}
 
@@
 \begin{lemma}
+\label{l:auxtask}
 Given $ID$ of sort \verb|MaybeNat| and $L$ of sort \verb|TaskList|,
@@
 \begin{lemma}
+\label{l:auxis}
 Given $ISRC$ of class \verb|IntSrc| representing an reasonable state
@@
 \end{IEEEproof}
+\begin{lemma}
+\label{l:auxhw}
+Given $HW$ of sort \verb|Hardware|, for all $r\le$ \mteIr{$HW$},
+\mteIr{$HW$} $=$ \mteIr{$HW$} \verb|monus| $r$.
+\end{lemma}
+\begin{IEEEproof}
+  It concludes by discussing on whether there exists an interrupt
+  request detected in $HW$.
+\end{IEEEproof}
 
@@
 Lemma~\ref{l:timerobustness} provided conditions (i-iv) hold.
-\begin{enumerate}
-\item[(i)] We must prove \verb|mte(delta(|$s$\verb|,|$r$\verb|))| $=$
-  \verb|mte(|$s$\verb|)| \verb|monus| $r$ for all $r\le$
+
+Condition~(i). We must prove \verb|mte(delta(|$s$\verb|,|$r$\verb|))|
+$=$ \verb|mte(|$s$\verb|)| \verb|monus| $r$ for all $r\le$
 \verb|mte(|$s$\verb|)|, with $s$ being a system state of sort
-  \verb|System|.
-\end{enumerate}
-
+\verb|System|. Let $s$ be of the form
+$(\mathit{L}~\mathit{T}~\mathit{STS}~\mathit{HW}~\mathit{ISRC})$ and
+$\mathit{ID}=\verb|(|\mathit{HW}\verb|).getPc|$. We only consider the
+case $\mathit{ID}$\verb|::MaybeNat| in detail, while the other case
+$\mathit{ID}$\verb|::Oid| is similar. By definitions of \verb|mte| and
+\verb|delta|,
+\begin{IEEEeqnarray*}{Cl}
+  & \mteS{\deltaS{s}{r}}
+\\  
+= & \mteS{\deltaTask{ID}{L}{r}
+\\
+  & \;\;\;\;\;\;\;\;\;T~STS~HW~\deltaIS{ISRC}{r}}
+\\
+= & \verb|minimum(|\mteTask{ID}{\deltaTask{ID}{L}{r}}\verb|,|
+\\
+  & \verb|        |\mteIS{\deltaIS{ISRC}{r}}\verb|,|
+\\
+  & \verb|        |\mteIr{HW}\verb|)|~.
+\end{IEEEeqnarray*}
+By Lemmas~\ref{l:auxtask},~\ref{l:auxis} and~\ref{l:auxhw}, it can be
+further reduced:
+\begin{IEEEeqnarray*}{Cl}
+  & \mteS{\deltaS{s}{r}}
+\\  
+= & \verb|minimum(|\mteTask{ID}{L}~\verb|monus|~r~\verb|,|
+\\
+  & \verb|        |\mteIS{ISRC}~\verb|monus|~r~\verb|,|
+\\
+  & \verb|        |\mteIr{HW}~\verb|monus|~r~\verb|)|
+\\
+= & \verb|minimum(|\mteTask{ID}{L}\verb|,|
+\\
+  & \verb|        |\mteIS{ISRC}\verb|,|
+\\
+  & \verb|        |\mteIr{HW}\verb|)|~\verb|monus|~r
+\\
+= & \mteS{s}~\verb|monus|~r~.
+\end{IEEEeqnarray*}
+
+Condition~(ii) follows from the fact that $r+0=r$ and
+$r$~\verb|monus|~$0=r$ for all $r$.
 \end{IEEEproof}

### 2016-03-22 RMS/submission.tex
finished the proof

@@
 \begin{lemma}[\cite{DBLP:journals/entcs/OlveczkyM07a}]
+\label{l:tickinv}
 Let $\cal R$ be a time-robust object-oriented specification with a
@@
 $r$~\verb|monus|~$0=r$ for all $r$.
+
+Condition~(iii). We must prove \deltaS{\deltaS{$s$}{$r$}}{$r'$} $=$
+\deltaS{$s$}{$r+r'$} for all $r+r'\le$ \mteS{$s$}, with $s$ being a
+system state of sort \verb|System|. Using the same symbols as in~(i),
+we only consider the case $\mathit{ID}$\verb|::MaybeNat| in detail. 
+By definition, the left side of the equation
+\begin{IEEEeqnarray*}{Cl}
+  & \deltaS{\deltaS{s}{r}}{r'}
+\\  
+= & \verb|(|\deltaTask{ID}{\deltaTask{ID}{L}{r}}{r'}
+\\
+  & \verb| |~T~STS~HW~\deltaIS{\deltaIS{ISRC}{r}}{r'}\verb|)|~\mbox{,}
+\end{IEEEeqnarray*}
+and the right side of the equation
+\begin{IEEEeqnarray*}{Cl}
+  & \deltaS{s}{r+r'}
+\\  
+= & \verb|(|\deltaTask{ID}{L}{r+r'}
+\\
+  & \verb| |~T~STS~HW~\deltaIS{ISRC}{r+r'}\verb|)|~\mbox{.}
+\end{IEEEeqnarray*}
+\deltaTask{$ID$}{\deltaTask{$ID$}{$L$}{$r$}}{$r'$} $=$
+\deltaTask{$ID$}{$L$}{$r+r'$} holds by the associativity of $+$, while
+\deltaIS{\deltaIS{$ISRC$}{$r$}}{$r'$} $=$ \deltaIS{$ISRC$}{$r+r'$}
+holds since $(v$ \verb|monus| $r)$ \verb|monus| $r'$ $=$ $v$
+\verb|monus| $(r+r')$ with $v$ of sort \verb|Time|. Thus
+condition~(iii) holds.
+
+Condition~(iv). We show that \verb|mte| of each instance of the
+left-hand side of any instantaneous rule is $0$. For example,
+considering the (conditional) rule \verb|interrupt-request|, with its
+condition \verb|(|$ISRC$\verb|).timeout|, we know that the \verb|val|
+of $ISRC$ equals $0$. Therefore,
+\begin{IEEEeqnarray*}{Cl}
+  & \mteS{L~T~STS~HW~ISRC}
+\\  
+= & \verb|minimum(|\mteTask{ID}{L}\verb|,|
+\\
+  & \verb|        |\mteIS{ISRC}\verb|,| \mteIr{HW}\verb|)|
+\\
+= & \verb|minimum(|\mteTask{ID}{L}\verb|,|~0~\verb|,| \mteIr{HW}\verb|)|
+\\
+= & 0~\mbox{.}
+\end{IEEEeqnarray*}
+The other rules can be similarly proved with their conditions. Hence
+our model is time-robust by Lemma~\ref{l:timerobustness}.
+
+Finally we prove the tick-invariance of the propositions used to
+analyze our model, i.e. \verb|taskTimeout| and \verb|correct|. By
+Lemma~\ref{l:tickinv}, we must prove
+$\verb|{|s\verb|}|\simeq_P\verb|{|\deltaS{s}{r}\verb|}|$ with $s$ of
+sort \verb|System| and $r<\mteS{s}$, that is, applying a tick rule
+advancing $r$ time units will not change the value of each
+proposition. Let $s$ be
+$(\mathit{L}~\mathit{T}~\mathit{STS}~\mathit{HW}~\mathit{ISRC})$ and
+$\verb|(|\mathit{HW}\verb|).getPc|=\mathit{ID}$.
+\begin{itemize}
+\item \verb|taskTimeout| holds if and only if $L$ contains an
+  \verb|error|. Since \verb|delta| does not produce or eliminate
+  \verb|error| in $L$, \verb|taskTimeout| holds in $s$ if and only if
+  \verb|taskTimeout| holds in $\deltaS{s}{r}$ for any $r<\mteS{s}$,
+  which means that our model is tick-invariant with respect to
+  \verb|taskTimeout|.
+\hide{ 
+In our model, an \verb|error| cannot be eliminated by any operations,
+hence, if \verb|taskTimeout| holds in $s$, it must hold in
+$\deltaS{s}{r}$. On the other hand, \verb|error| can pop up only when
+operation \verb|update_with_| is applied, i.e., only when the
+instantaneous rule \verb|interrupt-handle| applies. If
+\verb|taskTimeout| does not hold in $s$, it will not hold either in
+$\deltaS{s}{r}$ for any $r<\mteS{s}$, since instantaneous rules cannot
+apply in $\deltaS{s}{r'}$ for any $r'<\mteS{s}$ by time-robustness.}
+\item The value of \verb|correct| depends on $ID$ and the status of
+  each task in $L$. Similarly, \verb|delta| does not change $ID$ or
+  the status of any task in $L$, hence \verb|correct| holds in $s$ if
+  and only if \verb|correct| holds in $\deltaS{s}{r}$ for any
+  $r<\mteS{s}$. It concludes the tick-invariance of \verb|correct|.
+\end{itemize}
+
+Therefore, by Theorem~\ref{t:completeness}, our approach using untimed
+model checking to verify the schedulability and the correctness is
+complete.
 \end{IEEEproof}

### 2016-03-23 RMS/submission.tex
added related work and some comparison

@@
 
+\jx{
+
+  Using a model-based checking approach enhance the ability to check other scheduling
+  algorithms.
+
+  The chinese one:
+
+  - the model is ideal
+
+  - it should give a model to each task. And given different task sets, the model should be
+  adjusted. But our model need only an instantiation of the task set.
+
+  - the time domain. It uses a global integer to model the time, hence the time dense
+  must be discrete. But our model use a generic time domain, which can be instantiated on
+  both dense and discrete domain.
+}
+
 \hide{

### 2016-03-24 RMS/submission.tex
modified related work partialy.

@@
 with those theoretical analyses, our approach based on formal modeling
-and verification has a great advantage that if our schedulability test
-answers ``no'', it returns at the same time a real counterexample,
-which is able to guide our engineer to adjust the design.
+and verification has three advantages. One is that if our
+schedulability test answers ``no'', it returns at the same time a real
+counterexample, which is able to guide our engineer to adjust the
+design, by changing either the priorities or even the scheduling
+algorithm. The second is that, when a fresh scheduling strategy is
+applied, our analysis can be adjusted only by modifying the model,
+while theoretical approaches may need thorough analyses and reasoning.
+The last one is that, considering overhead and details of hardware do
+introduce some kind of non-determinism into the model. For example, in
+our model, if the running task is complete ``right'' at the time when
+an interrupt request is performed, two different behaviors are
+possible: (i) the system performs task switching, during which the
+interrupt request is masked, hence the scheduling may be delayed; (ii)
+the system answers the interrupt request immediately.
 
@@
 \deltaS{$s$}{$r+r'$} for all $r+r'\le$ \mteS{$s$}, with $s$ being a
-system state of sort \verb|System|. Using the same symbols as in~(i),
+system state of sort \verb|System|. Using the same notations as in~(i),
 we only consider the case $\mathit{ID}$\verb|::MaybeNat| in detail. 
@@
 
-  Using a model-based checking approach enhance the ability to check other scheduling
-  algorithms.
+  Using a model-based checking approach enhance the ability to check
+  other scheduling algorithms.
+
+  About non-determinism: task finishes right at the time interrupt
+  comes, theoretical results cannot solve
 

### 2016-03-24 RMS/submission.tex
finished related work

@@
 \end{itemize}
+Note that thanks to the powerful expressivity of Real-Time Maude, we
+only need to define an initial state of sort \verb|System| to specify
+a given task set. No necessity to modify the model is needed.
 
@@
 introduce some kind of non-determinism into the model. For example, in
-our model, if the running task is complete ``right'' at the time when
-an interrupt request is performed, two different behaviors are
+our model, if the running task is complete \emph{right} at the time
+when an interrupt request is performed, two different behaviors are
 possible: (i) the system performs task switching, during which the
 interrupt request is masked, hence the scheduling may be delayed; (ii)
-the system answers the interrupt request immediately.
-
-\cite{DBLP:conf/iceccs/CuiDT14} and~\cite{TianD2011} also made use of
+the system answers the interrupt request immediately, the switching
+being delayed. Tackling such non-determinism via theoretical analyses
+seems more complicated than our automatic approach.
+
+\cite{TianD2011} and~\cite{DBLP:conf/iceccs/CuiDT14} also made use of
 model checking to analyze the RMS algorithm along the same line but
-with different languages and tools. They considered only the ideal
-setting as in~\cite{DBLP:journals/jacm/LiuL73}, instead of an
-implementation which contains much more complex details. Our model of
-the implementation easily degenerates to a model of the RMS algorithm,
-if we let the times for scheduling and switching be zero.
+with different languages and tools. The RMS algorithm is analyzed
+using an extension of SPIN~\cite{DBLP:journals/tse/Holzmann97}
+in~\cite{TianD2011}, while the logic programming language
+TMSVL~\cite{DBLP:conf/icfem/HanDW12} and its model checker are applied
+in~\cite{DBLP:conf/iceccs/CuiDT14}. The work presented
+in~\cite{TianD2011} and~\cite{DBLP:conf/iceccs/CuiDT14} has two main
+differences with ours. The first one, which is also the motivational
+one, is that they considered only the ideal setting of the algorithm
+as in~\cite{DBLP:journals/jacm/LiuL73}, instead of an implementation
+which contains much more complex details. In fact, our model of the
+implementation can easily degenerate to a model of the RMS algorithm,
+if we let the times for scheduling and switching be zero. The other
+difference is that when adding a new task into the task set, the
+models in~\cite{TianD2011} and~\cite{DBLP:conf/iceccs/CuiDT14} should
+be modified by explicitly defining a sub-model of the new task and its
+behaviors. In particular, the scheduling part of the model
+in~\cite{TianD2011} needs adjustments as well to include a new
+task. Nevertheless, a new task set is specified in our approach merely
+by giving a new initial state, without necessity to modify the model,
+as already emphasized in Section~\ref{ss:results}. On the other hand,
+\cite{TianD2011} used a discrete time domain in the model, while we
+employ a generic time domain, which is flexible to be instantiated on
+either discrete or dense ones. In~\cite{DBLP:conf/iceccs/CuiDT14}, the
+time domain is dense, and a modeling strategy like our maximal time
+sampling strategy is applied to reduce the state space. However, a
+completeness statement like Theorem~\ref{t:main} was not given
+in~\cite{DBLP:conf/iceccs/CuiDT14}.
 

### 2016-03-25 Maude/maude24/case-generate.cpp
added codes to evaluate the RMS model

@@ -1,0 +1,47 @@
+#include <iostream>
+#include <ctime>
+#include <cstdlib>
+
+using namespace std;
+
+unsigned long long lcm(unsigned long long a, unsigned long long b) {
+    unsigned long long m = a, n = b;  
+    /* a, b不相等，大数减小数，直到相等为止。*/    
+    while (a != b) {   
+        if (a > b)  a = a - b;        
+        else b = b - a;
+    }
+   return (m * n / a);
+}
+
+int main() {
+    int N = 5;
+    int periods[N];
+    srand((unsigned)time(NULL));
+    for(int i = 0; i < N; i++) {
+        periods[i] = 1 + (rand() % 200);
+    }
+    
+    int i,j,temp;
+    for (i = 0 ; i < N; i++) {
+        for (j = 0; j < N - 1 - i; j++) {
+            if (periods[j] > periods[j+1]) {
+                temp = periods[j];
+                periods[j] = periods[j+1];
+                periods[j+1] = temp;
+            }
+        }
+    }
+    
+    
+    for(int i = 0; i < N; i++) {
+        cout << periods[i] << endl;
+    }    
+
+    unsigned long long macro = 1;
+    for (i = 0; i < 3; i++) {
+        macro = lcm(macro, periods[i]);
+    }
+    cout << macro << endl;
+    return 0;
+}

### 2016-03-25 Maude/maude24/evaluate.cpp

@@ -1,0 +1,39 @@
+#include <iostream>
+#include <fstream>
+#include <string>
+
+using namespace std;
+int main() {
+  ifstream filein("test1.log");
+
+  string pre2Line = "", preLine = "", curLine = "";
+  bool found = false; // the "untimed model check" line is found
+  int firstPos, lastPos;
+  int lineNum = 0;
+  string timeStr;
+  unsigned long time;
+  bool modelCheckResult;
+  for ( ; getline(filein, curLine); ) {
+    if (found) {
+      lineNum++;
+      if (lineNum == 3) {
+	if (curLine.size() < 25) modelCheckResult = true;
+	else modelCheckResult = false;
+	break;
+      }
+    } else if (curLine.size() >= 7 && curLine[0] == 'U' && curLine[1] == 'n') {
+      found = true;
+      lineNum = 0;
+      firstPos = pre2Line.find('(') + 1;
+      lastPos = pre2Line.find("ms real", firstPos);
+      timeStr = pre2Line.substr(firstPos, lastPos - firstPos);
+      time = stoul(timeStr);
+    } else {
+      pre2Line = preLine;
+      preLine = curLine;
+    }
+  }
+  cout << "result: " << (modelCheckResult ? "true" : "false") << endl;
+  cout << "time: " << time << endl;
+  return 0;
+}

### 2016-03-25 Maude/maude24/test-run.cpp

@@ -1,0 +1,10 @@
+#include <iostream>
+#include <stdlib.h>
+
+using namespace std;
+
+int main() {
+  system("./maude.linux64 real-time-maude.maude RMS.maude case.maude > test1.log");
+  cout << "good" << endl;
+  return 0;
+}

### 2016-03-26 Maude/maude24/case-generate.cpp
modified the testing codes

@@ -1,6 +1,8 @@
 #include <iostream>
 #include <ctime>
 #include <cstdlib>
+#include <fstream>
+#include <math.h>
 
 using namespace std;
 
@@ -15,12 +17,31 @@ unsigned long long lcm(unsigned long long a, unsigned long long b) {
 }
 
 int main() {
+  /*
     int N = 5;
-    int periods[N];
+    int TESTNUM = 50;
+    int caseNum = 0;
+  */
+
+  //  int N = 10;
+  int N;
+  int TESTNUM = 10;
+  int caseNum = 0;
+
+  for (N = 5; N <= 20; N++) { 
+    cout << "Task number is: " << N << endl;
+    
     srand((unsigned)time(NULL));
+
+    for (caseNum = 0; caseNum < TESTNUM; caseNum++ ) {
+
+      
+    int periods[N];
     for(int i = 0; i < N; i++) {
-        periods[i] = 1 + (rand() % 200);
+      //        periods[i] = 1 + (rand() % 100);
+      periods[i] = pow(2, i);
     }
+    
     
     int i,j,temp;
     for (i = 0 ; i < N; i++) {
@@ -34,14 +55,87 @@ int main() {
     }
     
     
-    for(int i = 0; i < N; i++) {
-        cout << periods[i] << endl;
-    }    
-
     unsigned long long macro = 1;
-    for (i = 0; i < 3; i++) {
+    for (i = 0; i < N; i++) {
         macro = lcm(macro, periods[i]);
     }
+    cout << "round: " << caseNum << endl;
     cout << macro << endl;
+
+    int computations[N];
+    for(int i = 0; i < N; i++) {
+        computations[i] = 1 + (rand() % (5000 * periods[i] / N));
+    }
+    
+    for(int i = 0; i < N; i++) {
+      cout << "period: " << periods[i] * 5 << ", computation: " << computations[i] << endl;
+    }
+
+
+    // write to the file
+
+    //    ofstream out(to_string(N) + "/test-case-" + to_string(caseNum) + ".maude");
+    ofstream out("pow/" + to_string(N) + "-" + to_string(caseNum) + ".maude");
+    if (out.is_open()) {
+      out << "set trace off ." << endl;
+      out << "set break off ." << endl;
+      out << "set profile off ." << endl;
+      out << endl;
+
+      out << "(tomod INSTANTIATION is " << endl;
[…]

### 2016-03-26 Maude/maude24/test-run.cpp

@@ -4,7 +4,25 @@
 using namespace std;
 
 int main() {
-  system("./maude.linux64 real-time-maude.maude RMS.maude case.maude > test1.log");
-  cout << "good" << endl;
+  int TESTNUM = 1;
+  int TIME = 1;
+  string command;
+
+  for (int N = 5; N <= 20; N++) {
+    cout << "task number " << N << " start:" << endl;
+  for (int i = 0; i < TESTNUM; i++) {
+    for (int j = 0; j < TIME; j++) {
+      command = "./maude.linux64 real-time-maude.maude RMS.maude pow/"
+	+ to_string(N) + "-" + to_string(i) + ".maude > pow-result/"
+	+ to_string(N) + "-" + to_string(i) + "-" + to_string(j) + ".result";
+      system(command.c_str());
+      cout << "Task number " << N << " test " << i << " round " << j << " done" << endl;
+    }
+    cout << "Task number " << N << " test " << i << " is done!" << endl;
+  }
+
+  cout << "Task number " << N << " done!" << endl << endl;
+  }
+
   return 0;
 }

### 2016-03-27 RMS/corrections.tex
up to modeling the hardware

@@
 
+ANSWER: TODO
+
 2) One of my biggest problems with the theoretical part of this work
@@
 in a technical report) a detailed proof.
+
+ANSWER: The detailed proof is now included in the appendix. It is true
+that readers may be interested in the detailed proof of Theorem~2 to
+feel convinced of the completeness of our approach. However, the proof
+needs a bit more theoretical background about rewriting logic and more
+details of our model, which we have simplified in the submission to
+ease the understanding of our approach. We would prefer to refer the
+detailed proof to a non-anonymous technical report, if possible, in
+the final version.
 
@@
 the presentation of the implementation.
+
+ANSWER: TODO. To revise the modeling section.
 
@@
 
+ANSWER: The related work section is now improved. More comparisons
+with the theoretical approaches and with [24,25] are added. The
+differences with [24,25] in the models and in the way of modeling are
+mainly discussed. On the other hand, it is a bit difficult to compare
+the efficiency and scalability between [24,25] and our approach. One
+reason is that we have a different setting with [24] and [25], because
+the objectives are different: we aim at verifying an RMS implemention
+from a real-world real-time system, while [24] and [25] targeted the
+RMS algorithm itself. Another reason is that [24] and [25] presented
+no discussion on the efficiency and scalability. Furthermore, they use
+\verb|TMSVL| and an extension of SPIN, respectively, as verification
+tools, which are not open-source, making it unable to re-implement
+their work.
+
 - Page 8, Conclusions. Where in the paper do you show that the details
@@
 briefly discussed.
+
+ANSWER: The statement has been corrected. The work presented in this
+submission aims at modeling and verifying a realistic RMS
+implementation in an industrial avonic system. It is a piece of real
+work in the industry. Even though we believe that our approach could
+be applied to other systems as well, it means more to that specific
+one. In this sense, ``sufficient'' means that the details described in
+our model meet the requirements and expectations from the users and
+the engineers.
 
@@
 
+ANSWER: TODO. to make the paper self-contained.
+
 Another concern is that the significance of the paper could be much
@@
 rather than a general method for modelling and analyzing RMS
-implementations.  Also, the discussion about soundness and
+implementations.
+
+ANSWER: Yes, we agree that we have two choices to do the work
+presented in the paper: one is to develop a general way to model RMS
+algorithms or implementations, and then instantiate the general model
+to get a concrete one for our target system; the other is to shape an
+accurate model of the target system directly. To us, there is a trade
+off between these two directions. We chose the latter with some
+concerns. By our experience, the engineers, who write the codes, and
+those, who are in charge of verifying the system or the codes, are
+usually not the same persons. When a verification engineer models a
+system, he is actually abstacting the system or the codes. It is
+difficult to ensure that the model behaves the same as the system or
+the codes.  And it is more difficult to let other engineers and users
+believe that the model behaves the same as the system or the
+codes. Furthermore, the developers and users hope that the model
+behaves not only the same as what they had in mind, but also the same
+as what is written in the codes. A way out is to make the model not
+only behave like the codes, but also ``look'' like the codes. This
+requires the model to be as accurate as possible. It makes the model
+specific, but improves the engineers' confidence in the model and the
+verification results. That is also why we emphasize the
+correspondences between the functions in the model and the lines in
+the pseudocode, when we introduce our model in Section~IV. On the
+other hand, we are also interested in the first choice. This will be
+the future work and we would try to get a better balance between them.
+
+Also, the discussion about soundness and
 completeness of the analysis (section V.C) is not fully developed and,
@@
 general result.
+
+ANSWER: The section about soundness and completeness is now made more
+self-contained. The detailed proof of Theorem~2 is included in the
+appendix. On the other hand, since we chose the accurate way to
+achieve the model as discussed above, yes, the proof is a specific
+one.
 
@@
 Detailed comments
+\begin{itemize}
+\item
+Section II.B
 
-Section II.B \\ In the definition of IR, it is not clear what s and s'
-are. I guess they are states, but the concept of state was not
-introduced. \\ In the definition of a class, the authors should
+- In the definition of $IR$, it is not clear what $s$
+and $s'$ are. I guess they are states, but the concept of state was
+not introduced.
+
+ANSWER: TODO
+
+- In the definition of a class, the authors should
 specify that a class includes a collection of rules, otherwise this
@@
 
-Section III \\ Page 2 right column, line -24 The implementation is
-shown as schedule() in Figure 1 -> The pseudocode of schedule() is
+ANSWER: TODO
+
+\item
+Section III
+
+- Page 2 right column, line -24: The implementation is shown as
+schedule() in Figure 1 $\rightarrow$ The pseudocode of schedule() is
 shown in Figure 1
 
-Section IV.A \\ I don't understand the meaning of [ctor] in the
-definition of some operations (maybe because I have no specific
-background on Maude). I could not find the explanation of this writing
-in the introduction to Maude. \\ For the stack sort, the authors
-mention operations push, pop and peek, but then you don't write the
-definitions of these operations. Instead, they write the definitions
-of bottom and \#, which are not explained in the text. This part should
-be made clearer. \\ Also, the meaning of NzNat is not explained.
+ANSWER: It is done.
 
-Section V.C \\ In the statement of theorem 1, the definition of
-time-robust real-time rewrite theory is missing. Also, the meaning of
-tick-stabilizing atomic propositions is not defined. \\ This makes the
-section not self-contained. \\ The proof of theorem 2 is missing. The
-authors just indicate how the proof could be developed, but they do
-not develop it. A possibility would be to point to a document where
-this proof has been developed.
+\item
+Section IV.A
+
+- I don't understand the meaning of [ctor] in the definition of some
+operations (maybe because I have no specific background on Maude). I
+could not find the explanation of this writing in the introduction to
+Maude.
+
+ANSWER: TODO
+
+- For the stack sort, the authors mention operations push, pop and
+peek, but then you don't write the definitions of these
+operations. Instead, they write the definitions of bottom and \#,
+which are not explained in the text. This part should be made clearer.
+
+ANSWER: TODO
+
+- Also, the meaning of NzNat is not explained.
+
+ANSWER: TODO
+
+\item
+Section V.C
+
+- In the statement of theorem 1, the definition of time-robust
+real-time rewrite theory is missing. Also, the meaning of
+tick-stabilizing atomic propositions is not defined. This makes the
+section not self-contained.
+
+ANSWER: TODO
+
+- The proof of theorem 2 is missing. The authors just indicate how the
+proof could be developed, but they do not develop it. A possibility
+would be to point to a document where this proof has been developed.
+
+ANSWER: The detailed proof is now included in the appendix.  The
+detailed proof requires a bit more theoretical background about
+rewriting logic and more details of our model, which we tried to
+simplify in the submission to ease the understanding of our
+approach. We would prefer to refer the detailed proof to a
+non-anonymous technical report, if possible, in the final version.
+\end{itemize}
 
@@
 1. Rate-monotonic scheduling is a very simple scheduling and has been
-sufficiently invesigated in the field of embedded system, the authors
+sufficiently investigated in the field of embedded system, the authors
 claim the innovation of this paper as the implementation using
@@
 
-2. RMS has many different realizatio methods, no comparison is given
+ANSWER: We agree that RMS is a very simple scheduling and is the
+optimum at the same time among the fixed-prority ones, making it
+widely applied and sufficiently investigated. Besides the ideal
+setting, the schedulability of RMS was also investigated under
+different kinds of implementations with consideration about overhead,
+as we discuss in the related work section (Section VI). Despite the
+reason that the existing results do not fit our target system using
+RMS, the most important motivation to develop the work presented is
+that, we aim at verifying the system not only for the schedulability,
+but also for the correctness. That is, we want to verify that the
+target system does schedule the tasks under the RMS algorithm. The
+work presented should be seen as a verification problem, instead of a
+schedulability test.
+
+2. RMS has many different realization methods, no comparison is given
 to justify the strong point of real-time maude when applied to RMS.
+
+ANSWER: The comparison is given in the related work section (Section
+VI). We would say that we are not implementing RMS algorithm in
+Real-Time Maude. In fact, we are using Real-Time Maude to model an
+realistic implementation of RMS from an industrial avionic
+system. There is no theoretical reason telling us that we have to use
+Real-Time Maude to model the RMS implementation. However, the existing
+verification work as far as we know cannot fit our needs, as discussed
+in Section VI. Therefore, we developed the work in the paper, as a
+piece of real work in the industry.
 
@@
 
+ANSWER: As an industrial application, we are not trying to make the
+problem as difficult as possible. Instead, we are trying to simplify
+the model so that the existing tools are able to solve, while the
+target system satisfies the assumptions on the model so that the
+verification results are trustworthy. On the other hand, the
+assumptions are not so rigid. For example, the mask mechanism
+considered as hardware details makes the job initiation times of task
+$\tau_i$ possibly not equal to $kT_i$, implying that the deadlines of
+the jobs may be not equal to $(k+1)T_i$ (see assumption A1'). Another
+example is that non-determinism exists in our model, as discussed in
+Section VI.
+
 4. The description in section IV (A-E) is trivial, it can only be
 viewed as a simple application of the rewriting logic.
+
+ANSWER: Yes, we agree that this is an application of rewriting
+logic. In this paper, we do apply the existing theories and techniques
+of rewriting logic to solve a real industrial problem, which has not
+yet been investigated by this sort of techniques, achieving an
+industrial contribution.
 
@@
 
+ANSWER: We do not agree that we should illustrate the mechanism behind
+the model checking commands, since the model checker is not part of
+our contributions in the paper.
+
 Based on the above comments, I thinks this paper is only a simple
 application [26] and [27] in RMS, hence I do not recommend this paper.
+
+ANSWER: ?
 

### 2016-03-27 RMS/submission.tex
up to modeling the hardware

@@
 formal modeling language and analysis tool for real-time systems, to
-model a realistic implementation of RMS, which serves as a simplified
+model a realistic implementation of RMS that serves as a simplified
 operating system within an avionic control system, and then verify
@@
   declarations of \emph{sorts}, \emph{subsorts} and \emph{function
-    symbols}. The function symbols are allowed to be mixfix.
+    symbols}. The function symbols are allowed to be mixfix, in which
+  case underscores ``\verb|_|'' indicate the positions of parameters.
+  \emph{Terms} are expressions built from function symbols and
+  variables.
 \item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
@@
   such as associativity, commutativity and identity.  $(\Sigma, E\cup
-  A)$ models the system's ``static'' states as an algebraic data type,
-  and is equipped with a built-in specification of a sort \verb|Time|.
+  A)$ models the system's ``static'' states as terms of some sort, and
+  is equipped with a built-in specification of a sort \verb|Time|.
 \item $IR$ is a set of \emph{labeled conditional rewrite rules}
   specifying the system's local transitions. Each rule has the form
-  $[l]~:~s\rightarrow s'\mbox{ \textbf{if} }\bigwedge^n_{j=1}cond_j$,
+  $[l]~:~t\rightarrow t'\mbox{ \textbf{if} }\bigwedge^n_{j=1}cond_j$,
   where each $cond_j$ is an equality $u_j=v_j$ and $l$ is a
-  \emph{label}. Such a rule specifies an \emph{instantaneous
-    transition}, without consuming time, from an instance of $s$ to
-  the corresponding instance of $s'$, \emph{provided} the conditions
-  hold.
+  \emph{label}, $t,t'$ are terms. Such a rule specifies an
+  \emph{instantaneous transition}, without consuming time, from an
+  instance of $t$ to the corresponding instance of $t'$,
+  \emph{provided} the conditions hold.
 \item $TR$ is a set of (\emph{labeled}) \emph{tick rules} of the form
-  $[l]~:~\{s\}\rightarrow\{s'\} \mbox{ \textbf{in time} }t\mbox{
+  $[l]~:~\{s\}\rightarrow\{s'\} \mbox{ \textbf{in time} }r\mbox{
   \textbf{if} }cond$ that specify \emph{timed transitions}, which
-  advances time in the \emph{entire} state $s$ by $t$ time units. $IR$
-  and $TR$ together model the ``dynamic'' behaviors of the system.
+  advances time by $r$ time units in the \emph{entire} state modeled
+  by term $s$. $IR$ and $TR$ together model the ``dynamic'' behaviors
+  of the system.
 \end{itemize}
@@
 In rewriting logic, rewrite rules are applied non-deterministically,
-that is, when several rules can be applied on a given $s$, any of them
-may be chosen. Hence non-deterministic behaviors can be modeled
+that is, when several rules can be applied on a given term $t$, any of
+them may be chosen. Hence non-deterministic behaviors can be modeled
 naturally in Real-Time Maude.  Real-Time Maude also supports
@@
 where $O$, of sort \verb|Oid|, is the object's \emph{identifier}, and
-$val_i$ is the value of the attribute $att_i$ with $i\in [1,n]$. A
-\emph{subclass} inherits all the attributes and rules of its
-superclasses.
+$val_i$ is the value of the attribute $att_i$ with $i\in [1,n]$. Rules
+can be defined on a given class. A \emph{subclass} inherits all the
+attributes and rules of its superclasses.
 
@@
 \label{s:imp}
-The implementation is in an industrial avionic control system.
-Interrupts would be triggered by, and only by, the clock every $T$,
-which we call \emph{interrupt cycle}. When an interrupt request
-occurs, if the system is interruptible, i.e. the interrupt mask bit is
-cleared, the handler function $schedule()$ will be invoked; otherwise
-$schedule()$ will be pending until the interrupt mask bit becomes
-cleared.  The implementation is shown as $schedule()$ in
+The implementation written in C is from an industrial avionic control
+system.  Interrupts would be triggered by, and only by, the clock
+every $T$, which we call \emph{interrupt cycle}. When an interrupt
+request occurs, if the system is interruptible, i.e. the interrupt
+mask bit is cleared, the handler function $schedule()$ will be
+invoked; otherwise $schedule()$ will be pending until the interrupt
+mask bit becomes cleared.  The pseudocode of $schedule()$ is shown in
 Figure~\ref{a:schedule}, where $taskList$ is the list of periodic
@@
 execution cannot be interrupted when it is updating status of tasks or
-searching the next task to execute, however, it can be interrupted while
-executing some task (Line~\ref{l:function}). This allows the execution
-of $schedule()$ to be nested.
+searching the next task to execute, however, it can be interrupted
+while executing some task (Line~\ref{l:function}). This allows the
+execution of $schedule()$ to be nested.
 
@@
 of $10$, because switching is performed and the interrupt mask bit is
-set at time $10$.
+set at time $10$, exemplifying differences between (A1') and (A1).
 
@@
 In this section, we introduce first how we model the states--the
-static aspect--of the system using algebraic data types, then how we
-specify the essential behaviors--the dynamic aspect--using rewrite
-rules. In particular, modeling of \emph{instantaneous behaviors} would
-be explained in Sections~\ref{ss:ir}, \ref{ss:init}
-and~\ref{ss:inthandling}, followed by \emph{timed behaviors} in
-Section~\ref{ss:timedbehavior}.
+static aspect--of the system using terms of given sorts, or called
+data types, then how we specify the essential behaviors--the dynamic
+aspect--using rewrite rules. In particular, modeling of
+\emph{instantaneous behaviors} would be explained in
+Sections~\ref{ss:ir}, \ref{ss:init} and~\ref{ss:inthandling}, followed
+by \emph{timed behaviors} in Section~\ref{ss:timedbehavior}.
 
@@
 \end{verbatim}
+where the keyword \verb|ctor| denotes the corresponding function
+symbol to be a constructor.
 
@@
 operations \verb|push|, \verb|pop| and \verb|peek| on it.
+\hide{
 \begin{verbatim}
@@
 \end{verbatim}
+}
 
@@
 requirement of a task.
+\hide{
 \begin{verbatim}
@@
 least common multiple of the periods of all tasks. A sort \verb|Timer|
-is defined:
+is defined to model the $timer$.
+\hide{
 \begin{verbatim}
@@
 \verb|priority|, \verb|period| and \verb|status|:
-\begin{verbatim}
-  class PTask | priority : Nat, period : NzNat, 
+%  class PTask | priority : Nat, period : NzNat, 
+\begin{verbatim}
+  class PTask | priority : Nat, period : Nat, 
                 status : Status .
@@
 \end{verbatim}
-where \verb|Status| is a sort with four constant constructors, same as
-in the implementation:
+where \verb|Status| is a sort with four constant constructors
+\verb|RUNNING|, \verb|INTERRUPT|, \verb|READY| and \verb|DORMANT|,
+same as in the implementation.
+\hide{
 \begin{verbatim}
@@
 \end{verbatim}
+}
+
 The list of periodic tasks, the variable $taskList$ in the
-implementation, is modeled as an instance of the sort \verb|TaskList|,
-which is a list of \verb|PTask|s\footnote{Following the Maude
-  convention, variables would be written in capital letters.}:
+implementation, is modeled as an instance of sort \verb|TaskList|,
+which is a list of \verb|PTask|s and/or \verb|error|s.
+\hide{
 \begin{verbatim}
@@
 \end{verbatim}
+}
 Periodic tasks are identified by their indexes in the list.
@@
 modeling some mechanism of the hardware, our model contains sufficient
-details to be analyzed for the behaviors of real systems. Two
-important properties--schedulability and correctness--are verified by
-model checking on our model, within several key scenarios. We
-demonstrate the soundness and completeness of our results.
+details to be analyzed for the behaviors of the real target
+system. Two important properties--schedulability and correctness--are
+verified by model checking on our model, within several key
+scenarios. We demonstrate the soundness and completeness of our
+results.
+
+\hide{
+% use section* for acknowledgment
+\ifCLASSOPTIONcompsoc
+  % The Computer Society usually uses the plural form
+  \section*{Acknowledgments}
+\else
+  % regular IEEE prefers the singular form
+  \section*{Acknowledgment}
+\fi
+
+The authors would like to thank...
+}
+
+% Can use something like this to put references on a page
+% by themselves when using endfloat and the captionsoff option.
+\ifCLASSOPTIONcaptionsoff
+  \newpage
+\fi
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+\bibliography{IEEEabrv,submission}
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+
+% biography section
+% 
+% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+% needed around the contents of the optional argument to biography to prevent
+% the LaTeX parser from getting confused when it sees the complicated
+% \includegraphics command within an optional argument. (You could create
+% your own custom macro containing the \includegraphics command to make things
+% simpler here.)
+%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
+% or if you just want to reserve a space for a photo:
 
 \appendix[Proof of Theorem~\ref{t:main}]
+\label{a:proof}
 \setcounter{theorem}{0}
@@
 
-\jx{
-
-  Using a model-based checking approach enhance the ability to check
-  other scheduling algorithms.
-
-  About non-determinism: task finishes right at the time interrupt
-  comes, theoretical results cannot solve
-
-  The chinese one:
-
-  - the model is ideal
-
-  - it should give a model to each task. And given different task sets, the model should be
-  adjusted. But our model need only an instantiation of the task set.
-
-  - the time domain. It uses a global integer to model the time, hence the time dense
-  must be discrete. But our model use a generic time domain, which can be instantiated on
-  both dense and discrete domain.
-}
-
-\hide{
-% use section* for acknowledgment
-\ifCLASSOPTIONcompsoc
-  % The Computer Society usually uses the plural form
-  \section*{Acknowledgments}
-\else
-  % regular IEEE prefers the singular form
-  \section*{Acknowledgment}
-\fi
-
-The authors would like to thank...
-}
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{IEEEabrv,submission}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
 \hide{

### 2016-03-27 RMS/submission.tex
up to Section V (not included)

@@
 \item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
-  theory}, with $E$ a set of conditional \emph{equations} and
+  theory}, with $E$ a set of \emph{conditional equations} and
   \emph{memberships} on $\Sigma$, and $A$ a set of equational axioms
@@
 \verb|mask| for the interrupt mask bit and \verb|ir| for the interrupt
-request bit, respectively.
+request bit, respectively:
 \begin{verbatim}
@@
 \end{verbatim}
-where the sort \verb|TaskID| is a supersort of \verb|MaybeNat| and
+where the sort \verb|TaskID| contains subsorts \verb|MaybeNat| and
 \verb|Oid|, referring to some task.
+\hide{
 \begin{verbatim}
@@
 \end{verbatim}
+}
 Some operations, such as \verb|getPc| and \verb|setMask|, are defined
@@
 
-Then the hardware is described by the sort \verb|Hardware|:
+Then the hardware is described by the sort \verb|Hardware| consisting
+of an instance of \verb|Regs| and a term of sort \verb|Stack|.  
+\hide{
 \begin{verbatim}
@@
 The entire system in our model is a composition of the parts
-introduced above, of a sort \verb|System|\footnote{Some variable
-  declarations are not shown for simplicity.}:
-\begin{verbatim}
-  op _____ : TaskList Timer 
-             SysTasks Hardware Object 
-               ~> System [ctor] .
+introduced above, of a sort \verb|System|\footnote{Following the Maude
+  convention, variables would be written in capital letters. Some
+  variable declarations are not shown for simplicity.}:
+\begin{verbatim}
+  op _____ : TaskList Timer SysTasks 
+             Hardware Object ~> System [ctor] .
   mb (L T STS HW < O : IntSrc |>) : System .
 \end{verbatim}
+where ``\verb|~>|'' means that the function defined is a partial
+function and the keyword \verb|mb| declares a membership axiom,
+stating here that a term composed of a \verb|TaskList|, a
+\verb|Timer|, a \verb|SysTasks|, a \verb|Hardware| and an object
+instance of class \verb|IntSrc| is of sort \verb|System|.
 
@@
 \verb|val| equals \verb|zero|, and \verb|_.intReq| sets the \verb|ir|
-bit indicating there exists an interrupt request to be handled:
+bit indicating there exists an interrupt request to be handled.
+\hide{
 \begin{verbatim}
@@
 \end{verbatim}
+}
+
 Then the request will wait to be handled, which is explained in
@@
 $updateStatus()$ in Figure~\ref{a:schedule}, which is treated as an
-instantaneous action in our model. It is modeled by the recursive
-function as below:
+instantaneous action in our model. It is modeled by a recursive
+function \verb|updateStatus_with_|:
 \begin{verbatim}
@@
                             -> TaskList . 
-  eq updateStatus null with TIMER = null .
-  eq updateStatus (TASK :: L) with TIMER
-     = (update TASK with TIMER) 
-       :: (updateStatus L with TIMER) .
-\end{verbatim}
-with \verb|TIMER| the current value of the global variable $timer$,
-and function \verb|update_with_| updating the status of individual
-task (Lines~\ref{l:startupdate}-\ref{l:endupdate} in
+\end{verbatim}
+%  eq updateStatus null with TIMER = null .
+%  eq updateStatus (TASK :: L) with TIMER
+%     = (update TASK with TIMER) 
+%       :: (updateStatus L with TIMER) .
+which applies function \verb|update_with_| on individual task
+sequentially to update the status
+(Lines~\ref{l:startupdate}-\ref{l:endupdate} in
 Figure~\ref{a:schedule}):
@@
        then < O : PTask | status : INTERRUPT >
-       else < O : PTask |> fi [owise] .
-\end{verbatim}
-Given a task, if \verb|TIMER|($timer$) can be divided by its period,
-this task should be initiated.  In the case where the task should be
-initiated, it is set \verb|READY| if its \verb|status| is
+       else < O : PTask |> fi [otherwise] .
+\end{verbatim}
+with \verb|TIMER| the current value of the global variable $timer$.
+Given a task, if \verb|TIMER|($timer$) can be divided by its period
+\verb|T|, this task should be initiated.  In the case where the task
+should be initiated, it is set \verb|READY| if its \verb|status| is
 \verb|DORMANT|; otherwise that means the previous job of this task is
@@
 We can see that \verb|updateStatus_with_| behaves the same as
-$updateStatus()$.
+$updateStatus()$ in Figure~\ref{a:schedule}.
 
@@
 four things: (i) clearing the bit \verb|ir|, which means the request
-has been handled; (ii) pushing the current \verb|pc| value into the
-stack, storing the interrupted context; (iii) assigning
-\verb|scheduling| of sort \verb|Oid| to \verb|pc|, which indicates
-that the system is scheduling; and (iv) setting the bit \verb|mask|,
-to mask coming interrupt requests.
+has been handled; (ii) pushing the current \verb|pc| into the stack,
+storing the interrupted context; (iii) assigning \verb|scheduling| of
+sort \verb|Oid| to \verb|pc|, which indicates that the system is
+scheduling; and (iv) setting the bit \verb|mask|, to mask coming
+interrupt requests.
 
@@
 When the execution time of the system task \verb|scheduling| reaches
-its computation requirement, the scheduling stage may finish. We model
-this instantaneous action with the following rule:
+its computation requirement, scheduling is finished. We model this
+instantaneous action with the following rule:
 \begin{verbatim}
@@
 
-Similar to scheduling, the switching stage is divided into timed
+Similar to scheduling, the switching stage is also divided into timed
 behaviors of \verb|switching| and its functionality. \verb|switching|
-starts when the execution time of the running periodic task reaches
-its computation requirement, and finishes when its own execution time
-does so. Two similar instantaneous rules are defined to model the
-functionality of switching:
+starts when the running periodic task is complete, and finishes when
+itself is so. Two similar instantaneous rules \verb|switching-start|
+and \verb|switching-finish| are defined to model the functionality of
+switching. 
+\hide{
 \begin{verbatim}
@@
 together by the following single \emph{standard} tick
-rule~\cite{DBLP:journals/entcs/OlveczkyM07a}:
+rule\footnote{The keyword \texttt{nonexec} should be given to allow
+  the Real-Time Maude engine to apply the rule with some
+  strategies.}~\cite{DBLP:journals/entcs/OlveczkyM07a}:
 \begin{verbatim}
@@
 \end{verbatim}
-We omit details for the case where \verb|ID| is of sort \verb|Oid| due
-to similarity. In that case, \verb|deltaTask| applies on \verb|STS|
-instead of \verb|L|.
+where the last condition states that \verb|ID| is of sort
+\verb|MaybeNat|. Due to similarity, we omit details for the case where
+\verb|ID| is of sort \verb|Oid| and \verb|deltaTask| applies on
+\verb|STS| instead of \verb|L|.
 
@@
   ceq mte(L T STS HW ISRC)
-      = minimum( mteTask(ID, L),
-                 minimum( mteIS(ISRC), 
-                          mteIr(HW)))
+      = minimum(mteTask(ID, L),
+                mteIS(ISRC), mteIr(HW))
       if ID := (HW).getPc /\ ID :: MaybeNat .

### 2016-03-27 Maude/maude24/case-generate.cpp
test cases files

@@ -28,6 +28,7 @@ int main() {
   int TESTNUM = 10;
   int caseNum = 0;
 
+
   for (N = 5; N <= 20; N++) { 
     cout << "Task number is: " << N << endl;
     
@@ -75,7 +76,7 @@ int main() {
     // write to the file
 
     //    ofstream out(to_string(N) + "/test-case-" + to_string(caseNum) + ".maude");
-    ofstream out("pow/" + to_string(N) + "-" + to_string(caseNum) + ".maude");
+    ofstream out("pow-ideal/" + to_string(N) + "-" + to_string(caseNum) + ".maude");
     if (out.is_open()) {
       out << "set trace off ." << endl;
       out << "set break off ." << endl;
@@ -98,7 +99,8 @@ int main() {
       out << endl;
 
       out << "  op tsts : -> SysTasks ." << endl;
-      out << "  eq tsts = [ < scheduling : Task | cnt : [ 0 / [ 38 , 38 ] ] > < switching : Task | cnt : [ 0 / [ 20 , 20 ] ] > ] ." << endl;
+      //      out << "  eq tsts = [ < scheduling : Task | cnt : [ 0 / [ 38 , 38 ] ] > < switching : Task | cnt : [ 0 / [ 20 , 20 ] ] > ] ." << endl;
+      out << "  eq tsts = [ < scheduling : Task | cnt : [ 0 / [ 0 , 0 ] ] > < switching : Task | cnt : [ 0 / [ 0 , 0 ] ] > ] ." << endl;      
       out << endl;
  
       out << "  op tHW : -> Hardware ." << endl;

### 2016-03-27 Maude/maude24/test-run.cpp

@@ -12,8 +12,8 @@ int main() {
     cout << "task number " << N << " start:" << endl;
   for (int i = 0; i < TESTNUM; i++) {
     for (int j = 0; j < TIME; j++) {
-      command = "./maude.linux64 real-time-maude.maude RMS.maude pow/"
-	+ to_string(N) + "-" + to_string(i) + ".maude > pow-result/"
+      command = "./maude.linux64 real-time-maude.maude RMS.maude pow-ideal/"
+	+ to_string(N) + "-" + to_string(i) + ".maude > pow-ideal-result/"
 	+ to_string(N) + "-" + to_string(i) + "-" + to_string(j) + ".result";
       system(command.c_str());
       cout << "Task number " << N << " test " << i << " round " << j << " done" << endl;

### 2016-03-27 RMS/submission.tex
almost finished the submission

@@
 the implementation schedules periodic tasks exactly with respect to
-their priorities and periods.
+the RMS algorithm.
 
@@
 define an atomic proposition \verb|taskTimeout| to hold if there
-exists an \verb|error| appearing in $taskList$ of the current state,
-that is, some task misses its deadline:
+exists an \verb|error| in $taskList$ of the current state, that is,
+some task misses its deadline:
 \begin{verbatim}
@@
 \end{verbatim}
-where \verb|containError| returns \verb|true| if there is an object
-\verb|error| existing in \verb|L|. Then our desired
-property--schedulability--can be formalized as the temporal logic
-formula: \verb|[](~taskTimeout)|. As the property is not
-\emph{clocked}, given an initial state \verb|init|, the following
-untimed model checking command returns \verb|true| if the
-schedulability property holds with no time limit; otherwise a trace
-showing a counterexample is provided:
+where \verb|containError| returns \verb|true| if there is an
+\verb|error| existing in \verb|L|. Then schedulability can be
+formalized as the temporal logic formula: \verb|[](~taskTimeout)|. As
+the property is not \emph{clock-related}, given an initial state
+\verb|init|, the following untimed model checking command returns
+\verb|true| if the schedulability property holds with no time limit;
+otherwise a trace showing a counterexample is provided:
 \begin{verbatim}
@@
 
-Another objective is to verify the correctness of the implementation.
-The atomic proposition \verb|correct| is hence defined to hold if the
-running periodic task is the one requested to be executed with the
-highest priority:
+Another important objective is to verify the correctness of the
+implementation.  The atomic proposition \verb|correct| is hence
+defined to hold if the running periodic task is the one requested to
+be executed with the highest priority:
 \begin{verbatim}
@@
 identified by \verb|ID|, probably \verb|none|, is the one possessing
-the highest priority among those whose status is \verb|READY|,
-\verb|RUNNING| or \verb|INTERRUPT|. Note that in this paper, we do not
-care the behaviors after some task misses its deadline. Therefore, the
+the highest priority among those whose status is not
+\verb|DORMANT|. Note that during verification, we do not care the
+behaviors after some task misses its deadline. Therefore, the
 correctness property is formalized by the temporal logic formula:
@@
 
-We have analyzed our model/implementation in ten different scenarios,
-including both realistic ones provided by our industrial partner and
-experimental ones designed by ourselves, four of them are described
-below:
+We have analyzed our model in ten different scenarios, including both
+realistic ones provided by our industrial partner and experimental
+ones designed by ourselves, four of them are described below:
 \begin{itemize}
@@
 to the schedulability property, it holds in Scenarios~(i-iii), but
-fails in Scenario~(iv).  One counterexample of the schedulability for
-Scenario~(iv), returned by the model checking command, is pictured in
-Figure~\ref{f:counterexample}, where the third task $\tau_3$ misses
-its deadline at the time $15ms$.
+fails in Scenario~(iv).  One counterexample of the schedulability
+within Scenario~(iv), returned by the model checking command, is
+pictured in Figure~\ref{f:counterexample}, where the third task
+$\tau_3$ misses its deadline at the time $15ms$.
+
+We also randomly generate test scenarios under the above setting to
+exam the efficiency of our approach for verifying the schedulability.
+Among the $50$ generated test scenarios with $5$ tasks, we find that
+the execution time of the model checking command for each scenario
+varies from about $300ms$ up to a timeout, which is set to $90$
+minutes. This is because the efficiency of model checking depends on
+the scale of the state space. And the scale is further positively
+correlated with $mn$, where $m$ is the upper bound of $timer$ and $n$
+is the number of periodic tasks. By the generated test scenarios, it
+turns out that the model checking command for schedulability in our
+model is able to handle scenarios, where $mn$ is up to about $10^6$,
+in an acceptable period of time say $90$ minutes.
 
@@
 of untimed temporal logic model checking, under the maximal time
-sampling strategy, for a large class of real-time
-systems~\cite{DBLP:journals/entcs/OlveczkyM07a}:
+sampling strategy, for a large class of real-time systems possessing a
+set of ``good'' properties that is called \emph{time-robustness}, and
+for a set of ``good'' LTL formulae constructed by
+\emph{tick-invariant} propositions\footnote{We avoid introducing the
+  definitions of time-robustness and tick-invariance, due to the
+  requirements of extra rewriting logic
+  background.}~\cite{DBLP:journals/entcs/OlveczkyM07a}:
 \begin{theorem}[\cite{DBLP:journals/entcs/OlveczkyM07a}]
 \label{t:completeness}
-Given a \emph{time-robust} real-time rewrite theory $\cal R$, a set
-$AP$ of \emph{tick-stabilizing} atomic propositions, an LTL formula
-$\Phi$ (excluding the \emph{next} operator $\bigcirc$) whose atomic
-propositions are contained in $AP$. The untimed temporal logic model
-checking verifying $\Phi$ is \emph{complete} under the maximal time
-sampling strategy.
+Given a time-robust real-time rewrite theory $\cal R$, a set $AP$ of
+tick-invariant atomic propositions, an LTL formula $\Phi$ (excluding
+the \emph{next} operator $\bigcirc$) whose atomic propositions are
+contained in $AP$. The untimed temporal logic model checking verifying
+$\Phi$ is \emph{complete} under the maximal time sampling strategy.
 \end{theorem}
@@
 atomic propositions--\verb|taskTimeout| and \verb|correct|--are
-tick-stabilizing, then using Theorem~\ref{t:completeness}.
+tick-invariant, then using Theorem~\ref{t:completeness}. For a more
+detailed proof, see the Appendix.
 \end{IEEEproof}
@@
 our model, if the running task is complete \emph{right} at the time
-when an interrupt request is performed, two different behaviors are
+when an interrupt request occurs, two different behaviors are
 possible: (i) the system performs task switching, during which the
-interrupt request is masked, hence the scheduling may be delayed; (ii)
-the system answers the interrupt request immediately, the switching
-being delayed. Tackling such non-determinism via theoretical analyses
-seems more complicated than our automatic approach.
+interrupt request is masked, hence the scheduling and initiation of
+tasks may be delayed; (ii) the system answers the interrupt request
+immediately, the switching being delayed. Tackling such
+non-determinism via theoretical analyses seems more complicated than
+our automatic approach.
 
@@
 model checking to analyze the RMS algorithm along the same line but
-with different languages and tools. The RMS algorithm is analyzed
+with different languages and tools. The RMS algorithm is investigated
 using an extension of SPIN~\cite{DBLP:journals/tse/Holzmann97}
@@
 
-The following lemma is needed to prove the time-robustness of our
-model:
+Time-robustness is a set of properties expected from a well-behaved
+real-time rewrite theory. We avoid introducing the accurate definition
+of time-robustness, but instead give the following lemma to prove
+time-robustness:
 \begin{lemma}[\cite{DBLP:journals/entcs/OlveczkyM07a}]
@@
 Let $\cal R$ be an object-oriented specification with a standard tick
-rule, let the infinity element \verb|INF| be the only element in the
-time domain which is not a normal time value, and let the time domain
-be \emph{linear}. Then $\cal R$ is time-robust if the following
-conditions are satisfied for all appropriate ground terms $t$ and
-$r,r'$:
+rule, and let the infinity element \verb|INF| be the only element in
+the time domain which is not a normal time value.
+%and let the time domain be \emph{linear}.
+Then $\cal R$ is time-robust if the following conditions are satisfied
+for all appropriate ground terms $t$ and $r,r'$:
 \begin{enumerate}
@@
 Let $\cal R$ be a time-robust object-oriented specification with a
-standard tick rule, let the infinity element \verb|INF| be the only
-element in the time domain which is not a normal time value, and let
-the time domain be \emph{linear}. Then $\cal R$ is tick-invariant with
-respect to a set $P$ of atomic propositions if \verb|{|$t$\verb|}|
-$\simeq_P$ \verb|{delta(|$t$\verb|,|$r$\verb|)}| for all $t,r$ with
-$r<$ \verb|mte(|$t$\verb|)|.
+standard tick rule, and let the infinity element \verb|INF| be the
+only element in the time domain which is not a normal time value.
+%and let the time domain be \emph{linear}. 
+Then $\cal R$ is tick-invariant with respect to a set $P$ of atomic
+propositions if \verb|{|$t$\verb|}| $\simeq_P$
+\verb|{delta(|$t$\verb|,|$r$\verb|)}| for all $t,r$ with $r<$
+\verb|mte(|$t$\verb|)|.
 \end{lemma}

### 2016-03-27 RMS/corrections.tex
first version done for major revision

@@
 \newtheorem{lemma}{Lemma}
+\newcommand{\ANSWER}{{\bf ANSWER}}
 
@@
 applications within the field of industrial real-time systems? How do
-the authors propose to handle very large scenarios? ¿How does it
-behave on typical real-time scheduling problems used in industry? I
-would like to see more complex examples to convince the reader of the
+the authors propose to handle very large scenarios? How does it behave
+on typical real-time scheduling problems used in industry? I would
+like to see more complex examples to convince the reader of the
 practicability of the approach on the assumptions given for the model,
@@
 
-ANSWER: TODO
+\ANSWER: As mentioned in the paper, the modeled RMS implementation
+serves in an avionic control systems from our industrial partner. It
+is a real-world application within the field of industrial real-time
+systems. And the scenarios presented in Section V.B are also real
+scenarios that our partner is using in the system. Our partner
+indicated that there would be at most $5$ tasks in the task set for
+the implementation. On the other hand, in the current version, we have
+randomly generated large numbers of test cases to examine the
+efficiency of our schedulability test that is based on model checking,
+as discussed in Section V.B. The capability of model checking is
+restricted by the scale of the state space of the model. In our model,
+the model checking can handle scenarios where $mn$ is up to $10^6$ in
+an acceptable period of time. With $mn=10^6$ and reasonable task
+periods, the number $n$ of tasks can be at least $10$, which has
+already fulfilled the requirements of the target
+implementation. Further with particular task periods, the number $n$
+of tasks can be $20$ or more.
 
@@
 
-ANSWER: The detailed proof is now included in the appendix. It is true
+\ANSWER: The detailed proof is now included in the Appendix. It is true
 that readers may be interested in the detailed proof of Theorem~2 to
@@
 
-ANSWER: TODO. To revise the modeling section.
+\ANSWER: Thank you for the invaluable suggestions. Section IV has been
+revised. Some unnecessary detailed definitions presented as codes are
+removed, and replaced by more explanations. We hope that the current
+presentation would make Section IV more easy-to-read, even for an
+audience who does not know Real-Time Maude before. On the other hand,
+Section VI (Related Work) is also improved. We compare our work with
+the existing theoretical work and the existing verification work in a
+more complete way.
 
@@
 
-ANSWER: The related work section is now improved. More comparisons
+\ANSWER: The related work section is now improved. More comparisons
 with the theoretical approaches and with [24,25] are added. The
@@
 
-ANSWER: The statement has been corrected. The work presented in this
+\ANSWER: The statement has been corrected. The work presented in this
 submission aims at modeling and verifying a realistic RMS
@@
 
-ANSWER: TODO. to make the paper self-contained.
+\ANSWER: The Sections II.B and IV are improved to be more
+self-contained now. The idea is that, Section II.B contains mainly an
+overview of Real-Time Maude, and then Section IV describes the model
+with introducing necessary syntax on-the-fly.
 
@@
 
-ANSWER: Yes, we agree that we have two choices to do the work
+\ANSWER: Yes, we agree that we have two choices to do the work
 presented in the paper: one is to develop a general way to model RMS
@@
 
-ANSWER: The section about soundness and completeness is now made more
+\ANSWER: The section about soundness and completeness is now made more
 self-contained. The detailed proof of Theorem~2 is included in the
@@
 
-- In the definition of $IR$, it is not clear what $s$
-and $s'$ are. I guess they are states, but the concept of state was
-not introduced.
+- In the definition of $IR$, it is not clear what $s$ and $s'$ are. I
+guess they are states, but the concept of state was not introduced.
 
-ANSWER: TODO
+\ANSWER: Yes, they can be states. But more generally, they are
+terms. This part has been modified to specify $s$ and $s'$ ($t$ and
+$t'$ now) clearly.
 
-- In the definition of a class, the authors should
-specify that a class includes a collection of rules, otherwise this
-fact may be missed.
+- In the definition of a class, the authors should specify that a
+class includes a collection of rules, otherwise this fact may be
+missed.
 
-ANSWER: TODO
+\ANSWER: Thanks very much for reminding. This is added now.
 
@@
 
-ANSWER: It is done.
+\ANSWER: It is done.
 
@@
 
-ANSWER: TODO
+\ANSWER: Sorry for missing the explanation of \verb|[ctor]|. It is now
+added when \verb|[ctor]| is used for the first time.
 
@@
 
-ANSWER: TODO
+\ANSWER: Sorry for the misleading in the text. In fact, \verb|bottom|
+and \verb|#| are constructors of sort \verb|Stack|. This part is
+modified now. Some detailed definitions in codes are removed, and are
+replaced by more explanations. We hope that the current presentation
+would make Section IV more easy-to-read.
 
@@
 
-ANSWER: TODO
+\ANSWER: Sorry for this incompleteness. \verb|NzNat| did mean non-zero
+natural numbers. \verb|NzNat| is now replaced by \verb|Nat| to reduce
+unnecessary complexity for the readers.
 
@@
 
-ANSWER: TODO
+\ANSWER: In fact, the definitions of time-robustness and
+tick-stabilization (which is now replaced with tick-invariance)
+require more knowledge about rewriting logic. We avoid introducing the
+accurate definitions of them. Instead, we now give short descriptions
+of them. More detailed introduction can be found in the Appendix.
 
@@
 
-ANSWER: The detailed proof is now included in the appendix.  The
+\ANSWER: The detailed proof is now included in the appendix.  The
 detailed proof requires a bit more theoretical background about
@@
 
-ANSWER: We agree that RMS is a very simple scheduling and is the
+\ANSWER: We agree that RMS is a very simple scheduling and is the
 optimum at the same time among the fixed-prority ones, making it
@@
 
-ANSWER: The comparison is given in the related work section (Section
+\ANSWER: The comparison is given in the related work section (Section
 VI). We would say that we are not implementing RMS algorithm in
@@
 
-ANSWER: As an industrial application, we are not trying to make the
+\ANSWER: As an industrial application, we are not trying to make the
 problem as difficult as possible. Instead, we are trying to simplify
@@
 
-ANSWER: Yes, we agree that this is an application of rewriting
+\ANSWER: Yes, we agree that this is an application of rewriting
 logic. In this paper, we do apply the existing theories and techniques
@@
 
-ANSWER: We do not agree that we should illustrate the mechanism behind
+\ANSWER: We do not agree that we should illustrate the mechanism behind
 the model checking commands, since the model checker is not part of
@@
 application [26] and [27] in RMS, hence I do not recommend this paper.
-
-ANSWER: ?
 

### 2016-03-29 RMS/corrections.tex
modified version wrt Zhou Min's comments

@@
 \newtheorem{lemma}{Lemma}
-\newcommand{\ANSWER}{{\bf ANSWER}}
+\newcommand{\ANSWER}{{\bf RESPONSE: }}
+\newcommand{\COMMENT}{{\bf COMMENT: }}
 
@@
     & with Real-Time Maude \\
-    Submitted to: & Transactions on Industrial Eletronics \\
+    Submitted to: & Transactions on Industrial Electronics \\
     Manuscript Type: & Regular paper \\
@@
 
-\section{Answers to the Reviewers}
-\subsection{Reviewer 1}
-Comments to the Author
+%\section{Answers to the Reviewers}
+\section{Reponses to Reviewer 1}
+\subsection{General Comments}
+\begin{itemize}
 
+\item
+\hide{
 The paper shows a realistic implementation of a Rate-Monotonic
@@
 of the model are verified by model checking, and validated within
-different realistic scenarios.
-
-On the positive side, this paper presents a solid piece of
+different realistic scenarios.}
+\COMMENT On the positive side, this paper presents a solid piece of
 work. Periodic task scheduling is an important (and difficult)
@@
 
-On the negative side:
+\ANSWER Thanks for the pros. We are happy that the work in the paper
+interests the readers. We hope that it provides a new and formal way
+to verify a real-time system, which is able to investigate important
+problems (such as periodic task scheduling) from a more realistic
+aspect.
 
-1) The weak point is the lack of evidence of practicality, efficiency
-and scalability. Since there are only small and simplistic scenarios
-to analyze this model, it is difficult to judge the effectiveness of
-the proposed implementation. The key scenarios appear conveniently
-small to allow the implementation fully supports all these examples,
-returning at the same time appropriate counterexamples to guide and
-adjust the design. Is this true for larger examples of "real world"
-applications within the field of industrial real-time systems? How do
-the authors propose to handle very large scenarios? How does it behave
-on typical real-time scheduling problems used in industry? I would
-like to see more complex examples to convince the reader of the
-practicability of the approach on the assumptions given for the model,
-and would probably increase the mentioned benefits. The paper does not
-give any directions to the above problems, and some sentences pointing
-out the difficulties in the implementation of more generic and
-realistic scenarios would be most welcome to understand the real
-contribution of the paper.
+\item
+\COMMENT The weak point is the lack of evidence of practicality,
+efficiency and scalability. Since there are only small and simplistic
+scenarios to analyze this model, it is difficult to judge the
+effectiveness of the proposed implementation. The key scenarios appear
+conveniently small to allow the implementation fully supports all
+these examples, returning at the same time appropriate counterexamples
+to guide and adjust the design. Is this true for larger examples of
+"real world" applications within the field of industrial real-time
+systems? How do the authors propose to handle very large scenarios?
+How does it behave on typical real-time scheduling problems used in
+industry? I would like to see more complex examples to convince the
+reader of the practicability of the approach on the assumptions given
+for the model, and would probably increase the mentioned benefits. The
+paper does not give any directions to the above problems, and some
+sentences pointing out the difficulties in the implementation of more
+generic and realistic scenarios would be most welcome to understand
+the real contribution of the paper.
 
-\ANSWER: As mentioned in the paper, the modeled RMS implementation
-serves in an avionic control systems from our industrial partner. It
-is a real-world application within the field of industrial real-time
-systems. And the scenarios presented in Section V.B are also real
-scenarios that our partner is using in the system. Our partner
-indicated that there would be at most $5$ tasks in the task set for
-the implementation. On the other hand, in the current version, we have
-randomly generated large numbers of test cases to examine the
-efficiency of our schedulability test that is based on model checking,
-as discussed in Section V.B. The capability of model checking is
-restricted by the scale of the state space of the model. In our model,
-the model checking can handle scenarios where $mn$ is up to $10^6$ in
-an acceptable period of time. With $mn=10^6$ and reasonable task
-periods, the number $n$ of tasks can be at least $10$, which has
-already fulfilled the requirements of the target
+\ANSWER Thanks for the suggestion. As mentioned in the paper, the
+system under verification is a real-world RMS implementation, which is
+used in an avionic control system. The scenarios presented in Section
+V.B are also real scenarios from the online system. Our industrial
+partner has very strict requirements in the timing. They use at most
+$5$ tasks for scheduling to avoid high overhead.
+
+On the other hand, ``larger'' scenarios are not the same as
+``complex'' scenarios in our model, as discussed in the revised
+Section V.B. We have examined our approach by verifying randomly
+generated scenarios where the number $n$ of tasks are over $10$. In
+that case, the least common multiple of the periods of all tasks can
+be as large as $10^5$ times the interrupt cycle $T$. All feasible
+combinations of execution traces are checked in our approach. Our
+industrial partner agrees that it satisfies their practical
+requirements. Furthermore, the number $n$ of tasks can be $20$ and
+even more if we allow different tasks possess a same period.
+
+\hide{
+the modeled RMS implementation serves in an avionic control systems
+from our industrial partner. It is a real-world application within the
+field of industrial real-time systems. And the scenarios presented in
+Section V.B are also real scenarios that our partner is using in the
+system. Our partner indicated that there would be at most $5$ tasks in
+the task set for the implementation. On the other hand, in the current
+version, we have randomly generated large numbers of test cases to
+examine the efficiency of our schedulability test that is based on
+model checking, as discussed in Section V.B. The capability of model
+checking is restricted by the scale of the state space of the
+model. In our model, the model checking can handle scenarios where
+$mn$ is up to $10^6$ in an acceptable period of time. With $mn=10^6$
+and reasonable task periods, the number $n$ of tasks can be at least
+$10$, which has already fulfilled the requirements of the target
 implementation. Further with particular task periods, the number $n$
 of tasks can be $20$ or more.
+}
 
-2) One of my biggest problems with the theoretical part of this work
-is that the paper is technically solid as far as I can tell, but
+\item
+\COMMENT One of my biggest problems with the theoretical part of this
+work is that the paper is technically solid as far as I can tell, but
 there's not much yet in the way of theorems and results about formal
@@
 
-\ANSWER: The detailed proof is now included in the Appendix. It is true
+\ANSWER We are happy that the readers are interested in the detailed
+and technical proof, which is now included in the Appendix. It is true
 that readers may be interested in the detailed proof of Theorem~2 to
@@
 needs a bit more theoretical background about rewriting logic and more
-details of our model, which we have simplified in the submission to
-ease the understanding of our approach. We would prefer to refer the
-detailed proof to a non-anonymous technical report, if possible, in
-the final version.
+technical details of our model, which we have simplified in the paper
+in order to ease the understanding of our approach. We would prefer to
+refer the detailed proof to a non-anonymous technical report, if
+possible, in the final version.
 
-3) Another important point which needs improvement is the description
-of the implementation. I guess other readers might have less
-difficulties with the motivations if they know Maude and the Real-Time
-Maude extension, but if you aim for a more general audience, it might
-not work. Many pages are spent for the description of the formal
-modeling of the implementation and the section is hard to read. I
-highly recommend the authors to thoroughly revise this part of the
-paper to make it easy-to-read. It would be better preferable to have a
-much shorter description of the principal insights for the
+\item
+\COMMENT Another important point which needs improvement is the
+description of the implementation. I guess other readers might have
+less difficulties with the motivations if they know Maude and the
+Real-Time Maude extension, but if you aim for a more general audience,
+it might not work. Many pages are spent for the description of the
+formal modeling of the implementation and the section is hard to
+read. I highly recommend the authors to thoroughly revise this part of
+the paper to make it easy-to-read. It would be better preferable to
+have a much shorter description of the principal insights for the
 implementation followed by more convincing examples and benchmarks
@@
 
-\ANSWER: Thank you for the invaluable suggestions. Section IV has been
-revised. Some unnecessary detailed definitions presented as codes are
+\ANSWER Thank you for the invaluable suggestions. Section IV has been
+revised. Some unnecessary detailed definitions presented as code are
 removed, and replaced by more explanations. We hope that the current
 presentation would make Section IV more easy-to-read, even for an
-audience who does not know Real-Time Maude before. On the other hand,
+audience who did not know Real-Time Maude before. On the other hand,
 Section VI (Related Work) is also improved. We compare our work with
@@
 
-In conclusion, the RMS implementation proposed by the authors by using
-Real-Time Maude is interesting, but not complete (theorems and results
-about the formal modeling and verification of the implementation in
-Maude ought be clearly demonstrated). Moreover, the weak point is the
-lack of evidence for practicality, and the presentation of Section IV
-can be improved. It's not clear at all how this kind of key scenarios
-could actually run in practice in more general real-time
-systems. However, I think that the paper is worthy of publication,
-because is the first time that Rate-Monotonic Scheduling is
-investigated using Real-Time Maude in a (more) realistic
-implementation, providing a solid semantic foundation for formal
-verification. Therefore, I recommend the (weak) acceptance of this
-paper.
+\end{itemize}
 
-Some minor remarks:
-
-- Page 7, Related Work. More comparisons with other approaches based
-on model checking would help to evaluate pros and cons of an
+\subsection{Detailed Comments}
+\begin{itemize}
+\item
+\COMMENT Page 7, Related Work. More comparisons with other approaches
+based on model checking would help to evaluate pros and cons of an
 implementation with Real-Time Maude with respect to different
@@
 
-\ANSWER: The related work section is now improved. More comparisons
-with the theoretical approaches and with [24,25] are added. The
-differences with [24,25] in the models and in the way of modeling are
-mainly discussed. On the other hand, it is a bit difficult to compare
-the efficiency and scalability between [24,25] and our approach. One
-reason is that we have a different setting with [24] and [25], because
-the objectives are different: we aim at verifying an RMS implemention
-from a real-world real-time system, while [24] and [25] targeted the
-RMS algorithm itself. Another reason is that [24] and [25] presented
-no discussion on the efficiency and scalability. Furthermore, they use
-\verb|TMSVL| and an extension of SPIN, respectively, as verification
-tools, which are not open-source, making it unable to re-implement
-their work.
+\ANSWER Thanks for the pointing this out. The related work section is
+now improved. More comparisons with the theoretical approaches and
+with [24,25] are added. The differences with [24,25] in the models and
+in the way of modeling are mainly discussed. On the other hand, it is
+a bit difficult to compare the efficiency and scalability between
+[24,25] and our approach. One reason is that we have a different
+setting with [24] and [25], because the objectives are different: we
+aim at verifying an RMS implemention from a real-world real-time
+system, while [24] and [25] targeted the RMS algorithm itself. Another
+reason is that [24] and [25] presented no discussion on the efficiency
+and scalability. Furthermore, they used \verb|TMSVL| and an extension
+of SPIN, respectively, as verification tools, which are not
+open-source, making us unable to re-implement their work.
 
-- Page 8, Conclusions. Where in the paper do you show that the details
-of your "realistic" implementation are "sufficient" for the behaviors
-of all real systems used in the current industry? This should be
-briefly discussed.
+\item
+\COMMENT Page 8, Conclusions. Where in the paper do you show that the
+details of your "realistic" implementation are "sufficient" for the
+behaviors of all real systems used in the current industry? This
+should be briefly discussed.
 
-\ANSWER: The statement has been corrected. The work presented in this
-submission aims at modeling and verifying a realistic RMS
-implementation in an industrial avonic system. It is a piece of real
+\ANSWER Sorry for that. The statement has been corrected. The work
+presented in the paper aims at modeling and verifying a realistic RMS
+implementation in an industrial avionic system. It is a piece of real
 work in the industry. Even though we believe that our approach could
-be applied to other systems as well, it means more to that specific
-one. In this sense, ``sufficient'' means that the details described in
-our model meet the requirements and expectations from the users and
-the engineers.
+be applied to other similar systems as well, it means more to that
+specific one. In this sense, ``sufficient'' means that the details
+described in our model meet the requirements and expectations from the
+users and the engineers.
 
-\subsection{Reviewer 2}
-Comments to the Author
+\end{itemize}
 
-The paper proposes a new way of modelling Rate Monotonic Scheduling
-(RMS).  The new modelling approach is more accurate than the
-simplified way originally proposed by Liu and Layland, as it also
-models some of the overhead that is present in a real system
-(e.g. scheduling and switching time).  This implies taking some of the
-hardware details into account.  The model, which is based on the
-formal language of Real-Time Maude, can be analyzed using the formal
-verification tools provided by Real-Time Maude.  The paper shows how
-this approach can be used for modelling and analyzing a particular RMS
-implementation.
+\section{Responses to Reviewer 2}
+\subsection{General Comments}
+\begin{itemize}
+\item
+\COMMENT One of the problems with this paper is that it is not
+completely self-contained.  Some knowledge about Real-Time Maude is
+necessary in order to fully understand it.  I found the short
+introduction about Real-Time Maude (section II.B) not enough for
+understanding the formalism used in the rest of the paper (see details
+below).
 
-Up to my knowledge, this is original work. Related papers address
-different aspects and do not take implementation overhead into
-account.
+\ANSWER Thank you very much for pointing this out. The Sections II.B
+and IV are improved to be more self-contained now. The idea is that,
+Section II.B presents mainly an overview of Real-Time Maude, and then
+Section IV describes the model with introducing necessary syntax
+on-the-fly.
 
-The technique proposed by the paper is of industrial interest because
-it improves the accuracy of analyzing schedulability in RMS
-implementations with respect to the bare application of the theoretic
-schedulability result.
+\item
+\COMMENT Another concern is that the significance of the paper could
+be much better if the paper addressed the problem of modelling RMS in
+a more general way. Instead, the paper takes the form of a case study,
+where the formal modelling of one specific RMS implementation is
+presented, rather than a general method for modelling and analyzing
+RMS implementations.
 
-The paper is well written and it looks sound, but I could not check it
-completely.
+\ANSWER Thank you for the suggestion. Yes, we agree that we have two
+choices to do the work presented in the paper: one is to develop a
+general way to model RMS algorithms or implementations, and then
+instantiate the general model to get a concrete one for our target
+system; the other is to shape an accurate model of the target system
+directly.
 
-One of the problems with this paper is that it is not completely
-self-contained.  Some knowledge about Real-Time Maude is necessary in
-order to fully understand it.  I found the short introduction about
-Real-Time Maude (section II.B) not enough for understanding the
-formalism used in the rest of the paper (see details below).
-
-\ANSWER: The Sections II.B and IV are improved to be more
-self-contained now. The idea is that, Section II.B contains mainly an
-overview of Real-Time Maude, and then Section IV describes the model
-with introducing necessary syntax on-the-fly.
-
-Another concern is that the significance of the paper could be much
-better if the paper addressed the problem of modelling RMS in a more
-general way. Instead, the paper takes the form of a case study, where
-the formal modelling of one specific RMS implementation is presented,
-rather than a general method for modelling and analyzing RMS
-implementations.
-
-\ANSWER: Yes, we agree that we have two choices to do the work
-presented in the paper: one is to develop a general way to model RMS
-algorithms or implementations, and then instantiate the general model
-to get a concrete one for our target system; the other is to shape an
-accurate model of the target system directly. To us, there is a trade
-off between these two directions. We chose the latter with some
-concerns. By our experience, the engineers, who write the codes, and
-those, who are in charge of verifying the system or the codes, are
-usually not the same persons. When a verification engineer models a
+To us, there is a trade off between these two directions. We did
+choose the latter according to the following considerations. By our
+experience, \emph{the development engineers (who write the code) and
+  verification engineers (who verify the code or the system) are
+  usually not the same persons.} When a verification engineer models a
 system, he is actually abstacting the system or the codes. It is
 difficult to ensure that the model behaves the same as the system or
-the codes.  And it is more difficult to let other engineers and users
+the codes.  And it is more difficult to make other engineers and users
 believe that the model behaves the same as the system or the
@@
 behaves not only the same as what they had in mind, but also the same
-as what is written in the codes. A way out is to make the model not
-only behave like the codes, but also ``look'' like the codes. This
-requires the model to be as accurate as possible. It makes the model
-specific, but improves the engineers' confidence in the model and the
-verification results. That is also why we emphasize the
-correspondences between the functions in the model and the lines in
-the pseudocode, when we introduce our model in Section~IV. On the
-other hand, we are also interested in the first choice. This will be
-the future work and we would try to get a better balance between them.
+as what is written in the code. A way out is to make the model not
+only \emph{behave like} the code, but also \emph{``look'' like} the
+code. This requires the model to be as accurate as possible, based on
+a fact that the expressivity of the modeling language is powerful
+enough. It makes the model specific, but improves the engineers'
+confidence in the model and the verification results. That is also why
+we emphasize the correspondences between the functions in the model
+and the lines in the pseudocode, when we introduce our model in
+Section~IV.
 
-Also, the discussion about soundness and
-completeness of the analysis (section V.C) is not fully developed and,
-once again, it refers to the specific model rather than being a
-general result.
+On the other hand, we are also interested in the first direction. This
+will be the future work and we would try to get a better balance
+between them.
 
-\ANSWER: The section about soundness and completeness is now made more
-self-contained. The detailed proof of Theorem~2 is included in the
-appendix. On the other hand, since we chose the accurate way to
-achieve the model as discussed above, yes, the proof is a specific
-one.
+\item
+\COMMENT Also, the discussion about soundness and completeness of the
+analysis (section V.C) is not fully developed and, once again, it
+refers to the specific model rather than being a general result.
 
-As a conclusion, even if the significance of the paper is not as much
-as it could be, I think the paper provides something novel and
-interesting for the readers. Hence, my recommendation is to accept
-this paper provided it is made more self-contained (without assuming
-any reader's knowledge about Maude) and the proof of completeness and
-soundness is fully developed.
+\ANSWER Thanks for this comment. The section about soundness and
+completeness is now made more self-contained. The detailed proof of
+Theorem~2 is included in the Appendix. On the other hand, since we
+chose the accurate way to achieve the model as discussed above, yes,
+the proof is a specific one.
 
-Detailed comments
+\end{itemize}
+
+\subsection{Detailed Comments}
 \begin{itemize}
 \item
-Section II.B
+\COMMENT [Section II.B] In the definition of $IR$, it is not clear
+what $s$ and $s'$ are. I guess they are states, but the concept of
+state was not introduced.
 
-- In the definition of $IR$, it is not clear what $s$ and $s'$ are. I
-guess they are states, but the concept of state was not introduced.
-
-\ANSWER: Yes, they can be states. But more generally, they are
-terms. This part has been modified to specify $s$ and $s'$ ($t$ and
-$t'$ now) clearly.
-
-- In the definition of a class, the authors should specify that a
-class includes a collection of rules, otherwise this fact may be
-missed.
-
-\ANSWER: Thanks very much for reminding. This is added now.
+\ANSWER Yes, they can be states. But more generally, they are
+terms. This part has been modified to specify $s$ and $s'$ (in fact,
+$t$ and $t'$ now) clearly.
 
 \item 
-Section III
+\COMMENT [Section II.B] In the definition of a class, the authors
+should specify that a class includes a collection of rules, otherwise
+this fact may be missed.
 
-- Page 2 right column, line -24: The implementation is shown as
-schedule() in Figure 1 $\rightarrow$ The pseudocode of schedule() is
-shown in Figure 1
-
-\ANSWER: It is done.
+\ANSWER Thanks very much for reminding. This is added now.
 
 \item
-Section IV.A
+\COMMENT [Section III] Page 2 right column, line -24: The
+implementation is shown as schedule() in Figure 1 $\rightarrow$ The
+pseudocode of schedule() is shown in Figure 1
 
-- I don't understand the meaning of [ctor] in the definition of some
-operations (maybe because I have no specific background on Maude). I
-could not find the explanation of this writing in the introduction to
-Maude.
+\ANSWER Thanks for the careful reading. It is done now.
 
-\ANSWER: Sorry for missing the explanation of \verb|[ctor]|. It is now
+\item 
+\COMMENT [Section IV.A] I don't understand the meaning of
+\verb|[ctor]| in the definition of some operations (maybe because I
+have no specific background on Maude). I could not find the
+explanation of this writing in the introduction to Maude.
+
+\ANSWER Sorry for missing the explanation of \verb|[ctor]|. It is now
 added when \verb|[ctor]| is used for the first time.
 
-- For the stack sort, the authors mention operations push, pop and
-peek, but then you don't write the definitions of these
-operations. Instead, they write the definitions of bottom and \#,
-which are not explained in the text. This part should be made clearer.
+\item
+\COMMENT [Section IV.A] For the stack sort, the authors mention
+operations push, pop and peek, but then you don't write the
+definitions of these operations. Instead, they write the definitions
+of bottom and \#, which are not explained in the text. This part
+should be made clearer.
 
-\ANSWER: Sorry for the misleading in the text. In fact, \verb|bottom|
+\ANSWER Sorry for the misleading in the text. In fact, \verb|bottom|
 and \verb|#| are constructors of sort \verb|Stack|. This part is
-modified now. Some detailed definitions in codes are removed, and are
+modified now. Some detailed definitions in code are removed, and are
 replaced by more explanations. We hope that the current presentation
@@
 
-- Also, the meaning of NzNat is not explained.
+\item
+\COMMENT [Section IV.A] Also, the meaning of NzNat is not explained.
 
-\ANSWER: Sorry for this incompleteness. \verb|NzNat| did mean non-zero
+\ANSWER Sorry for this incompleteness. \verb|NzNat| did mean non-zero
 natural numbers. \verb|NzNat| is now replaced by \verb|Nat| to reduce
@@
 \item
-Section V.C
-
-- In the statement of theorem 1, the definition of time-robust
-real-time rewrite theory is missing. Also, the meaning of
-tick-stabilizing atomic propositions is not defined. This makes the
+\COMMENT [Section V.C] In the statement of Theorem~1, the definition
+of time-robust real-time rewrite theory is missing. Also, the meaning
+of tick-stabilizing atomic propositions is not defined. This makes the
 section not self-contained.
 
-\ANSWER: In fact, the definitions of time-robustness and
-tick-stabilization (which is now replaced with tick-invariance)
-require more knowledge about rewriting logic. We avoid introducing the
-accurate definitions of them. Instead, we now give short descriptions
-of them. More detailed introduction can be found in the Appendix.
+\ANSWER Sorry for the inconvenience for reading. In fact, the
+definitions of time-robustness and tick-stabilization (which is now
+replaced with tick-invariance) require more knowledge about rewriting
+logic. We avoid introducing the accurate definitions of them. Instead,
+now we give short descriptions of them before Theorem~1. More detailed
+introduction can be found in the Appendix.
 
-- The proof of theorem 2 is missing. The authors just indicate how the
-proof could be developed, but they do not develop it. A possibility
-would be to point to a document where this proof has been developed.
+\item
+\COMMENT [Section V.C] The proof of theorem 2 is missing. The authors
+just indicate how the proof could be developed, but they do not
+develop it. A possibility would be to point to a document where this
+proof has been developed.
 
-\ANSWER: The detailed proof is now included in the appendix.  The
-detailed proof requires a bit more theoretical background about
+\ANSWER We are very happy that the readers are interested in the
+detailed and technical proof, which is now included in the Appendix.
+The detailed proof requires a bit more theoretical background about
 rewriting logic and more details of our model, which we tried to
-simplify in the submission to ease the understanding of our
+simplify in the paper in order to ease the understanding of our
 approach. We would prefer to refer the detailed proof to a
@@
 
-\subsection{Reviewer 3}
-Comments to the Author
+\section{Responses to Reviewer 3}
+\begin{itemize}
+\item
+\COMMENT RMS has many different realization methods, no comparison is
+given to justify the strong point of real-time maude when applied to
+RMS.
 
-This paper stuides the implementation of a rate-monotonic scheduling
-with real-time maude, according to my carefully reading of this paper,
-I do not think this paper is qualified for TIE due to the following
-reasons:
+\ANSWER The comparison could be found in Section VI (and we have
+expanded according to the reviewers' comments :-)). We would like to
+clarify that we are \emph{not implementing} RMS, we are
+\emph{verifying} it. We choose Real-Time Maude since it verifies the
+model using model checking technique. If verification passes, no
+deadline will be missed in the implementation as long as the model
+assumptions are met.
 
-1. Rate-monotonic scheduling is a very simple scheduling and has been
-sufficiently investigated in the field of embedded system, the authors
-claim the innovation of this paper as the implementation using
-real-time maude, however, I cannot see any special point (or
-advantage) when using this real-time maude in modelling RMS.
-
-\ANSWER: We agree that RMS is a very simple scheduling and is the
-optimum at the same time among the fixed-prority ones, making it
-widely applied and sufficiently investigated. Besides the ideal
-setting, the schedulability of RMS was also investigated under
-different kinds of implementations with consideration about overhead,
-as we discuss in the related work section (Section VI). Despite the
-reason that the existing results do not fit our target system using
-RMS, the most important motivation to develop the work presented is
-that, we aim at verifying the system not only for the schedulability,
-but also for the correctness. That is, we want to verify that the
-target system does schedule the tasks under the RMS algorithm. The
-work presented should be seen as a verification problem, instead of a
-schedulability test.
-
-2. RMS has many different realization methods, no comparison is given
-to justify the strong point of real-time maude when applied to RMS.
-
-\ANSWER: The comparison is given in the related work section (Section
+\hide{
+The comparison is given in the related work section (Section
 VI). We would say that we are not implementing RMS algorithm in
@@
 piece of real work in the industry.
+}
 
-3. The assumptions given in IV is too rigid, which makes the
+\item
+\COMMENT Rate-monotonic scheduling is a very simple scheduling and has
+been sufficiently investigated in the field of embedded system, the
+authors claim the innovation of this paper as the implementation using
+real-time maude, however, I cannot see any special point (or
+advantage) when using this real-time maude in modelling RMS.
+
+\ANSWER Thank you for the insightful comment. We agree that RMS has
+been intensively studied, because of its importance. However, most of
+the results are based on the assumption that \emph{task switching does
+  not take time}. That assumption is not realistic. Models with and
+without the assumption have totally different behaviors. For instance,
+as shown in Figure~2(b), in the RMS implementation we verified, the
+switching from time $9$ to $11$ blocks the interrupt handling, hence
+delaying the initiation time of $\tau_1$. To our knowledge, this kind
+of phenomenon would not happen in the theoretical analysis
+models. Although there is very few results that take into account the
+switching overhead (as discussed in Section VI), none of them is
+generic and our system under verification is not in their scope.
+
+Despite the above reason, the most important motivation of this paper
+is to verify the system not only for the schedulability, but also for
+the correctness. That is, we want to verify that the target system
+does schedule the tasks under the RMS algorithm. The work presented
+should be seen as a verification problem, instead of a schedulability
+test. From verification point of view, this paper models a real-world
+RMS implementation with sufficient technical details. Two important
+properties--schedulability and correctness--are verified by model
+checking technique, and the soundness and completeness of the results
+are demonstrated.
+
+\hide{
+is a very simple scheduling and is the optimum at the same time among
+the fixed-prority ones, making it widely applied and sufficiently
+investigated. Besides the ideal setting, the schedulability of RMS was
+also investigated under different kinds of implementations with
+consideration about overhead, as we discuss in the related work
+section (Section VI). Despite the reason that the existing results do
+not fit our target system using RMS, the most important motivation to
+develop the work presented is that, we aim at verifying the system not
+only for the schedulability, but also for the correctness. That is, we
+want to verify that the target system does schedule the tasks under
+the RMS algorithm. The work presented should be seen as a verification
+problem, instead of a schedulability test.
+}
+
+\item
+\COMMENT The assumptions given in IV is too rigid, which makes the
 scheduling problem to be investigated by very simple, then what is the
@@
 
-\ANSWER: As an industrial application, we are not trying to make the
-problem as difficult as possible. Instead, we are trying to simplify
-the model so that the existing tools are able to solve, while the
-target system satisfies the assumptions on the model so that the
-verification results are trustworthy. On the other hand, the
-assumptions are not so rigid. For example, the mask mechanism
-considered as hardware details makes the job initiation times of task
-$\tau_i$ possibly not equal to $kT_i$, implying that the deadlines of
-the jobs may be not equal to $(k+1)T_i$ (see assumption A1'). Another
-example is that non-determinism exists in our model, as discussed in
-Section VI.
+\ANSWER Thank you for the question. When an automatic formal
+verification tool (such as model checker) is used to verify a given
+system, it explores the whole system state space to check whether the
+given property holds. Then the state space explosion is the most
+common problem for an automatic verification tool. That means the
+state space of the system/model is too huge for the tool to explore
+with acceptable temporal and spatial cost. The scale of the state
+space depends on the complexity of the model of the system.
 
-4. The description in section IV (A-E) is trivial, it can only be
-viewed as a simple application of the rewriting logic.
+As an industrial verification application, we are not trying to make
+the problem as difficult as possible. Instead, we are trying to
+simplify the model so that the existing tools are able to solve, while
+the target system satisfies the assumptions on the model so that the
+verification results are trustworthy.
 
-\ANSWER: Yes, we agree that this is an application of rewriting
-logic. In this paper, we do apply the existing theories and techniques
-of rewriting logic to solve a real industrial problem, which has not
-yet been investigated by this sort of techniques, achieving an
-industrial contribution.
+On the other hand, the assumptions are not so rigid. For example, the
+mask mechanism considered makes the job initiation times of task
+$\tau_i$ possibly not equal $kT_i$, implying that the deadlines of the
+jobs may be not equal to $(k+1)T_i$ (see assumption A1'). This is also
+discussed in the beginning of Section IV, pointing out the blocking at
+time $10$ in Figure~2(b). Another example is that non-determinism
+exists in our model, as discussed in Section~VI.
 
-5. The model checking part is not sufficiently discussed, the authors
-only list the commands but not illustrate the mechanism behind these
-commands.
+\item
+\COMMENT The description in section IV (A-E) is trivial, it can only
+be viewed as a simple application of the rewriting logic.
 
-\ANSWER: We do not agree that we should illustrate the mechanism behind
-the model checking commands, since the model checker is not part of
-our contributions in the paper.
+\ANSWER Thanks for the careful reading. We agree that this is an
+application of rewriting logic. In this paper, we do apply the
+existing theories and techniques of rewriting logic to solve a real
+industrial problem, which has not yet been investigated by this sort
+of techniques, achieving an industrial contribution.
 
-Based on the above comments, I thinks this paper is only a simple
-application [26] and [27] in RMS, hence I do not recommend this paper.
+\item
+\COMMENT The model checking part is not sufficiently discussed, the
+authors only list the commands but not illustrate the mechanism behind
+these commands.
+
+\ANSWER Thank you for the suggestion. However, since the model checker
+is not part of our contributions in the paper, we do not think it is
+appropriate to illustrate the mechanism behind the model checking
+commands, which may confuse the readers on the other hand.
+
+\end{itemize}
 

### 2016-03-29 RMS/submission.tex
first version done for major revision
modified version wrt Zhou Min's comments

@@
 We also randomly generate test scenarios under the above setting to
-exam the efficiency of our approach for verifying the schedulability.
-Among the $50$ generated test scenarios with $5$ tasks, we find that
-the execution time of the model checking command for each scenario
-varies from about $300ms$ up to a timeout, which is set to $90$
-minutes. This is because the efficiency of model checking depends on
-the scale of the state space. And the scale is further positively
-correlated with $mn$, where $m$ is the upper bound of $timer$ and $n$
-is the number of periodic tasks. By the generated test scenarios, it
-turns out that the model checking command for schedulability in our
-model is able to handle scenarios, where $mn$ is up to about $10^6$,
-in an acceptable period of time say $90$ minutes.
+exam the efficiency of our approach for verifying the schedulability,
+on an Intel Core 2 Quad Q9550, 2.83GHz, 4-cores machine with 8GB RAM
+running 64-bit Ubuntu 15.04. Among the $50$ generated test scenarios
+with $5$ tasks, we find that the execution time of the model checking
+command for each scenario varies from about $300ms$ up to a timeout,
+which is set to $90$ minutes. This is because the efficiency of model
+checking depends on the scale of the state space. And the scale is
+further positively correlated with $mn$, where $m$ is the upper bound
+of $timer$ and $n$ is the number of periodic tasks. By the generated
+test scenarios, it turns out that the model checking command for
+schedulability in our model is able to handle scenarios, where $mn$ is
+up to about $10^6$, in an acceptable period of time say $90$ minutes.
 
@@
 
-\hide{
-% use section* for acknowledgment
-\ifCLASSOPTIONcompsoc
-  % The Computer Society usually uses the plural form
-  \section*{Acknowledgments}
-\else
-  % regular IEEE prefers the singular form
-  \section*{Acknowledgment}
-\fi
-
-The authors would like to thank...
-}
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{IEEEabrv,submission}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
 \appendix[Proof of Theorem~\ref{t:main}]
@@
 \hide{
+% use section* for acknowledgment
+\ifCLASSOPTIONcompsoc
+  % The Computer Society usually uses the plural form
+  \section*{Acknowledgments}
+\else
+  % regular IEEE prefers the singular form
+  \section*{Acknowledgment}
+\fi
+
+The authors would like to thank...
+}
+
+% Can use something like this to put references on a page
+% by themselves when using endfloat and the captionsoff option.
+\ifCLASSOPTIONcaptionsoff
+  \newpage
+\fi
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+\bibliography{IEEEabrv,submission}
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+
+% biography section
+% 
+% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+% needed around the contents of the optional argument to biography to prevent
+% the LaTeX parser from getting confused when it sees the complicated
+% \includegraphics command within an optional argument. (You could create
+% your own custom macro containing the \includegraphics command to make things
+% simpler here.)
+%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
+% or if you just want to reserve a space for a photo:
+
+\hide{
 

### 2016-03-30 RMS/responses.tex
almost finished, ready to be final version of revision

--- 2016-03-29 RMS/corrections.tex
@@
 % Do not put math or special symbols in the title.
-\title{Corrections to Manuscript No. 15-TIE-3480}
+%\title{Corrections to Manuscript No. 15-TIE-3480}
+\title{Responses to Reviews}
 %
@@
 
+\section{General Response}
+We thank all the reviewers for their careful considerations on our
+paper. The comments are very insightful and invaluable. Thanks to the
+comments, we have improved the paper a lot to make it clearer and
+better presented.
+
+The main changes in the paper are as following:
+\begin{itemize}
+\item
+Section~IV about the formal model of the target implementation is
+revised. Some technical details have been simplified and more literal
+explanations are used to deliver our ideas.
+
+\item
+Section~V.B is expanded. Some discussion on the efficiency of our
+approach is added.
+
+\item 
+The detailed technical proof of Theorem~2 in Section~V.C has been
+included in the Appendix.
+
+\item
+Section~VI about related work has been improved. 
+\end{itemize}
+
+Detailed responses to all the comments are shown in the rest of this
+document.
+
 %\section{Answers to the Reviewers}
-\section{Reponses to Reviewer 1}
+\section{Responses to Reviewer 1}
 \subsection{General Comments}
@@
 \item
-\hide{
-The paper shows a realistic implementation of a Rate-Monotonic
-Scheduling algorithm using Real-Time Maude (a modeling language based
-on rewriting logic) by taking into account the overhead of scheduling
-and some other details of the hardware platform. The correctness of
-the implementation with respect to the algorithm and the completeness
-of the model are verified by model checking, and validated within
-different realistic scenarios.}
+\hide{ The paper shows a realistic implementation of a Rate-Monotonic
+  Scheduling algorithm using Real-Time Maude (a modeling language
+  based on rewriting logic) by taking into account the overhead of
+  scheduling and some other details of the hardware platform. The
+  correctness of the implementation with respect to the algorithm and
+  the completeness of the model are verified by model checking, and
+  validated within different realistic scenarios.}  
 \COMMENT On the positive side, this paper presents a solid piece of
@@
 to verify a real-time system, which is able to investigate important
-problems (such as periodic task scheduling) from a more realistic
-aspect.
+problems (such as periodic task scheduling) in a more realistic level.
 
@@
 
-\ANSWER Thanks for the suggestion. As mentioned in the paper, the
+\ANSWER Thanks for the suggestions. As mentioned in the paper, the
 system under verification is a real-world RMS implementation, which is
@@
 V.B are also real scenarios from the online system. Our industrial
-partner has very strict requirements in the timing. They use at most
-$5$ tasks for scheduling to avoid high overhead.
-
-On the other hand, ``larger'' scenarios are not the same as
-``complex'' scenarios in our model, as discussed in the revised
-Section V.B. We have examined our approach by verifying randomly
-generated scenarios where the number $n$ of tasks are over $10$. In
-that case, the least common multiple of the periods of all tasks can
-be as large as $10^5$ times the interrupt cycle $T$. All feasible
-combinations of execution traces are checked in our approach. Our
-industrial partner agrees that it satisfies their practical
-requirements. Furthermore, the number $n$ of tasks can be $20$ and
-even more if we allow different tasks possess a same period.
+partner has very strict timing requirements. They use at most 5 tasks
+for scheduling to avoid high overhead. They agree that the
+verification results presented in the paper satisfy their practical
+requirements.
+
+On the other hand, as presented in the revised Section V.B, we have
+examined our approach by verifying randomly generated scenarios where
+the number $n$ of tasks are over $10$. In that case, the least common
+multiple of the periods of all tasks can be as large as $10^5$ times
+the interrupt cycle $T$. All feasible combinations of execution traces
+are checked in our approach. Furthermore, the number $n$ of tasks can
+be $20$ and even more if we allow different tasks possess a same
+period.
 
@@
 \ANSWER We are happy that the readers are interested in the detailed
-and technical proof, which is now included in the Appendix. It is true
-that readers may be interested in the detailed proof of Theorem~2 to
-feel convinced of the completeness of our approach. However, the proof
-needs a bit more theoretical background about rewriting logic and more
-technical details of our model, which we have simplified in the paper
-in order to ease the understanding of our approach. We would prefer to
-refer the detailed proof to a non-anonymous technical report, if
-possible, in the final version.
+technical proof, and we have now included it in the Appendix. It is
+true that readers may be interested in the detailed proof of Theorem~2
+to feel convinced of the completeness of our approach. However, the
+proof needs a bit more theoretical background about rewriting logic
+and more technical details of our model, which we have simplified in
+the paper in order to ease the understanding of our approach. We would
+prefer to refer the detailed proof to a non-anonymous technical
+report, if possible, in the final version.
 
@@
 revised. Some unnecessary detailed definitions presented as code are
-removed, and replaced by more explanations. We hope that the current
-presentation would make Section IV more easy-to-read, even for an
-audience who did not know Real-Time Maude before. On the other hand,
-Section VI (Related Work) is also improved. We compare our work with
-the existing theoretical work and the existing verification work in a
-more complete way.
+removed, and replaced by more literal explanations. We hope that the
+current presentation would make Section IV more easy-to-read, even for
+an audience who did not know Real-Time Maude before. On the other
+hand, Section VI (Related Work) is also improved. We compare our work
+with the existing theoretical work and the existing verification work
+in a more complete way.
 
@@
 [24,25] and our approach. One reason is that we have a different
-setting with [24] and [25], because the objectives are different: we
-aim at verifying an RMS implemention from a real-world real-time
-system, while [24] and [25] targeted the RMS algorithm itself. Another
-reason is that [24] and [25] presented no discussion on the efficiency
-and scalability. Furthermore, they used \verb|TMSVL| and an extension
-of SPIN, respectively, as verification tools, which are not
-open-source, making us unable to re-implement their work.
+setting with [24] and [25], since the objectives are different: we aim
+at verifying an RMS implementation from a real-world real-time system,
+while [24] and [25] targeted the RMS algorithm itself. Another reason
+is that [24] and [25] presented no discussion on the efficiency and
+scalability. Furthermore, they used \verb|TMSVL| and an extension of
+SPIN, respectively, as verification tools, which are not open-source,
+making us unable to re-implement their work.
 
@@
 
-\ANSWER Sorry for that. The statement has been corrected. The work
-presented in the paper aims at modeling and verifying a realistic RMS
-implementation in an industrial avionic system. It is a piece of real
-work in the industry. Even though we believe that our approach could
-be applied to other similar systems as well, it means more to that
-specific one. In this sense, ``sufficient'' means that the details
-described in our model meet the requirements and expectations from the
-users and the engineers.
+\ANSWER Sorry for the confusion. The statement has been corrected. The
+work presented in the paper aims at modeling and verifying a realistic
+RMS implementation in an industrial avionic system. It is a piece of
+real work in the industry. In this sense, ``sufficient'' means that
+the details described in our model meet the requirements and
+expectations from the users and the engineers. On the other hand, we
+believe that our approach could be applied to other similar systems as
+well.
 
@@
 
-To us, there is a trade off between these two directions. We did
-choose the latter according to the following considerations. By our
+We chose the latter according to the following considerations. By
 experience, \emph{the development engineers (who write the code) and
@@
   usually not the same persons.} When a verification engineer models a
-system, he is actually abstacting the system or the codes. It is
+system, he is actually abstracting the system or the code. It is
 difficult to ensure that the model behaves the same as the system or
-the codes.  And it is more difficult to make other engineers and users
+the code.  And it is more difficult to make other engineers and users
 believe that the model behaves the same as the system or the
-codes. Furthermore, the developers and users hope that the model
+code. Furthermore, the developers and users hope that the model
 behaves not only the same as what they had in mind, but also the same
@@
 code. This requires the model to be as accurate as possible, based on
-a fact that the expressivity of the modeling language is powerful
+a fact that the expressiveness of the modeling language is powerful
 enough. It makes the model specific, but improves the engineers'
 confidence in the model and the verification results. That is also why
-we emphasize the correspondences between the functions in the model
-and the lines in the pseudocode, when we introduce our model in
-Section~IV.
+we emphasize the corresponding relationship between the functions in
+the model and the lines in the pseudocode, when we introduce our model
+in Section~IV.
 
@@
 
-\ANSWER Thanks for this comment. The section about soundness and
-completeness is now made more self-contained. The detailed proof of
-Theorem~2 is included in the Appendix. On the other hand, since we
-chose the accurate way to achieve the model as discussed above, yes,
-the proof is a specific one.
+\ANSWER Thanks for this comment. The detailed proof of Theorem~2 is
+now included in the Appendix. On the other hand, since we chose the
+accurate way to achieve the model as discussed above, yes, the proof
+is a specific one.
 
@@
 
-\ANSWER Sorry for the misleading in the text. In fact, \verb|bottom|
-and \verb|#| are constructors of sort \verb|Stack|. This part is
-modified now. Some detailed definitions in code are removed, and are
-replaced by more explanations. We hope that the current presentation
-would make Section IV more easy-to-read.
+\ANSWER Sorry for the misleading presentation in the text. In fact,
+\verb|bottom| and \verb|#| are constructors of sort \verb|Stack|. This
+part is modified now. Some detailed definitions in code are removed,
+and are replaced by more explanations. We hope that the current
+presentation would make Section IV more easy-to-read.
 
@@
 
-\ANSWER Sorry for this incompleteness. \verb|NzNat| did mean non-zero
+\ANSWER Sorry for this incompleteness. \verb|NzNat| meant non-zero
 natural numbers. \verb|NzNat| is now replaced by \verb|Nat| to reduce
@@
 \ANSWER Thank you for the insightful comment. We agree that RMS has
-been intensively studied, because of its importance. However, most of
+been intensively studied because of its importance. However, most of
 the results are based on the assumption that \emph{task switching does
@@
 is a very simple scheduling and is the optimum at the same time among
-the fixed-prority ones, making it widely applied and sufficiently
+the fixed-priority ones, making it widely applied and sufficiently
 investigated. Besides the ideal setting, the schedulability of RMS was
@@
 
-\ANSWER Thank you for the question. When an automatic formal
-verification tool (such as model checker) is used to verify a given
-system, it explores the whole system state space to check whether the
-given property holds. Then the state space explosion is the most
-common problem for an automatic verification tool. That means the
-state space of the system/model is too huge for the tool to explore
-with acceptable temporal and spatial cost. The scale of the state
-space depends on the complexity of the model of the system.
+\ANSWER Thank you for the question. When model checking technique is
+used to verify a given system, the tool (model checker) explores the
+whole system state space to check whether the given property
+holds. All feasible combinations of execution traces are checked. As a
+result, the state space explosion is the most common problem for a
+model checker. That means the state space of the system/model is too
+huge for the tool to explore with acceptable temporal and spatial
+cost. The scale of the state space depends on the complexity of the
+model of the system.
 
@@
 
-On the other hand, the assumptions are not so rigid. For example, the
-mask mechanism considered makes the job initiation times of task
-$\tau_i$ possibly not equal $kT_i$, implying that the deadlines of the
-jobs may be not equal to $(k+1)T_i$ (see assumption A1'). This is also
-discussed in the beginning of Section IV, pointing out the blocking at
-time $10$ in Figure~2(b). Another example is that non-determinism
-exists in our model, as discussed in Section~VI.
+On the other hand, the assumptions are actually not that rigid. For
+example, the mask mechanism considered makes the job initiation times
+of task $\tau_i$ possibly not equal $kT_i$, implying that the
+deadlines of the jobs may be not equal to $(k+1)T_i$ (see assumption
+A1'). This is also discussed in the beginning of Section IV, pointing
+out the blocking at time $10$ in Figure~2(b). Another example is that
+non-determinism exists in our model, as discussed in Section~VI.
 

### 2016-03-30 RMS/submission.tex
almost finished, ready to be final version of revision

--- 2016-03-27 RMS/submission.tex
@@
 \end{itemize}
-Note that thanks to the powerful expressivity of Real-Time Maude, we
+Note that thanks to the powerful expressiveness of Real-Time Maude, we
 only need to define an initial state of sort \verb|System| to specify
@@
 
-We also randomly generate test scenarios under the above setting to
-exam the efficiency of our approach for verifying the schedulability.
-Among the $50$ generated test scenarios with $5$ tasks, we find that
-the execution time of the model checking command for each scenario
-varies from about $300ms$ up to a timeout, which is set to $90$
-minutes. This is because the efficiency of model checking depends on
-the scale of the state space. And the scale is further positively
+The results above have demonstrated that our approach is capable of
+handling realistic industrial systems. However to further exam the
+efficiency of our approach, we also apply our method to larger test
+scenarios. Test scenarios are generated randomly. We verify the
+schedulability of them under the above setting on an Intel Core 2 Quad
+Q9550, 2.83GHz, 4-cores machine with 8GB RAM running 64-bit Ubuntu
+15.04. Among the 50 generated test scenarios with 5 tasks, we find
+that the execution time of the model checking command for each
+scenario varies from about $300ms$ up to a timeout, which is set to
+$90$ minutes. This is because the efficiency of model checking depends
+on the scale of the state space. And the scale is further positively
 correlated with $mn$, where $m$ is the upper bound of $timer$ and $n$
@@
 \verb|mte(|$t$\verb|) monus |$r$, for all $r\le$
-\verb|mte(|$t$\verb|)|;
+\verb|mte(|$t$\verb|)|, where \verb|monus| is the minus operation
+defined on sort \verb|Time|;
 

### 2016-03-30 RMS/responses.tex
finished the final version of revision 1

@@
 \newtheorem{lemma}{Lemma}
-\newcommand{\ANSWER}{{\bf RESPONSE: }}
-\newcommand{\COMMENT}{{\bf COMMENT: }}
+\newcommand{\ANSWER}{\medskip\noindent{\bf RESPONSE: }}
+\newcommand{\COMMENT}{\medskip\noindent{\bf COMMENT: }}
 
@@
 
-The main changes in the paper are as following:
+The main changes in the paper are as following, which we have also
+highlighted in the revised manuscript:
 \begin{itemize}
@@
 
-%\section{Answers to the Reviewers}
 \section{Responses to Reviewer 1}
 \subsection{General Comments}
-\begin{itemize}
-
-\item
+
 \hide{ The paper shows a realistic implementation of a Rate-Monotonic
@@
   validated within different realistic scenarios.}
-\COMMENT On the positive side, this paper presents a solid piece of
+
+\COMMENT
+
+On the positive side, this paper presents a solid piece of
 work. Periodic task scheduling is an important (and difficult)
@@
 
-\ANSWER Thanks for the pros. We are happy that the work in the paper
-interests the readers. We hope that it provides a new and formal way
-to verify a real-time system, which is able to investigate important
-problems (such as periodic task scheduling) in a more realistic level.
-
-\item
-\COMMENT The weak point is the lack of evidence of practicality,
-efficiency and scalability. Since there are only small and simplistic
-scenarios to analyze this model, it is difficult to judge the
-effectiveness of the proposed implementation. The key scenarios appear
-conveniently small to allow the implementation fully supports all
-these examples, returning at the same time appropriate counterexamples
-to guide and adjust the design. Is this true for larger examples of
-"real world" applications within the field of industrial real-time
-systems? How do the authors propose to handle very large scenarios?
-How does it behave on typical real-time scheduling problems used in
-industry? I would like to see more complex examples to convince the
-reader of the practicability of the approach on the assumptions given
-for the model, and would probably increase the mentioned benefits. The
-paper does not give any directions to the above problems, and some
-sentences pointing out the difficulties in the implementation of more
-generic and realistic scenarios would be most welcome to understand
-the real contribution of the paper.
-
-\ANSWER Thanks for the suggestions. As mentioned in the paper, the
-system under verification is a real-world RMS implementation, which is
-used in an avionic control system. The scenarios presented in Section
-V.B are also real scenarios from the online system. Our industrial
-partner has very strict timing requirements. They use at most 5 tasks
-for scheduling to avoid high overhead. They agree that the
-verification results presented in the paper satisfy their practical
-requirements.
+\ANSWER
+
+Thanks for the pros. We are happy that the work in the paper interests
+the readers. We hope that it provides a new and formal way to verify a
+real-time system, which is able to investigate important problems
+(such as periodic task scheduling) in a more realistic level.
+
+\COMMENT
+
+The weak point is the lack of evidence of practicality, efficiency and
+scalability. Since there are only small and simplistic scenarios to
+analyze this model, it is difficult to judge the effectiveness of the
+proposed implementation. The key scenarios appear conveniently small
+to allow the implementation fully supports all these examples,
+returning at the same time appropriate counterexamples to guide and
+adjust the design. Is this true for larger examples of "real world"
+applications within the field of industrial real-time systems? How do
+the authors propose to handle very large scenarios?  How does it
+behave on typical real-time scheduling problems used in industry? I
+would like to see more complex examples to convince the reader of the
+practicability of the approach on the assumptions given for the model,
+and would probably increase the mentioned benefits. The paper does not
+give any directions to the above problems, and some sentences pointing
+out the difficulties in the implementation of more generic and
+realistic scenarios would be most welcome to understand the real
+contribution of the paper.
+
+\ANSWER
+
+Thanks for the suggestions. As mentioned in the paper, the system
+under verification is a real-world RMS implementation, which is used
+in an avionic control system. The scenarios presented in Section V.B
+are also real scenarios from the online system. Our industrial partner
+has very strict timing requirements. They use at most 5 tasks for
+scheduling to avoid high overhead. They agree that the verification
+results presented in the paper satisfy their practical requirements.
 
@@
 
-\item
-\COMMENT One of my biggest problems with the theoretical part of this
-work is that the paper is technically solid as far as I can tell, but
-there's not much yet in the way of theorems and results about formal
+\COMMENT
+
+One of my biggest problems with the theoretical part of this work is
+that the paper is technically solid as far as I can tell, but there's
+not much yet in the way of theorems and results about formal
 properties in Maude. The complete and detailed proof of the Theorem 2
@@
 
-\ANSWER We are happy that the readers are interested in the detailed
-technical proof, and we have now included it in the Appendix. It is
-true that readers may be interested in the detailed proof of Theorem~2
-to feel convinced of the completeness of our approach. However, the
-proof needs a bit more theoretical background about rewriting logic
-and more technical details of our model, which we have simplified in
-the paper in order to ease the understanding of our approach. We would
-prefer to refer the detailed proof to a non-anonymous technical
-report, if possible, in the final version.
-
-\item
-\COMMENT Another important point which needs improvement is the
-description of the implementation. I guess other readers might have
-less difficulties with the motivations if they know Maude and the
-Real-Time Maude extension, but if you aim for a more general audience,
-it might not work. Many pages are spent for the description of the
-formal modeling of the implementation and the section is hard to
-read. I highly recommend the authors to thoroughly revise this part of
-the paper to make it easy-to-read. It would be better preferable to
-have a much shorter description of the principal insights for the
-implementation followed by more convincing examples and benchmarks
-with respect to related work to convince the reader of the
-practicability of the approach. You should try to summarize this
-section and to extend the original contribution. From my point of
-view, there is a trade off in this paper between the contributions and
-the presentation of the implementation.
-
-\ANSWER Thank you for the invaluable suggestions. Section IV has been
+\ANSWER
+
+We are happy that the readers are interested in the detailed technical
+proof, and we have now included it in the Appendix. It is true that
+readers may be interested in the detailed proof of Theorem~2 to feel
+convinced of the completeness of our approach. However, the proof
+needs a bit more theoretical background about rewriting logic and more
+technical details of our model, which we have simplified in the paper
+in order to ease the understanding of our approach. We would prefer to
+refer the detailed proof to a non-anonymous technical report, if
+possible, in the final version.
+
+\COMMENT
+
+Another important point which needs improvement is the description of
+the implementation. I guess other readers might have less difficulties
+with the motivations if they know Maude and the Real-Time Maude
+extension, but if you aim for a more general audience, it might not
+work. Many pages are spent for the description of the formal modeling
+of the implementation and the section is hard to read. I highly
+recommend the authors to thoroughly revise this part of the paper to
+make it easy-to-read. It would be better preferable to have a much
+shorter description of the principal insights for the implementation
+followed by more convincing examples and benchmarks with respect to
+related work to convince the reader of the practicability of the
+approach. You should try to summarize this section and to extend the
+original contribution. From my point of view, there is a trade off in
+this paper between the contributions and the presentation of the
+implementation.
+
+\ANSWER
+
+Thank you for the invaluable suggestions. Section IV has been
 revised. Some unnecessary detailed definitions presented as code are
@@
 
-\end{itemize}
-
 \subsection{Detailed Comments}
-\begin{itemize}
-\item
-\COMMENT Page 7, Related Work. More comparisons with other approaches
-based on model checking would help to evaluate pros and cons of an
+
+\COMMENT
+
+Page 7, Related Work. More comparisons with other approaches based on
+model checking would help to evaluate pros and cons of an
 implementation with Real-Time Maude with respect to different
@@
 
-\ANSWER Thanks for the pointing this out. The related work section is
-now improved. More comparisons with the theoretical approaches and
-with [24,25] are added. The differences with [24,25] in the models and
-in the way of modeling are mainly discussed. On the other hand, it is
-a bit difficult to compare the efficiency and scalability between
+\ANSWER
+
+Thanks for the pointing this out. The related work section is now
+improved. More comparisons with the theoretical approaches and with
+[24,25] are added. The differences with [24,25] in the models and in
+the way of modeling are mainly discussed. On the other hand, it is a
+bit difficult to compare the efficiency and scalability between
 [24,25] and our approach. One reason is that we have a different
@@
 
-\item
-\COMMENT Page 8, Conclusions. Where in the paper do you show that the
-details of your "realistic" implementation are "sufficient" for the
-behaviors of all real systems used in the current industry? This
-should be briefly discussed.
-
-\ANSWER Sorry for the confusion. The statement has been corrected. The
-work presented in the paper aims at modeling and verifying a realistic
-RMS implementation in an industrial avionic system. It is a piece of
-real work in the industry. In this sense, ``sufficient'' means that
-the details described in our model meet the requirements and
-expectations from the users and the engineers. On the other hand, we
-believe that our approach could be applied to other similar systems as
-well.
-
-\end{itemize}
+\COMMENT
+
+Page 8, Conclusions. Where in the paper do you show that the details
+of your "realistic" implementation are "sufficient" for the behaviors
+of all real systems used in the current industry? This should be
+briefly discussed.
+
+\ANSWER
+
+Sorry for the confusion. The statement has been corrected. The work
+presented in the paper aims at modeling and verifying a realistic RMS
+implementation in an industrial avionic system. It is a piece of real
+work in the industry. In this sense, ``sufficient'' means that the
+details described in our model meet the requirements and expectations
+from the users and the engineers. On the other hand, we believe that
+our approach could be applied to other similar systems as well.
 
@@
 \subsection{General Comments}
-\begin{itemize}
-\item
-\COMMENT One of the problems with this paper is that it is not
-completely self-contained.  Some knowledge about Real-Time Maude is
-necessary in order to fully understand it.  I found the short
-introduction about Real-Time Maude (section II.B) not enough for
-understanding the formalism used in the rest of the paper (see details
-below).
-
-\ANSWER Thank you very much for pointing this out. The Sections II.B
-and IV are improved to be more self-contained now. The idea is that,
-Section II.B presents mainly an overview of Real-Time Maude, and then
-Section IV describes the model with introducing necessary syntax
-on-the-fly.
-
-\item
-\COMMENT Another concern is that the significance of the paper could
-be much better if the paper addressed the problem of modelling RMS in
-a more general way. Instead, the paper takes the form of a case study,
-where the formal modelling of one specific RMS implementation is
-presented, rather than a general method for modelling and analyzing
-RMS implementations.
-
-\ANSWER Thank you for the suggestion. Yes, we agree that we have two
-choices to do the work presented in the paper: one is to develop a
-general way to model RMS algorithms or implementations, and then
-instantiate the general model to get a concrete one for our target
-system; the other is to shape an accurate model of the target system
-directly.
+
+\COMMENT
+
+One of the problems with this paper is that it is not completely
+self-contained.  Some knowledge about Real-Time Maude is necessary in
+order to fully understand it.  I found the short introduction about
+Real-Time Maude (section II.B) not enough for understanding the
+formalism used in the rest of the paper (see details below).
+
+\ANSWER
+
+Thank you very much for pointing this out. The Sections II.B and IV
+are improved to be more self-contained now. The idea is that, Section
+II.B presents mainly an overview of Real-Time Maude, and then Section
+IV describes the model with introducing necessary syntax on-the-fly.
+
+\COMMENT
+
+Another concern is that the significance of the paper could be much
+better if the paper addressed the problem of modelling RMS in a more
+general way. Instead, the paper takes the form of a case study, where
+the formal modelling of one specific RMS implementation is presented,
+rather than a general method for modelling and analyzing RMS
+implementations.
+
+\ANSWER
+
+Thank you for the suggestion. Yes, we agree that we have two choices
+to do the work presented in the paper: one is to develop a general way
+to model RMS algorithms or implementations, and then instantiate the
+general model to get a concrete one for our target system; the other
+is to shape an accurate model of the target system directly.
 
@@
 
-\item
-\COMMENT Also, the discussion about soundness and completeness of the
-analysis (section V.C) is not fully developed and, once again, it
-refers to the specific model rather than being a general result.
-
-\ANSWER Thanks for this comment. The detailed proof of Theorem~2 is
-now included in the Appendix. On the other hand, since we chose the
+\COMMENT
+
+Also, the discussion about soundness and completeness of the analysis
+(section V.C) is not fully developed and, once again, it refers to the
+specific model rather than being a general result.
+
+\ANSWER
+
+Thanks for this comment. The detailed proof of Theorem~2 is now
+included in the Appendix. On the other hand, since we chose the
 accurate way to achieve the model as discussed above, yes, the proof
@@
 
-\end{itemize}
-
 \subsection{Detailed Comments}
-\begin{itemize}
-\item
-\COMMENT [Section II.B] In the definition of $IR$, it is not clear
-what $s$ and $s'$ are. I guess they are states, but the concept of
-state was not introduced.
-
-\ANSWER Yes, they can be states. But more generally, they are
-terms. This part has been modified to specify $s$ and $s'$ (in fact,
-$t$ and $t'$ now) clearly.
-
-\item 
-\COMMENT [Section II.B] In the definition of a class, the authors
-should specify that a class includes a collection of rules, otherwise
-this fact may be missed.
-
-\ANSWER Thanks very much for reminding. This is added now.
-
-\item
-\COMMENT [Section III] Page 2 right column, line -24: The
-implementation is shown as schedule() in Figure 1 $\rightarrow$ The
-pseudocode of schedule() is shown in Figure 1
-
-\ANSWER Thanks for the careful reading. It is done now.
-
-\item 
-\COMMENT [Section IV.A] I don't understand the meaning of
-\verb|[ctor]| in the definition of some operations (maybe because I
-have no specific background on Maude). I could not find the
-explanation of this writing in the introduction to Maude.
-
-\ANSWER Sorry for missing the explanation of \verb|[ctor]|. It is now
-added when \verb|[ctor]| is used for the first time.
-
-\item
-\COMMENT [Section IV.A] For the stack sort, the authors mention
-operations push, pop and peek, but then you don't write the
-definitions of these operations. Instead, they write the definitions
-of bottom and \#, which are not explained in the text. This part
-should be made clearer.
-
-\ANSWER Sorry for the misleading presentation in the text. In fact,
+
+\COMMENT
+
+[Section II.B] In the definition of $IR$, it is not clear what $s$ and
+$s'$ are. I guess they are states, but the concept of state was not
+introduced.
+
+\ANSWER
+
+Yes, they can be states. But more generally, they are terms. This part
+has been modified to specify $s$ and $s'$ (in fact, $t$ and $t'$ now)
+clearly.
+
+\COMMENT
+
+[Section II.B] In the definition of a class, the authors should
+specify that a class includes a collection of rules, otherwise this
+fact may be missed.
+
+\ANSWER
+
+Thanks very much for reminding. This is added now.
+
+\COMMENT
+
+[Section III] Page 2 right column, line -24: The implementation is
+shown as schedule() in Figure 1 $\rightarrow$ The pseudocode of
+schedule() is shown in Figure 1
+
+\ANSWER
+
+Thanks for the careful reading. It is done now.
+
+\COMMENT
+
+[Section IV.A] I don't understand the meaning of \verb|[ctor]| in the
+definition of some operations (maybe because I have no specific
+background on Maude). I could not find the explanation of this writing
+in the introduction to Maude.
+
+\ANSWER
+
+Sorry for missing the explanation of \verb|[ctor]|. It is now added
+when \verb|[ctor]| is used for the first time.
+
+\COMMENT
+
+[Section IV.A] For the stack sort, the authors mention operations
+push, pop and peek, but then you don't write the definitions of these
+operations. Instead, they write the definitions of bottom and \#,
+which are not explained in the text. This part should be made clearer.
+
+\ANSWER
+
+Sorry for the misleading presentation in the text. In fact,
 \verb|bottom| and \verb|#| are constructors of sort \verb|Stack|. This
@@
 
-\item
-\COMMENT [Section IV.A] Also, the meaning of NzNat is not explained.
-
-\ANSWER Sorry for this incompleteness. \verb|NzNat| meant non-zero
-natural numbers. \verb|NzNat| is now replaced by \verb|Nat| to reduce
+\COMMENT
+
+[Section IV.A] Also, the meaning of NzNat is not explained.
+
+\ANSWER
+
+Sorry for this incompleteness. \verb|NzNat| meant non-zero natural
+numbers. \verb|NzNat| is now replaced by \verb|Nat| to reduce
 unnecessary complexity for the readers.
 
-\item
-\COMMENT [Section V.C] In the statement of Theorem~1, the definition
-of time-robust real-time rewrite theory is missing. Also, the meaning
-of tick-stabilizing atomic propositions is not defined. This makes the
+\COMMENT
+
+[Section V.C] In the statement of Theorem~1, the definition of
+time-robust real-time rewrite theory is missing. Also, the meaning of
+tick-stabilizing atomic propositions is not defined. This makes the
 section not self-contained.
 
-\ANSWER Sorry for the inconvenience for reading. In fact, the
-definitions of time-robustness and tick-stabilization (which is now
-replaced with tick-invariance) require more knowledge about rewriting
-logic. We avoid introducing the accurate definitions of them. Instead,
-now we give short descriptions of them before Theorem~1. More detailed
+\ANSWER
+
+Sorry for the inconvenience for reading. In fact, the definitions of
+time-robustness and tick-stabilization (which is now replaced with
+tick-invariance) require more knowledge about rewriting logic. We
+avoid introducing the accurate definitions of them. Instead, now we
+give short descriptions of them before Theorem~1. More detailed
 introduction can be found in the Appendix.
 
-\item
-\COMMENT [Section V.C] The proof of theorem 2 is missing. The authors
-just indicate how the proof could be developed, but they do not
-develop it. A possibility would be to point to a document where this
-proof has been developed.
-
-\ANSWER We are very happy that the readers are interested in the
-detailed and technical proof, which is now included in the Appendix.
-The detailed proof requires a bit more theoretical background about
-rewriting logic and more details of our model, which we tried to
-simplify in the paper in order to ease the understanding of our
-approach. We would prefer to refer the detailed proof to a
-non-anonymous technical report, if possible, in the final version.
-\end{itemize}
+\COMMENT
+
+[Section V.C] The proof of theorem 2 is missing. The authors just
+indicate how the proof could be developed, but they do not develop
+it. A possibility would be to point to a document where this proof has
+been developed.
+
+\ANSWER
+
+We are very happy that the readers are interested in the detailed and
+technical proof, which is now included in the Appendix.  The detailed
+proof requires a bit more theoretical background about rewriting logic
+and more details of our model, which we tried to simplify in the paper
+in order to ease the understanding of our approach. We would prefer to
+refer the detailed proof to a non-anonymous technical report, if
+possible, in the final version.
 
 \section{Responses to Reviewer 3}
-\begin{itemize}
-\item
-\COMMENT RMS has many different realization methods, no comparison is
-given to justify the strong point of real-time maude when applied to
-RMS.
-
-\ANSWER The comparison could be found in Section VI (and we have
-expanded according to the reviewers' comments :-)). We would like to
-clarify that we are \emph{not implementing} RMS, we are
+
+\COMMENT
+
+RMS has many different realization methods, no comparison is given to
+justify the strong point of real-time maude when applied to RMS.
+
+\ANSWER
+
+The comparison could be found in Section VI (and we have expanded
+according to the reviewers' comments :-)). We would like to clarify
+that we are \emph{not implementing} RMS, we are actually
 \emph{verifying} it. We choose Real-Time Maude since it verifies the
@@
 
-\item
-\COMMENT Rate-monotonic scheduling is a very simple scheduling and has
-been sufficiently investigated in the field of embedded system, the
-authors claim the innovation of this paper as the implementation using
+\COMMENT
+
+Rate-monotonic scheduling is a very simple scheduling and has been
+sufficiently investigated in the field of embedded system, the authors
+claim the innovation of this paper as the implementation using
 real-time maude, however, I cannot see any special point (or
@@
 
-\ANSWER Thank you for the insightful comment. We agree that RMS has
-been intensively studied because of its importance. However, most of
-the results are based on the assumption that \emph{task switching does
-  not take time}. That assumption is not realistic. Models with and
+\ANSWER
+
+Thank you for the insightful comment. We agree that RMS has been
+intensively studied because of its importance. However, most of the
+results are based on the assumption that \emph{task switching does not
+  take time}. That assumption is not realistic. Models with and
 without the assumption have totally different behaviors. For instance,
@@
 switching from time $9$ to $11$ blocks the interrupt handling, hence
-delaying the initiation time of $\tau_1$. To our knowledge, this kind
-of phenomenon would not happen in the theoretical analysis
+delaying the initiation time of $\tau_1$. This kind of phenomenon, to
+our knowledge, would not happen in the theoretical analysis
 models. Although there is very few results that take into account the
@@
 
-\item
-\COMMENT The assumptions given in IV is too rigid, which makes the
-scheduling problem to be investigated by very simple, then what is the
+\COMMENT
+
+The assumptions given in IV is too rigid, which makes the scheduling
+problem to be investigated by very simple, then what is the
 difficulty?
 
-\ANSWER Thank you for the question. When model checking technique is
-used to verify a given system, the tool (model checker) explores the
-whole system state space to check whether the given property
-holds. All feasible combinations of execution traces are checked. As a
-result, the state space explosion is the most common problem for a
-model checker. That means the state space of the system/model is too
-huge for the tool to explore with acceptable temporal and spatial
-cost. The scale of the state space depends on the complexity of the
-model of the system.
+\ANSWER
+
+Thank you for the question. When model checking technique is used to
+verify a given system, the tool (model checker) explores the whole
+system state space to check whether the given property holds. All
+feasible combinations of execution traces are checked. As a result,
+the state space explosion is the most common problem for a model
+checker. That means the state space of the system/model is too huge
+for the tool to explore with acceptable temporal and spatial cost. The
+scale of the state space depends on the complexity of the model of the
+system.
 
@@
 
-\item
-\COMMENT The description in section IV (A-E) is trivial, it can only
-be viewed as a simple application of the rewriting logic.
-
-\ANSWER Thanks for the careful reading. We agree that this is an
-application of rewriting logic. In this paper, we do apply the
-existing theories and techniques of rewriting logic to solve a real
-industrial problem, which has not yet been investigated by this sort
-of techniques, achieving an industrial contribution.
-
-\item
-\COMMENT The model checking part is not sufficiently discussed, the
-authors only list the commands but not illustrate the mechanism behind
-these commands.
-
-\ANSWER Thank you for the suggestion. However, since the model checker
-is not part of our contributions in the paper, we do not think it is
-appropriate to illustrate the mechanism behind the model checking
-commands, which may confuse the readers on the other hand.
-
-\end{itemize}
+\COMMENT
+
+The description in section IV (A-E) is trivial, it can only be viewed
+as a simple application of the rewriting logic.
+
+\ANSWER
+
+Thanks for the careful reading. We agree that this is an application
+of rewriting logic. In this paper, we do apply the existing theories
+and techniques of rewriting logic to solve a real industrial problem,
+which has not yet been investigated by this sort of techniques,
+achieving an industrial contribution.
+
+\COMMENT
+
+The model checking part is not sufficiently discussed, the authors
+only list the commands but not illustrate the mechanism behind these
+commands.
+
+\ANSWER
+
+Thank you for the suggestion. Our work does focus on how to model a
+realistic industrial system and how to apply formal techniques (such
+as model checking) to verify important properties of the system. The
+mechanism behind the model checking commands (i.e. of a model checker)
+is another issue.
+
+The field of model checking techniques and the implementation of model
+checkers have been intensively studied for decades. If the reviewer is
+interested in the mechanism of the model checker provided by Real-Time
+Maude, we would recommend the reference [A] to the reviewer:
+
+\noindent
+[A] S. Eker, J. Meseguer, and A. Sridharanarayanan, ``The Maude LTL
+Model Checker'', {\it Electr. Notes Theor. Comput. Sci.}, vol. 71,
+pp. 162-187, 2002.
+
+\hide{
+However, since the model checker is not part of our contributions in
+the paper, we do not think it is appropriate to illustrate the
+mechanism behind the model checking commands, which may confuse the
+readers on the other hand.}
 

### 2016-03-30 RMS/submission.tex
finished the final version of revision 1

@@
 \usepackage{mathabx}
+
+% for highlighting
+\usepackage{color,soul}
+\soulregister\cite7
+\soulregister\ref7
+\soulregister\pageref7
+
 \newcommand{\hide}[1]{\ignorespaces}
@@
 %due to the large number of control systems that require cyclic activities~\cite{buttazzo2011hard}. 
-A set of periodic tasks is said to be \emph{schedulable} with respect
+{A set of periodic tasks is said to be \emph{schedulable} with respect
 to some scheduling algorithm if all jobs meet their
@@
   case underscores ``\verb|_|'' indicate the positions of parameters.
-  \emph{Terms} are expressions built from function symbols and
-  variables.
+  \hl{\emph{Terms} are expressions built from function symbols and
+  variables.}
 \item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
@@
   such as associativity, commutativity and identity.  $(\Sigma, E\cup
-  A)$ models the system's ``static'' states as terms of some sort, and
+  A)$ models the system's ``static'' states \hl{as terms of some sort}, and
   is equipped with a built-in specification of a sort \verb|Time|.
@@
   where each $cond_j$ is an equality $u_j=v_j$ and $l$ is a
-  \emph{label}, $t,t'$ are terms. Such a rule specifies an
+  \emph{label}, \hl{$t,t'$ are terms}. Such a rule specifies an
   \emph{instantaneous transition}, without consuming time, from an
@@
 where $O$, of sort \verb|Oid|, is the object's \emph{identifier}, and
-$val_i$ is the value of the attribute $att_i$ with $i\in [1,n]$. Rules
-can be defined on a given class. A \emph{subclass} inherits all the
+$val_i$ is the value of the attribute $att_i$ with $i\in [1,n]$. \hl{Rules
+can be defined on a given class.} A \emph{subclass} inherits all the
 attributes and rules of its superclasses.
@@
 
-\section{Formal Modeling of the Implementation}
+\section{\hl{Formal Modeling of the Implementation}}
 \label{s:formalism}
@@
 \end{itemize}
-Note that thanks to the powerful expressiveness of Real-Time Maude, we
-only need to define an initial state of sort \verb|System| to specify
-a given task set. No necessity to modify the model is needed.
+\hl{Note that thanks to the powerful expressiveness of Real-Time Maude, we
+only need to define an initial state of sort} \verb|System| \hl{to specify
+a given task set. No necessity to modify the model is needed.}
 
@@
 
-The results above have demonstrated that our approach is capable of
+\hl{The results above have demonstrated that our approach is capable of
 handling realistic industrial systems. However to further exam the
@@
 model is able to handle scenarios, where $mn$ is up to about $10^6$,
-in an acceptable period of time say $90$ minutes.
+in an acceptable period of time say $90$ minutes.}
 
@@
 of untimed temporal logic model checking, under the maximal time
-sampling strategy, for a large class of real-time systems possessing a
+sampling strategy, \hl{for a large class of real-time systems possessing a
 set of ``good'' properties that is called \emph{time-robustness}, and
@@
   requirements of extra rewriting logic
-  background.}~\cite{DBLP:journals/entcs/OlveczkyM07a}:
+  background.}~\cite{DBLP:journals/entcs/OlveczkyM07a}:}
 \begin{theorem}[\cite{DBLP:journals/entcs/OlveczkyM07a}]
@@
 atomic propositions--\verb|taskTimeout| and \verb|correct|--are
-tick-invariant, then using Theorem~\ref{t:completeness}. For a more
-detailed proof, see the Appendix.
+tick-invariant, then using Theorem~\ref{t:completeness}. \hl{For a more
+detailed proof, see the Appendix.}
 \end{IEEEproof}
@@
 implementations~\cite{DBLP:journals/tse/KatcherAS93}.  However, our
-target implementation is not in their scope. Furthermore, compared
+target implementation is not in their scope. \hl{Furthermore, compared
 with those theoretical analyses, our approach based on formal modeling
@@
 non-determinism via theoretical analyses seems more complicated than
-our automatic approach.
-
-\cite{TianD2011} and~\cite{DBLP:conf/iceccs/CuiDT14} also made use of
+our automatic approach.}
+
+\hl{\cite{TianD2011} and~\cite{DBLP:conf/iceccs/CuiDT14} also made use of
 model checking to analyze the RMS algorithm along the same line but
@@
 completeness statement like Theorem~\ref{t:main} was not given
-in~\cite{DBLP:conf/iceccs/CuiDT14}.
+in~\cite{DBLP:conf/iceccs/CuiDT14}.}
 
@@
 
-\appendix[Proof of Theorem~\ref{t:main}]
+\appendix[\hl{Proof of Theorem~\ref{t:main}}]
 \label{a:proof}

### 2016-07-05 RMS/responses.tex
updated response.tex, ready for 2nd rev

@@
     & \\
-    Manuscript Number: & 15-TIE-3480\\
+    Manuscript Number: & 15-TIE-3480.R1\\
     Manuscript Title: & Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation\\
@@
 \section{Responses to Reviewer 1}
-\subsection{General Comments}
-
-\hide{ The paper shows a realistic implementation of a Rate-Monotonic
-  Scheduling algorithm using Real-Time Maude (a modeling language
-  based on rewriting logic) by taking into account the overhead of
-  scheduling and some other details of the hardware platform. The
-  correctness of the implementation with respect to the algorithm and
-  the completeness of the model are verified by model checking, and
-  validated within different realistic scenarios.}
 
@@
 
-On the positive side, this paper presents a solid piece of
-work. Periodic task scheduling is an important (and difficult)
-problem, and the topic of the paper appears to be well suited within
-the field of the industrial real-time systems. Overall the paper is
-well structured, technically accurate, presents the work in a
-comprehensive and reasonable way, and tackles theoretical as well as
-practical aspects. There are two principal contributions of the paper:
+I have read the revised version of the article. Overall, the authors
+did a very good job at addressing the reviewers' comments and I now
+consider the paper to be acceptable for publication.
 
-1) A novel implementation of the Rate-Monotonic Scheduling algorithm,
-which contains more complex and realistic details instead of the ideal
-setting.
+The revised version of this paper has been improved following the
+suggestions given by the reviewers of the original submission:
 
-2) Rate-Monotonic Scheduling is investigated using Real-Time Maude for
-the first time, to apply formal methods such as model checking and
-theorem proving to analyze theoretical results, verify desired
-properties, and evaluate results.
+(1) Sections II.B and IV are improved to be more self-contained now.
+
+(2) A more detailed but simplified version of a proof of Theorem 2 is
+now included in an Appendix, and the authors refer the detailed proof
+to a non-anonymous technical report.
+
+However, due to the importance of this theorem, I suggest to put the
+complete detailed proof in the printed version.
+
+In summary, I am satisfied with the revisions made by the authors and
+consider that the paper can now be accepted for publication.
 
@@
 
-Thanks for the pros. We are happy that the work in the paper interests
-the readers. We hope that it provides a new and formal way to verify a
-real-time system, which is able to investigate important problems
-(such as periodic task scheduling) in a more realistic level.
+\section{Responses to Reviewer 2}
 
@@
 
-The weak point is the lack of evidence of practicality, efficiency and
-scalability. Since there are only small and simplistic scenarios to
-analyze this model, it is difficult to judge the effectiveness of the
-proposed implementation. The key scenarios appear conveniently small
-to allow the implementation fully supports all these examples,
-returning at the same time appropriate counterexamples to guide and
-adjust the design. Is this true for larger examples of "real world"
-applications within the field of industrial real-time systems? How do
-the authors propose to handle very large scenarios?  How does it
-behave on typical real-time scheduling problems used in industry? I
-would like to see more complex examples to convince the reader of the
-practicability of the approach on the assumptions given for the model,
-and would probably increase the mentioned benefits. The paper does not
-give any directions to the above problems, and some sentences pointing
-out the difficulties in the implementation of more generic and
-realistic scenarios would be most welcome to understand the real
-contribution of the paper.
+My most important concerns have been addressed, so I think the paper
+is now in a shape acceptable for publication. I couldn't check the
+proof completely, but it appears sound.
+
+The significance of the paper remains not very high, because the paper
+shows the proposed technique can be used in one particular case while
+it does not provide results of general validity.
+
+Nevertheless, as I said in my previous review, I believe these initial
+results may be useful for readers, since there seem to be no other
+paper providing a similar detail level in the models.
+
+Detailed comments:
+
+Section II.B, page 2
+
+left column line 37-38
+
+What are uj and vj? Are they terms too? This should be specified in
+the text.
+
+left column lines 42-46
+
+I guess s' is the destination state. This should be specifioed in the
+text.  The sentence "IR and TR together..." should not be part of the
+item. It should go into a new paragraph after the list.
+
+right column lines 22-24
+
+As it seems the timed operators are not used, I suggest to avoid
+mentioning them. By the way, this mention without any other detail is
+useless.
+
+Page 4, line 45
+
+Why is a period of sort Nat? Shouldn't it be Counter?
 
 \ANSWER
-
-Thanks for the suggestions. As mentioned in the paper, the system
-under verification is a real-world RMS implementation, which is used
-in an avionic control system. The scenarios presented in Section V.B
-are also real scenarios from the online system. Our industrial partner
-has very strict timing requirements. They use at most 5 tasks for
-scheduling to avoid high overhead. They agree that the verification
-results presented in the paper satisfy their practical requirements.
-
-On the other hand, as presented in the revised Section V.B, we have
-examined our approach by verifying randomly generated scenarios where
-the number $n$ of tasks are over $10$. In that case, the least common
-multiple of the periods of all tasks can be as large as $10^5$ times
-the interrupt cycle $T$. All feasible combinations of execution traces
-are checked in our approach. Furthermore, the number $n$ of tasks can
-be $20$ and even more if we allow different tasks possess a same
-period.
-
-\hide{
-the modeled RMS implementation serves in an avionic control systems
-from our industrial partner. It is a real-world application within the
-field of industrial real-time systems. And the scenarios presented in
-Section V.B are also real scenarios that our partner is using in the
-system. Our partner indicated that there would be at most $5$ tasks in
-the task set for the implementation. On the other hand, in the current
-version, we have randomly generated large numbers of test cases to
-examine the efficiency of our schedulability test that is based on
-model checking, as discussed in Section V.B. The capability of model
-checking is restricted by the scale of the state space of the
-model. In our model, the model checking can handle scenarios where
-$mn$ is up to $10^6$ in an acceptable period of time. With $mn=10^6$
-and reasonable task periods, the number $n$ of tasks can be at least
-$10$, which has already fulfilled the requirements of the target
-implementation. Further with particular task periods, the number $n$
-of tasks can be $20$ or more.
-}
-
-\COMMENT
-
-One of my biggest problems with the theoretical part of this work is
-that the paper is technically solid as far as I can tell, but there's
-not much yet in the way of theorems and results about formal
-properties in Maude. The complete and detailed proof of the Theorem 2
-should be provided somewhere. If the proof of the main results of
-schedulability and correctness of the model is straightforward (as is
-suggested) it seems not necessary to present a complex formalism on
-Real-Time Maude and all the theorems provided are natural consequences
-of Theorem 1. I agree that even non-surprising results need to be
-investigated in the proof of Theorem 2, some sentences pointing out
-the difficulties in the theoretical formalization in Real-Time Maude
-would be most welcome. Please, include (e.g., in an appendix or even
-in a technical report) a detailed proof.
-
-\ANSWER
-
-We are happy that the readers are interested in the detailed technical
-proof, and we have now included it in the Appendix. It is true that
-readers may be interested in the detailed proof of Theorem~2 to feel
-convinced of the completeness of our approach. However, the proof
-needs a bit more theoretical background about rewriting logic and more
-technical details of our model, which we have simplified in the paper
-in order to ease the understanding of our approach. We would prefer to
-refer the detailed proof to a non-anonymous technical report, if
-possible, in the final version.
-
-\COMMENT
-
-Another important point which needs improvement is the description of
-the implementation. I guess other readers might have less difficulties
-with the motivations if they know Maude and the Real-Time Maude
-extension, but if you aim for a more general audience, it might not
-work. Many pages are spent for the description of the formal modeling
-of the implementation and the section is hard to read. I highly
-recommend the authors to thoroughly revise this part of the paper to
-make it easy-to-read. It would be better preferable to have a much
-shorter description of the principal insights for the implementation
-followed by more convincing examples and benchmarks with respect to
-related work to convince the reader of the practicability of the
-approach. You should try to summarize this section and to extend the
-original contribution. From my point of view, there is a trade off in
-this paper between the contributions and the presentation of the
-implementation.
-
-\ANSWER
-
-Thank you for the invaluable suggestions. Section IV has been
-revised. Some unnecessary detailed definitions presented as code are
-removed, and replaced by more literal explanations. We hope that the
-current presentation would make Section IV more easy-to-read, even for
-an audience who did not know Real-Time Maude before. On the other
-hand, Section VI (Related Work) is also improved. We compare our work
-with the existing theoretical work and the existing verification work
-in a more complete way.
-
-\subsection{Detailed Comments}
-
-\COMMENT
-
-Page 7, Related Work. More comparisons with other approaches based on
-model checking would help to evaluate pros and cons of an
-implementation with Real-Time Maude with respect to different
-languages and tools. The authors should review the comparison with
-[24] and [25] more thoroughly. You should benchmark your approach
-against others.
-
-\ANSWER
-
-Thanks for the pointing this out. The related work section is now
-improved. More comparisons with the theoretical approaches and with
-[24,25] are added. The differences with [24,25] in the models and in
-the way of modeling are mainly discussed. On the other hand, it is a
-bit difficult to compare the efficiency and scalability between
-[24,25] and our approach. One reason is that we have a different
-setting with [24] and [25], since the objectives are different: we aim
-at verifying an RMS implementation from a real-world real-time system,
-while [24] and [25] targeted the RMS algorithm itself. Another reason
-is that [24] and [25] presented no discussion on the efficiency and
-scalability. Furthermore, they used \verb|TMSVL| and an extension of
-SPIN, respectively, as verification tools, which are not open-source,
-making us unable to re-implement their work.
-
-\COMMENT
-
-Page 8, Conclusions. Where in the paper do you show that the details
-of your "realistic" implementation are "sufficient" for the behaviors
-of all real systems used in the current industry? This should be
-briefly discussed.
-
-\ANSWER
-
-Sorry for the confusion. The statement has been corrected. The work
-presented in the paper aims at modeling and verifying a realistic RMS
-implementation in an industrial avionic system. It is a piece of real
-work in the industry. In this sense, ``sufficient'' means that the
-details described in our model meet the requirements and expectations
-from the users and the engineers. On the other hand, we believe that
-our approach could be applied to other similar systems as well.
-
-\section{Responses to Reviewer 2}
-\subsection{General Comments}
-
-\COMMENT
-
-One of the problems with this paper is that it is not completely
-self-contained.  Some knowledge about Real-Time Maude is necessary in
-order to fully understand it.  I found the short introduction about
-Real-Time Maude (section II.B) not enough for understanding the
-formalism used in the rest of the paper (see details below).
-
-\ANSWER
-
-Thank you very much for pointing this out. The Sections II.B and IV
-are improved to be more self-contained now. The idea is that, Section
-II.B presents mainly an overview of Real-Time Maude, and then Section
-IV describes the model with introducing necessary syntax on-the-fly.
-
-\COMMENT
-
-Another concern is that the significance of the paper could be much
-better if the paper addressed the problem of modelling RMS in a more
-general way. Instead, the paper takes the form of a case study, where
-the formal modelling of one specific RMS implementation is presented,
-rather than a general method for modelling and analyzing RMS
-implementations.
-
-\ANSWER
-
-Thank you for the suggestion. Yes, we agree that we have two choices
-to do the work presented in the paper: one is to develop a general way
-to model RMS algorithms or implementations, and then instantiate the
-general model to get a concrete one for our target system; the other
-is to shape an accurate model of the target system directly.
-
-We chose the latter according to the following considerations. By
-experience, \emph{the development engineers (who write the code) and
-  verification engineers (who verify the code or the system) are
-  usually not the same persons.} When a verification engineer models a
-system, he is actually abstracting the system or the code. It is
-difficult to ensure that the model behaves the same as the system or
-the code.  And it is more difficult to make other engineers and users
-believe that the model behaves the same as the system or the
-code. Furthermore, the developers and users hope that the model
-behaves not only the same as what they had in mind, but also the same
-as what is written in the code. A way out is to make the model not
-only \emph{behave like} the code, but also \emph{``look'' like} the
-code. This requires the model to be as accurate as possible, based on
-a fact that the expressiveness of the modeling language is powerful
-enough. It makes the model specific, but improves the engineers'
-confidence in the model and the verification results. That is also why
-we emphasize the corresponding relationship between the functions in
-the model and the lines in the pseudocode, when we introduce our model
-in Section~IV.
-
-On the other hand, we are also interested in the first direction. This
-will be the future work and we would try to get a better balance
-between them.
-
-\COMMENT
-
-Also, the discussion about soundness and completeness of the analysis
-(section V.C) is not fully developed and, once again, it refers to the
-specific model rather than being a general result.
-
-\ANSWER
-
-Thanks for this comment. The detailed proof of Theorem~2 is now
-included in the Appendix. On the other hand, since we chose the
-accurate way to achieve the model as discussed above, yes, the proof
-is a specific one.
-
-\subsection{Detailed Comments}
-
-\COMMENT
-
-[Section II.B] In the definition of $IR$, it is not clear what $s$ and
-$s'$ are. I guess they are states, but the concept of state was not
-introduced.
-
-\ANSWER
-
-Yes, they can be states. But more generally, they are terms. This part
-has been modified to specify $s$ and $s'$ (in fact, $t$ and $t'$ now)
-clearly.
-
-\COMMENT
-
-[Section II.B] In the definition of a class, the authors should
-specify that a class includes a collection of rules, otherwise this
-fact may be missed.
-
-\ANSWER
-
-Thanks very much for reminding. This is added now.
-
-\COMMENT
-
-[Section III] Page 2 right column, line -24: The implementation is
-shown as schedule() in Figure 1 $\rightarrow$ The pseudocode of
-schedule() is shown in Figure 1
-
-\ANSWER
-
-Thanks for the careful reading. It is done now.
-
-\COMMENT
-
-[Section IV.A] I don't understand the meaning of \verb|[ctor]| in the
-definition of some operations (maybe because I have no specific
-background on Maude). I could not find the explanation of this writing
-in the introduction to Maude.
-
-\ANSWER
-
-Sorry for missing the explanation of \verb|[ctor]|. It is now added
-when \verb|[ctor]| is used for the first time.
-
-\COMMENT
-
-[Section IV.A] For the stack sort, the authors mention operations
-push, pop and peek, but then you don't write the definitions of these
-operations. Instead, they write the definitions of bottom and \#,
-which are not explained in the text. This part should be made clearer.
-
-\ANSWER
-
-Sorry for the misleading presentation in the text. In fact,
-\verb|bottom| and \verb|#| are constructors of sort \verb|Stack|. This
-part is modified now. Some detailed definitions in code are removed,
-and are replaced by more explanations. We hope that the current
-presentation would make Section IV more easy-to-read.
-
-\COMMENT
-
-[Section IV.A] Also, the meaning of NzNat is not explained.
-
-\ANSWER
-
-Sorry for this incompleteness. \verb|NzNat| meant non-zero natural
-numbers. \verb|NzNat| is now replaced by \verb|Nat| to reduce
-unnecessary complexity for the readers.
-
-\COMMENT
-
-[Section V.C] In the statement of Theorem~1, the definition of
-time-robust real-time rewrite theory is missing. Also, the meaning of
-tick-stabilizing atomic propositions is not defined. This makes the
-section not self-contained.
-
-\ANSWER
-
-Sorry for the inconvenience for reading. In fact, the definitions of
-time-robustness and tick-stabilization (which is now replaced with
-tick-invariance) require more knowledge about rewriting logic. We
-avoid introducing the accurate definitions of them. Instead, now we
-give short descriptions of them before Theorem~1. More detailed
-introduction can be found in the Appendix.
-
-\COMMENT
-
-[Section V.C] The proof of theorem 2 is missing. The authors just
-indicate how the proof could be developed, but they do not develop
-it. A possibility would be to point to a document where this proof has
-been developed.
-
-\ANSWER
-
-We are very happy that the readers are interested in the detailed and
-technical proof, which is now included in the Appendix.  The detailed
-proof requires a bit more theoretical background about rewriting logic
-and more details of our model, which we tried to simplify in the paper
-in order to ease the understanding of our approach. We would prefer to
-refer the detailed proof to a non-anonymous technical report, if
-possible, in the final version.
 
@@
 
-RMS has many different realization methods, no comparison is given to
-justify the strong point of real-time maude when applied to RMS.
+This paper has been revised according to reviewers comments and
+suggestions, I recommend to accept it for publication after minor
+revisions on possible typos, such as the word "monus" on page 9 and
+10.
 
 \ANSWER
-
-The comparison could be found in Section VI (and we have expanded
-according to the reviewers' comments :-)). We would like to clarify
-that we are \emph{not implementing} RMS, we are actually
-\emph{verifying} it. We choose Real-Time Maude since it verifies the
-model using model checking technique. If verification passes, no
-deadline will be missed in the implementation as long as the model
-assumptions are met.
-
-\hide{
-The comparison is given in the related work section (Section
-VI). We would say that we are not implementing RMS algorithm in
-Real-Time Maude. In fact, we are using Real-Time Maude to model an
-realistic implementation of RMS from an industrial avionic
-system. There is no theoretical reason telling us that we have to use
-Real-Time Maude to model the RMS implementation. However, the existing
-verification work as far as we know cannot fit our needs, as discussed
-in Section VI. Therefore, we developed the work in the paper, as a
-piece of real work in the industry.
-}
-
-\COMMENT
-
-Rate-monotonic scheduling is a very simple scheduling and has been
-sufficiently investigated in the field of embedded system, the authors
-claim the innovation of this paper as the implementation using
-real-time maude, however, I cannot see any special point (or
-advantage) when using this real-time maude in modelling RMS.
-
-\ANSWER
-
-Thank you for the insightful comment. We agree that RMS has been
-intensively studied because of its importance. However, most of the
-results are based on the assumption that \emph{task switching does not
-  take time}. That assumption is not realistic. Models with and
-without the assumption have totally different behaviors. For instance,
-as shown in Figure~2(b), in the RMS implementation we verified, the
-switching from time $9$ to $11$ blocks the interrupt handling, hence
-delaying the initiation time of $\tau_1$. This kind of phenomenon, to
-our knowledge, would not happen in the theoretical analysis
-models. Although there is very few results that take into account the
-switching overhead (as discussed in Section VI), none of them is
-generic and our system under verification is not in their scope.
-
-Despite the above reason, the most important motivation of this paper
-is to verify the system not only for the schedulability, but also for
-the correctness. That is, we want to verify that the target system
-does schedule the tasks under the RMS algorithm. The work presented
-should be seen as a verification problem, instead of a schedulability
-test. From verification point of view, this paper models a real-world
-RMS implementation with sufficient technical details. Two important
-properties--schedulability and correctness--are verified by model
-checking technique, and the soundness and completeness of the results
-are demonstrated.
-
-\hide{
-is a very simple scheduling and is the optimum at the same time among
-the fixed-priority ones, making it widely applied and sufficiently
-investigated. Besides the ideal setting, the schedulability of RMS was
-also investigated under different kinds of implementations with
-consideration about overhead, as we discuss in the related work
-section (Section VI). Despite the reason that the existing results do
-not fit our target system using RMS, the most important motivation to
-develop the work presented is that, we aim at verifying the system not
-only for the schedulability, but also for the correctness. That is, we
-want to verify that the target system does schedule the tasks under
-the RMS algorithm. The work presented should be seen as a verification
-problem, instead of a schedulability test.
-}
-
-\COMMENT
-
-The assumptions given in IV is too rigid, which makes the scheduling
-problem to be investigated by very simple, then what is the
-difficulty?
-
-\ANSWER
-
-Thank you for the question. When model checking technique is used to
-verify a given system, the tool (model checker) explores the whole
-system state space to check whether the given property holds. All
-feasible combinations of execution traces are checked. As a result,
-the state space explosion is the most common problem for a model
-checker. That means the state space of the system/model is too huge
-for the tool to explore with acceptable temporal and spatial cost. The
-scale of the state space depends on the complexity of the model of the
-system.
-
-As an industrial verification application, we are not trying to make
-the problem as difficult as possible. Instead, we are trying to
-simplify the model so that the existing tools are able to solve, while
-the target system satisfies the assumptions on the model so that the
-verification results are trustworthy.
-
-On the other hand, the assumptions are actually not that rigid. For
-example, the mask mechanism considered makes the job initiation times
-of task $\tau_i$ possibly not equal $kT_i$, implying that the
-deadlines of the jobs may be not equal to $(k+1)T_i$ (see assumption
-A1'). This is also discussed in the beginning of Section IV, pointing
-out the blocking at time $10$ in Figure~2(b). Another example is that
-non-determinism exists in our model, as discussed in Section~VI.
-
-\COMMENT
-
-The description in section IV (A-E) is trivial, it can only be viewed
-as a simple application of the rewriting logic.
-
-\ANSWER
-
-Thanks for the careful reading. We agree that this is an application
-of rewriting logic. In this paper, we do apply the existing theories
-and techniques of rewriting logic to solve a real industrial problem,
-which has not yet been investigated by this sort of techniques,
-achieving an industrial contribution.
-
-\COMMENT
-
-The model checking part is not sufficiently discussed, the authors
-only list the commands but not illustrate the mechanism behind these
-commands.
-
-\ANSWER
-
-Thank you for the suggestion. Our work does focus on how to model a
-realistic industrial system and how to apply formal techniques (such
-as model checking) to verify important properties of the system. The
-mechanism behind the model checking commands (i.e. of a model checker)
-is another issue.
-
-The field of model checking techniques and the implementation of model
-checkers have been intensively studied for decades. If the reviewer is
-interested in the mechanism of the model checker provided by Real-Time
-Maude, we would recommend the reference [A] to the reviewer:
-
-\noindent
-[A] S. Eker, J. Meseguer, and A. Sridharanarayanan, ``The Maude LTL
-Model Checker'', {\it Electr. Notes Theor. Comput. Sci.}, vol. 71,
-pp. 162-187, 2002.
-
-\hide{
-However, since the model checker is not part of our contributions in
-the paper, we do not think it is appropriate to illustrate the
-mechanism behind the model checking commands, which may confuse the
-readers on the other hand.}
 

### 2016-07-09 RMS/responses.tex
corrected wrt some comments

@@
 
+\subsection{General Comments}
+
 \COMMENT
@@
 
-Detailed comments:
+\ANSWER
 
-Section II.B, page 2
+\subsection{Detailed Comments}
 
-left column line 37-38
+\COMMENT
 
-What are uj and vj? Are they terms too? This should be specified in
-the text.
+[Section II.B, page 2] left column, lines 37-38:
+What are $u_j$ and $v_j$? Are they terms too? This should be specified
+in the text.
 
-left column lines 42-46
+\ANSWER
 
-I guess s' is the destination state. This should be specifioed in the
+Yes, they are also terms. This is specified now.
+
+\COMMENT
+
+[Section II.B, page 2] left column, lines 42-46:
+I guess $s'$ is the destination state. This should be specified in the
 text.  The sentence "IR and TR together..." should not be part of the
@@
 
-right column lines 22-24
+\ANSWER
 
+Yes, thank you for pointing this out. They are modified now.
+
+\COMMENT
+
+[Section II.B, page 2] right column, lines 22-24:
 As it seems the timed operators are not used, I suggest to avoid
@@
 
-Page 4, line 45
+\ANSWER
 
+\COMMENT
+
+[Page 4] line 45:
 Why is a period of sort Nat? Shouldn't it be Counter?

### 2016-07-09 RMS/submission.tex
corrected wrt some comments

--- 2016-03-30 RMS/submission.tex
@@
 \hyphenation{op-tical net-works semi-conduc-tor}
+
+\usepackage{microtype}
 
@@
 Real-Time Maude models systems as \emph{modules}. A module specifies a
-\emph{real-time rewrite theory} ${\cal R} = (\Sigma, E\cup A , IR,
-TR)$, where:
+\emph{real-time rewrite theory} ${\cal R} = (\Sigma, E\cup A ,
+\mathit{IR}, \mathit{TR})$, where:
 \begin{itemize}
@@
   is equipped with a built-in specification of a sort \verb|Time|.
-\item $IR$ is a set of \emph{labeled conditional rewrite rules}
-  specifying the system's local transitions. Each rule has the form
-  $[l]~:~t\rightarrow t'\mbox{ \textbf{if} }\bigwedge^n_{j=1}cond_j$,
-  where each $cond_j$ is an equality $u_j=v_j$ and $l$ is a
-  \emph{label}, $t,t'$ are terms. Such a rule specifies an
-  \emph{instantaneous transition}, without consuming time, from an
-  instance of $t$ to the corresponding instance of $t'$,
-  \emph{provided} the conditions hold.
-\item $TR$ is a set of (\emph{labeled}) \emph{tick rules} of the form
-  $[l]~:~\{s\}\rightarrow\{s'\} \mbox{ \textbf{in time} }r\mbox{
-  \textbf{if} }cond$ that specify \emph{timed transitions}, which
-  advances time by $r$ time units in the \emph{entire} state modeled
-  by term $s$. $IR$ and $TR$ together model the ``dynamic'' behaviors
-  of the system.
+\item $\mathit{IR}$ is a set of \emph{labeled conditional rewrite
+  rules} specifying the system's local transitions. Each rule has the
+  form $[l]~:~t\rightarrow t'\mbox{ \textbf{if}
+  }\bigwedge^n_{j=1}cond_j$, where each $cond_j$ is an equality
+  $u_j=v_j$, and $l$ is a \emph{label}, \hl{$t,t',u_j,v_j$ are terms}. Such
+  a rule specifies an \emph{instantaneous transition}, without
+  consuming time, from an instance of $t$ to the corresponding
+  instance of $t'$, \emph{provided} the conditions hold.
+\item $\mathit{TR}$ is a set of (\emph{labeled}) \emph{tick rules} of
+  the form $[l]~:~\{s\}\rightarrow\{s'\} \mbox{\textbf{ in time}
+  }r\mbox{ \textbf{if} }cond$ that specify \emph{timed
+    transitions}. \hl{Each tick rule advances time by $r$ time units from
+  the \emph{entire} state modeled by term $s$ to the destination state
+  $s'$.}
 \end{itemize}
+
+\hl{$\mathit{IR}$ and $\mathit{TR}$ together model the ``dynamic''
+behaviors of the system.}
 

### 2016-07-10 RMS/submission.tex
modified a bit

@@
 \verb|true|. A temporal logic \emph{formula} is constructed by state
-propositions and temporal logic operators such as \verb|True|,
-\verb|False|, \verb|~|(negation), \verb|/\|, \verb|\/|,
-\verb|->|(implication), \verb|[]|(``always'') and
+propositions and temporal logic operators such as \verb|~|(negation),
+\verb|\/|(or), \verb|[]|(``always'') and
 \verb|U|(``until''). Real-Time Maude supports both \emph{timed} and
@@
 \verb|error| existing in \verb|L|. Then schedulability can be
-formalized as the temporal logic formula: \verb|[](~taskTimeout)|. As
+formalized as the temporal logic formula: \verb|[](~taskTimeout)|,
+\hl{expressing that the proposition} \verb|taskTimeout| \hl{is always false}. As
 the property is not \emph{clock-related}, given an initial state
@@
 correctness property is formalized by the temporal logic formula:
-\verb|([]correct) \/ (correct U taskTimeout)|, and can be verified by
-the following untimed model checking command provided an initial state
-\verb|init|:
+\verb|([]correct)\/(correct U taskTimeout)|, \hl{stating that}
+\verb|correct| \hl{is always true, or is true until} \verb|taskTimeout|
+\hl{holds}. It can be verified by the following untimed model checking
+command provided an initial state \verb|init|:
 \begin{verbatim}

### 2016-07-10 RMS/responses.tex
complete responses to reviewer 2

@@
 
+Thanks for pointing this out. Actually some of the timed operators are
+used in Section V.A when describing the properties we verify. This
+little problem is addressed now. We now only mention the necessary
+timed operators which will be used, and also add explanations when
+using them in Section V.A.
+
 \COMMENT
@@
 [Page 4] line 45: 
-Why is a period of sort Nat? Shouldn't it be Counter?
+Why is a period of sort \verb|Nat|? Shouldn't it be \verb|Counter|?
 
 \ANSWER
+
+This is a good question!
+
+In our model, as we discuss in Section IV.A, a \verb|Counter| contains
+two elements: the execution time (the time how long a task has been
+executing for) and the computation requirement (the time how long a
+task should execute for). A \verb|Counter| is some kind of
+``dynamic''. It is like a countdown timer to complete the execution of
+a task. Different from \verb|Counter|, a period is a ``static''
+property of a task. Therefore, a period is modeled as a term of sort
+\verb|Nat| instead of \verb|Counter|.
+
+On the other hand, a period can also be modeled as a \verb|Counter|.
+Then it becomes a countdown timer to trigger an execution request of
+the task, while the execution requests are currently triggered by the
+periodic interrupts in our model.
+
+Both ways to model periods are feasible. We choose the former since
+its behaviors are more faithful to the real implementation we model
+and verify.
 

### 2016-07-10 RMS/responses.tex
modified a bit

@@
 suggestions, I recommend to accept it for publication after minor
-revisions on possible typos, such as the word "monus" on page 9 and
+revisions on possible typos, such as the word ``monus'' on page 9 and
 10.
@@
 \ANSWER
-
-\hide{
-% use section* for acknowledgment
-\ifCLASSOPTIONcompsoc
-  % The Computer Society usually uses the plural form
-  \section*{Acknowledgments}
-\else
-  % regular IEEE prefers the singular form
-  \section*{Acknowledgment}
-\fi
-
-The authors would like to thank...
-}
 

### 2016-07-10 RMS/submission.tex
complete responses to reviewer 2
modified a bit

@@
 % thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
+\interdisplaylinepenalty=2500
 % after loading amsmath to restore such page breaks as IEEEtran.cls normally
@@
 \verb|true|. A temporal logic \emph{formula} is constructed by state
-propositions and temporal logic operators such as \verb|~|(negation),
-\verb|\/|(or), \verb|[]|(``always'') and
-\verb|U|(``until''). Real-Time Maude supports both \emph{timed} and
+propositions and \hl{temporal logic operators such as} \verb|~|\hl{(negation),}
+\verb|\/|\hl{(disjunction),} \verb|[]|\hl{(``always''),}
+\verb|U|\hl{(``until'')}. Real-Time Maude supports both \emph{timed} and
 \emph{untimed LTL model checking}. The untimed model checking command
@@
 \verb|mte(|$t$\verb|) monus |$r$, for all $r\le$
-\verb|mte(|$t$\verb|)|, where \verb|monus| is the minus operation
-defined on sort \verb|Time|;
+\verb|mte(|$t$\verb|)|, where \verb|monus| is the built-in minus
+operation defined on sort \verb|Time|;
 

### 2016-07-11 RMS/responses.tex
responsed more comments

@@
 
+Thank you for the approval.
+
+Yes, we also agree that Theorem 2 is important. We would consider
+including the detailed proof in the printed version, if the page limit
+of TIE permits.
+
 \section{Responses to Reviewer 2}
@@
 
+Thanks for the pros and the careful reading.
+
+``monus'' is the name of the built-in minus operation defined in
+Real-Time Maude, as we introduced in Lemma A.1 at page 8 in the
+Appendix. It is not a typo. We have also spell checked the whole
+manuscript again to avoid typos.
+
 % Can use something like this to put references on a page

### 2016-07-11 RMS/responses.tex
first version of 2nd revision is complete

@@
 \section{General Response}
-We thank all the reviewers for their careful considerations on our
-paper. The comments are very insightful and invaluable. Thanks to the
-comments, we have improved the paper a lot to make it clearer and
-better presented.
+We thank all the reviewers for their invaluable comments, which help
+us a lot in improving the paper. We believe that the paper is now more
+self-contained and better presented than the original submission.
 
-The main changes in the paper are as following, which we have also
-highlighted in the revised manuscript:
-\begin{itemize}
-\item
-Section~IV about the formal model of the target implementation is
-revised. Some technical details have been simplified and more literal
-explanations are used to deliver our ideas.
-
-\item
-Section~V.B is expanded. Some discussion on the efficiency of our
-approach is added.
-
-\item 
-The detailed technical proof of Theorem~2 in Section~V.C has been
-included in the Appendix.
-
-\item
-Section~VI about related work has been improved. 
-\end{itemize}
-
-Detailed responses to all the comments are shown in the rest of this
-document.
+According to the comments, we make some minor revisions, which are
+highlighted in the manuscript.  And detailed responses to all the
+comments are shown in the rest of this document.
 
@@
 
-Thank you for the approval.
+Thanks for your positive comments.
 
@@
 
+Thank you very much for the approval.
+
 \subsection{Detailed Comments}
@@
 
-Yes, they are also terms. This is specified now.
+Yes, they are terms as well. This is specified now.
 
@@
 
-Thanks for pointing this out. Actually some of the timed operators are
+Thanks for the suggestion. Actually some of the timed operators are
 used in Section V.A when describing the properties we verify. This

### 2016-07-12 RMS/responses.tex
changed responses.tex into single-column template

@@
-\documentclass[10pt,journal]{IEEEtran}
+\documentclass[a4paper]{article}
 %
@@
 %
-\ifCLASSOPTIONcompsoc
+% \ifCLASSOPTIONcompsoc
   % IEEE Computer Society needs nocompress option
   % requires cite.sty v4.0 or later (November 2003)
-  \usepackage[nocompress,noadjust]{cite}
-\else
+%   \usepackage[nocompress,noadjust]{cite}
+% \else
   % normal IEEE
-  \usepackage[noadjust]{cite}
-\fi
+%  \usepackage[noadjust]{cite}
+%\fi
 % cite.sty was written by Donald Arseneau
@@
 %
-\ifCLASSINFOpdf
+%\ifCLASSINFOpdf
   % \usepackage[pdftex]{graphicx}
@@
   % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
+%\else
   % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
@@
   % \DeclareGraphicsExtensions{.eps}
-\fi
+%\fi
 % graphicx was written by David Carlisle and Sebastian Rahtz. It is
@@
 % *** SUBFIGURE PACKAGES ***
-\ifCLASSOPTIONcompsoc
-  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
-\else
-  \usepackage[caption=false,font=footnotesize]{subfig}
-\fi
+%% \ifCLASSOPTIONcompsoc
+%%   \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
+%% \else
+%%   \usepackage[caption=false,font=footnotesize]{subfig}
+%% \fi
 % subfig.sty, written by Steven Douglas Cochran, is the modern replacement
@@
 \newcommand{\hide}[1]{\ignorespaces}
-\newcommand{\jx}[1]{{\bf Jiaxiang: }#1{ \bf End}}
+\newcommand{\jx}[1]{{\textbf{Jiaxiang: }}#1{ \textbf{ End}}}
 \newtheorem{theorem}{Theorem}
 \newtheorem{lemma}{Lemma}
-\newcommand{\ANSWER}{\medskip\noindent{\bf RESPONSE: }}
-\newcommand{\COMMENT}{\medskip\noindent{\bf COMMENT: }}
+\newcommand{\ANSWER}{\medskip\noindent\textbf{ RESPONSE: }}
+\newcommand{\COMMENT}{\medskip\noindent\textbf{ COMMENT: }}
 
@@
 % make the title area
-%\maketitle
+% \maketitle
 
@@
 % papers do.
-%\IEEEdisplaynontitleabstractindextext
+% \IEEEdisplaynontitleabstractindextext
 % \IEEEdisplaynontitleabstractindextext has no effect when using
@@
 
-\twocolumn[
-  \begin{@twocolumnfalse}
+%% \twocolumn[
+%%   \begin{@twocolumnfalse}
 \maketitle
@@
     Manuscript Number: & 15-TIE-3480.R1\\
-    Manuscript Title: & Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation\\
+    Manuscript Title: & Formal Modeling and Verification of a \\
+    & Rate-Monotonic Scheduling Implementation \\
     & with Real-Time Maude \\
@@
 
-  \end{@twocolumnfalse}
-]
+  %% \end{@twocolumnfalse}
+
+%% \setlength\parindent{10pt}
+
+%% ]
 
@@
 
-[Section II.B, page 2] left column, lines 37-38:
+{[Section II.B, page 2]} left column, lines 37-38:
 What are $u_j$ and $v_j$? Are they terms too? This should be specified
@@
 
-[Section II.B, page 2] left column, lines 42-46:
+{[Section II.B, page 2]} left column, lines 42-46:
 I guess $s'$ is the destination state. This should be specified in the
@@
 
-[Section II.B, page 2] right column, lines 22-24:
+{[Section II.B, page 2]} right column, lines 22-24:
 As it seems the timed operators are not used, I suggest to avoid
@@
 
-[Page 4] line 45: 
+{[Page 4]} line 45: 
 Why is a period of sort \verb|Nat|? Shouldn't it be \verb|Counter|?
@@
 
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,submission}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
-\hide{
-
-\begin{IEEEbiography}{Jiaxiang Liu}
-Biography text here.
-\end{IEEEbiography}
-
-% if you will not have a photo at all:
-\begin{IEEEbiographynophoto}{John Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-\begin{IEEEbiographynophoto}{Jane Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
-}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-% that's all folks
 \end{document}

### 2016-07-12 RMS/responses.tex
almost finish 2nd revision, spell check needed

@@
 \newtheorem{lemma}{Lemma}
-\newcommand{\ANSWER}{\medskip\noindent\textbf{ RESPONSE: }}
-\newcommand{\COMMENT}{\medskip\noindent\textbf{ COMMENT: }}
+\newcommand{\ANSWER}{\medskip\noindent\textbf{RESPONSE: }}
+\newcommand{\COMMENT}{\medskip\noindent\textbf{COMMENT: }}
 
@@
 \title{Responses to Reviews}
+\date{}
 %
@@
 \maketitle
-
+\vspace{-30pt}
 \begin{center}
@@
 We thank all the reviewers for their invaluable comments, which help
-us a lot in improving the paper. We believe that the paper is now more
-self-contained and better presented than the original submission.
+us a lot in improving the paper.
 
-According to the comments, we make some minor revisions, which are
+%% We believe that the paper is now more
+%% self-contained and better presented than the original submission.
+
+According to the comments, we make several minor revisions, which are
 highlighted in the manuscript.  And detailed responses to all the
@@
 
-Yes, we also agree that Theorem 2 is important. We would consider
-including the detailed proof in the printed version, if the page limit
-of TIE permits.
+%% As to Theorem~2, we also agree that it is important. But due to the
+%% page limit of TIE, we have to refer the detailed proof of this theorem
+%% to the technical report, where the proof is more detailed and more
+%% self-contained.
+
+We agree that Theorem~2 is very important and that is also the reason
+we have carefully revised the proof and extended it to contain all
+necessary deduction steps. However, due to the space limit of TIE, we
+found it almost impossible to include the proof without comprising
+other important details of the paper. As a result, we have to put the
+detailed proof as a separate technical document.
+
+%% Yes, we also agree that Theorem 2 is important. We would consider
+%% including the detailed proof in the printed version, if the page limit
+%% of TIE permits.
 
@@
 
-{[Section II.B, page 2]} left column, lines 37-38:
+[Section II.B, page 2] left column, lines 37-38:
 What are $u_j$ and $v_j$? Are they terms too? This should be specified
@@
 
-{[Section II.B, page 2]} left column, lines 42-46:
+[Section II.B, page 2] left column, lines 42-46:
 I guess $s'$ is the destination state. This should be specified in the
@@
 
-{[Section II.B, page 2]} right column, lines 22-24:
+[Section II.B, page 2] right column, lines 22-24:
 As it seems the timed operators are not used, I suggest to avoid
@@
 
-Thanks for the suggestion. Actually some of the timed operators are
-used in Section V.A when describing the properties we verify. This
-little problem is addressed now. We now only mention the necessary
-timed operators which will be used, and also add explanations when
-using them in Section V.A.
+Thanks for the suggestion. It is addressed now. Actually some of the
+timed operators are used in Section~V.A when describing the properties
+we verify. We now only mention the necessary timed operators which
+will be used, and also add explanations when using them in
+Section~V.A.
 
@@
 
-{[Page 4]} line 45: 
+[Page 4] line 45: 
 Why is a period of sort \verb|Nat|? Shouldn't it be \verb|Counter|?
@@
 
-In our model, as we discuss in Section IV.A, a \verb|Counter| contains
-two elements: the execution time (the time how long a task has been
-executing for) and the computation requirement (the time how long a
-task should execute for). A \verb|Counter| is some kind of
-``dynamic''. It is like a countdown timer to complete the execution of
-a task. Different from \verb|Counter|, a period is a ``static''
-property of a task. Therefore, a period is modeled as a term of sort
-\verb|Nat| instead of \verb|Counter|.
+In our model, a period is of sort \verb|Nat| instead of
+\verb|Counter|.
+%% as we discuss in Section IV.A, a \verb|Counter| contains
+%% two elements: the execution time (the time how long a task has been
+%% executing for) and the computation requirement (the time how long a
+%% task should execute for).
+A \verb|Counter| is some kind of ``dynamic''. It is like a countdown
+timer to complete the execution of a task. However, a period is a
+``static'' property of a task. Therefore, a period is modeled as a
+term of sort \verb|Nat| instead of \verb|Counter|.
 
@@
 Then it becomes a countdown timer to trigger an execution request of
-the task, while the execution requests are currently triggered by the
-periodic interrupts in our model.
+the task.
+%% while the execution requests are currently triggered by the
+%% periodic interrupts in our model.
 
@@
 
-Thanks for the pros and the careful reading.
+Thanks for your pros and carefully reading. However, ``monus'' is not
+a typo but the name of the built-in minus operation defined in
+Real-Time Maude (as explained in Lemma A.1). We have done proof
+checking again to avoid other typos.
 
-``monus'' is the name of the built-in minus operation defined in
-Real-Time Maude, as we introduced in Lemma A.1 at page 8 in the
-Appendix. It is not a typo. We have also spell checked the whole
-manuscript again to avoid typos.
+%% Thanks for the pros and the careful reading. We have spell checked
+%% again the whole manuscript to avoid typos.
+
+%% ``monus'' is not a typo. It is the name of the built-in minus
+%% operation defined in Real-Time Maude, as we introduced in Lemma A.1 at
+%% page 8 in the Appendix.
 

### 2016-09-05 presentation/main.tex
add a slide file

\documentclass{beamer}
\usepackage[latin1]{inputenc}
\usepackage{hyperref}
\usepackage{colortbl}
\usetheme{Warsaw}
\title[Make a LaTeX presentation using Beamer]
      {Termination Analysis of Imperative Programs Using Bitvector Arithmetic}
\author{Stephan Falke\inst{1}, Deepak Kapur\inst{2}, and Carsten Sinz\inst{1}}
\institute{\inst{1} Institute for Theoretical Computer Science, KIT, Germany \and %
  \inst{2} Dept. of Computer Science, University of New Mexico, USA}
\date{\footnotesize Verified Software: Theories, Tools, Experiments \\ VSTTE 2012}

\AtBeginSubsection[]
{
  \begin{frame}<beamer>
    \frametitle{Layout}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Summary}
This paper proposes a novel method for \textcolor{red}{encoding the wrap-around
  behavior of bitvector arithmetic within integer arithmetic}, such
that existing methods for reasoning about the termination of integer
arithmetic programs can be employed for reasoning about the
termination of bitvector arithmetic programs.
\end{frame}

\section{Introduction}

\begin{frame}{Existing Methods}
  Bitvectors are treated as (unbounded) integers (or as real numbers).

  This approximation can cause errors in both directions:

%  \begin{itemize}
\begin{columns}
  \begin{column}{5cm}
    \begin{block}{Block title}
This is a block in blue
\end{block}

%  \item First column
\end{column}
\begin{column}{5cm}
%\item Second column
\end{column}
\end{columns}
 % \end{itemize}

\end{frame}

\subsection{sub1}
\begin{frame}{1st}
  List:
\begin{itemize}
\pause \item Beamer is a wonderful class
\pause \item One can make animations
\pause \item One uses the\textbf{pause} command, for example
\pause \item in order to bring in important ideas
\end{itemize}
\end{frame}

\subsection{sub2}
\begin{frame}{2}
  This is a short introduction to Beamer class.
  \begin{itemize}
\item<2-> appears from slide 2 on
\item<3-> appears from slide 3 on
\item<4-> appears from slide 4 on
\item<5-> appears from slide 5 on
\end{itemize}
\end{frame}

\section{TWO}
\begin{frame}{3}
  This is a short introduction to Beamer class.
  \begin{itemize}
\item<2-> appears from slide 2 on
\item<2-3> appears from slide 2 to slide 4
\item<4> appears on slide 4
\item<3-> appears from slide 3 on
\end{itemize}
\end{frame}

\begin{frame}{4}
  See
\begin{itemize}[<+->]
\item L
\item A
\item T
\item E
\item X
\end{itemize}
\end{frame}

\begin{frame}
\uncover<2->
{appear from slide 2 on\\}
\uncover<3-4>
{appears from 3 to slide 4\\}
\uncover<4>{appears on slide 4\\}
\uncover<3->{appears from slide 3 on\\}
\end{frame}

\begin{frame}

\only<2->
{appear from slide 2 on\\}
\only<3-4>
{appears from 3 to slide 4\\}
\only<4>{appear on slide 4\\}
\only<3->{appear from slide 2 on\\}

\end{frame}

\begin{frame}

\begin{itemize}
\item Language used by Beamer: L\uncover<2->{A}TEX
\item Language used by Beamer: L\only<2->{A}TEX
\end{itemize}

\end{frame}

\begin{frame}

\invisible<2>{This text will be invisible on slide 2, but not on others slides}\\
This text is always visible\\
\uncover<1->{Beamer} \uncover<2->{is}  \uncover<3->{super} \uncover<4->{powerful}

\end{frame}

\begin{frame}{5}
  \alt<3>{I am on slide 3\\}{I am not on slide 3\\}
\only<2->
{appears from slide 2 on\\}
\only<3-4>
{appears from slide 3 to slide 4\\}
\only<4>{appears on slide 4\\}
\only<3->{appears from slide 3 on\\}
\alert<1>{This text} \alert<2>{is} \alert<3>{red}
\end{frame}

\begin{frame}{6}
\begin{itemize}
\item <+-| alert@+> Robert De Niro
\item <+-| alert@+> Brian De Palma
\item <+-| alert@+> Gerard Depardieu
\item <+-| alert@+> Tux
\end{itemize}
\end{frame}

\begin{frame}{7}
  Some colors ...\\
\color<2>{green}{Green color} \\
Great !!!
\end{frame}

\begin{frame}[label=link]
The link will point to this frame
\end{frame}

\begin{frame}{8}
  \hyperlink{link}{\beamergotobutton{Refer to this page}}

  \begin{block}{Block title}
This is a block in blue
\end{block}

\invisible<3->{
\begin{alertblock}{Alert-block title}
This is a block in red
\end{alertblock}}

\invisible<2>{
\begin{exampleblock}{Example-block title}
This is a block in green
\end{exampleblock}}
  \end{frame}

\begin{frame}{9}
\begin{tabular}{lcccc}
  Class & A & B & C & D \\\hline
  X     & 1 & 2 & 3 & 4 \\\pause
  Y     & 3 & 4 & 5 & 6 \pause\\
  Z     &5&6&7&8
\end{tabular}
\end{frame}

\begin{frame}{10}
\begin{tabular}{lc<{\onslide<2->}c<{\onslide<3->}c<{\onslide<4->}c<{\onslide}c}
  Class & A & B & C & D \\
  X     & 1 & 2 & 3 & 4 \\
  Y     & 3 & 4 & 5 & 6 \\
  Z     &5&6&7&8
\end{tabular}
\end{frame}

\begin{frame}{11}
\begin{columns}
\begin{column}{0.5\textwidth}
First column
\end{column}
\begin{column}{0.5\textwidth}
Second column
\end{column}
\end{columns}
\end{frame}

\end{document}

### 2016-09-05 presentation/main.tex
first version of the slides

@@
 \usepackage{colortbl}
+\usepackage{alltt}
+%\usepackage{amsmath,amssymb, latexsym}
+\usepackage{stmaryrd}
 \usetheme{Warsaw}
-\title[Make a LaTeX presentation using Beamer]
-      {Termination Analysis of Imperative Programs Using Bitvector Arithmetic}
+\title[Termination Analysis Using Bitvector Arithmetic]{Termination Analysis of Imperative Programs Using Bitvector Arithmetic}
 \author{Stephan Falke\inst{1}, Deepak Kapur\inst{2}, and Carsten Sinz\inst{1}}
@@
 
-\AtBeginSubsection[]
+\AtBeginSection[]
 {
   \begin{frame}<beamer>
-    \frametitle{Layout}
+    \frametitle{Outline}
     \tableofcontents[currentsection,currentsubsection]
@@
 }
+
+\makeatletter
+% add a macro that saves its argument
+\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
+\newbox\footlineextrabox
+
+% add a beamer template that sets the saved argument in a box.
+% The * means that the beamer font and color "footline extra" are automatically added. 
+\defbeamertemplate*{footline extra}{default}{
+    \begin{beamercolorbox}[ht=2.25ex,dp=1ex,leftskip=\Gm@lmargin]{footline extra}
+    \insertfootlineextra
+    %\par\vspace{2.5pt}
+    \end{beamercolorbox}
+}
+
+\addtobeamertemplate{footline}{%
+    % set the box with the extra footline material but make it add no vertical space
+    \setbox\footlineextrabox=\vbox{\usebeamertemplate*{footline extra}}
+    \vskip -\ht\footlineextrabox
+    \vskip -\dp\footlineextrabox
+    \box\footlineextrabox%
+}
+{}
+
+% patch \begin{frame} to reset the footline extra material
+\let\beamer@original@frame=\frame
+\def\frame{\gdef\insertfootlineextra{}\beamer@original@frame}
+\footlineextra{}
+\makeatother
+
+\setbeamercolor{footline extra}{fg=structure.fg}% for instance
 
@@
 termination of bitvector arithmetic programs.
+
+\end{frame}
+
+\begin{frame}{Outline}
+\tableofcontents
 \end{frame}
@@
 
-\begin{frame}{Existing Methods}
+\begin{frame}[fragile]{Existing Methods}
   Bitvectors are treated as (unbounded) integers (or as real numbers).
 
+\medskip
   This approximation can cause errors in both directions:
 
-%  \begin{itemize}
+\begin{itemize}
+
 \begin{columns}
-  \begin{column}{5cm}
-    \begin{block}{Block title}
-This is a block in blue
-\end{block}
+  \begin{column}{4.5cm}
+\item Terminating wrt bitvector arithmetic, but non-terminating wrt
+  integer arithmetic.
 
-%  \item First column
+\begin{exampleblock}{Example}
+\begin{verbatim}
+void f(int i) {
+  while (i > 0)  
+    i++;
+}
+\end{verbatim}
+\end{exampleblock}
+
 \end{column}
-\begin{column}{5cm}
-%\item Second column
+
+\begin{column}{4.5cm}
+\item Terminating wrt integer arithmetic, but non-terminating wrt
+  bitvector arithmetic.
+
+\begin{exampleblock}{Example}
+\begin{verbatim}
+void g(int i, int j) {
+  while (i <= j) 
+    i++;
+}
+\end{verbatim}
+\end{exampleblock}
+
 \end{column}
 \end{columns}
- % \end{itemize}
+
+\end{itemize}
 
@@
 
-\subsection{sub1}
-\begin{frame}{1st}
-  List:
+\begin{frame}{Related Work [CKR+10]}
+Main differences:
 \begin{itemize}
-\pause \item Beamer is a wonderful class
-\pause \item One can make animations
-\pause \item One uses the\textbf{pause} command, for example
-\pause \item in order to bring in important ideas
+\item The use of quantifiers. Quantifier elimination before ranking
+  function synthesis is expensive.
+\item Template matching for linear ranking functions allows to use
+  SAT, QBF and SMT solver.
 \end{itemize}
+
+\footlineextra{[CKR+10] Byron Cook, Daniel Kroening, Philipp Rümmer,
+  Christoph M. Wintersteiger: Ranking Function Synthesis for
+  Bit-Vector Relations. TACAS 2010: 236-250}
 \end{frame}
 
-\subsection{sub2}
-\begin{frame}{2}
-  This is a short introduction to Beamer class.
-  \begin{itemize}
-\item<2-> appears from slide 2 on
-\item<3-> appears from slide 3 on
-\item<4-> appears from slide 4 on
-\item<5-> appears from slide 5 on
-\end{itemize}
+\section{Termination Analysis in \texttt{KITTeL}}
+
+\begin{frame}{The Approach of \texttt{KITTeL}}
+\texttt{KITTeL} is a termination analysis tool on LLVM-IR.
+
+\begin{block}{Bird's-eye view of \texttt{KITTeL}'s approach}
+\begin{figure}
+  \includegraphics[width=\textwidth]{view.png}
+\end{figure}
+\end{block}
+
 \end{frame}
 
-\section{TWO}
-\begin{frame}{3}
-  This is a short introduction to Beamer class.
-  \begin{itemize}
-\item<2-> appears from slide 2 on
-\item<2-3> appears from slide 2 to slide 4
-\item<4> appears on slide 4
-\item<3-> appears from slide 3 on
-\end{itemize}
+\begin{frame}{From C to LLVM-IR}
+From C code to LLVM-IR code, and then \emph{basic block graph}:
+\begin{exampleblock}{Example 1}
+\begin{figure}
+  \includegraphics[width=\textwidth]{CtoLLVM.png}
+\end{figure}
+\end{exampleblock}
 \end{frame}
 
-\begin{frame}{4}
-  See
-\begin{itemize}[<+->]
-\item L
-\item A
-\item T
-\item E
-\item X
+\begin{frame}{From LLVM-IR to Transition System}
+The corresponding transition system of Example~1:
+\begin{exampleblock}{Example 1}
+\begin{figure}
+  \includegraphics[width=\textwidth]{LLVMtoTS.png}
+\end{figure}
+\end{exampleblock}
+\end{frame}
+
+\begin{frame}[fragile]{From Transition Systems to TRSs}
+\begin{itemize}
+\item A transition system can be represented in the form of an
+  \texttt{int}-based TRS.
+\item Each transition $s_1 \rightarrow^\lambda s_2$ gives rise to a
+  rewrite rule
+\begin{center}
+$s_1(x_1,\ldots,x_n) \rightarrow s_2(e_1,\ldots,e_n) ~ \llbracket\varphi\rrbracket$
+\end{center}
+\end{itemize}
+\begin{exampleblock}{TRS of Example 1}
+\footnotesize
+\begin{tabular}{rcl}
+$\verb|entry|(\verb|x|, \verb|y|, \verb|y.0|, \verb|r.0|, \verb|%1|, \verb|%2|)$ 
+  & $\!\!\!\!\rightarrow\!\!\!\!$ 
+  & $\verb|bb1|(\verb|x|, \verb|y|, \verb|y|, 1, \verb|%1|, \verb|%2|)$ \\
+$\verb|bb1|(\verb|x|, \verb|y|, \verb|y.0|, \verb|r.0|, \verb|%1|, \verb|%2|)$ 
+  & $\!\!\!\!\rightarrow\!\!\!\!$ 
+  & $\verb|bb|(\verb|x|, \verb|y|, \verb|y.0|, \verb|r.0|, \verb|%1|, \verb|%2|) 
+  ~ \llbracket \verb|y.0| > 0 \rrbracket$ \\
+$\verb|bb1|(\verb|x|, \verb|y|, \verb|y.0|, \verb|r.0|, \verb|%1|, \verb|%2|)$ 
+  & $\!\!\!\!\rightarrow\!\!\!\!$ 
+  & $\verb|return|(\verb|x|, \verb|y|, \verb|y.0|, \verb|r.0|, \verb|%1|, \verb|%2|) 
+  ~ \llbracket \neg(\verb|y.0| > 0) \rrbracket$ \\
+$\verb|bb|(\verb|x|, \verb|y|, \verb|y.0|, \verb|r.0|, \verb|%1|, \verb|%2|)$ 
+  & $\!\!\!\!\rightarrow\!\!\!\!$ 
+  & $\verb|bb1|(\verb|x|, \verb|y|, \verb|y.0| - 1, \verb|r.0|, \verb|r.0| * \verb|x|, \verb|y.0| - 1)$
+\end{tabular}
+\end{exampleblock}
+\end{frame}
+
+\begin{frame}[fragile]{Reducing TRSs}
+The number of arguments, hence the TRS, can be further reduced by
+standard compiler techniques:
+\begin{itemize}
+\item \emph{Backward slicing} removes all variables that are not
+  relevant for the control flow of the program. (\verb|x|, \verb|r.0|,
+  \verb|%1|, and \verb|%2| in Example~1)
+\item \emph{Liveness analysis} removes variables before they are
+  defined or after they are no longer needed. (\verb|y.0| in
+  \verb|entry| and \verb|return|; \verb|y| in all function symbols but
+  \verb|entry|)
+\end{itemize}
+
+\begin{exampleblock}{Reduced TRS of Example 1}
+\footnotesize
+\begin{tabular}{rcl}
+$\verb|entry|(\verb|y|)$ 
+  & $\rightarrow$ 
+  & $\verb|bb1|(\verb|y|)$ \\
+$\verb|bb1|(\verb|y.0|)$ 
+  & $\rightarrow$ 
+  & $\verb|bb|(\verb|y.0|) 
+  ~ \llbracket \verb|y.0| > 0 \rrbracket$ \\
+$\verb|bb1|(\verb|y.0|)$ 
+  & $\rightarrow$ 
+  & $\verb|return|() 
+  ~ \llbracket \neg(\verb|y.0| > 0) \rrbracket$ \\
+$\verb|bb|(\verb|y.0|)$ 
+  & $\rightarrow$ 
+  & $\verb|bb1|(\verb|y.0| - 1)$
+\end{tabular}
+\end{exampleblock}
+\end{frame}
+
+\section{Encoding Bitvector Arithmetic}
+
+\begin{frame}{Overview of the Encoding}
+The bitvector $b_{n-1}\cdots b_0$ is represented by its \emph{signed}
+(two's complement) integer 
+\begin{center}
+$-b_{n-1}\cdot 2^{n-1} + \Sigma^{n-2}_{i=0}b_i\cdot 2^i \;\;\in \{
+  -2^{n-1},\ldots,2^{n-1}-1\}$.
+\end{center}
+
+The semantics of the bitvector operations and the wrap-around behavior
+of bitvector arithmetic is handled by two phases:
+\begin{enumerate}
+\item The conversion of \emph{comparison}, \emph{arithmetical},
+  \emph{bitwise} and \emph{extension/truncation} instructions is
+  adapted.  In particular, signed and unsigned operations are
+  distinguished.
+\item The wrap-around behavior of the arithmetical instructions is
+  modeled in order to ensure that they are within the appropriate
+  ranges.
+\end{enumerate}
+\end{frame}
+
+\begin{frame}{Phase 1}
+Phase 1 is performed during the generation of the transition
+system/\texttt{int}-based TRS. The conversion of instructions is
+adapted in order to correspond to their semantics on bitvectors.
+
+\medskip
+The comparison instructions:
+\begin{figure}
+  \includegraphics[width=\textwidth]{ins1.png}
+\end{figure}
+
+For example,
+\footnotesize
+\begin{eqnarray}
+ugt(x,y) & = & (x \ge 0 \land y \ge 0 \land x > y) \nonumber\\
+& & \lor\; (x \ge 0 \land y < 0) \nonumber\\
+& & \lor\; (x < 0 \land y < 0 \land x > y) \nonumber
+\end{eqnarray}
+\end{frame}
+
+\begin{frame}{Phase 1 (cont'd)}
+\begin{figure}
+  \includegraphics[width=\textwidth]{ins2.png}
+\end{figure}
+\end{frame}
+
+\begin{frame}[fragile]{Phase 1 (cont'd)}
+Some instructions are approximated by introducing new variables and
+constraints.
+
+\medskip
+For example, the \verb|and| instruction, its constraint:
+\begin{eqnarray}
+and(x,y,n_i) & = & (x \ge 0 \land y \ge 0 \land n_i \ge 0 \land n_i \le x \land n_i \le y) \nonumber\\
+& & \lor\; (x \ge 0 \land y < 0 \land n_i \ge 0 \land n_i \le x) \nonumber\\
+& & \lor\; (x < 0 \land y \ge 0 \land n_i \ge 0 \land n_i \le y) \nonumber\\
+& & \lor\; (x < 0 \land y < 0 \land n_i < 0 \land n_i \le x \land n_i \le y) \nonumber
+\end{eqnarray}
+\end{frame}
+
+\begin{frame}{Phase 2}
+Phase 2 is performed after generating the \texttt{int}-based TRS. The
+wrap-around behavior of the arithmetical instructions is modeled by
+modifying the generated \texttt{int}-based TRS.
+
+For this, the wrap-around behavior is simulated by explicitly
+normalizing the resulting integers to be in the appropriate ranges.
+
+Each rewrite rule
+\begin{center}
+$\rho : f(x_1,\ldots,x_n) \rightarrow g(p_1,\ldots,p_m) ~ \llbracket \varphi \rrbracket$
+\end{center}
+should be replaced by:
+\begin{figure}
+  \includegraphics[width=0.6\textwidth]{rules.png}
+\end{figure}
+
+\end{frame}
+
+\begin{frame}[fragile]{Phase 2 (cont'd)}
+For example, the rule 
+\begin{center}
+$\verb|bb|(\verb|i.0|) \rightarrow \verb|bb1|(\verb|i.0|) + 1)$
+\end{center}
+is replaced by
+\begin{block}{}
+\begin{tabular}{rcl}
+$\verb|bb|(\verb|i.0|)$ & $\rightarrow$ 
+  & $\verb|bb1|^\#(\verb|i.0| + 1) ~ \llbracket inrange(\verb|i.0|) \rrbracket$ \\
+$\verb|bb1|^\#(\verb|i.0|)$ & $\rightarrow$ 
+  & $\verb|bb1|^\#(\verb|i.0| + 2^{32}) ~ \llbracket \verb|i.0| < intmin(32) \rrbracket$ \\
+$\verb|bb1|^\#(\verb|i.0|)$ & $\rightarrow$ 
+  & $\verb|bb1|^\#(\verb|i.0| - 2^{32}) ~ \llbracket \verb|i.0| > intmax(32) \rrbracket$ \\
+$\verb|bb1|^\#(\verb|i.0|)$ & $\rightarrow$ 
+  & $\verb|bb1|(\verb|i.0|) ~ \llbracket inrange(\verb|i.0|) \rrbracket$ \\
+\end{tabular}
+\end{block}
+\end{frame}
+
+\section{Conclusion}
+
+\begin{frame}{Conclusion}
+\begin{itemize}
+\item The approach is \emph{sound}.
+\begin{itemize}
+\item The instructions are \emph{soundly} approximated.
+\item The wrap-around behavior is correctly modeled.
+\end{itemize}
+\item The implementation is powerful than the related approach in
+  [CKR+10], with a comparable average time.
+\item The approach can be combined with other existing techniques for
+  analyzing termination of transition systems/\texttt{int}-based TRSs.
 \end{itemize}
@@
 \begin{frame}
-\uncover<2->
-{appear from slide 2 on\\}
-\uncover<3-4>
-{appears from 3 to slide 4\\}
-\uncover<4>{appears on slide 4\\}
-\uncover<3->{appears from slide 3 on\\}
-\end{frame}
-
-\begin{frame}
-
-\only<2->
-{appear from slide 2 on\\}
-\only<3-4>
-{appears from 3 to slide 4\\}
-\only<4>{appear on slide 4\\}
-\only<3->{appear from slide 2 on\\}
-
-\end{frame}
-
-\begin{frame}
-
-\begin{itemize}
-\item Language used by Beamer: L\uncover<2->{A}TEX
-\item Language used by Beamer: L\only<2->{A}TEX
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}
-
-\invisible<2>{This text will be invisible on slide 2, but not on others slides}\\
-This text is always visible\\
-\uncover<1->{Beamer} \uncover<2->{is}  \uncover<3->{super} \uncover<4->{powerful}
-
-\end{frame}
-
-\begin{frame}{5}
-  \alt<3>{I am on slide 3\\}{I am not on slide 3\\}
-\only<2->
-{appears from slide 2 on\\}
-\only<3-4>
-{appears from slide 3 to slide 4\\}
-\only<4>{appears on slide 4\\}
-\only<3->{appears from slide 3 on\\}
-\alert<1>{This text} \alert<2>{is} \alert<3>{red}
-\end{frame}
-
-\begin{frame}{6}
-\begin{itemize}
-\item <+-| alert@+> Robert De Niro
-\item <+-| alert@+> Brian De Palma
-\item <+-| alert@+> Gerard Depardieu
-\item <+-| alert@+> Tux
-\end{itemize}
-\end{frame}
-
-\begin{frame}{7}
-  Some colors ...\\
-\color<2>{green}{Green color} \\
-Great !!!
-\end{frame}
-
-\begin{frame}[label=link]
-The link will point to this frame
-\end{frame}
-
-\begin{frame}{8}
-  \hyperlink{link}{\beamergotobutton{Refer to this page}}
-
-  \begin{block}{Block title}
-This is a block in blue
-\end{block}
-
-\invisible<3->{
-\begin{alertblock}{Alert-block title}
-This is a block in red
-\end{alertblock}}
-
-\invisible<2>{
-\begin{exampleblock}{Example-block title}
-This is a block in green
-\end{exampleblock}}
-  \end{frame}
-
-\begin{frame}{9}
-\begin{tabular}{lcccc}
-  Class & A & B & C & D \\\hline
-  X     & 1 & 2 & 3 & 4 \\\pause
-  Y     & 3 & 4 & 5 & 6 \pause\\
-  Z     &5&6&7&8
-\end{tabular}
-\end{frame}
-
-\begin{frame}{10}
-\begin{tabular}{lc<{\onslide<2->}c<{\onslide<3->}c<{\onslide<4->}c<{\onslide}c}
-  Class & A & B & C & D \\
-  X     & 1 & 2 & 3 & 4 \\
-  Y     & 3 & 4 & 5 & 6 \\
-  Z     &5&6&7&8
-\end{tabular}
-\end{frame}
-
-\begin{frame}{11}
-\begin{columns}
-\begin{column}{0.5\textwidth}
-First column
-\end{column}
-\begin{column}{0.5\textwidth}
-Second column
-\end{column}
-\end{columns}
+\begin{center}
+\LARGE Thank you!
+\end{center}
 \end{frame}

### 2016-09-09 paper-discussion/main.tex
renamed the directory for paper discussion slides

--- 2016-09-05 presentation/main.tex
@@
   \begin{columns}
+
     \begin{column}{4.5cm}
@@
 \end{exampleblock}
-
   \end{column}
@@
 \end{column}
+
 \end{columns}
@@
 \begin{figure}
-  \includegraphics[width=\textwidth]{view.png}
+  \includegraphics[width=\textwidth]{figs/view.png}
 \end{figure}
@@
 \begin{figure}
-  \includegraphics[width=\textwidth]{CtoLLVM.png}
+  \includegraphics[width=\textwidth]{figs/CtoLLVM.png}
 \end{figure}
@@
 \begin{figure}
-  \includegraphics[width=\textwidth]{LLVMtoTS.png}
+  \includegraphics[width=\textwidth]{figs/LLVMtoTS.png}
 \end{figure}
@@
 \item A transition system can be represented in the form of an
-  \texttt{int}-based TRS.
+  \textcolor{red}{\texttt{int}-based TRS}.
 \item Each transition $s_1 \rightarrow^\lambda s_2$ gives rise to a
@@
 \begin{itemize}
-\item \emph{Backward slicing} removes all variables that are not
+\item<2-> \textcolor{red}{Backward slicing} removes all variables that are not
   relevant for the control flow of the program. (\verb|x|, \verb|r.0|,
   \verb|%1|, and \verb|%2| in Example~1)
-\item \emph{Liveness analysis} removes variables before they are
+\item<3-> \textcolor{red}{Liveness analysis} removes variables before they are
   defined or after they are no longer needed. (\verb|y.0| in
@@
 \end{itemize}
-
 \begin{exampleblock}{Reduced TRS of Example 1}
@@
 \begin{frame}{Overview of the Encoding}
+\uncover<2->{
 The bitvector $b_{n-1}\cdots b_0$ is represented by its \emph{signed}
@@
 \end{center}
+}
 
+\uncover<3->{
 The semantics of the bitvector operations and the wrap-around behavior
 of bitvector arithmetic is handled by two phases:
+}
 \begin{enumerate}
-\item The conversion of \emph{comparison}, \emph{arithmetical},
-  \emph{bitwise} and \emph{extension/truncation} instructions is
+\item<4-> The conversion of \textcolor{red}{comparison}, \textcolor{red}{arithmetical},
+  \textcolor{red}{bitwise} and \textcolor{red}{extension/truncation instructions} is
   adapted.  In particular, signed and unsigned operations are
   distinguished.
-\item The wrap-around behavior of the arithmetical instructions is
+\item<5-> The \textcolor{red}{wrap-around behavior} of the arithmetical instructions is
   modeled in order to ensure that they are within the appropriate
@@
 \medskip
+\uncover<2->{
 The comparison instructions:
 \begin{figure}
-  \includegraphics[width=\textwidth]{ins1.png}
+  \includegraphics[width=\textwidth]{figs/ins1.png}
 \end{figure}
+}
 
+\uncover<3->{
 For example,
@@
 \end{eqnarray}
+}
 \end{frame}
@@
 \begin{figure}
-  \includegraphics[width=\textwidth]{ins2.png}
+  \includegraphics[width=\textwidth]{figs/ins2.png}
 \end{figure}
@@
 
+\uncover<2->{
 For this, the wrap-around behavior is simulated by explicitly
 normalizing the resulting integers to be in the appropriate ranges.
+}
 
+\uncover<3->{
 Each rewrite rule
@@
 $\rho : f(x_1,\ldots,x_n) \rightarrow g(p_1,\ldots,p_m) ~ \llbracket \varphi \rrbracket$
-\end{center}
+\end{center}}
+\uncover<4->{
 should be replaced by:
 \begin{figure}
-  \includegraphics[width=0.6\textwidth]{rules.png}
+  \includegraphics[width=0.6\textwidth]{figs/rules.png}
 \end{figure}
+}
 
@@
 \begin{frame}{Conclusion}
-\begin{itemize}
-\item The approach is \emph{sound}.
+\begin{itemize}[<+->]
+\item The approach is \textcolor{red}{sound}.
 \begin{itemize}

### 2016-10-25 RMS/final-version/main.tex
initialization of final version

--- 2016-07-10 RMS/submission.tex
@@
-\documentclass[10pt,journal]{IEEEtran}
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[10pt,journal,compsoc]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-\ifCLASSOPTIONcompsoc
-  % IEEE Computer Society needs nocompress option
-  % requires cite.sty v4.0 or later (November 2003)
-  \usepackage[nocompress,noadjust]{cite}
-\else
-  % normal IEEE
+%\documentclass[onecolumn]{IEEEtranTIE}
+\documentclass[journal]{IEEEtranTIE}
+\usepackage{graphicx}
 \usepackage[noadjust]{cite}
-\fi
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
-%
-% Note that some packages require special options to format as the Computer
-% Society requires. In particular, Computer Society  papers do not use
-% compressed citation ranges as is done in typical IEEE papers
-% (e.g., [1]-[4]). Instead, they list every citation separately in order
-% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
-% package with the nocompress option which is supported by cite.sty v4.0
-% and later. Note also the use of a CLASSOPTION conditional provided by
-% IEEEtran.cls V1.7 and later.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/tex-archive/info/epslatex/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-\usepackage[cmex10]{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
+\usepackage{picinpar}
+\usepackage{amsmath}
+\usepackage{stfloats}
+%%\usepackage{dblfloatfix}
+\usepackage{url}
+\usepackage{flushend}
+\usepackage[latin1]{inputenc}
+\usepackage{colortbl}
+\usepackage{soul}
+\usepackage{multirow}
+\usepackage{pifont}
+\usepackage{color}
+\usepackage{alltt}
+\usepackage[hidelinks]{hyperref}
+\usepackage{enumerate}
+\usepackage{siunitx}
+\usepackage{breakurl}
+\usepackage{epstopdf}
+\usepackage{pbox}
+
+%% My packages
+%% \usepackage[cmex10]{amsmath}
+%% \interdisplaylinepenalty=2500
 \usepackage{algpseudocode}
-
-% *** ALIGNMENT PACKAGES ***
-%
-\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-\ifCLASSOPTIONcompsoc
-  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
-\else
+%% \usepackage{array}
 \usepackage[caption=false,font=footnotesize]{subfig}
-\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a sans serif font rather
-% than the serif font used in traditional IEEE formatting and thus the need
-% to invoke different subfig.sty package options depending on whether
-% compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Do not use the stfloats baselinefloat ability as IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-\usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
-% Axel Sommerfeldt. This package may be useful when used in conjunction with 
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-\usepackage{alltt}
+
 \usepackage{tikz}
 \usetikzlibrary{arrows.meta}
-\usepackage{mathabx}
-
-% for highlighting
-\usepackage{color,soul}
-\soulregister\cite7
-\soulregister\ref7
-\soulregister\pageref7
+%% \usepackage{mathabx}
 
@@
 
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
 \usepackage{microtype}
@@
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
 \title{Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude}
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-%
-%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
-% lists the Computer Society journals use for "first footnote" author
-% affiliations. Use \IEEEcompsocthanksitem which works much like \item
-% for each affiliation group. When not in compsoc mode,
-% \IEEEcompsocitemizethanks becomes like \thanks and
-% \IEEEcompsocthanksitem becomes a line break with idention. This
-% facilitates dual compilation, although admittedly the differences in the
-% desired content of \author between the different types of papers makes a
-% one-size-fits-all approach a daunting prospect. For instance, compsoc 
-% journal papers have the author affiliations above the "Manuscript
-% received ..."  text while in non-compsoc journals this is reversed. Sigh.
-
-\hide{
-\author{Jiaxiang~Liu,
+
+\author{
+  \vskip 1em
+  Jiaxiang~Liu,
   Min~Zhou,
-        Xiaoyu~Song,
+  Xiaoyu~Song, \emph{Member}, \emph{IEEE},
   Ming~Gu,
-        and~Jiaguang~Sun% <-this % stops a space
-\IEEEcompsocitemizethanks{%
-\IEEEcompsocthanksitem J. Liu is with the School of Software, Tsinghua
-University, Beijing 100084, China, and also with LIX, \'Ecole
-Polytechnique, Palaiseau 91120, France.\protect\\ E-mail:
-jiaxiang.liu@hotmail.com
-\IEEEcompsocthanksitem M. Zhou, M. Gu and J. Sun are with the School
-of Software, Tsinghua University, Beijing 100084, China.
-\IEEEcompsocthanksitem X. Song is with the Department of Electrical \&
-Computer Engineering, Portland State University, Portland, OR
-97207-0751, USA.}% <-this % stops an unwanted space
+  and Jiaguang~Sun
+
+  \thanks{
+    Manuscript received November 8, 2015; revised March 30, 2016 and
+    July 13, 2016; accepted October 20, 2016. This work was supported
+    in part by NSFC Program (No. 91218302, No. 61527812), National
+    Science and Technology Major Project (No. 2016ZX01038101), MIIT
+    IT funds (Research and application of TCN key technologies) of
+    China, and The National Key Technology R\&D Program
+    (No. 2015BAG14B01-02).
+
+    J. Liu is with the Department of Computer Science \& Technology,
+    Tsinghua University, Beijing 100084, China, and also with LIX,
+    \'Ecole Polytechnique, Palaiseau 91120, France (e-mail:
+    jiaxiang.liu@hotmail.com).
+
+    M. Zhou is with the School of Software, Tsinghua University,
+    Beijing 100084, China (corresponding author; phone:
+    +86-xxx-xxxx-xxxx; fax: xxx-xxxx-xxx; e-mail: zhoumin@gmail.com).
+
+    X. Song is with the Department of Electrical \& Computer
+    Engineering, Portland State University, Portland, OR 97207-0751,
+    USA.
+
+    M. Gu and J. Sun are with the School of Software, Tsinghua
+    University, Beijing 100084, China.
   }
-%\thanks{Manuscript received April 19, 2005; revised September 17, 2014.}}
-
-% note the % following the last \IEEEmembership and also \thanks - 
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-% 
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
 }
 
-% The paper headers
-\markboth{IEEE Transaction on xxx,~Vol.~$x$, No.~$x$, xx~$x$}%
-{Liu \MakeLowercase{\textit{et al.}}: Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% The publisher's ID mark at the bottom of the page is less important with
-% Computer Society journal papers as those publications place the marks
-% outside of the main text columns and, therefore, unlike regular IEEE
-% journals, the available text space is not reduced by their presence.
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2014 IEEE}
-% or like this to get the Computer Society new two part style.
-%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2014 IEEE}%
-%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark (Computer Society jorunal
-% papers don't need this extra clearance.)
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% for Computer Society papers, we must declare the abstract and index terms
-% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
-% command as these need to go into the title area created by \maketitle.
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
-\IEEEtitleabstractindextext{%
+\maketitle
+
 \begin{abstract}
-Rate-Monotonic Scheduling (RMS) is one of the most important real-time
+Rate-monotonic scheduling (RMS) is one of the most important real-time
 scheduling used in industry. There are a large number of results about
@@
 
-% Note that keywords are not normally used for peerreview papers.
 \begin{IEEEkeywords}
-  Real-time systems, scheduling, embedded systems, modeling, formal
-  verification, rewriting logic.
+Embedded systems, formal verification, modeling, real-time systems,
+rewriting logic, scheduling.
 \end{IEEEkeywords}
-}
-
-% make the title area
-\maketitle
-
-% To allow for easy dual compilation without having to reenter the
-% abstract/keywords data, the \IEEEtitleabstractindextext text will
-% not be used in maketitle, but will appear (i.e., to be "transported")
-% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
-% or transmag modes are not selected <OR> if conference mode is selected 
-% - because all conference papers position the abstract like regular
-% papers do.
-\IEEEdisplaynontitleabstractindextext
-% \IEEEdisplaynontitleabstractindextext has no effect when using
-% compsoc or transmag under a non-conference mode.
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-%\IEEEraisesectionheading{\section{Introduction}\label{s:introduction}}
+
+\markboth{IEEE TRANSACTIONS ON INDUSTRIAL ELECTRONICS}%
+{}
+
+\definecolor{limegreen}{rgb}{0.2, 0.8, 0.2}
+\definecolor{forestgreen}{rgb}{0.13, 0.55, 0.13}
+\definecolor{greenhtml}{rgb}{0.0, 0.5, 0.0}
+
 \section{Introduction}\label{s:introduction}
-% Computer Society journal (but not conference!) papers do something unusual
-% with the very first section heading (almost always called "Introduction").
-% They place it ABOVE the main text! IEEEtran.cls does not automatically do
-% this for you, but you can achieve this effect with the provided
-% \IEEEraisesectionheading{} command. Note the need to keep any \label that
-% is to refer to the section immediately after \section in the above as
-% \IEEEraisesectionheading puts \section within a raised box.
-
-% The very first letter is a 2 line initial drop letter followed
-% by the rest of the first word in caps (small caps for compsoc).
-% 
-% form to use if the first word consists of a single letter:
-% \IEEEPARstart{A}{demo} file is ....
-% 
-% form to use if you need the single drop letter followed by
-% normal text (unknown if ever used by IEEE):
-% \IEEEPARstart{A}{}demo file is ....
-% 
-% Some journals put the first two words in caps:
-% \IEEEPARstart{T}{his demo} file is ....
-% 
-% Here we have the typical use of a "T" for an initial drop letter
-% and "HIS" in caps to complete the first word.
+
 \IEEEPARstart{P}{eriodic} task scheduling is one of the most important
-topics within the field of industrial real-time systems.
-%due to the large number of control systems that require cyclic activities~\cite{buttazzo2011hard}. 
-{A set of periodic tasks is said to be \emph{schedulable} with respect
-to some scheduling algorithm if all jobs meet their
-deadlines. \emph{Rate-Monotonic Scheduling} (\emph{RMS}) is a
+topics within the field of industrial real-time systems. A set of
+periodic tasks is said to be \emph{schedulable} with respect to some
+scheduling algorithm if all jobs meet their
+deadlines. \emph{Rate-monotonic scheduling} (\emph{RMS}) is a
 \emph{fixed} priority scheduling algorithm for preemptive hard
@@
 \label{ss:rms}
-%\subsection{Formulation of the Standard Setting}
 A task set consists of \emph{only} $n$ periodic tasks
@@
   }\bigwedge^n_{j=1}cond_j$, where each $cond_j$ is an equality
-  $u_j=v_j$, and $l$ is a \emph{label}, \hl{$t,t',u_j,v_j$ are terms}. Such
+  $u_j=v_j$, and $l$ is a \emph{label}, $t,t',u_j,v_j$ are terms. Such
   a rule specifies an \emph{instantaneous transition}, without
@@
   }r\mbox{ \textbf{if} }cond$ that specify \emph{timed
-    transitions}. \hl{Each tick rule advances time by $r$ time units from
+    transitions}. Each tick rule advances time by $r$ time units from
   the \emph{entire} state modeled by term $s$ to the destination state
-  $s'$.}
+  $s'$.
 \end{itemize}
 
-\hl{$\mathit{IR}$ and $\mathit{TR}$ together model the ``dynamic''
-behaviors of the system.}
+$\mathit{IR}$ and $\mathit{TR}$ together model the ``dynamic''
+behaviors of the system.
 
@@
 propositions and temporal logic operators such as \verb|~|(negation),
-\verb|\/|(or), \verb|[]|(``always'') and
+\verb|\/|(disjunction), \verb|[]|(``always''),
 \verb|U|(``until''). Real-Time Maude supports both \emph{timed} and
@@
 formalized as the temporal logic formula: \verb|[](~taskTimeout)|,
-\hl{expressing that the proposition} \verb|taskTimeout| \hl{is always false}. As
+expressing that the proposition \verb|taskTimeout| is always false. As
 the property is not \emph{clock-related}, given an initial state
@@
 correctness property is formalized by the temporal logic formula:
-\verb|([]correct)\/(correct U taskTimeout)|, \hl{stating that}
-\verb|correct| \hl{is always true, or is true until} \verb|taskTimeout|
-\hl{holds}. It can be verified by the following untimed model checking
+\verb|([]correct)\/(correct U taskTimeout)|, stating that
+\verb|correct| is always true, or is true until \verb|taskTimeout|
+holds. It can be verified by the following untimed model checking
 command provided an initial state \verb|init|:
@@
 
-\hide{
-\begin{figure*}[!t]
-\centering
-\begin{picture}(300,120)(0,-10)
-\thicklines
-\put(0,0){\vector(1,0){320}}
-\put(305,5){time(${\mu}s$)}
-\thinlines
-\put(0,0){\line(0,1){110}}
-\put(-25,97){task$0$}
-\put(-25,77){task$1$}
-\put(-25,57){task$2$}
-\put(-50,37){scheduling}
-\put(-45,17){switching}
-\put(-2,-8){$0$}
-
-\dashline[30]{3}(0,100)(250,100)
-\dashline[30]{3}(0,80)(280,80)
-\dashline[30]{3}(0,60)(300,60)
-\dashline[30]{3}(0,40)(210,40)
-\dashline[30]{3}(0,20)(285,20)
-
-\dashline[30]{3}(10,-10)(10,100)
-\thicklines
-\textcolor{red}{\put(0,40){\line(1,0){10}}}
-\put(8,-18){$9$}
-
-\thinlines
-\dashline[30]{3}(50,0)(50,100)
-\thicklines
-\textcolor{blue}{\put(10,100){\line(1,0){40}}}
-\put(35,-8){$2509$}
-
-\thinlines
-\dashline[30]{3}(55,-10)(55,80)
-\thicklines
-\textcolor{red}{\put(50,20){\line(1,0){5}}}
-\put(46,-18){$2513$}
-
-\thinlines
-\dashline[30]{3}(80,0)(80,80)
-\thicklines
-\textcolor{blue}{\put(55,80){\line(1,0){25}}}
-\put(65,-8){$4013$}
-
-\thinlines
-\dashline[30]{3}(85,-10)(85,60)
-\thicklines
-\textcolor{red}{\put(80,20){\line(1,0){5}}}
-\put(76,-18){$4017$}
-
-\thinlines
-\dashline[30]{3}(100,0)(100,60)
-\thicklines
-\textcolor{blue}{\put(85,60){\line(1,0){15}}}
-\put(90,-8){$5000$}
-
-\thinlines
-\dashline[30]{3}(110,-10)(110,100)
-\thicklines
-\textcolor{red}{\put(100,40){\line(1,0){10}}}
-\put(101,-18){$5009$}
-
-\thinlines
-\dashline[30]{3}(150,0)(150,100)
-\thicklines
-\textcolor{blue}{\put(110,100){\line(1,0){40}}}
-\put(135,-8){$7509$}
-
-\thinlines
-\dashline[30]{3}(155,-10)(155,60)
-\thicklines
-\textcolor{red}{\put(150,20){\line(1,0){5}}}
-\put(146,-18){$7513$}
-
-\thinlines
-\dashline[30]{3}(200,0)(200,60)
-\thicklines
-\textcolor{blue}{\put(155,60){\line(1,0){45}}}
-\put(185,-8){$10000$}
-
-\thinlines
-\dashline[30]{3}(210,-10)(210,100)
-\thicklines
-\textcolor{red}{\put(200,40){\line(1,0){10}}}
-\put(198,-18){$10009$}
-
-\thinlines
-\dashline[30]{3}(250,0)(250,100)
-\thicklines
-\textcolor{blue}{\put(210,100){\line(1,0){40}}}
-\put(230,-8){$12509$}
-
-\thinlines
-\dashline[30]{3}(255,-10)(255,80)
-\thicklines
-\textcolor{red}{\put(250,20){\line(1,0){5}}}
-\put(243,-18){$12513$}
-
-\thinlines
-\dashline[30]{3}(280,0)(280,80)
-\thicklines
-\textcolor{blue}{\put(255,80){\line(1,0){25}}}
-\put(260,-8){$14013$}
-
-\thinlines
-\dashline[30]{3}(285,-10)(285,60)
-\thicklines
-\textcolor{red}{\put(280,20){\line(1,0){5}}}
-\put(272,-18){$14017$}
-
-\thinlines
-\dashline[30]{3}(300,0)(300,60)
-\thicklines
-\textcolor{blue}{\put(285,60){\line(1,0){15}}}
-\put(289,-8){$15000$}
-
-\textcolor{red}{\put(300,60){\vector(-1,0){0}}}
-
-\end{picture}
-\caption{A Counterexample of Scenario (iv).}
-\label{f:counterexample}
-\end{figure*}
-}
-
 \subsection{Evaluation}
-%\subsection{Soundness and Completeness of the Analysis}
 We now show in this section that our results are both sound and
@@
 \end{IEEEproof}
-
-\hide{
-In order to prove the completeness of our verification, we need little
-adjustments to our model.  For each task $\tau_i$, we collapse its
-computation requirement $[C_i^{min},C_i^{max}]$ into the single value
-$C_i^{max}$.  That is, in the adjusted model, we use the maximum time
-that is possible to be required to complete the task, as in the
-standard setting. The adjustment is reasonable for verifying our
-properties, since the schedulability and correctness of the adjusted
-model imply the schedulability and correctness of our original
-model. In particular, this is because we can prove the followings.
-\begin{lemma}
-\label{l:max}
-Assume $t_s, t_f$ are the times at which a job of $\tau_i$ starts and
-completes its execution, respectively. Let $S_i$ be the set of tasks,
-which have priorities higher than $\tau_i$ or equal to it, including
-the system tasks scheduling and switching. Assumed $t_s$ is fixed,
-$t_f$ reaches its maximum, if all job instances of each task
-$\tau_j\in S_i$, which execute between $t_s$ and $t_f$, are completed
-in time $C_j^{max}$.
-\end{lemma}
-\begin{IEEEproof} 
-Note that each job instance that executes between $t_s$ and $t_f$
-corresponds to some task in $S_i$. Assume the number of job instances
-of task $\tau_j\in S_i$ is $m_j$, and they execute for time
-$C_j^1,C_j^2,\ldots,C_j^{m_j}$ respectively to complete. We have
-$m_i=1$. Then assume the number of interrupts between $t_s$ and $t_f$
-is $m_{int}$, the corresponding $m_{int}$ scheduling stages take time
-$C_{sch}^1,\ldots,C_{sch}^{m_{int}}$, respectively. By our definition
-of switching, the number of switching stages between $t_s$ and $t_f$
-is $M_{swi}=\Sigma_{k=1}^{i-1}m_k$, we assuming they execute for
-$C_{swi}^1,\ldots,C_{swi}^{M_{swi}}$ to complete. It follows that
-$t_f-t_s=\Sigma_{j=1}^i\Sigma_{k=1}^{m_j}C_j^k+\Sigma_{k=1}^{m_{int}}C_{sch}^k+\Sigma_{k=1}^{M_{swi}}C_{swi}^k$. Along
-the timeline, when $C_j^k$, $C_{sch}^k$ or $C_{swi}^k$ increases,
-$m_j$, $m_{int}$ and/or $M_{swi}$ may increase as well. Therefore,
-$t_f$ reaches its maximum when $C_j^k$, $C_{sch}^k$ and $C_{swi}^k$
-reach their maximum, hence the statement.
-\end{IEEEproof}
-\begin{theorem}
-\label{th:max}
-Given a set of tasks that is schedulable when the computation
-requirement of each task $\tau_i$ equals $C_i^{max}$, this set remains
-still schedulable when some job instances of some $\tau_i$ become
-possible to terminate in time $t\le C_i^{max}$.
-\end{theorem}
-\begin{IEEEproof}
-By investigating the effects on the completion time of some job
-instance when reducing other job instances' computation requirements,
-and using Lemma~\ref{l:max}.
-\end{IEEEproof}
-
-We achieve the same verification results in the adjusted model as in
-our original one: while correctness holds within all scenarios,
-schedulability holds only in Scenarios~(i-iii)\footnote{In fact,
-  positive results in the original model imply positive results in the
-  adjusted one, since the set of behaviors of the adjusted model is a
-  subset of those of the original.} but fail in Scenario~(iv). Since
-the adjusted model is time-robust and our defined atomic
-propositions--\verb|taskTimeout| and \verb|correct|--are
-tick-stabilizing, our analysis using untimed model checking on the
-adjusted model is complete by Theorem~\ref{t:completeness}. Therefore
-by Theorem~\ref{th:max}, the results shown in Section~\ref{ss:results}
-for our original model are complete.
-}
-
-\hide{
-To apply Theorem~\ref{t:completeness} on our analysis to show the
-completeness, we only need to prove time-robustness of our model and
-tick-stabilization of our defined atomic propositions,
-\verb|taskTimeout| and \verb|scheduleCorrectly|. The latter is quite
-trivial, while the former requires little adjustments to the model,
-which collapse the possible finishing interval for some periodic task
-into a single value that should be assigned to the possible maximum
-computation time. Then we can apply Lemma~\ref{l:timerobustness} to
-prove the time-robustness of our (adjusted) model.
-\begin{lemma}
-\label{l:timerobustness}
-An object-oriented specification $\cal R$, with a conventional tick
-rule, is \emph{time-robust} if the following conditions are satisfied
-for all appropriate \emph{ground} terms $t$ and $r,r'$:
-
-\noindent
-(i) $mte(\delta(t,r))=mte(t)\dotdiv r$, for all $r\le mte(t)$;
-
-\noindent
-(ii) $\delta(t,0)=t$;
-
-\noindent
-(iii) $\delta(\delta(t,r),r')=\delta(t,r+r')$, for $r+r'\le mte(t)$;
-
-\noindent
-(iv) $mte(\sigma(l))=0$ for each ground instance $\sigma(l)$ of a
-left-hand side of an instantaneous rewrite rule.
-\end{lemma}
-
-We achieve the same verification results for the adjusted model as for
-the original one: schedulability and correctness hold in Scenarios
-(i-iii) but fail in Scenario~(iv). The only thing remained to show the
-completeness of our results is to prove the reasonability of the
-adjustments, that is, if a set of tasks (including system ones) is
-schedulable when the computation time of some task $\tau_i$ in it
-equals to $C_i^{max}$, then when some jobs of $\tau_i$ become possible
-to finish in time $r\le C_i^{max}$, the set of tasks remains still
-schedulable. This is done by proving Lemma~\ref{l:max} and considering
-\verb|scheduling| and \verb|switching| as having same and higher
-priority than all periodic tasks.
-\begin{lemma}
-\label{l:max}
-Assume the time $r_s$ at which a job of $\tau_i$ starts running is
-fixed. The time $r_f$, at which this job finishes, reaches its maximum
-if all job instances of tasks $\tau$'s, the priorities of which are
-higher than or equal to that of $\tau_i$, running between $r_s$ and
-$r_f$ finish in their maximum possible computation time.
-\end{lemma}
-}
 
@@
 
+%% \begin{figure}[!t]\centering
+%% 	\includegraphics[width=8.5cm]{FIG1.eps}
+%% 	\caption{Magnetization as a function of applied field.
+Note that ``Fig.'' is abbreviated.
+There is a period after the figure number, followed by two spaces.
+It is good practice to explain the significance of the figure in the caption.}\label{FIG_1}
+%% \end{figure}
+
 \appendix[Proof of Theorem~\ref{t:main}]
@@
 
-\hide{
-% use section* for acknowledgment
-\ifCLASSOPTIONcompsoc
-  % The Computer Society usually uses the plural form
-  \section*{Acknowledgments}
-\else
-  % regular IEEE prefers the singular form
 \section*{Acknowledgment}
-\fi
-
-The authors would like to thank...
-}
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-\bibliography{IEEEabrv,submission}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
-\hide{
-
-\begin{IEEEbiography}{Jiaxiang Liu}
-Biography text here.
+The authors would like to thank the reviewers for their invaluable
+comments and suggestions.
+
+%% References
+
+\bibliographystyle{Bibliography/IEEEtranTIE}
+\bibliography{Bibliography/IEEEabrv,Bibliography/main}\ %IEEEabrv instead of IEEEfull
+
+%% Biographies
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J_Liu.jpg}}]%
+{Jiaxiang Liu} received his B.S. degree from the School of Software,
+Tsinghua University, China, in 2010. He is now a Ph.D. candidate in
+the Department of Computer Science and Technology, Tsinghua
+University. His research interests include formal methods, rewrite
+systems and embedded systems.
 \end{IEEEbiography}
 
-% if you will not have a photo at all:
-\begin{IEEEbiographynophoto}{John Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-\begin{IEEEbiographynophoto}{Jane Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
-}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-% that's all folks
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Zhou.jpg}}]%
+{Min Zhou} received his B.S. degree from the Department of
+Mathematical Science and Ph.D. degree from the Department of Computer
+Science and Technology, Tsinghua University, China, in 2007 and 2014,
+respectively. He is now a lecturer at the School of Software, Tsinghua
+University. His research interests include model checking, program
+analysis and testing.
+\end{IEEEbiography}
+
+%% \vspace{-2cm}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{X_Song.jpg}}]%
+{Xiaoyu Song} () received the Ph.D. degree from the University of
+Pisa, Italy, in 1991. From 1992 to 1998, he was on the faculty at the
+University of Montreal, Canada. He joined the Department of Electrical
+and Computer Engineering at Portland State University in 1998, where
+he is now a professor. He was an editor of IEEE Transactions on VLSI
+Systems and IEEE Transactions on Circuits and Systems. He was awarded
+an Intel Faculty Fellowship from 2000 to 2005. His research interests
+include formal methods, design automation, embedded systems and
+emerging technologies.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Gu.jpg}}]%
+{Ming Gu} is a professor at the School of Software, Tsinghua
+University and vice-director of Ministry of Education Key Laboratory
+of Information Security, China. Her research interests include
+software formal methods, software trustworthiness and middleware
+technology.
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J_Sun.jpg}}]%
+{Jiaguang Sun} is a professor and dean of the School of Information
+Science and Technology in Tsinghua University, China. He is also a
+member of the Chinese Academy of Engineering, director of Ministry of
+Education Key Laboratory of Information Security, and director of
+Tsinghua National Laboratory for Information Science and Technology,
+China. His research interests include computer graphics,
+computer-aided design, formal verification of software, software
+engineering, and system architecture.
+\end{IEEEbiography}
+
 \end{document}

### 2016-10-26 RMS/final-version/main.tex
modified fig rms

@@
 Layland~\cite{DBLP:journals/jacm/LiuL73}, which assigns priorities to
-jobs according to the periods of the corresponding tasks: the smaller
+jobs according to the periods of
+the
+corresponding tasks: the smaller
 period, the higher priority. RMS is proven to be the \emph{optimal}
@@
 A simple example showing this algorithm is depicted in
-Figure~\ref{sf:rmsalg}. However in this paper, we consider an
+Fig.~\ref{f:example}(a). However in this paper, we consider an
 implementation instead of the RMS algorithm itself, thus the model
@@
 assumptions, an example showing the execution of tasks scheduled by
-the implementation is depicted in Figure~\ref{sf:rmsimp}. Note that
+the implementation is depicted in Fig.~\ref{f:example}(b). Note that
 the second job instance of $\tau_1$ is initiated at time $11$ instead
@@
 \centering
-\subfloat[RMS Algorithm]{
-  \begin{tikzpicture}[font=\small,scale=1.25,
-    % styles
-    system task/.style={fill=gray!70,draw=gray},
-    periodic task/.style={fill=gray!70!black,draw=gray!50!black},
-    task line/.style={gray!30,very thin},
-    time line/.style={gray!50,very thin,dashed},
-    short line/.style={gray!50,very thin,dashed},
-    init/.style={{Triangle[fill=white,scale=1.1]}-},
-    complete/.style={{Triangle[scale=1.1]}-}]
-
-  % legend
-  \begin{scope}[xshift=-2cm]  
-    \draw [fill=gray!25,draw=gray!50,dashed] (1.5,2.3) rectangle +(4,-1);
-    \draw (1.5,2.3) node [below right] {LEGEND};
-    \draw [init] (2,1.85) -- +(0,-0.01);
-    \draw (2.1,2) node [below right] {: Initiation of Tasks};
-    \draw [complete] (2,1.42) -- +(0,0.1);
-    \draw (2.1,1.7) node [below right] {: Completion of Tasks};
-  \end{scope}
-
-    % grid
-    \foreach \x in {0.3,0.7}
-      \draw[task line] (0,\x) -- (5.2,\x);
-
-    % axes
-    \draw[->,thick] (0,0) node [below] {$0$} -- (5.3,0) node [above] {time};
-    \draw[thin] (0,0) -- (0,1);
-
-    % time indicator
-    \draw [time line] (0.75,0.7) -- (0.75,0);
-    \draw (0.75,0) node [below] {$3$} -- +(0,2pt);
-    \draw [time line] (1.25,0.3) -- (1.25,0);
-    \draw (1.25,0) node [below] {$5$} -- +(0,2pt);
-    \draw [time line] (2.5,0.7) -- (2.5,0);
-    \draw (2.5,0) node [below] {$10$} -- +(0,2pt);
-    \draw [time line] (3.25,0.7) -- (3.25,0);
-    \draw (3.25,0) node [below] {$13$} -- +(0,2pt);
-
-    \draw [time line] (5,0.7) -- (5,0);
-    \draw (5,0) node [below] {$20$} -- +(0,2pt);
-
-    % tasks
-    \draw [periodic task] (0,0.7) rectangle +(0.75,0.14);
-    \draw [periodic task] (0.75,0.3) rectangle +(0.5,0.14);
-    \draw [periodic task] (2.5,0.7) rectangle +(0.75,0.14);
-
-    % text
-    \draw (0,0.75) node [left] {$\tau_1$};
-    \draw (0,0.35) node [left] {$\tau_2$};
-    \path (0,0.75) node [left,text opacity=0] {scheduling};
-    \path (0,0.35) node [left,text opacity=0] {switching};
-
-    % initiation of tasks
-    \foreach \x in {0,2.5,5}
-      \draw [init] (\x,0.7) -- +(0,-0.01);
-    \foreach \x in {0,5}
-      \draw [init] (\x,0.3) -- +(0,-0.01);
-
-    % completion of tasks
-    \draw [complete] (0.75,0.84) -- +(0,0.01);
-    \draw [complete] (3.25,0.84) -- +(0,0.01);
-    \draw [complete] (1.25,0.44) -- +(0,0.01);
-  \end{tikzpicture}
-\label{sf:rmsalg}}\\
-\subfloat[RMS Implementation]{
-  \begin{tikzpicture}[font=\small,scale=1.25,
-    % styles
-    system task/.style={fill=gray!70,draw=gray},
-    periodic task/.style={fill=gray!70!black,draw=gray!50!black},
-    task line/.style={gray!30,very thin},
-    time line/.style={gray!50,very thin,dashed},
-    short line/.style={gray!50,very thin,dashed},
-    init/.style={{Triangle[fill=white,scale=1.1]}-},
-    complete/.style={{Triangle[scale=1.1]}-}]
-
-    % grid
-    \foreach \x in {0.3,0.7,1.1,1.5}
-      \draw[task line] (0,\x) -- (5.2,\x);
-
-    % axes
-    \draw[->,thick] (0,0) node [below] {$0$} -- (5.3,0) node [above] {time};
-    \draw[thin] (0,0) -- (0,1.8);
-
-    % time indicator
-    \draw [time line] (0.5,1.5) -- (0.5,0);
-    \draw (0.5,0) node [below] {$2$} -- +(0,2pt);
-    \draw [time line] (1.25,1.5) -- (1.25,0);
-    \draw (1.25,0) node [below] {$5$} -- +(0,2pt);
-    \draw [time line] (1.75,1.1) -- (1.75,0);
-    \draw (1.75,0) node [below] {$7$} -- +(0,2pt);
-    \draw [time line] (2.25,1.1) -- (2.25,0);
-    \draw (2.25,0) node [below] {$9$} -- +(0,2pt);
-    \draw [time line] (2.75,1.5) -- (2.75,0);
-    \draw (2.75,0) node [below] {$11$} -- +(0,2pt);
-    \draw [time line] (3.25,1.5) -- (3.25,0);
-    \draw (3.25,0) node [below] {$13$} -- +(0,2pt);
-    \draw [time line] (4,1.5) -- (4,0);
-    \draw (4,0) node [below] {$16$} -- +(0,2pt);
-    \draw [time line] (4.5,0.3) -- (4.5,0);
-    \draw (4.5,0) -- +(0,2pt);
-    \draw (4.5,0) node [below] {$18$};
-    \draw [time line] (5,1.5) -- (5,0);
-    \draw (5,0) node [below] {$20$} -- +(0,2pt);
-
-    % tasks
-    \draw [system task] (0,0.7) rectangle +(0.5,0.14);
-    \draw [periodic task] (0.5,1.5) rectangle +(0.75,0.14);
-    \draw [system task] (1.25,0.3) rectangle +(0.5,0.14);
-    \draw [periodic task] (1.75,1.1) rectangle +(0.5,0.14);
-    \draw [system task] (2.25,0.3) rectangle +(0.5,0.14);
-    \draw [system task] (2.75,0.7) rectangle +(0.5,0.14);
-    \draw [periodic task] (3.25,1.5) rectangle +(0.75,0.14);
-    \draw [system task] (4,0.3) rectangle +(0.5,0.14);
-
-    % text
-    \draw (0,1.55) node [left] {$\tau_1$};
-    \draw (0,1.15) node [left] {$\tau_2$};
-    \draw (0,0.75) node [left] {scheduling};
-    \draw (0,0.35) node [left] {switching};
-
-    % initiation of tasks
-    \foreach \x in {0,2.75,5}
-      \draw [init] (\x,1.5) -- +(0,-0.01);
-    \foreach \x in {0,5}
-      \draw [init] (\x,1.1) -- +(0,-0.01);
-
-    % completion of tasks
-    \draw [complete] (1.25,1.64) -- +(0,0.01);
-    \draw [complete] (2.25,1.24) -- +(0,0.01);
-    \draw [complete] (4,1.64) -- +(0,0.01);
-  \end{tikzpicture}
-\label{sf:rmsimp}}
+\includegraphics{rms.pdf}
 \caption{A set of $2$ periodic tasks scheduled under RMS algorithm and
   the implementation, respectively. $T=T_1=10$, $T_2=20$, $C_1=3$,
-  $C_2=2$. In Figure~\ref{sf:rmsimp}, we assume both scheduling time
-  and switching time are $2$.}
+  $C_2=2$. In~(b), we assume both scheduling time and switching time
+  are $2$.}
 \label{f:example}
@@
 {Jiaxiang Liu} received his B.S. degree from the School of Software,
-Tsinghua University, China, in 2010. He is now a Ph.D. candidate in
-the Department of Computer Science and Technology, Tsinghua
-University. His research interests include formal methods, rewrite
-systems and embedded systems.
+Tsinghua University, China, in 2010. He is now a co-supervised
+Ph.D. candidate between the Department of Computer Science and
+Technology, Tsinghua University, China and LIX, \'Ecole Polytechnique,
+France. His research interests include formal methods, rewrite systems
+and embedded systems.
 \end{IEEEbiography}

### 2016-10-31 RMS/final-version/main.tex
modified a bit

@@
 \usepackage{stfloats}
-%%\usepackage{dblfloatfix}
 \usepackage{url}
@@
 %% \usepackage{array}
-\usepackage[caption=false,font=footnotesize]{subfig}
+%%\usepackage{dblfloatfix}
+%%\usepackage[caption=false,font=footnotesize]{subfig}
 
@@
     Beijing 100084, China (corresponding author; phone:
-    +86-xxx-xxxx-xxxx; fax: xxx-xxxx-xxx; e-mail: zhoumin@gmail.com).
+    +86-10-6277-3275; fax: +86-10-6278-3549; e-mail: zhoumin03@gmail.com).
 
@@
 implementation instead of the RMS algorithm itself, thus the model
-would be more complicated than this standard, ideal
-setting. Assumption~(A1) will be modified because of the interrupt
-mask mechanism, while (A4) is relaxed to obtain a more realistic
-analysis model.
+would be more complicated than this standard, ideal setting.
+%% Assumption
+(A1) will be modified because of the interrupt mask
+mechanism, while (A4) is relaxed to obtain a more realistic analysis
+model.
 
@@
 Real-Time Maude models systems as \emph{modules}. A module specifies a
-\emph{real-time rewrite theory} ${\cal R} = (\Sigma, E\cup A ,
-\mathit{IR}, \mathit{TR})$, where:
+\emph{real-time rewrite theory} $\mathcal{R} = (\Sigma,
+\mathit{E}\cup\mathit{A} , \mathit{IR}, \mathit{TR})$, where:
 \begin{itemize}
@@
   variables.
-\item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
-  theory}, with $E$ a set of \emph{conditional equations} and
-  \emph{memberships} on $\Sigma$, and $A$ a set of equational axioms
-  such as associativity, commutativity and identity.  $(\Sigma, E\cup
-  A)$ models the system's ``static'' states as terms of some sort, and
-  is equipped with a built-in specification of a sort \verb|Time|.
+\item $(\Sigma, \mathit{E}\cup\mathit{A})$ is a \emph{membership
+  equational logic theory}, with $\mathit{E}$ a set of
+  \emph{conditional equations} and \emph{memberships} on $\Sigma$, and
+  $\mathit{A}$ a set of equational axioms such as associativity,
+  commutativity and identity.  $(\Sigma, \mathit{E}\cup\mathit{A})$
+  models the system's ``static'' states as terms of some sort, and is
+  equipped with a built-in specification of a sort \verb|Time|.
 \item $\mathit{IR}$ is a set of \emph{labeled conditional rewrite
@@
   instance of $t'$, \emph{provided} the conditions hold.
-\item $\mathit{TR}$ is a set of (\emph{labeled}) \emph{tick rules} of
+\item $\mathit{TR}$ is a set of \emph{(labeled) tick rules} of
   the form $[l]~:~\{s\}\rightarrow\{s'\} \mbox{\textbf{ in time}
@@
 \end{itemize}
-
-$\mathit{IR}$ and $\mathit{TR}$ together model the ``dynamic''
-behaviors of the system.
+$\mathit{IR}$ and $\mathit{TR}$ together model the system's ``dynamic''
+behaviors.
 

### 2016-11-02 RMS/final-version/main.tex
finish modifying section III

@@
 symbolically; given an initial state, \verb|search| is used to search
-reachable states satisfying the desired properties; the Maude's
+reachable states satisfying desired properties; the Maude's
 \emph{Inductive Theorem Prover} (ITP) can be applied to interactively
@@
 semantics is defined by conditional equations of the form $\texttt{ceq
-} statePattern \texttt{ |= } prop \texttt{ = } b \texttt{ if } cond$,
-with $b$ a term of sort \verb|Bool|, stating that $prop$ evaluates to
-$b$ in states which are instances of $statePattern$ provided the
-condition $cond$ holds. These equations together define $prop$ to hold
-in all states $s$ that make $s \texttt{ |= } prop$ evaluate to
+} \mathit{statePattern} \texttt{ |= } \mathit{prop} \texttt{ = } b \texttt{ if } cond$,
+with $b$ a term of sort \verb|Bool|, stating that $\mathit{prop}$ evaluates to
+$b$ in states which are instances of $\mathit{statePattern}$ provided the
+condition $cond$ holds. These equations together define $\mathit{prop}$ to hold
+in all states $s$ that make $s \texttt{ |= } \mathit{prop}$ evaluate to
 \verb|true|. A temporal logic \emph{formula} is constructed by state
@@
 \emph{untimed LTL model checking}. The untimed model checking command
+%% \indent
+%% $\texttt{(mc } s \texttt{ |=u } \Phi \texttt{ .)}$\\
 \begin{alltt}
@@
 request occurs, if the system is interruptible, i.e. the interrupt
-mask bit is cleared, the handler function $schedule()$ will be
-invoked; otherwise $schedule()$ will be pending until the interrupt
-mask bit becomes cleared.  The pseudocode of $schedule()$ is shown in
-Figure~\ref{a:schedule}, where $taskList$ is the list of periodic
-tasks to be scheduled. We assume that the list is in descending order
-of priority, and both variables $taskList$ and $timer$ are global. In
-this implementation, there is only one kind of interrupt, the period
-$T_i$ of each task is a multiple of $T$, and the tasks are
-independent, meeting assumption~(A3).
+mask bit is cleared, the handler function $\mathit{schedule()}$ will
+be invoked; otherwise $\mathit{schedule()}$ will be pending until the
+interrupt mask bit becomes cleared.  The pseudocode of
+$\mathit{schedule()}$ is shown in Fig.~\ref{f:schedule}, where
+$\mathit{taskList}$ is the list of periodic tasks to be scheduled. We
+assume that the list is in descending order of priority, and both
+variables $\mathit{taskList}$ and $\mathit{timer}$ are global. In this
+implementation, there is only one kind of interrupt, the period $T_i$
+of each task is a multiple of $T$, and the tasks are independent,
+meeting assumption~(A3).
 
 \begin{figure}[!t]
-\hrule\vspace{1mm}
-  \begin{algorithmic}[1]\small
-\Function{$schedule$}{$ $}{}
-  \State \Call{$int\_o\!f\!\!f$}{$ $}; \Comment{to disable interrupts} \label{l:1stline}
-  \State \Call{$updateStatus$}{$taskList$}; \label{l:updatestatus}
-  \State $timer = timer + 1$; \label{l:timer} \label{l:inc}
-  \State $p = taskList$;
-  \While{$p$} \label{l:startrun1st}
-    \If{$p\rightarrow status == \textit{INTERRUPT}$}
-      \State \Return; \label{l:return}
-    \ElsIf{$p\rightarrow status == \textit{READY}$}      
-      \State $p\rightarrow status = \textit{RUNNING}$;
-      \State \Call{$int\_on$}{$ $}; \Comment{to enable interrupts} \label{l:endrun1st}
-      \State $p\rightarrow function()$; \Comment{to execute the task} \label{l:function}
-      \State \Call{$int\_o\!f\!\!f$}{$ $};
-      \State $p\rightarrow status = \textit{DORMANT}$;
-    \EndIf
-    \State $p = p\rightarrow next$;
-  \EndWhile
-\EndFunction
-\Function{$updateStatus$}{$p$}
-  \While{$p$}
-    \If{$p\rightarrow status == \textit{RUNNING}$} \label{l:startupdate}
-      \State $p\rightarrow status = \textit{INTERRUPT}$;
-    \EndIf
-    \If{$timer~\%~(p\rightarrow period) == 0$} \Comment{the task should be initiated}
-      \If{$p\rightarrow status == \textit{DORMANT}$} \Comment{the previous job finishes} 
-        \State $p\rightarrow status = \textit{READY}$;
-      \Else \Comment{the status is \textit{READY} or \textit{INTERRUPT}}
-  \State \Call{$reportTaskError$}{$p$}; \Comment{task misses its deadline}
-      \EndIf
-    \EndIf \label{l:endupdate}
-    \State $p = p\rightarrow next$;
-  \EndWhile
-\EndFunction
-  \end{algorithmic}
-\hrule
+\centering
+\includegraphics[width=8.8cm]{rms-pseudocode.pdf}
 \caption{The C-Like Pseudo-code of $schedule()$}
-  \label{a:schedule}
+\label{f:schedule}
 \end{figure}
 
-In Figure~\ref{a:schedule}, the handler function $schedule()$ first
-updates status of all tasks in $taskList$ via function
-$updateStatus()$. This updating actually initiates tasks that should
-be scheduled in the current interrupt cycle. Then $schedule()$
-traverses the list to execute the ready tasks one by one, or to do a
-return when encountering an interrupted\footnote{Note that the status
-  \textit{INTERRUPT} indicates the task is interrupted for the moment,
-  or was interrupted before but its execution is not complete yet.}
-task. As for the function $updateStatus()$, it updates each task in
-two steps: firstly, if the task is running, it becomes interrupted;
-secondly for the task at its initiation time, if its previous job is
-complete, it would be set ready, otherwise it misses its deadline,
-producing an error. Notice that $schedule()$ is invoked only when the
+In Fig.~\ref{f:schedule}, the handler function $\mathit{schedule()}$
+first updates status of all tasks in $\mathit{taskList}$ via function
+$\mathit{updateStatus()}$. This updating actually initiates tasks that
+should be scheduled in the current interrupt cycle. Then
+$\mathit{schedule()}$ traverses the list to execute the ready tasks
+one by one, or to do a return when encountering an
+interrupted\footnote{Note that the status \textit{INTERRUPT} indicates
+  the task is interrupted currently, or was interrupted before but its
+  execution is not complete yet.}  task. As for the function
+$\mathit{updateStatus()}$, it updates each task in two steps: firstly,
+if the task is running, it becomes interrupted; secondly for the task
+at its initiation time, if its previous job is complete, it would be
+set ready, otherwise it misses its deadline, producing an
+error. Notice that $\mathit{schedule()}$ is invoked only when the
 interrupt request is handled, not when the interrupt is disabled (the
@@
 searching the next task to execute, however, it can be interrupted
-while executing some task (Line~\ref{l:function}). This allows the
-execution of $schedule()$ to be nested.
+while executing some task (Line~12). This allows the execution of
+$\mathit{schedule()}$ to be nested.
 
@@
 is detected, to the moment when the first should-be-run periodic task
-starts executing, i.e. Line~\ref{l:return} or~\ref{l:function} in
-Figure~\ref{a:schedule}. Therefore, \emph{scheduling time} mainly
-consists of three parts: (i) the time for switching context from the
-running task, possibly none, to $schedule()$ when an interrupt request
-is handled, (ii) the time spent by $schedule()$ searching and setting
-the \emph{first} should-be-run periodic task
-(Lines~\ref{l:1stline}-\ref{l:endrun1st} in Figure~\ref{a:schedule}),
-and (iii) the time for switching context from $schedule()$ to that
-task. \emph{Switching} refers to the stage, from the moment when a
-periodic task completes its execution, to the moment when the next
+starts executing, i.e. Line~8 or~12 in
+Fig.~\ref{f:schedule}. Therefore, \emph{scheduling time} mainly
+consists of three parts: (i)~the time for switching context from the
+running task, possibly none, to $\mathit{schedule()}$ when an
+interrupt request is handled, (ii)~the time spent by
+$\mathit{schedule()}$ searching and setting the \emph{first}
+should-be-run periodic task (Lines~2--11 in Fig.~\ref{f:schedule}),
+and (iii)~the time for switching context from $\mathit{schedule()}$ to
+that task. \emph{Switching} refers to the stage, from the moment when
+a periodic task completes its execution, to the moment when the next
 should-be-run periodic task starts executing. \emph{Switching time}
-thus also consists of three parts: (i) the time for switching context
-from the complete task back to $schedule()$, (ii) the time spent by
-$schedule()$ searching and setting the \emph{next} should-be-run
-periodic task, and (iii) the time for switching context from
-$schedule()$ to that task.
+thus also consists of three parts: (i)~the time for switching context
+from the complete task back to $\mathit{schedule()}$, (ii)~the time
+spent by $\mathit{schedule()}$ searching and setting the \emph{next}
+should-be-run periodic task, and (iii)~the time for switching context
+from $\mathit{schedule()}$ to that task.
 
@@
 upper bound while increasing (see Line~\ref{l:timer} in
-Figure~\ref{a:schedule}) in the model. Then $timer$ is of sort
+Figure~\ref{f:schedule}) in the model. Then $timer$ is of sort
 \verb|Timer| and the upper bound would be the least common multiple of
@@
 while increasing, which is not shown in detail in
-Figure~\ref{a:schedule} but is reasonable. The upper bound is the
+Figure~\ref{f:schedule} but is reasonable. The upper bound is the
 least common multiple of the periods of all tasks. A sort \verb|Timer|
@@
 Periodic tasks are initiated sequentially by the function
-$updateStatus()$ in Figure~\ref{a:schedule}, which is treated as an
+$updateStatus()$ in Figure~\ref{f:schedule}, which is treated as an
 instantaneous action in our model. It is modeled by a recursive
@@
 (Lines~\ref{l:startupdate}-\ref{l:endupdate} in
-Figure~\ref{a:schedule}):
+Figure~\ref{f:schedule}):
 \begin{verbatim}
@@
 We can see that \verb|updateStatus_with_| behaves the same as
-$updateStatus()$ in Figure~\ref{a:schedule}.
+$updateStatus()$ in Figure~\ref{f:schedule}.
 
@@
 corresponds to Lines~\ref{l:updatestatus}-\ref{l:inc} in
-Figure~\ref{a:schedule}. It updates the status of $taskList$ and
+Figure~\ref{f:schedule}. It updates the status of $taskList$ and
 increases $timer$ by $1$. This part is modeled by function
@@
 Lines~\ref{l:startrun1st}-\ref{l:endrun1st} in
-Figure~\ref{a:schedule}, searching the task with highest priority
+Figure~\ref{f:schedule}, searching the task with highest priority
 that has status \verb|INTERRUPT| or \verb|READY| then performing an

### 2016-11-03 RMS/final-version/main.tex
polished all the text

@@
 years~\cite{DBLP:journals/tie/MiyawakiMSYV05,DBLP:journals/iandc/MeseguerR13,DBLP:journals/cacm/Leroy09,DBLP:conf/sosp/KleinEHACDEEKNSTW09}. However,
-as far as we know, few~\cite{DBLP:conf/iceccs/CuiDT14,TianD2011}
+as far as we know, few~\cite{TianD2011,DBLP:conf/iceccs/CuiDT14}
 attempt to analyze the RMS algorithm, while no work for
@@
 These assumptions make our model different from the standard one. For
-instance, with assumption~(A1'), an interrupt request that occurs
-during switching will be pending, such that jobs of task $\tau_i$
-cannot initiate at $kT_i$. They should wait until switching finishes
-and the interrupt mask bit is cleared, which is different
-from~(A1). Note that (A3) says that jobs are ready to run at their
-initiation times, however, no one can start running at exactly its
-initiation time, because scheduling takes time. Under these
-assumptions, an example showing the execution of tasks scheduled by
-the implementation is depicted in Fig.~\ref{f:example}(b). Note that
-the second job instance of $\tau_1$ is initiated at time $11$ instead
-of $10$, because switching is performed and the interrupt mask bit is
-set at time $10$, exemplifying differences between (A1') and (A1).
+instance, with~(A1'), an interrupt request that occurs during
+switching will be pending, such that jobs of task $\tau_i$ cannot
+initiate at $kT_i$. They should wait until switching finishes and the
+interrupt mask bit is cleared, which is different from~(A1). (A3) says
+that jobs are ready to run at their initiation times, however, no one
+can start running at exactly its initiation time, because scheduling
+takes time. Under these assumptions, an example showing the execution
+of tasks scheduled by the implementation is depicted in
+Fig.~\ref{f:example}(b). Note that the second job instance of $\tau_1$
+is initiated at time $11$ instead of $10$, because switching is
+performed and the interrupt mask bit is set at time $10$, exemplifying
+differences between (A1') and (A1).
 
@@
 
-In this section, we introduce first how we model the states--the
-static aspect--of the system using terms of given sorts, or called
-data types, then how we specify the essential behaviors--the dynamic
-aspect--using rewrite rules. In particular, modeling of
-\emph{instantaneous behaviors} would be explained in
-Sections~\ref{ss:ir}, \ref{ss:init} and~\ref{ss:inthandling}, followed
-by \emph{timed behaviors} in Section~\ref{ss:timedbehavior}.
+In this section, we introduce first how we model states -- the static
+aspect -- of the system using terms of given sorts, or called data
+types, then how we specify essential behaviors -- the dynamic aspect
+-- using rewrite rules. In particular, modeling of \emph{instantaneous
+  behaviors} would be explained in Sections~\ref{ss:ir}, \ref{ss:init}
+and~\ref{ss:inthandling}, followed by \emph{timed behaviors} in
+Section~\ref{ss:timedbehavior}.
 
@@
 In our model, tasks are identified by their indexes of sort \verb|Nat|
-in the $taskList$. We define a sort \verb|MaybeNat| wrapping
+in $\mathit{taskList}$. We define a sort \verb|MaybeNat| wrapping
 \verb|Nat|s to refer to some task, with \emph{constructor} \verb|some|
@@
 operations \verb|push|, \verb|pop| and \verb|peek| on it.
-\hide{
-\begin{verbatim}
-  op bottom : -> Stack [ctor] .
-  op _#_ : Nat Stack -> Stack [ctor] .
-\end{verbatim}
-}
 
@@
 requirement of a task.
-\hide{
-\begin{verbatim}
-  op [_/_] : Time Time -> Counter [ctor] .
-\end{verbatim}
-}
-
-\hide{
-At last, to make our model checkable by untimed model checking, it is
-reasonable to reset the global variable $timer$ when it reaches an
-upper bound while increasing (see Line~\ref{l:timer} in
-Figure~\ref{f:schedule}) in the model. Then $timer$ is of sort
-\verb|Timer| and the upper bound would be the least common multiple of
-the periods of all tasks.}
-
-The global variable $timer$ is reset when it reaches an upper bound
-while increasing, which is not shown in detail in
-Figure~\ref{f:schedule} but is reasonable. The upper bound is the
-least common multiple of the periods of all tasks. A sort \verb|Timer|
-is defined to model the $timer$.
-\hide{
-\begin{verbatim}
-  op [_/_] : Nat NzNat -> Timer [ctor] .
-\end{verbatim}
-}
+
+The global variable $\mathit{timer}$ is reset when it reaches an upper
+bound while increasing, which is not shown in detail in
+Fig.~\ref{f:schedule} but is reasonable. The upper bound is the least
+common multiple of periods of all tasks. A sort \verb|Timer| is
+defined to model $\mathit{timer}$.
 
@@
 registers and stacks, and the interrupt source. The scheduler,
-i.e. the function $schedule()$, can be described by a single variable
-$timer$. We present the models of the other parts one by one.
+i.e.\ the function $\mathit{schedule()}$, can be described by a single
+variable $\mathit{timer}$. We present the models of the other parts
+one by one.
 
@@
 \verb|priority|, \verb|period| and \verb|status|:
-%  class PTask | priority : Nat, period : NzNat, 
 \begin{verbatim}
@@
 same as in the implementation.
+
+The list of periodic tasks, the variable $\mathit{taskList}$ in the
+implementation, is modeled as an instance of sort \verb|TaskList|,
+which is a list of \verb|PTask|s and/or \verb|error|s.  Periodic tasks
+are identified by their indexes in the list.
+
+On the other hand, a system task is an object instance of the subclass
+\verb|SysTask| of \verb|Task| with no extra attributes.
 \hide{
-\begin{verbatim}
-  ops RUNNING INTERRUPT READY DORMANT 
-        : -> Status [ctor] .
-\end{verbatim}
-}
-
-The list of periodic tasks, the variable $taskList$ in the
-implementation, is modeled as an instance of sort \verb|TaskList|,
-which is a list of \verb|PTask|s and/or \verb|error|s.
-\hide{
-\begin{verbatim}
-  op null : -> TaskList [ctor] .
-  op _::_ : Object TaskList 
-              ~> TaskList [ctor] .
-  mb (< O:Oid : PTask |> :: L:TaskList) 
-       : TaskList .
-  mb (error :: L:TaskList) : TaskList .
-\end{verbatim}
-}
-Periodic tasks are identified by their indexes in the list.
-
-On the other hand, a system task is an object instance of the subclass
-\verb|SysTask| of \verb|Task| with no extra attributes:
 \begin{verbatim}
@@
 \end{verbatim}
+}
 Different from periodic tasks, system tasks are organized in a
 multiset of sort \verb|SysTasks|, and identified by their \verb|Oid|s.
-%We abstract here from the detailed definitions thanks to the
-%similarity.
 
 \subsubsection{Hardware}
-Our model considers two parts of hardware related to the interrupt
-handling mechanism: the registers and the stack.
-
-The set of registers is modeled as an object instance of the class
+Our model considers two parts of hardware related to interrupt
+handling: the registers and the stack.
+
+The set of registers is modeled as an object instance of class
 \verb|Regs|, with attributes \verb|pc| denoting the program counter,
 \verb|mask| for the interrupt mask bit and \verb|ir| for the interrupt
-request bit, respectively:
+request bit:
 \begin{verbatim}
@@
 where the sort \verb|TaskID| contains subsorts \verb|MaybeNat| and
-\verb|Oid|, referring to some task.
-\hide{
-\begin{verbatim}
-  subsorts MaybeNat Oid < TaskID .
-\end{verbatim}
-}
-Some operations, such as \verb|getPc| and \verb|setMask|, are defined
-on the class \verb|Regs|.
+\verb|Oid|, referring to some task. Some operations, such as
+\verb|getPc| and \verb|setMask|, are defined on the class \verb|Regs|.
 
@@
 of an instance of \verb|Regs| and a term of sort \verb|Stack|.
-\hide{
-\begin{verbatim}
-  op [_;_] : Object Stack ~> Hardware [ctor] .
-  mb ([ < O:Oid : Regs |> ; S:Stack ]) 
-       : Hardware .
-\end{verbatim}
-}
 
@@
 introduced above, of a sort \verb|System|\footnote{Following the Maude
-  convention, variables would be written in capital letters. Some
-  variable declarations are not shown for simplicity.}:
+  convention, variables would be written in capital letters. Variable
+  declarations are not shown for simplicity.}:
 \begin{verbatim}
@@
 bit indicating there exists an interrupt request to be handled.
-\hide{
-\begin{verbatim}
-  op _.intReq : Hardware -> Hardware .
-  eq [ REGS ; S ].intReq 
-       = [ (REGS).setIr ; S ] .
-\end{verbatim}
-}
-
 Then the request will wait to be handled, which is explained in
@@
 \label{ss:init}
-Periodic tasks are initiated sequentially by the function
-$updateStatus()$ in Figure~\ref{f:schedule}, which is treated as an
-instantaneous action in our model. It is modeled by a recursive
-function \verb|updateStatus_with_|:
+Periodic tasks are initiated sequentially by $\mathit{updateStatus()}$
+in Fig.~\ref{f:schedule}, which is treated as an instantaneous action
+in our model. It is modeled by function \verb|updateStatus_with_|:
 \begin{verbatim}
@@
 \end{verbatim}
-%  eq updateStatus null with TIMER = null .
-%  eq updateStatus (TASK :: L) with TIMER
-%     = (update TASK with TIMER) 
-%       :: (updateStatus L with TIMER) .
 which applies function \verb|update_with_| on individual task
-sequentially to update the status
-(Lines~\ref{l:startupdate}-\ref{l:endupdate} in
-Figure~\ref{f:schedule}):
+sequentially to update the status (Lines~21--30 in
+Fig.~\ref{f:schedule}):
 \begin{verbatim}
@@
 \end{verbatim}
-with \verb|TIMER| the current value of the global variable $timer$.
-Given a task, if \verb|TIMER|($timer$) can be divided by its period
+with \verb|TIMER| the current value of the global variable $\mathit{timer}$.
+Given a task, if \verb|TIMER|($\mathit{timer}$) can be divided by its period
 \verb|T|, this task should be initiated.  In the case where the task
@@
 We can see that \verb|updateStatus_with_| behaves the same as
-$updateStatus()$ in Figure~\ref{f:schedule}.
+$\mathit{updateStatus()}$ in Fig.~\ref{f:schedule}.
 
@@
 pushing context into stack and so on), and to invoke the function
-$schedule()$. This behavior is modeled by the following instantaneous
+$\mathit{schedule()}$. This behavior is modeled by the following instantaneous
 rewrite rule:
@@
 the interrupt handling mechanism performed by the hardware and does
-four things: (i) clearing the bit \verb|ir|, which means the request
-has been handled; (ii) pushing the current \verb|pc| into the stack,
-storing the interrupted context; (iii) assigning \verb|scheduling| of
+four things: (i)~clearing the bit \verb|ir|, which means the request
+has been handled; (ii)~pushing the current \verb|pc| into the stack,
+storing the interrupted context; (iii)~assigning \verb|scheduling| of
 sort \verb|Oid| to \verb|pc|, which indicates that the system is
-scheduling; and (iv) setting the bit \verb|mask|, to mask coming
+scheduling; and (iv)~setting the bit \verb|mask|, to mask coming
 interrupt requests.
@@
 The other two parts together define its functionality. The second part
-corresponds to Lines~\ref{l:updatestatus}-\ref{l:inc} in
-Figure~\ref{f:schedule}. It updates the status of $taskList$ and
-increases $timer$ by $1$. This part is modeled by function
-\verb|_.startScheduling| which applies instantaneously at the
-beginning of scheduling, as shown in rule \verb|interrupt-handle|:
+corresponds to Lines~3--4 in Fig.~\ref{f:schedule}. It updates the
+status of $\mathit{taskList}$ and increases $\mathit{timer}$ by
+$1$. This part is modeled by function \verb|_.startScheduling| which
+applies instantaneously at the beginning of scheduling, as shown in
+rule \verb|interrupt-handle|:
 \begin{verbatim}
@@
 \end{verbatim}
-The third part corresponds to
-Lines~\ref{l:startrun1st}-\ref{l:endrun1st}, searching the first
+The third part corresponds to Lines~6--11, searching the first
 should-be-run periodic task and setting it to execute. It is modeled
@@
 where \verb|finish_in_| resets the counter of task \verb|scheduling|,
-and \verb|_.run1stTask| models
-Lines~\ref{l:startrun1st}-\ref{l:endrun1st} in
-Figure~\ref{f:schedule}, searching the task with highest priority
-that has status \verb|INTERRUPT| or \verb|READY| then performing an
-\emph{interrupt return} or executing it, respectively.
+and \verb|_.run1stTask| models Lines~6--11,
+searching the task with highest priority that has status
+\verb|INTERRUPT| or \verb|READY| then performing an \emph{interrupt
+  return} or executing it, respectively.
 
@@
 time of the task reaches its computation requirement.
-\hide{
-\begin{verbatim}
-  op _mayFinish?in_ : Oid SysTasks ~> Bool .
-  eq O mayFinish?in [ < O : SysTask | cnt : C > REST ] 
-       = C mayFinish? .
-  op _mayFinish? : Counter -> Bool .
-  eq [ R / [ MIN , MAX ] ] mayFinish?
-       = if R lt MIN then false else true fi .
-\end{verbatim}}
 
@@
 switching.
-\hide{
-\begin{verbatim}
-  crl [task-finish] :
-    (L T STS HW ISRC) 
-    => (SYSTEM).startSwitching
-    if SYSTEM := (L T STS HW ISRC)
-       /\ some N := (SYSTEM).running
-       /\ some N isComplete?in L .
-  crl [switching-finish] :
-    (L T STS HW ISRC) 
-    => (SYSTEM).finishSwitching
-    if SYSTEM := (L T STS HW ISRC)
-       /\ (SYSTEM).running == switching
-       /\ switching isComplete?in STS .
-\end{verbatim}
-}
 
@@
 tasks and the execution of the interrupt source. Both are modeled
-together by the following single \emph{standard} tick
+together by the  single \emph{standard} tick
 rule\footnote{The keyword \texttt{nonexec} should be given to allow
@@
 \end{verbatim}
-where \verb|delta| defines the effects of time elapse on the system,
-and \verb|mte| denotes the \emph{m}aximum amount of \emph{t}ime
-allowed to \emph{e}lapse from the current state until an instantaneous
-transition \emph{must} be performed. In fact, the core to model timed
-behaviors is to define functions \verb|delta| and \verb|mte|. Notice
-that the variable \verb|R| is \emph{continuous} with respect to the
-specific time domain\footnote{Real-Time Maude contains built-in
-  modules to define the time domain to be natural numbers and rational
-  numbers, specifying \emph{discrete} time domains and \emph{dense}
-  time domains, respectively.}  that we choose to instantiate our
-model on, which is different from timed automata that discretize dense
-time by defining ``clock region''.
-
-Time affects the system by advancing both the running task whose $ID$
-is loaded at \verb|pc| and the interrupt source simultaneously.  While
-time elapses, \verb|cnt| of the former increases and \verb|val| of the
-latter decreases, respectively:
+where \verb|delta| defines effects of time elapse on the system, and
+\verb|mte| denotes the \emph{m}aximum amount of \emph{t}ime allowed to
+\emph{e}lapse from the current state until an instantaneous action
+\emph{must} happen. In fact, the key to modeling timed behaviors is to
+define \verb|delta| and \verb|mte|. Note that the variable \verb|R| is
+\emph{continuous} with respect to the specific time
+domain\footnote{Real-Time Maude contains built-in modules to define
+  the time domain to be natural numbers and rational numbers,
+  specifying \emph{discrete} time domains and \emph{dense} time
+  domains, respectively.}  that we choose to instantiate our model on,
+which is different from timed automata that discretize dense time by
+defining ``clock region''.
+
+Time affects the system by advancing both the running task, whose
+$\mathit{ID}$ is loaded at \verb|pc|, and the interrupt source
+simultaneously.  While time elapses, \verb|cnt| of the former
+increases and \verb|val| of the latter decreases, respectively:
 \begin{verbatim}
@@
 \end{verbatim}
-where the last condition states that \verb|ID| is of sort
+where the last condition indicates that \verb|ID| is of sort
 \verb|MaybeNat|. Due to similarity, we omit details for the case where
@@
 
-\verb|mte|, the maximum amount of time allowed to elapse, depends on
-when the next instantaneous action must perform. Therefore, it is
-decided by three arguments: the remaining time to complete the running
-task, the remaining time to request the next interrupt, and whether or
-not there exists an interrupt request detected for the moment:
+\verb|mte| depends on when the next instantaneous transition must
+perform. Therefore, it is decided by three arguments: the remaining
+time to complete the running task, the remaining time to request the
+next interrupt, and whether or not there exists an interrupt request
+detected for the moment:
 \begin{verbatim}
@@
 request detected in the system, or \verb|INF| which represents
-\emph{infinity} otherwise. Again we do not show the case where
-\verb|ID| is of sort \verb|Oid|, which is very similar. 
-\hide{
-We should
-point out that \verb|mteTask| computes the remaining time to reach the
-maximum of the computation requirement of the task, since that is the
-time at which a \verb|task-finish| transition \emph{must} happen.
-}
+\emph{infinity} otherwise. The case where \verb|ID| is of sort
+\verb|Oid| is similar.
 
@@
 given initial state, the number of reachable states is finite, but may
-be unknown, thanks to the upper bound given to $timer$, which provides
-the potential for applying the untimed model checker.
+be unknown, thanks to the upper bound given to $\mathit{timer}$, which
+provides the potential for applying the untimed model checker.
 
 \subsection{Properties}
-We consider two properties in this paper: schedulability and
+We take two properties into account in this paper: schedulability and
 correctness. By schedulability, we examine whether a given task set is
@@
 define an atomic proposition \verb|taskTimeout| to hold if there
-exists an \verb|error| in $taskList$ of the current state, that is,
-some task misses its deadline:
+exists an \verb|error| in $\mathit{taskList}$ of the current state,
+that is, some task misses its deadline:
 \begin{verbatim}
@@
 \item The interrupt cycle $T$ is $5ms$.
-\item The scheduling time is $38{\mu}s$ and the switching time is
-  $20{\mu}s$.  
-\hide{\item The scheduling time ranges from $5{\mu}s$
-  to $9{\mu}s$, and the switching time ranges from $2{\mu}s$ to
-  $4{\mu}s$.}
+\item The scheduling time is $38{\mu}s$, switching time is $20{\mu}s$.
 \item The initial state is with empty stack, empty \verb|pc|, cleared 
@@
 \begin{itemize}
-\item Scenario~(i) with two tasks $\tau_1$ and $\tau_2$: $T_1=5ms$,
-  $C_1=3ms$, $T_2=25ms$ and $C_2=7ms$.
-\item Scenario~(ii) with two tasks $\tau_1$ and $\tau_2$: $T_1=5ms$,
-  $C_1=2ms$, $T_2=25ms$ and $C_2=2.3ms$.
-\item Scenario~(iii) with three tasks $\tau_1$, $\tau_2$ and $\tau_3$:
-  $T_1=5ms$, $C_1=2.7ms$, $T_2=10ms$, $C_2=2ms$, $T_3=25ms$ and
+\item Scenario~(i) with 2 tasks $\tau_1$ and $\tau_2$: $T_1=5ms$,
+  $C_1=3ms$, $T_2=25ms$, $C_2=7ms$.
+\item Scenario~(ii) with 2 tasks $\tau_1$ and $\tau_2$: $T_1=5ms$,
+  $C_1=2ms$, $T_2=25ms$, $C_2=2.3ms$.
+\item Scenario~(iii) with 3 tasks $\tau_1$, $\tau_2$, $\tau_3$:
+  $T_1=5ms$, $C_1=2.7ms$, $T_2=10ms$, $C_2=2ms$, $T_3=25ms$,
   $C_3=3ms$.
-\item Scenario~(iv) with three tasks $\tau_1$, $\tau_2$ and $\tau_3$:
-  $T_1=5ms$, $C_1=2.5ms$, $T_2=10ms$, $C_2=1.5ms$, $T_3=15ms$ and
-$C_3=4.5ms$.
+\item Scenario~(iv) with 3 tasks $\tau_1$, $\tau_2$, $\tau_3$:
+  $T_1\!=\!5ms$, $C_1\!=\!2.5ms$, $T_2\!=\!10ms$, $C_2\!=\!1.5ms$,
+  $T_3\!=\!15ms$, $C_3\!=\!4.5ms$.
 \end{itemize}
-Note that thanks to the powerful expressiveness of Real-Time Maude, we
+Note that thanks to the expressiveness of Real-Time Maude, we
 only need to define an initial state of sort \verb|System| to specify
@@
 
-\hide{
-\begin{itemize}
-\item Scenario (i) with two tasks: one having period $5ms$ and
-  computation requirement $[2.4ms, 3ms]$, and the other having period
-  $25ms$ and computation requirement $[6.1ms, 7ms]$.
-\item Scenario (ii) with two tasks: one having period $5ms$ and
-  computation requirement $[1.8ms, 2ms]$, and the other having period
-  $25ms$ and computation requirement $[2.1ms, 2.3ms]$.
-\item Scenario (iii) with three tasks: the first having period $5ms$
-  and computation requirement $[2.5ms, 2.7ms]$, the second having
-  period $10ms$ and computation requirement $[1.5ms, 2ms]$, and the
-  third having period $25ms$ and computation requirement $[2.6ms,
-    3ms]$.
-\item Scenario (iv) with three tasks: the first having period $5ms$
-  and computation requirement $[2.2ms, 2.5ms]$, the second having
-  period $10ms$ and computation requirement $[1.4ms, 1.5ms]$, and the
-  third having period $15ms$ and computation requirement $[4.3ms,
-    4.5ms]$.
-\end{itemize}
-}
-
 \begin{figure*}[!t]
 \centering
-\begin{tikzpicture}[font=\small,
-    % styles
-    system task/.style={fill=gray!70,draw=gray},
-    periodic task/.style={fill=gray!70!black,draw=gray!50!black},
-    task line/.style={gray!30,very thin},
-    time line/.style={gray!50,very thin,dashed},
-    short line/.style={gray!50,very thin,dashed},
-    init/.style={{Triangle[fill=white,scale=1.3]}-},
-    complete/.style={{Triangle[scale=1.3]}-}]
-
-  % grid
-  \foreach \x in {0.5,1.2,...,3.3}
-    \draw[task line] (0,\x) -- (15.7,\x);
-
-  % time indicator
-  \draw (0,0) node [below] {$0$};
-  \draw[time line] (0.5,3.3) -- (0.5,0);
-  \draw (0.5,-0.35) node [below] {$38$} [short line] -- +(0,0.35);
-  \draw (0.5,-3pt) -- (0.5,3pt);
-  \draw[time line] (2.5,3.3) -- (2.5,0);
-  \draw (2.3,0) node [below] {$2538$};
-  \draw (2.5,0) -- (2.5,3pt);
-  \draw[time line] (2.75,2.6) -- (2.75,0);
-  \draw (2.75,-0.35) node [below] {$2558$} [short line] -- +(0,0.35);
-  \draw (2.75,-3pt) -- (2.75,3pt);
-  \draw[time line] (4,2.6) -- (4,0);
-  \draw (3.8,0) node [below] {$4058$};
-  \draw (4,0) -- (4,3pt);
-  \draw[time line] (4.25,1.9) -- (4.25,0);
-  \draw (4.25,-0.35) node [below] {$4078$} [short line] -- +(0,0.35);
-  \draw (4.25,-3pt) -- (4.25,3pt);
-
-  \draw[time line] (5,3.3) -- (5,0);
-  \draw (5,0) node [below] {$5000$};
-  \draw (5,0) -- (5,3pt);
-  \draw[time line] (5.5,3.3) -- (5.5,0);
-  \draw (5.5,-0.35) node [below] {$5038$} [short line] -- +(0,0.35);
-  \draw (5.5,-3pt) -- (5.5,3pt);
-  \draw[time line] (7.5,3.3) -- (7.5,0);
-  \draw (7.3,0) node [below] {$7538$};
-  \draw (7.5,0) -- (7.5,3pt);
-  \draw[time line] (7.75,1.9) -- (7.75,0);
-  \draw (7.75,-0.35) node [below] {$7558$} [short line] -- +(0,0.35);
-  \draw (7.75,-3pt) -- (7.75,3pt);
-
-  \draw[time line] (10,3.3) -- (10,0);
-  \draw (9.9,0) node [below] {$10000$};
-  \draw (10,0) -- (10,3pt);
-  \draw[time line] (10.5,3.3) -- (10.5,0);
-  \draw (10.5,-0.35) node [below] {$10038$} [short line] -- +(0,0.35);
-  \draw (10.5,-3pt) -- (10.5,3pt);
-  \draw[time line] (12.5,3.3) -- (12.5,0);
-  \draw (12.2,0) node [below] {$12538$};
-  \draw (12.5,0) -- (12.5,3pt);
-  \draw[time line] (12.75,2.6) -- (12.75,0);
-  \draw (12.75,-0.35) node [below] {$12558$} [short line] -- +(0,0.35);
-  \draw (12.75,-3pt) -- (12.75,3pt);
-  \draw[time line] (14,2.6) -- (14,0);
-  \draw (13.7,0) node [below] {$14058$};
-  \draw (14,0) -- (14,3pt);
-  \draw[time line] (14.25,1.9) -- (14.25,0);
-  \draw (14.25,-0.35) node [below] {$14078$} [short line] -- +(0,0.35);
-  \draw (14.25,-3pt) -- (14.25,3pt);
-  \draw[time line] (15,1.9) -- (15,0);
-  \draw (15,0) node [below] {$15000$};
-  \draw (15,0) -- (15,3pt);
-
-  % axes
-  \draw[->,thick] (0,0) -- (15.7,0) node [above] {time(${\mu}s$)};
-  \draw[thin] (0,0) -- (0,3.8);
-
-  % tips of tasks
-  \draw (0,0.6) node [left] {switching};
-  \draw (0,1.3) node [left] {scheduling};
-  \draw (0,2) node [left] {$\tau_3$};
-  \draw (0,2.7) node [left] {$\tau_2$};
-  \draw (0,3.4) node [left] {$\tau_1$};
-
-  % tasks
-  \filldraw[system task] (0,1.2) rectangle +(0.5,0.2);
-  \filldraw[periodic task] (0.5,3.3) rectangle +(2,0.2);
-  \filldraw[system task] (2.5,0.5) rectangle +(0.25,0.2);
-  \filldraw[periodic task] (2.75,2.6) rectangle +(1.25,0.2);
-  \filldraw[system task] (4,0.5) rectangle +(0.25,0.2);
-  \filldraw[periodic task] (4.25,1.9) rectangle +(0.75,0.2);
-
-  \filldraw[system task] (5,1.2) rectangle +(0.5,0.2);
-  \filldraw[periodic task] (5.5,3.3) rectangle +(2,0.2);
-  \filldraw[system task] (7.5,0.5) rectangle +(0.25,0.2);
-  \filldraw[periodic task] (7.75,1.9) rectangle +(2.25,0.2);
-
-  \filldraw[system task] (10,1.2) rectangle +(0.5,0.2);
-  \filldraw[periodic task] (10.5,3.3) rectangle +(2,0.2);
-  \filldraw[system task] (12.5,0.5) rectangle +(0.25,0.2);
-  \filldraw[periodic task] (12.75,2.6) rectangle +(1.25,0.2);
-  \filldraw[system task] (14,0.5) rectangle +(0.25,0.2);
-  \filldraw[periodic task] (14.25,1.9) rectangle +(0.75,0.2);
-
-  % initiation of tasks
-  \foreach \x in {0,5,10}
-    \draw [init] (\x,3.3) -- +(0,-0.1);
-  \foreach \x in {0,10}
-    \draw [init] (\x,2.6) -- +(0,-0.1);  
-  \foreach \x in {0,15}
-    \draw [init] (\x,1.9) -- +(0,-0.1);
-
-  % completion of tasks
-  \draw [complete] (2.5,3.5) -- +(0,0.1);
-  \draw [complete] (4,2.8) -- +(0,0.1);
-  \draw [complete] (7.5,3.5) -- +(0,0.1);
-  \draw [complete] (12.5,3.5) -- +(0,0.1);
-  \draw [complete] (14,2.8) -- +(0,0.1);
-
-  % text
-  \draw[{Stealth}-,thick] (15,2.2) -- +(0,1.5)
-    node [above] {\emph{Misses Deadline!}};
-
-  % legend
-  \begin{scope}[xshift = -1.2cm]  
-    \draw [fill=gray!25,draw=gray!50,dashed] (1.5,4) rectangle +(8,1);
-    \draw (1.5,4.5) node [above right] {LEGEND};
-    \draw [init] (2,4.4) -- +(0,-0.1);
-    \draw (2.2,4.55) node [below right] {: Initiation of Tasks};
-    \draw [complete] (6,4.2) -- +(0,0.1);
-    \draw (6.2,4.55) node [below right] {: Completion of Tasks};
-  \end{scope}
-\end{tikzpicture}
+\includegraphics{ce.pdf}
 \caption{A counterexample of schedulability in Scenario~(iv). The first
@@
 \emph{maximal time sampling strategy}, the results of the model
-checking show that the correctness property holds in all scenarios. As
-to the schedulability property, it holds in Scenarios~(i-iii), but
+checking show that correctness property holds in all scenarios. 
+%% As to the 
+Schedulability property holds in Scenarios~(i--iii), but
 fails in Scenario~(iv).  One counterexample of the schedulability
 within Scenario~(iv), returned by the model checking command, is
-pictured in Figure~\ref{f:counterexample}, where the third task
-$\tau_3$ misses its deadline at the time $15ms$.
+pictured in Fig.~\ref{f:counterexample}, where
+$\tau_3$ misses its deadline at time $15ms$.
 
 The results above have demonstrated that our approach is capable of
-handling realistic industrial systems. However to further exam the
+handling realistic industrial systems. However, to further exam the
 efficiency of our approach, we also apply our method to larger test
@@
 schedulability of them under the above setting on an Intel Core 2 Quad
-Q9550, 2.83GHz, 4-cores machine with 8GB RAM running 64-bit Ubuntu
+Q9550, 2.83GHz, 4-core machine with 8GB RAM running 64-bit Ubuntu
 15.04. Among the 50 generated test scenarios with 5 tasks, we find
@@
 on the scale of the state space. And the scale is further positively
-correlated with $mn$, where $m$ is the upper bound of $timer$ and $n$
-is the number of periodic tasks. By the generated test scenarios, it
-turns out that the model checking command for schedulability in our
-model is able to handle scenarios, where $mn$ is up to about $10^6$,
-in an acceptable period of time say $90$ minutes.
+correlated with $mn$, where $m$ is the upper bound of $\mathit{timer}$
+and $n$ is the number of periodic tasks. By the generated test
+scenarios, it turns out that the model checking command for
+schedulability in our model is able to handle scenarios, where $mn$ is
+up to about $10^6$, in an acceptable period of time say $90$ minutes.
 
@@
 examining the counterexamples found. For instance, the counterexample
-shown in Figure~\ref{f:counterexample} is a real counterexample,
+shown in Fig.~\ref{f:counterexample} is a real counterexample,
 implying that the result for schedulability of Scenario~(iv) is
@@
 \label{t:main}
-Our approach using untimed model checking to verify the schedulability
-and the correctness of our model is complete.
+Our approach using untimed model checking to verify schedulability
+and correctness of our model is complete.
 \end{theorem}
@@
 By showing that our model is time-robust and that the two defined
-atomic propositions--\verb|taskTimeout| and \verb|correct|--are
-tick-invariant, then using Theorem~\ref{t:completeness}. For a more
+atomic propositions -- \verb|taskTimeout| and \verb|correct| -- are
+tick-invariant, then applying Theorem~\ref{t:completeness}. For a more
 detailed proof, see the Appendix.
@@
 on the task set. Nevertheless, all these results take no overhead into
-account, being not as realistic as ours. Katcher et al. did consider
+account, being not as realistic as ours. Katcher et al.\ did consider
 overhead in their schedulability analysis, under several models based
@@
 while theoretical approaches may need thorough analyses and reasoning.
-The last one is that, considering overhead and details of hardware do
+The last one is that, considering overhead and details of hardware does
 introduce some kind of non-determinism into the model. For example, in
@@
 when an interrupt request occurs, two different behaviors are
-possible: (i) the system performs task switching, during which the
+possible: (i)~the system performs task switching, during which the
 interrupt request is masked, hence the scheduling and initiation of
-tasks may be delayed; (ii) the system answers the interrupt request
+tasks may be delayed; (ii)~the system answers the interrupt request
 immediately, the switching being delayed. Tackling such
@@
 modeling some mechanism of the hardware, our model contains sufficient
-details to be analyzed for the behaviors of the real target
-system. Two important properties--schedulability and correctness--are
-verified by model checking on our model, within several key
+details to be analyzed for behaviors of the real target
+system. Two important properties -- schedulability and correctness --
+are verified by model checking on our model, within several key
 scenarios. We demonstrate the soundness and completeness of our
 results.
-
-%% \begin{figure}[!t]\centering
-%% 	\includegraphics[width=8.5cm]{FIG1.eps}
-%% 	\caption{Magnetization as a function of applied field.
-Note that ``Fig.'' is abbreviated.
-There is a period after the figure number, followed by two spaces.
-It is good practice to explain the significance of the figure in the caption.}\label{FIG_1}
-%% \end{figure}
 
@@
 [(iv)] \verb|mte(|$\sigma(l)$\verb|)|$= 0$ for each ground instance
-$\sigma(l)$ of each left-hand side of an instantaneous rewrite rule.
+$\sigma(l)$ of each left-hand side $l$ of an instantaneous rewrite rule.
 \end{enumerate}
@@
 A one-step rewrite $t\lrps{r}{1}t'$ using a tick rule and having
-duration $r$ is:\\
-- a \emph{maximal tick step}, written $t\lrps{r}{max}t'$, if there is
-no time value $r'>r$ such that $t\lrps{r'}{1}t''$ for some $t''$; \\
-- an \emph{$\infty$ tick step}, written $t\lrps{r}{\infty}t'$, if
-for each time value $r'>0$, there is a tick rewrite step
-$t\lrps{r'}{1}t''$; and \\
-- a \emph{non-maximal tick step} if there is a maximal tick step
-$t\lrps{r'}{max}t''$ for $r'>r$.
+duration $r$ is:
+\begin{itemize}
+\item[--] a \emph{maximal tick step}, written $t\lrps{r}{max}t'$, if
+  there is no time value $r'>r$ such that $t\lrps{r'}{1}t''$ for some
+  $t''$;
+\item[--] an \emph{$\infty$ tick step}, written $t\lrps{r}{\infty}t'$,
+  if for each time value $r'>0$, there is a tick rewrite step
+  $t\lrps{r'}{1}t''$; and
+\item[--] a \emph{non-maximal tick step} if there is a maximal tick
+  step $t\lrps{r'}{max}t''$ for $r'>r$.
+\end{itemize}
 \end{definition}
 \begin{definition}[\cite{DBLP:journals/entcs/OlveczkyM07a}]
-  A time-robust specification $\cal R$ is \emph{tick-invariant} with
-  respect to a set $P$ of propositions if and only if it is the case
-  that $t\simeq_P t'$ holds for each non-maximal or $\infty$ tick step
-  $t\lrps{r}{}t'$.
+  A time-robust specification $\mathcal{R}$ is \emph{tick-invariant} with
+  respect to a set $P$ of propositions if and only if $t\simeq_P t'$
+  holds for each non-maximal or $\infty$ tick step $t\lrps{r}{}t'$.
 \end{definition}
@@
 \label{l:tickinv}
-Let $\cal R$ be a time-robust object-oriented specification with a
+Let $\mathcal{R}$ be a time-robust object-oriented specification with a
 standard tick rule, and let the infinity element \verb|INF| be the
 only element in the time domain which is not a normal time value.
-%and let the time domain be \emph{linear}. 
-Then $\cal R$ is tick-invariant with respect to a set $P$ of atomic
+Then $\mathcal{R}$ is tick-invariant with respect to a set $P$ of atomic
 propositions if \verb|{|$t$\verb|}| $\simeq_P$
@@
 \label{l:auxtask}
-Given $ID$ of sort \verb|MaybeNat| and $L$ of sort \verb|TaskList|,
-\verb|mteTask(|$ID$\verb|,deltaTask(|$ID$\verb|,|$L$\verb|,|$r$\verb|))|
-$=$ \verb|mteTask(|$ID$\verb|,|$L$\verb|)| \verb|monus| $r$ for all
-$r\le$ \verb|mteTask(|$ID$\verb|,|$L$\verb|)|.
+Given $\mathit{ID}$ of sort \verb|MaybeNat| and $L$ of sort
+\verb|TaskList|, $\mteTask{\mathit{ID}}{\deltaTask{\mathit{ID}}{L}{r}}
+= \mteTask{\mathit{ID}}{L}\; \verb|monus|\;r$ for all
+$r\le\mteTask{\mathit{ID}}{L}$.
 \end{lemma}
 \begin{IEEEproof}
-If $ID=$ \verb|none|, the case is trivial. By definition,
-\verb|mteTask(none,deltaTask(none,|$L$\verb|,|$r$\verb|))| $=$
-\verb|mteTask(none,|$L$\verb|)| $=$ \verb|INF| $=$
-\verb|mteTask(none,|$L$\verb|)| \verb|monus| $r$. Otherwise, $ID=$
-\verb|some| $N$ with $N$ of sort \verb|Nat|. Assume that the
-\verb|cnt| of the $N$th task in $L$ is
+If $\mathit{ID}=\verb|none|$, the case is trivial. By definition,
+$\mteTask{\texttt{none}}{\deltaTask{\texttt{none}}{L}{r}} =
+\mteTask{\texttt{none}}{L} = \verb|INF| =
+\mteTask{\texttt{none}}{L}\\ \verb|monus|\; r$. Otherwise,
+$\mathit{ID}= \verb|some|~N$ with $N$ of sort \verb|Nat|. Assume that
+the \verb|cnt| of the $N$th task in $L$ is
 \verb|[|$r_e$\verb|/|$C$\verb|]|. Then by definition,
-\verb|deltaTask(|$ID$\verb|,|$L$\verb|,|$r$\verb|)| $= L'$, where the
+$\deltaTask{\mathit{ID}}{L}{r}=L'$, where the
 $N$th task in $L'$ has \verb|cnt| value being
@@
 \\
-= & \mteTask{ID}{L}~\verb|monus|~r~. 
+= & \mteTask{ID}{L}~\verb|monus|~r\;. \hfill\IEEEQEDhere
 \end{IEEEeqnarray*}
@@
 \label{l:auxis}
-Given $ISRC$ of class \verb|IntSrc| representing an reasonable state
-of interrupt source in our model, \mteIS{\deltaIS{$ISRC$}{$r$}} $=$
-\mteIS{$ISRC$} \verb|monus| $r$ for all $r\le$ \mteIS{$ISRC$}.
+Given $\mathit{ISRC}$ of class \verb|IntSrc| representing an
+reasonable state of interrupt source in our model,
+$\mteIS{\deltaIS{\mathit{ISRC}}{r}} = \mteIS{\mathit{ISRC}}\;
+\verb|monus|\\ r$ for all $r\le\mteIS{\mathit{ISRC}}$.
 \end{lemma}
 \begin{IEEEproof}
-A reasonable $ISRC$ must be of the form \IntSrc{$O$}{$v$}{$T$} with
-$v\le T$. Thus by definition, 
+A reasonable $\mathit{ISRC}$ must be of the form
+\IntSrc{$O$}{$v$}{$T$} with $v\le T$. Thus,
 \begin{IEEEeqnarray*}{Cl}
-  & \mteIS{\deltaIS{ISRC}{r}}
+  & \mteIS{\deltaIS{\mathit{ISRC}}{r}}
 \\  
@@
 \\
-= & v~\verb|monus|~r
-= \mteIS{ISRC}~\verb|monus|~r~.
+= & v~\texttt{monus}~r
+= \mteIS{\mathit{ISRC}}~\texttt{monus}~r\;. \hfill\IEEEQEDhere
 \end{IEEEeqnarray*}
@@
 \label{l:auxhw}
-Given $HW$ of sort \verb|Hardware|, for all $r\le$ \mteIr{$HW$},
-\mteIr{$HW$} $=$ \mteIr{$HW$} \verb|monus| $r$.
+Given $\mathit{HW}$ of sort \verb|Hardware|, for all
+$r\le\mteIr{\mathit{HW}}$, $\mteIr{\mathit{HW}} =
+\mteIr{\mathit{HW}}\; \verb|monus|\; r$.
 \end{lemma}
@@
   It concludes by discussing on whether there exists an interrupt
-  request detected in $HW$.
+  request detected in $\mathit{HW}$.
 \end{IEEEproof}
@@
 defined. Hence our model is time-robust by
-Lemma~\ref{l:timerobustness} provided conditions (i-iv) hold.
+Lemma~\ref{l:timerobustness} provided conditions (i--iv) hold.
 
@@
 \verb|System|. Let $s$ be of the form
-$(\mathit{L}~\mathit{T}~\mathit{STS}~\mathit{HW}~\mathit{ISRC})$ and
+$(L~T~\mathit{STS}~\mathit{HW}~\mathit{ISRC})$ and
 $\mathit{ID}=\verb|(|\mathit{HW}\verb|).getPc|$. We only consider the
@@
 \\  
-= & \mteS{\deltaTask{ID}{L}{r}
-\\
-  & \;\;\;\;\;\;\;\;\;T~STS~HW~\deltaIS{ISRC}{r}}
-\\
-= & \verb|minimum(|\mteTask{ID}{\deltaTask{ID}{L}{r}}\verb|,|
-\\
-  & \verb|        |\mteIS{\deltaIS{ISRC}{r}}\verb|,|
-\\
-  & \verb|        |\mteIr{HW}\verb|)|~.
+= & \mteS{\deltaTask{\mathit{ID}}{L}{r}
+\\
+  & \;\;\;\;\;\;\;\;\;T~\mathit{STS}~\mathit{HW}~\deltaIS{\mathit{ISRC}}{r}}
+\\
+= & \verb|minimum(|\mteTask{\mathit{ID}}{\deltaTask{\mathit{ID}}{L}{r}}\verb|,|
+\\
+  & \verb|        |\mteIS{\deltaIS{\mathit{ISRC}}{r}}\verb|,|
+\\
+  & \verb|        |\mteIr{\mathit{HW}}\verb|)|\;.
 \end{IEEEeqnarray*}
@@
 \\  
-= & \verb|minimum(|\mteTask{ID}{L}~\verb|monus|~r~\verb|,|
-\\
-  & \verb|        |\mteIS{ISRC}~\verb|monus|~r~\verb|,|
-\\
-  & \verb|        |\mteIr{HW}~\verb|monus|~r~\verb|)|
-\\
-= & \verb|minimum(|\mteTask{ID}{L}\verb|,|
-\\
-  & \verb|        |\mteIS{ISRC}\verb|,|
-\\
-  & \verb|        |\mteIr{HW}\verb|)|~\verb|monus|~r
-\\
-= & \mteS{s}~\verb|monus|~r~.
+= & \verb|minimum(|\mteTask{\mathit{ID}}{L}~\verb|monus|~r~\verb|,|
+\\
+  & \verb|        |\mteIS{\mathit{ISRC}}~\verb|monus|~r~\verb|,|
+\\
+  & \verb|        |\mteIr{\mathit{HW}}~\verb|monus|~r~\verb|)|
+\\
+= & \verb|minimum(|\mteTask{\mathit{ID}}{L}\verb|,|
+\\
+  & \verb|        |\mteIS{\mathit{ISRC}}\verb|,|
+\\
+  & \verb|        |\mteIr{\mathit{HW}}\verb|)|~\verb|monus|~r
+\\
+= & \mteS{s}~\verb|monus|~r\;.
 \end{IEEEeqnarray*}
@@
 Condition~(ii) follows from the fact that $r+0=r$ and
-$r$~\verb|monus|~$0=r$ for all $r$.
-
-Condition~(iii). We must prove \deltaS{\deltaS{$s$}{$r$}}{$r'$} $=$
-\deltaS{$s$}{$r+r'$} for all $r+r'\le$ \mteS{$s$}, with $s$ being a
-system state of sort \verb|System|. Using the same notations as in~(i),
-we only consider the case $\mathit{ID}$\verb|::MaybeNat| in detail. 
-By definition, the left side of the equation
+$r~\verb|monus|~0=r$ for all $r$.
+
+Condition~(iii). We must prove $\deltaS{\deltaS{s}{r}}{r'}\\ =
+\deltaS{s}{r+r'}$ for all $r+r'\le\mteS{s}$, with $s$ being a system
+state of sort \verb|System|. Using the same notations as in~(i), we
+only consider the case $\mathit{ID}$\verb|::MaybeNat| in detail. By
+definition, the left side of the equation
 \begin{IEEEeqnarray*}{Cl}
@@
 \\  
-= & \verb|(|\deltaTask{ID}{\deltaTask{ID}{L}{r}}{r'}
-\\
-  & \verb| |~T~STS~HW~\deltaIS{\deltaIS{ISRC}{r}}{r'}\verb|)|~\mbox{,}
+= & \verb|(|\deltaTask{\mathit{ID}}{\deltaTask{\mathit{ID}}{L}{r}}{r'}
+\\
+  & \verb| |~T~\mathit{STS}~\mathit{HW}~\deltaIS{\deltaIS{\mathit{ISRC}}{r}}{r'}\verb|)|~\mbox{,}
 \end{IEEEeqnarray*}
@@
 \\  
-= & \verb|(|\deltaTask{ID}{L}{r+r'}
-\\
-  & \verb| |~T~STS~HW~\deltaIS{ISRC}{r+r'}\verb|)|~\mbox{.}
+= & \verb|(|\deltaTask{\mathit{ID}}{L}{r+r'}
+\\
+  & \verb| |~T~\mathit{STS}~\mathit{HW}~\deltaIS{\mathit{ISRC}}{r+r'}\verb|)|~\mbox{.}
 \end{IEEEeqnarray*}
-\deltaTask{$ID$}{\deltaTask{$ID$}{$L$}{$r$}}{$r'$} $=$
-\deltaTask{$ID$}{$L$}{$r+r'$} holds by the associativity of $+$, while
-\deltaIS{\deltaIS{$ISRC$}{$r$}}{$r'$} $=$ \deltaIS{$ISRC$}{$r+r'$}
-holds since $(v$ \verb|monus| $r)$ \verb|monus| $r'$ $=$ $v$
-\verb|monus| $(r+r')$ with $v$ of sort \verb|Time|. Thus
-condition~(iii) holds.
+$\deltaTask{\mathit{ID}}{\deltaTask{\mathit{ID}}{L}{r}}{r'}
+=\deltaTask{\mathit{ID}}{L}{r+r'}$ holds by the associativity of $+$,
+while
+$\deltaIS{\deltaIS{\mathit{ISRC}}{r}}{r'}\!=\!\deltaIS{\mathit{ISRC}}{r+r'}$
+holds since $(v\; \verb|monus|\; r)\; \verb|monus|\; r'\\ = v\;
+\verb|monus|\; (r+r')$ with $v$ of sort \verb|Time|. Thus (iii) holds.
 
@@
 left-hand side of any instantaneous rule is $0$. For example,
-considering the (conditional) rule \verb|interrupt-request|, with its
-condition \verb|(|$ISRC$\verb|).timeout|, we know that the \verb|val|
-of $ISRC$ equals $0$. Therefore,
+considering the rule \verb|interrupt-request|, with its
+condition \verb|(|$\mathit{ISRC}$\verb|).timeout|, we know that \verb|val|
+of $\mathit{ISRC}$ equals $0$. Therefore,
 \begin{IEEEeqnarray*}{Cl}
-  & \mteS{L~T~STS~HW~ISRC}
-\\  
-= & \verb|minimum(|\mteTask{ID}{L}\verb|,|
-\\
-  & \verb|        |\mteIS{ISRC}\verb|,| \mteIr{HW}\verb|)|
-\\
-= & \verb|minimum(|\mteTask{ID}{L}\verb|,|~0~\verb|,| \mteIr{HW}\verb|)|
+  & \mteS{L~T~\mathit{STS}~\mathit{HW}~\mathit{ISRC}}
+\\  
+= & \verb|minimum(|\mteTask{\mathit{ID}}{L}\verb|,|
+\\
+  & \verb|        |\mteIS{\mathit{ISRC}}\verb|,| \mteIr{\mathit{HW}}\verb|)|
+\\
+= & \verb|minimum(|\mteTask{\mathit{ID}}{L}\verb|,|~0~\verb|,| \mteIr{\mathit{HW}}\verb|)|
 \\
@@
 Finally we prove the tick-invariance of the propositions used to
-analyze our model, i.e. \verb|taskTimeout| and \verb|correct|. By
+analyze our model, i.e.\ \verb|taskTimeout| and \verb|correct|. By
 Lemma~\ref{l:tickinv}, we must prove
@@
 advancing $r$ time units will not change the value of each
-proposition. Let $s$ be
-$(\mathit{L}~\mathit{T}~\mathit{STS}~\mathit{HW}~\mathit{ISRC})$ and
-$\verb|(|\mathit{HW}\verb|).getPc|=\mathit{ID}$.
+proposition. Let $s$ be $(L~T~\mathit{STS}~\mathit{HW}~\mathit{ISRC})$
+and $\verb|(|\mathit{HW}\verb|).getPc|=\mathit{ID}$.
 \begin{itemize}
-\item \verb|taskTimeout| holds if and only if $L$ contains an
-  \verb|error|. Since \verb|delta| does not produce or eliminate
+\item \verb|taskTimeout| holds if and only if $L$ contains
+  \verb|error|s. Since \verb|delta| does not produce or eliminate
   \verb|error| in $L$, \verb|taskTimeout| holds in $s$ if and only if
   \verb|taskTimeout| holds in $\deltaS{s}{r}$ for any $r<\mteS{s}$,
-  which means that our model is tick-invariant with respect to
+  implying our model is tick-invariant with respect to
   \verb|taskTimeout|.
-\hide{ 
-In our model, an \verb|error| cannot be eliminated by any operations,
-hence, if \verb|taskTimeout| holds in $s$, it must hold in
-$\deltaS{s}{r}$. On the other hand, \verb|error| can pop up only when
-operation \verb|update_with_| is applied, i.e., only when the
-instantaneous rule \verb|interrupt-handle| applies. If
-\verb|taskTimeout| does not hold in $s$, it will not hold either in
-$\deltaS{s}{r}$ for any $r<\mteS{s}$, since instantaneous rules cannot
-apply in $\deltaS{s}{r'}$ for any $r'<\mteS{s}$ by time-robustness.}
-\item The value of \verb|correct| depends on $ID$ and the status of
-  each task in $L$. Similarly, \verb|delta| does not change $ID$ or
-  the status of any task in $L$, hence \verb|correct| holds in $s$ if
-  and only if \verb|correct| holds in $\deltaS{s}{r}$ for any
-  $r<\mteS{s}$. It concludes the tick-invariance of \verb|correct|.
+\item The value of \verb|correct| depends on $\mathit{ID}$ and
+  status of each task in $L$. Similarly, \verb|delta| does not change
+  $\mathit{ID}$ or status of any task in $L$, hence \verb|correct|
+  holds in $s$ if and only if \verb|correct| holds in $\deltaS{s}{r}$
+  for any $r<\mteS{s}$. It concludes the tick-invariance of
+  \verb|correct|.
 \end{itemize}
@@
 Therefore, by Theorem~\ref{t:completeness}, our approach using untimed
-model checking to verify the schedulability and the correctness is
-complete.
+model checking to verify schedulability and correctness is complete.
 \end{IEEEproof}
@@
 \section*{Acknowledgment}
-The authors would like to thank the reviewers for their invaluable
-comments and suggestions.
+The authors would like to thank the reviewers and editors for their
+invaluable comments and suggestions.
 
@@
 \bibliographystyle{Bibliography/IEEEtranTIE}
-\bibliography{Bibliography/IEEEabrv,Bibliography/main}\ %IEEEabrv instead of IEEEfull
+\bibliography{Bibliography/IEEEabrv,Bibliography/main}\ 
+%IEEEabrv instead of IEEEfull
 

### 2016-11-03 RMS/final-version/main.tex
polished whole file

@@
 \usepackage{picinpar}
-\usepackage{amsmath}
+\usepackage[cmex10]{amsmath}
+\interdisplaylinepenalty=2500
 \usepackage{stfloats}
@@
 %% \interdisplaylinepenalty=2500
-\usepackage{algpseudocode}
+%% \usepackage{algpseudocode}
 %% \usepackage{array}
@@
 
-\usepackage{tikz}
-\usetikzlibrary{arrows.meta}
+%% \usepackage{tikz}
+%% \usetikzlibrary{arrows.meta}
 %% \usepackage{mathabx}
@@
   \thanks{ 
-    Manuscript received November 8, 2015; revised March 30, 2016 and
-    July 13, 2016; accepted October 20, 2016. This work was supported
-    in part by NSFC Program (No. 91218302, No. 61527812), National
-    Science and Technology Major Project (No. 2016ZX01038101), MIIT
-    IT funds (Research and application of TCN key technologies) of
-    China, and The National Key Technology R\&D Program
-    (No. 2015BAG14B01-02).
-
-    J. Liu is with the Department of Computer Science \& Technology,
-    Tsinghua University, Beijing 100084, China, and also with LIX,
-    \'Ecole Polytechnique, Palaiseau 91120, France (e-mail:
+    Manuscript received November 8, 2015; revised March 30,
+    2016 and July 13, 2016; accepted October 20, 2016. This work was
+    supported in part by NSFC Program (No.\ 91218302, No.\ 61527812,
+    No.\ 91218302), National Science and Technology Major Project
+    (No.\ 2016ZX01038101), MIIT IT funds (Research and application of
+    TCN key technologies) of China, and The National Key Technology
+    R\&D Program (No.\ 2015BAG14B01-02).
+
+    J.\ Liu is with the Department of Computer Science \& Technology,
+    Tsinghua University, Beijing, China 
+    \hide{, and also with LIX,
+    \'Ecole Polytechnique, Palaiseau 91120, France} (e-mail:
     jiaxiang.liu@hotmail.com).
 
-    M. Zhou is with the School of Software, Tsinghua University,
+    M.\ Zhou is with the School of Software, Tsinghua University,
     Beijing 100084, China (corresponding author; phone:
-    +86-10-6277-3275; fax: +86-10-6278-3549; e-mail: zhoumin03@gmail.com).
-
-    X. Song is with the Department of Electrical \& Computer
+    +86-10-6277-3275; fax: +86-10-6278-3549; e-mail:
+    zhoumin03@gmail.com).
+
+    X.\ Song is with the Department of Electrical \& Computer
     Engineering, Portland State University, Portland, OR 97207-0751,
@@
 
-    M. Gu and J. Sun are with the School of Software, Tsinghua
+    M.\ Gu and J.\ Sun are with the School of Software, Tsinghua
     University, Beijing 100084, China.
+
+    J.\ Liu, M.\ Zhou, M.\ Gu and J.\ Sun are also with Key Laboratory
+    for Information System Security, Ministry of Education, China, and
+    Tsinghua National Laboratory for Information Science and
+    Technology, China.  
   }  
@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J_Liu.jpg}}]%
-{Jiaxiang Liu} received his B.S. degree from the School of Software,
-Tsinghua University, China, in 2010. He is now a co-supervised
-Ph.D. candidate between the Department of Computer Science and
-Technology, Tsinghua University, China and LIX, \'Ecole Polytechnique,
-France. His research interests include formal methods, rewrite systems
-and embedded systems.
+{Jiaxiang Liu} received his B.S.\ degree in computer software from
+Tsinghua University, China in 2010. He is now a Ph.D.\ candidate in
+the Department of Computer Science and Technology, Tsinghua
+University, China. His research interests include formal methods,
+rewrite systems and embedded systems.
 \end{IEEEbiography}
@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Zhou.jpg}}]%
-{Min Zhou} received his B.S. degree from the Department of
-Mathematical Science and Ph.D. degree from the Department of Computer
-Science and Technology, Tsinghua University, China, in 2007 and 2014,
+{Min Zhou} received his B.S.\ degree from the Department of
+Mathematical Science and Ph.D.\ degree from the Department of Computer
+Science and Technology, Tsinghua University, China in 2007 and 2014,
 respectively. He is now a lecturer at the School of Software, Tsinghua
@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{X_Song.jpg}}]%
-{Xiaoyu Song} () received the Ph.D. degree from the University of
+{Xiaoyu Song} () received the Ph.D.\ degree from the University of
 Pisa, Italy, in 1991. From 1992 to 1998, he was on the faculty at the
@@
 {Ming Gu} is a professor at the School of Software, Tsinghua
-University and vice-director of Ministry of Education Key Laboratory
-of Information Security, China. Her research interests include
-software formal methods, software trustworthiness and middleware
-technology.
+University, China. She is also vice-director of Key Laboratory for
+Information System Security, Ministry of Education, China. Her
+research interests include software formal methods, software
+trustworthiness and middleware technology.
 \end{IEEEbiography}
@@
 member of the Chinese Academy of Engineering, director of Ministry of
-Education Key Laboratory of Information Security, and director of
-Tsinghua National Laboratory for Information Science and Technology,
-China. His research interests include computer graphics,
+Education Key Laboratory for Information System Security, and director
+of Tsinghua National Laboratory for Information Science and
+Technology, China. His research interests include computer graphics,
 computer-aided design, formal verification of software, software

### 2016-11-04 RMS/final-version/main.tex
first final version finished

@@
   Min~Zhou,
-  Xiaoyu~Song, \emph{Member}, \emph{IEEE},
+  Xiaoyu~Song, \emph{Senior Member}, \emph{IEEE},
   Ming~Gu,
@@
     supported in part by NSFC Program (No.\ 91218302, No.\ 61527812,
-    No.\ 91218302), National Science and Technology Major Project
+    No.\ 61402248), National Science and Technology Major Project
     (No.\ 2016ZX01038101), MIIT IT funds (Research and application of
@@
 safety-critical systems for the past few
-years~\cite{DBLP:journals/tie/MiyawakiMSYV05,DBLP:journals/iandc/MeseguerR13,DBLP:journals/cacm/Leroy09,DBLP:conf/sosp/KleinEHACDEEKNSTW09}. However,
+years~\cite{DBLP:journals/tie/JiangZLDSGS15,DBLP:journals/iandc/MeseguerR13,DBLP:journals/cacm/Leroy09,DBLP:conf/sosp/KleinEHACDEEKNSTW09}. However,
 as far as we know, few~\cite{TianD2011,DBLP:conf/iceccs/CuiDT14}
@@
 
-\section*{Acknowledgment}
-The authors would like to thank the reviewers and editors for their
-invaluable comments and suggestions.
+%% \section*{Acknowledgment}
+%% The authors would like to thank the reviewers and editors for their
+%% invaluable comments and suggestions.
 
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J_Liu.jpg}}]%
-{Jiaxiang Liu} received his B.S.\ degree in computer software from
-Tsinghua University, China in 2010. He is now a Ph.D.\ candidate in
-the Department of Computer Science and Technology, Tsinghua
-University, China. His research interests include formal methods,
-rewrite systems and embedded systems.
+\vspace{-5mm}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{1.jpg}}]%
+{Jiaxiang Liu} received his B.S.\ degree in software engineering from
+Tsinghua University, China in 2010. He is currently working toward the
+Ph.D.\ degree in computer science at Tsinghua University, China.
+
+His research interests include formal methods, rewrite systems and
+embedded systems.
 \end{IEEEbiography}
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Zhou.jpg}}]%
-{Min Zhou} received his B.S.\ degree from the Department of
-Mathematical Science and Ph.D.\ degree from the Department of Computer
-Science and Technology, Tsinghua University, China in 2007 and 2014,
-respectively. He is now a lecturer at the School of Software, Tsinghua
-University. His research interests include model checking, program
-analysis and testing.
+\vspace{-5mm}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Zhou1.jpg}}]%
+{Min Zhou} received his B.S.\ degree in mathematics and applied
+mathematics, and the Ph.D.\ degree in computer science from Tsinghua
+University, China in 2007 and 2014, respectively.
+
+He is currently a lecturer at the School of Software, Tsinghua
+University, China. His research interests include model checking,
+program analysis and testing.
 \end{IEEEbiography}
 
-%% \vspace{-2cm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{X_Song.jpg}}]%
-{Xiaoyu Song} () received the Ph.D.\ degree from the University of
-Pisa, Italy, in 1991. From 1992 to 1998, he was on the faculty at the
+\vspace{-5mm}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{X_Song1.jpg}}]%
+{Xiaoyu Song} received the Ph.D.\ degree from the University of Pisa,
+Italy, in 1991. From 1992 to 1998, he was on the faculty at the
 University of Montreal, Canada. He joined the Department of Electrical
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Gu.jpg}}]%
-{Ming Gu} is a professor at the School of Software, Tsinghua
-University, China. She is also vice-director of Key Laboratory for
-Information System Security, Ministry of Education, China. Her
-research interests include software formal methods, software
+\vspace{-5mm}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Gu1.jpg}}]%
+{Ming Gu} received the B.S.\ degree in computer science from the
+National University of Defense Technology, China in 1984, and the
+M.S.\ degree in computer science from the Chinese Academy of Science,
+China in 1986.
+
+She is currently a professor at the School of Software, Tsinghua
+University, China. 
+%% She is also vice-director of Key Laboratory for
+%% Information System Security, Ministry of Education, China. 
+Her research interests include software formal methods, software
 trustworthiness and middleware technology.
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J_Sun.jpg}}]%
-{Jiaguang Sun} is a professor and dean of the School of Information
-Science and Technology in Tsinghua University, China. He is also a
-member of the Chinese Academy of Engineering, director of Ministry of
-Education Key Laboratory for Information System Security, and director
-of Tsinghua National Laboratory for Information Science and
-Technology, China. His research interests include computer graphics,
-computer-aided design, formal verification of software, software
-engineering, and system architecture.
+\vspace{-5mm}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J_Sun1.jpg}}]%
+{Jiaguang Sun} received the B.S.\ degree in automation science from
+Tsinghua University, China in 1970.
+
+He is currently a professor and
+dean of the School of Information Science and Technology in Tsinghua
+University, China. He is also a member of the Chinese Academy of
+Engineering, and director of Tsinghua National Laboratory for
+Information Science and Technology, China. 
+His research interests
+include computer graphics, computer-aided design, formal verification
+of software, software engineering and system architecture.
 \end{IEEEbiography}

### 2016-11-08 RMS/final-version/ALL_15-TIE-3480.tex
final version: modified photos and renamed

--- 2016-11-04 RMS/final-version/main.tex
@@
 \usepackage{picinpar}
-\usepackage[cmex10]{amsmath}
-\interdisplaylinepenalty=2500
+\usepackage{amsmath}
 \usepackage{stfloats}
@@
 
-%% My packages
-%% \usepackage[cmex10]{amsmath}
-%% \interdisplaylinepenalty=2500
-%% \usepackage{algpseudocode}
-%% \usepackage{array}
-%%\usepackage{dblfloatfix}
-%%\usepackage[caption=false,font=footnotesize]{subfig}
-
-%% \usepackage{tikz}
-%% \usetikzlibrary{arrows.meta}
-%% \usepackage{mathabx}
-
-\newcommand{\hide}[1]{\ignorespaces}
-\newcommand{\jx}[1]{{\bf Jiaxiang: }#1{ \bf End}}
 \newtheorem{theorem}{Theorem}
@@
 \def\verbatim{\small\@verbatim \frenchspacing\@vobeyspaces \@xverbatim}
-%\def\verbatim@font{\small\ttfamily}
 \makeatother
@@
   Min~Zhou,
-  Xiaoyu~Song, \emph{Senior Member}, \emph{IEEE},
+  Xiaoyu~Song,
   Ming~Gu,
@@
     J.\ Liu is with the Department of Computer Science \& Technology,
-    Tsinghua University, Beijing, China 
-    \hide{, and also with LIX,
-    \'Ecole Polytechnique, Palaiseau 91120, France} (e-mail:
+    Tsinghua University, Beijing, China (e-mail:
     jiaxiang.liu@hotmail.com).
@@
 Layland~\cite{DBLP:journals/jacm/LiuL73}, which assigns priorities to
-jobs according to the periods of
-the
-corresponding tasks: the smaller
+jobs according to the periods of the corresponding tasks: the smaller
 period, the higher priority. RMS is proven to be the \emph{optimal}
@@
 condition for the schedulability of a set of $n$ tasks scheduled by
-RMS: $\displaystyle\Sigma^n_{i=1}C_i/T_i \le n(2^{1/n}-1)$, where
-$C_i$ and $T_i$ are the \emph{computation (time) requirement} and the
-period of task $\tau_i$, respectively. Two main directions on RMS have
-been explored since then. One is to relax the assumptions on the
-original RMS model, making it applicable on more systems.  For
-instance,
+RMS: $\Sigma^n_{i=1}C_i/T_i \le n(2^{1/n}-1)$, where $C_i$ and $T_i$
+are the \emph{computation (time) requirement} and the period of task
+$\tau_i$, respectively. Two main directions on RMS have been explored
+since then. One is to relax the assumptions on the original RMS model,
+making it applicable on more systems.  For instance,
 \cite{DBLP:conf/rtss/LehoczkySS87,DBLP:journals/rts/SpruntSL89,DBLP:conf/rtss/LehoczkyR92,DBLP:journals/tc/StrosniderLS95}
@@
 model extends the standard RMS model proposed
-in~\cite{DBLP:journals/jacm/LiuL73}, by considering overhead and other
-details of the hardware platform.
+in~\cite{DBLP:journals/jacm/LiuL73}, by taking into account overhead
+and other details of the hardware platform.
 
@@
 $\tau_i$.  The RMS algorithm chooses the labeling such that $T_1\le
-T_2\le \ldots \le T_n$. Consequently, $\tau_i$ receives priority $i$,
+T_2\le \ldots \le T_n$. Consequently, $\tau_i$ is given priority $i$,
 assuming smaller numbers have higher priorities. The following
@@
 implementation instead of the RMS algorithm itself, thus the model
-would be more complicated than this standard, ideal setting.
-%% Assumption
-(A1) will be modified because of the interrupt mask
-mechanism, while (A4) is relaxed to obtain a more realistic analysis
-model.
+would be more complicated than this standard, ideal setting.  (A1)
+will be modified because of the interrupt mask mechanism, while (A4)
+is relaxed to obtain a more realistic analysis model.
 
@@
 semantics is defined by conditional equations of the form $\texttt{ceq
-} \mathit{statePattern} \texttt{ |= } \mathit{prop} \texttt{ = } b \texttt{ if } cond$,
-with $b$ a term of sort \verb|Bool|, stating that $\mathit{prop}$ evaluates to
-$b$ in states which are instances of $\mathit{statePattern}$ provided the
-condition $cond$ holds. These equations together define $\mathit{prop}$ to hold
-in all states $s$ that make $s \texttt{ |= } \mathit{prop}$ evaluate to
-\verb|true|. A temporal logic \emph{formula} is constructed by state
-propositions and temporal logic operators such as \verb|~|(negation),
+} \mathit{statePattern} \texttt{ |= } \mathit{prop} \texttt{ = } b
+\texttt{ if } cond$, with $b$ a term of sort \verb|Bool|, stating that
+$\mathit{prop}$ evaluates to $b$ in states which are instances of
+$\mathit{statePattern}$ provided the condition $cond$ holds. These
+equations together define $\mathit{prop}$ to hold in all states $s$
+that make $s \texttt{ |= } \mathit{prop}$ evaluate to \verb|true|. A
+temporal logic \emph{formula} is constructed by state propositions and
+temporal logic operators such as \verb|~|(negation),
 \verb|\/|(disjunction), \verb|[]|(``always''),
@@
 \emph{untimed LTL model checking}. The untimed model checking command
-%% \indent
-%% $\texttt{(mc } s \texttt{ |=u } \Phi \texttt{ .)}$\\
 \begin{alltt}
@@
 \centering
-\includegraphics[width=8.8cm]{rms-pseudocode.pdf}
-\caption{The C-Like Pseudo-code of $schedule()$}
+\includegraphics[width=8.8cm]{FIG1_15-TIE-3480.pdf}
+\caption{The C-Like Pseudocode of $schedule()$}
 \label{f:schedule}
@@
 \centering
-\includegraphics{rms.pdf}
+\includegraphics{FIG2_15-TIE-3480.pdf}
 \caption{A set of $2$ periodic tasks scheduled under RMS algorithm and
@@
 
-We also need
-%a sort \verb|Interval| to denote computation requirements of tasks, and 
-a sort \verb|Counter| to record the execution of tasks.  We call
-\emph{execution time} the time how long a task has been executing
-for. A \verb|Counter| records the execution time and the computation
-requirement of a task.
+We also need a sort \verb|Counter| to record the execution of tasks.
+We call \emph{execution time} the time how long a task has been
+executing for. A \verb|Counter| records the execution time and the
+computation requirement of a task.
 
@@
 On the other hand, a system task is an object instance of the subclass
-\verb|SysTask| of \verb|Task| with no extra attributes.
-\hide{
-\begin{verbatim}
-  class SysTask | .  
-  subclass SysTask < Task .
-\end{verbatim}
-}
-Different from periodic tasks, system tasks are organized in a
-multiset of sort \verb|SysTasks|, and identified by their \verb|Oid|s.
+\verb|SysTask| of \verb|Task| with no extra attributes.  Different
+from periodic tasks, system tasks are organized in a multiset of sort
+\verb|SysTasks|, and identified by their \verb|Oid|s.
 
@@
 pushing context into stack and so on), and to invoke the function
-$\mathit{schedule()}$. This behavior is modeled by the following instantaneous
-rewrite rule:
+$\mathit{schedule()}$. This behavior is modeled by the following
+instantaneous rewrite rule:
 \begin{verbatim}
@@
   crl [scheduling-finish] :
-    (L T STS HW ISRC) 
-    => (SYSTEM).finishScheduling
+    SYSTEM => (SYSTEM).finishScheduling
     if SYSTEM := (L T STS HW ISRC) 
@@
 \item Scenario~(iv) with 3 tasks $\tau_1$, $\tau_2$, $\tau_3$:
-  $T_1\!=\!5ms$, $C_1\!=\!2.5ms$, $T_2\!=\!10ms$, $C_2\!=\!1.5ms$,
-  $T_3\!=\!15ms$, $C_3\!=\!4.5ms$.
+  $T_1=5ms$, $C_1=2.5ms$, $T_2=10ms$, $C_2=1.5ms$,
+  $T_3=15ms$, $C_3=4.5ms$.
 \end{itemize}
@@
 \centering
-\includegraphics{ce.pdf}
+\includegraphics{FIG3_15-TIE-3480.pdf}
 \caption{A counterexample of schedulability in Scenario~(iv). The first
@@
 checking show that correctness property holds in all scenarios.
-%% As to the 
-Schedulability property holds in Scenarios~(i--iii), but
-fails in Scenario~(iv).  One counterexample of the schedulability
-within Scenario~(iv), returned by the model checking command, is
-pictured in Fig.~\ref{f:counterexample}, where
-$\tau_3$ misses its deadline at time $15ms$.
+Schedulability property holds in Scenarios~(i--iii), but fails in
+Scenario~(iv).  One counterexample of the schedulability within
+Scenario~(iv), returned by the model checking command, is pictured in
+Fig.~\ref{f:counterexample}, where $\tau_3$ misses its deadline at
+time $15ms$.
 
@@
 \label{t:completeness}
-Given a time-robust real-time rewrite theory $\cal R$, a set $AP$ of
-tick-invariant atomic propositions, an LTL formula $\Phi$ (excluding
-the \emph{next} operator $\bigcirc$) whose atomic propositions are
-contained in $AP$. The untimed temporal logic model checking verifying
-$\Phi$ is \emph{complete} under the maximal time sampling strategy.
+Given a time-robust real-time rewrite theory $\mathcal{R}$, a set $AP$
+of tick-invariant atomic propositions, an LTL formula $\Phi$
+(excluding the \emph{next} operator $\bigcirc$) whose atomic
+propositions are contained in $AP$. The untimed temporal logic model
+checking verifying $\Phi$ is \emph{complete} under the maximal time
+sampling strategy.
 \end{theorem}
@@
 condition that a set of periodic tasks is schedulable with respect to
-RMS if $\displaystyle \Sigma^n_{i=1} C_i/T_i \le n(2^{1/n}-1)$
-holds. Then a more sufficient condition, known as \emph{Hyperbolic
-  Bound}, which has the same complexity as Liu and Layland's, was
-proposed in~\cite{DBLP:journals/tc/BiniBB03}. On the other hand,
-necessary and sufficient conditions for schedulability were derived
-independently in~\cite{DBLP:journals/rts/SpruntSL89}
-and~\cite{audsley1993deadline}, requiring more sophisticated analysis
-on the task set. Nevertheless, all these results take no overhead into
-account, being not as realistic as ours. Katcher et al.\ did consider
-overhead in their schedulability analysis, under several models based
-on different kinds of popular
-implementations~\cite{DBLP:journals/tse/KatcherAS93}.  However, our
-target implementation is not in their scope. Furthermore, compared
-with those theoretical analyses, our approach based on formal modeling
-and verification has three advantages. One is that if our
+RMS if $\Sigma^n_{i=1} C_i/T_i \le n(2^{1/n}-1)$ holds. Then a more
+sufficient condition, known as \emph{Hyperbolic Bound}, which has the
+same complexity as Liu and Layland's, was proposed
+in~\cite{DBLP:journals/tc/BiniBB03}. On the other hand, necessary and
+sufficient conditions for schedulability were derived independently
+in~\cite{DBLP:journals/rts/SpruntSL89} and~\cite{audsley1993deadline},
+requiring more sophisticated analysis on the task set. Nevertheless,
+all these results take no overhead into account, being not as
+realistic as ours. Katcher et al.\ did consider overhead in their
+schedulability analysis, under several models based on different kinds
+of popular implementations~\cite{DBLP:journals/tse/KatcherAS93}.
+However, our target implementation is not in their scope. Furthermore,
+compared with those theoretical analyses, our approach based on formal
+modeling and verification has three advantages. One is that if our
 schedulability test answers ``no'', it returns at the same time a real
@@
 while theoretical approaches may need thorough analyses and reasoning.
-The last one is that, considering overhead and details of hardware does
-introduce some kind of non-determinism into the model. For example, in
-our model, if the running task is complete \emph{right} at the time
-when an interrupt request occurs, two different behaviors are
+The last one is that, considering overhead and details of hardware
+does introduce some kind of non-determinism into the model. For
+example, in our model, if the running task is complete \emph{right} at
+the time when an interrupt request occurs, two different behaviors are
 possible: (i)~the system performs task switching, during which the
@@
 \label{l:timerobustness}
-Let $\cal R$ be an object-oriented specification with a standard tick
-rule, and let the infinity element \verb|INF| be the only element in
-the time domain which is not a normal time value.
-%and let the time domain be \emph{linear}.
-Then $\cal R$ is time-robust if the following conditions are satisfied
+Let $\mathcal{R}$ be an object-oriented specification with a standard
+tick rule, and let the infinity element \verb|INF| be the only element
+in the time domain which is not a normal time value.  Then
+$\mathcal{R}$ is time-robust if the following conditions are satisfied
 for all appropriate ground terms $t$ and $r,r'$:
@@
 [(iv)] \verb|mte(|$\sigma(l)$\verb|)|$= 0$ for each ground instance
-$\sigma(l)$ of each left-hand side $l$ of an instantaneous rewrite rule.
+$\sigma(l)$ of each left-hand side $l$ of an instantaneous rewrite
+rule.
 \end{enumerate}
@@
 \begin{IEEEeqnarray*}{Cl}
-  & \mteTask{ID}{\deltaTask{ID}{L}{r}}
-\\  
-= & \mteTask{ID}{L'}
+  & \mteTask{\mathit{ID}}{\deltaTask{\mathit{ID}}{L}{r}}
+\\  
+= & \mteTask{\mathit{ID}}{L'}
 \\
@@
 \\
-= & \mteTask{ID}{L}~\verb|monus|~r\;. \hfill\IEEEQEDhere
+= & \mteTask{\mathit{ID}}{L}~\verb|monus|~r\;. \hfill\IEEEQEDhere
 \end{IEEEeqnarray*}
 \end{IEEEproof}
+
 \begin{lemma}
@@
 A reasonable $\mathit{ISRC}$ must be of the form
-\IntSrc{$O$}{$v$}{$T$} with $v\le T$. Thus,
+$\IntSrc{O}{v}{T}$ with $v\le T$. Thus,
 \begin{IEEEeqnarray*}{Cl}
@@
 \end{IEEEproof}
+
 \begin{lemma}
@@
 Now we can present the detailed proof of Theorem~\ref{t:main}:
-\noindent
 \begin{IEEEproof}[Proof of Theorem~\ref{t:main}]
@@
 $\deltaTask{\mathit{ID}}{\deltaTask{\mathit{ID}}{L}{r}}{r'}
-=\deltaTask{\mathit{ID}}{L}{r+r'}$ holds by the associativity of $+$,
-while
+=\deltaTask{\mathit{ID}}{L}{r+r'}$ holds thanks to the associativity
+of $+$, while
 $\deltaIS{\deltaIS{\mathit{ISRC}}{r}}{r'}\!=\!\deltaIS{\mathit{ISRC}}{r+r'}$
@@
 
-%% \section*{Acknowledgment}
-%% The authors would like to thank the reviewers and editors for their
-%% invaluable comments and suggestions.
-
 %% References
@@
 \bibliographystyle{Bibliography/IEEEtranTIE}
-\bibliography{Bibliography/IEEEabrv,Bibliography/main}\ 
-%IEEEabrv instead of IEEEfull
+\bibliography{Bibliography/IEEEabrv,Bibliography/BIB_15-TIE-3480}\
 
@@
 
-\vspace{-5mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{1.jpg}}]%
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Jiaxiang_Liu.jpeg}}]%
 {Jiaxiang Liu} received his B.S.\ degree in software engineering from
-Tsinghua University, China in 2010. He is currently working toward the
-Ph.D.\ degree in computer science at Tsinghua University, China.
+Tsinghua University, Beijing, China in 2010. Since 2010, he has been
+working toward the Ph.D.\ degree in computer science at the Department
+of Computer Science and Technology, Tsinghua University, Beijing,
+China.
 
@@
 \vspace{-5mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Zhou1.jpg}}]%
-{Min Zhou} received his B.S.\ degree in mathematics and applied
-mathematics, and the Ph.D.\ degree in computer science from Tsinghua
-University, China in 2007 and 2014, respectively.
-
-He is currently a lecturer at the School of Software, Tsinghua
-University, China. His research interests include model checking,
-program analysis and testing.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Min_Zhou.jpeg}}]%
+{Min Zhou} received his B.S.\ degree in mathematics, and the
+Ph.D.\ degree in computer science from Tsinghua University, Beijing,
+China in 2007 and 2014, respectively.
+
+He is currently working as a lecturer at the School of Software,
+Tsinghua University, Beijing, China. His research interests include
+model checking, program analysis and testing.
 \end{IEEEbiography}
@@
 \vspace{-5mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{X_Song1.jpg}}]%
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Xiaoyu_Song.jpeg}}]%
 {Xiaoyu Song} received the Ph.D.\ degree from the University of Pisa,
@@
 \vspace{-5mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{M_Gu1.jpg}}]%
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Ming_Gu.jpeg}}]%
 {Ming Gu} received the B.S.\ degree in computer science from the
@@
 She is currently a professor at the School of Software, Tsinghua
-University, China. 
-%% She is also vice-director of Key Laboratory for
-%% Information System Security, Ministry of Education, China. 
-Her research interests include software formal methods, software
-trustworthiness and middleware technology.
+University, China.  Her research interests include software formal
+methods, software trustworthiness and middleware technology.
 \end{IEEEbiography}
@@
 \vspace{-5mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{J_Sun1.jpg}}]%
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Jiaguang_Sun.jpeg}}]%
 {Jiaguang Sun} received the B.S.\ degree in automation science from
@@
 
-He is currently a professor and
-dean of the School of Information Science and Technology in Tsinghua
-University, China. He is also a member of the Chinese Academy of
-Engineering, and director of Tsinghua National Laboratory for
-Information Science and Technology, China. 
-His research interests
-include computer graphics, computer-aided design, formal verification
-of software, software engineering and system architecture.
+He is currently a professor and dean of the School of Information
+Science and Technology in Tsinghua University, China. He is also a
+member of the Chinese Academy of Engineering, and director of Tsinghua
+National Laboratory for Information Science and Technology, China.
+His research interests include computer graphics, computer-aided
+design, formal verification of software, software engineering and
+system architecture.
 \end{IEEEbiography}
-
 \end{document}

### 2016-11-08 RMS/final-version/ALL_15-TIE-3480.tex
renamed the photos

@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Jiaxiang_Liu.jpeg}}]%
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{AUTHOR_JIAXIANG_LIU.jpeg}}]%
 {Jiaxiang Liu} received his B.S.\ degree in software engineering from
@@
 \vspace{-5mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Min_Zhou.jpeg}}]%
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{AUTHOR_MIN_ZHOU.jpeg}}]%
 {Min Zhou} received his B.S.\ degree in mathematics, and the
@@
 \vspace{-5mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Xiaoyu_Song.jpeg}}]%
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{AUTHOR_XIAOYU_SONG.jpeg}}]%
 {Xiaoyu Song} received the Ph.D.\ degree from the University of Pisa,
@@
 \vspace{-5mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Ming_Gu.jpeg}}]%
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{AUTHOR_MING_GU.jpeg}}]%
 {Ming Gu} received the B.S.\ degree in computer science from the
@@
 \vspace{-5mm}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Jiaguang_Sun.jpeg}}]%
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{AUTHOR_JIAGUANG_SUN.jpeg}}]%
 {Jiaguang Sun} received the B.S.\ degree in automation science from

### 2016-11-08 RMS/final-version/ALL_15-TIE-3480.tex
modified FIG2

@@
 \includegraphics{FIG2_15-TIE-3480.pdf}
-\caption{A set of $2$ periodic tasks scheduled under RMS algorithm and
-  the implementation, respectively. $T=T_1=10$, $T_2=20$, $C_1=3$,
-  $C_2=2$. In~(b), we assume both scheduling time and switching time
+\caption{A set of $2$ periodic tasks scheduled under (a) RMS algorithm
+  and (b) the RMS implementation, respectively. $T=T_1=10$, $T_2=20$,
+  $C_1=3$, $C_2=2$. In~(b), both scheduling time and switching time
   are $2$.}

### 2016-11-09 RMS/final-version/TXT_15-TIE-3480.tex
included bbl into TXT.tex

--- 2016-11-08 RMS/final-version/ALL_15-TIE-3480.tex
@@
 \usepackage{alltt}
-\usepackage[hidelinks]{hyperref}
+\usepackage[hidelinks,bookmarks=false]{hyperref}
 \usepackage{enumerate}
@@
 
-\bibliographystyle{Bibliography/IEEEtranTIE}
-\bibliography{Bibliography/IEEEabrv,Bibliography/BIB_15-TIE-3480}\
+% Generated by IEEEtran.bst, version: 1.12 (2007/01/11)
+\begin{thebibliography}{10}
+\providecommand{\url}[1]{#1}
+\csname url@samestyle\endcsname
+\providecommand{\newblock}{\relax}
+\providecommand{\bibinfo}[2]{#2}
+\providecommand{\BIBentrySTDinterwordspacing}{\spaceskip=0pt\relax}
+\providecommand{\BIBentryALTinterwordstretchfactor}{4}
+\providecommand{\BIBentryALTinterwordspacing}{\spaceskip=\fontdimen2\font plus
+\BIBentryALTinterwordstretchfactor\fontdimen3\font minus
+  \fontdimen4\font\relax}
+\providecommand{\BIBforeignlanguage}[2]{{%
+\expandafter\ifx\csname l@#1\endcsname\relax
+\typeout{** WARNING: IEEEtran.bst: No hyphenation pattern has been}%
+\typeout{** loaded for the language `#1'. Using the pattern for}%
+\typeout{** the default language instead.}%
+\else
+\language=\csname l@#1\endcsname
+\fi
+#2}}
+\providecommand{\BIBdecl}{\relax}
+\BIBdecl
+
+\bibitem{DBLP:journals/jacm/LiuL73}
+C.~L. Liu and J.~W. Layland, ``Scheduling algorithms for multiprogramming in a
+  hard-real-time environment,'' \emph{J. {ACM}}, vol.~20,
+  \href{http://dx.doi.org/10.1145/321738.321743}{DOI 10.1145/321738.321743},
+  no.~1, pp. 46--61, 1973.
+
+\bibitem{DBLP:conf/rtss/LehoczkySS87}
+J.~P. Lehoczky, L.~Sha, and J.~K. Strosnider, ``Enhanced aperiodic
+  responsiveness in hard real-time environments,'' in \emph{Proceedings of the
+  8th {IEEE} Real-Time Systems Symposium {(RTSS} '87)}, 1987, pp. 261--270.
+
+\bibitem{DBLP:journals/rts/SpruntSL89}
+B.~Sprunt, L.~Sha, and J.~P. Lehoczky, ``Aperiodic task scheduling for hard
+  real-time systems,'' \emph{Real-Time Systems}, vol.~1,
+  \href{http://dx.doi.org/10.1007/BF02341920}{DOI 10.1007/BF02341920}, no.~1,
+  pp. 27--60, 1989.
+
+\bibitem{DBLP:conf/rtss/LehoczkyR92}
+J.~P. Lehoczky and S.~Ramos{-}Thuel, ``An optimal algorithm for scheduling
+  soft-aperiodic tasks in fixed-priority preemptive systems,'' in
+  \emph{Proceedings of the Real-Time Systems Symposium},
+  \href{http://dx.doi.org/10.1109/REAL.1992.242671}{DOI
+  10.1109/REAL.1992.242671}, 1992, pp. 110--123.
+
+\bibitem{DBLP:journals/tc/StrosniderLS95}
+J.~K. Strosnider, J.~P. Lehoczky, and L.~Sha, ``The deferrable server algorithm
+  for enhanced aperiodic responsiveness in hard real-time environments,''
+  \emph{{IEEE} Trans. Comput.}, vol.~44,
+  \href{http://dx.doi.org/10.1109/12.368008}{DOI 10.1109/12.368008}, no.~1, pp.
+  73--91, 1995.
+
+\bibitem{DBLP:journals/pe/LeungW82}
+J.~Y. Leung and J.~Whitehead, ``On the complexity of fixed-priority scheduling
+  of periodic, real-time tasks,'' \emph{Perform. Eval.}, vol.~2,
+  \href{http://dx.doi.org/10.1016/0166-5316(82)90024-4}{DOI
+  10.1016/0166-5316(82)90024-4}, no.~4, pp. 237--250, 1982.
+
+\bibitem{audsley1993deadline}
+N.~Audsley, A.~Burns, and A.~Wellings, ``Deadline monotonic scheduling theory
+  and application,'' \emph{Control Engineering Practice}, vol.~1, no.~1, pp.
+  71--78, 1993.
+
+\bibitem{DBLP:journals/tc/ShaRL90}
+L.~Sha, R.~Rajkumar, and J.~P. Lehoczky, ``Priority inheritance protocols: An
+  approach to real-time synchronization,'' \emph{{IEEE} Trans. Comput.},
+  vol.~39, \href{http://dx.doi.org/10.1109/12.57058}{DOI 10.1109/12.57058},
+  no.~9, pp. 1175--1185, 1990.
+
+\bibitem{dhall1978real}
+S.~K. Dhall and C.~Liu, ``On a real-time scheduling problem,'' \emph{Operations
+  Research}, vol.~26, no.~1, pp. 127--140, 1978.
+
+\bibitem{DBLP:journals/rts/LopezGDG03}
+J.~M. L{\'{o}}pez, M.~Garc{\'{\i}}a, J.~L. D{\'{\i}}az, and D.~F.
+  Garc{\'{\i}}a, ``Utilization bounds for multiprocessor rate-monotonic
+  scheduling,'' \emph{Real-Time Systems}, vol.~24,
+  \href{http://dx.doi.org/10.1023/A:1021749005009}{DOI
+  10.1023/A:1021749005009}, no.~1, pp. 5--28, 2003.
+
+\bibitem{DBLP:journals/tpds/LopezDG04}
+J.~M. L{\'{o}}pez, J.~L. D{\'{\i}}az, and D.~F. Garc{\'{\i}}a, ``Minimum and
+  maximum utilization bounds for multiprocessor rate monotonic scheduling,''
+  \emph{{IEEE} Trans. Parallel Distrib. Syst.}, vol.~15,
+  \href{http://dx.doi.org/10.1109/TPDS.2004.25}{DOI 10.1109/TPDS.2004.25},
+  no.~7, pp. 642--653, 2004.
+
+\bibitem{DBLP:journals/tc/BaruahG03}
+S.~K. Baruah and J.~Goossens, ``Rate-monotonic scheduling on uniform
+  multiprocessors,'' \emph{{IEEE} Trans. Comput.}, vol.~52,
+  \href{http://dx.doi.org/10.1109/TC.2003.1214344}{DOI
+  10.1109/TC.2003.1214344}, no.~7, pp. 966--970, 2003.
+
+\bibitem{DBLP:journals/rts/OhS94}
+Y.~Oh and S.~H. Son, ``Enhancing fault-tolerance in rate-monotonic
+  scheduling,'' \emph{Real-Time Systems}, vol.~7,
+  \href{http://dx.doi.org/10.1007/BF01088524}{DOI 10.1007/BF01088524}, no.~3,
+  pp. 315--329, 1994.
+
+\bibitem{DBLP:journals/rts/GhoshMMS98}
+S.~Ghosh, R.~G. Melhem, D.~Moss{\'{e}}, and J.~S. Sarma, ``Fault-tolerant
+  rate-monotonic scheduling,'' \emph{Real-Time Systems}, vol.~15,
+  \href{http://dx.doi.org/10.1023/A:1008046012844}{DOI
+  10.1023/A:1008046012844}, no.~2, pp. 149--181, 1998.
+
+\bibitem{DBLP:journals/tpds/BertossiMR99}
+A.~A. Bertossi, L.~V. Mancini, and F.~Rossini, ``Fault-tolerant rate-monotonic
+  first-fit scheduling in hard-real-time systems,'' \emph{{IEEE} Trans.
+  Parallel Distrib. Syst.}, vol.~10,
+  \href{http://dx.doi.org/10.1109/71.798317}{DOI 10.1109/71.798317}, no.~9, pp.
+  934--945, 1999.
+
+\bibitem{DBLP:conf/rtss/LehoczkySD89}
+J.~P. Lehoczky, L.~Sha, and Y.~Ding, ``The rate monotonic scheduling algorithm:
+  Exact characterization and average case behavior,'' in \emph{Proceedings of
+  the Real-Time Systems Symposium},
+  \href{http://dx.doi.org/10.1109/REAL.1989.63567}{DOI
+  10.1109/REAL.1989.63567}, 1989, pp. 166--171.
+
+\bibitem{DBLP:conf/rtss/KuoM91}
+T.~Kuo and A.~K. Mok, ``Load adjustment in adaptive real-time systems,'' in
+  \emph{Proceedings of the Real-Time Systems Symposium},
+  \href{http://dx.doi.org/10.1109/REAL.1991.160369}{DOI
+  10.1109/REAL.1991.160369}, 1991, pp. 160--170.
+
+\bibitem{DBLP:journals/tc/BiniBB03}
+E.~Bini, G.~C. Buttazzo, and G.~M. Buttazzo, ``Rate monotonic analysis: The
+  hyperbolic bound,'' \emph{{IEEE} Trans. Comput.}, vol.~52,
+  \href{http://dx.doi.org/10.1109/TC.2003.1214341}{DOI
+  10.1109/TC.2003.1214341}, no.~7, pp. 933--942, 2003.
+
+\bibitem{gardner1999}
+M.~K. Gardner, ``Probabilistic analysis and scheduling of critical soft
+  real-time systems,'' Ph.D. dissertation, University of Illinois at
+  Urbana-Champaign, 1999.
+
+\bibitem{DBLP:journals/tie/JiangZLDSGS15}
+Y.~Jiang, H.~Zhang, Z.~Li, Y.~Deng, X.~Song, M.~Gu, and J.~Sun, ``Design and
+  optimization of multiclocked embedded systems using formal techniques,''
+  \emph{{IEEE} Trans. Ind. Electron.}, vol.~62,
+  \href{http://dx.doi.org/10.1109/TIE.2014.2316234}{DOI
+  10.1109/TIE.2014.2316234}, no.~2, pp. 1270--1278, 2015.
+
+\bibitem{DBLP:journals/iandc/MeseguerR13}
+J.~Meseguer and G.~Rosu, ``The rewriting logic semantics project: A progress
+  report,'' \emph{Inf. Comput.}, vol. 231,
+  \href{http://dx.doi.org/10.1016/j.ic.2013.08.004}{DOI
+  10.1016/j.ic.2013.08.004}, pp. 38--69, 2013.
+
+\bibitem{DBLP:journals/cacm/Leroy09}
+X.~Leroy, ``Formal verification of a realistic compiler,'' \emph{Commun.
+  {ACM}}, vol.~52, \href{http://dx.doi.org/10.1145/1538788.1538814}{DOI
+  10.1145/1538788.1538814}, no.~7, pp. 107--115, 2009.
+
+\bibitem{DBLP:conf/sosp/KleinEHACDEEKNSTW09}
+G.~Klein, K.~Elphinstone, G.~Heiser, J.~Andronick, D.~Cock, P.~Derrin,
+  D.~Elkaduwe, K.~Engelhardt, R.~Kolanski, M.~Norrish, T.~Sewell, H.~Tuch, and
+  S.~Winwood, ``sel4: formal verification of an {OS} kernel,'' in
+  \emph{Proceedings of the 22nd {ACM} Symposium on Operating Systems Principles
+  2009}, \href{http://dx.doi.org/10.1145/1629575.1629596}{DOI
+  10.1145/1629575.1629596}, 2009, pp. 207--220.
+
+\bibitem{TianD2011}
+C.~Tian and Z.~Duan, ``Model checking rate monotonic scheduling algorithm based
+  on propositional projection temporal logic,'' \emph{Journal of Software},
+  vol.~22, no.~2, pp. 211--221, 2011, in {Chinese}.
+
+\bibitem{DBLP:conf/iceccs/CuiDT14}
+J.~Cui, Z.~Duan, and C.~Tian, ``Model checking rate-monotonic scheduler with
+  {TMSVL},'' in \emph{19th International Conference on Engineering of Complex
+  Computer Systems}, \href{http://dx.doi.org/10.1109/ICECCS.2014.37}{DOI
+  10.1109/ICECCS.2014.37}, 2014, pp. 202--205.
+
+\bibitem{DBLP:journals/lisp/OlveczkyM07}
+P.~C. {\"{O}}lveczky and J.~Meseguer, ``Semantics and pragmatics of {Real-Time
+  Maude},'' \emph{Higher-Order and Symbolic Computation}, vol.~20,
+  \href{http://dx.doi.org/10.1007/s10990-007-9001-5}{DOI
+  10.1007/s10990-007-9001-5}, no. 1-2, pp. 161--196, 2007.
+
+\bibitem{DBLP:journals/tcs/ClavelDELMMQ02}
+M.~Clavel, F.~Dur{\'{a}}n, S.~Eker, P.~Lincoln, N.~Mart{\'{\i}}{-}Oliet,
+  J.~Meseguer, and J.~F. Quesada, ``Maude: specification and programming in
+  rewriting logic,'' \emph{Theor. Comput. Sci.}, vol. 285,
+  \href{http://dx.doi.org/10.1016/S0304-3975(01)00359-0}{DOI
+  10.1016/S0304-3975(01)00359-0}, no.~2, pp. 187--243, 2002.
+
+\bibitem{DBLP:journals/jlp/Meseguer12}
+J.~Meseguer, ``Twenty years of rewriting logic,'' \emph{J. Log. Algebr.
+  Program.}, vol.~81, \href{http://dx.doi.org/10.1016/j.jlap.2012.06.003}{DOI
+  10.1016/j.jlap.2012.06.003}, no. 7-8, pp. 721--781, 2012.
+
+\bibitem{DBLP:journals/entcs/OlveczkyM07a}
+P.~C. {\"{O}}lveczky and J.~Meseguer, ``Abstraction and completeness for
+  {Real-Time Maude},'' \emph{Electr. Notes Theor. Comput. Sci.}, vol. 176,
+  \href{http://dx.doi.org/10.1016/j.entcs.2007.06.005}{DOI
+  10.1016/j.entcs.2007.06.005}, no.~4, pp. 5--27, 2007.
+
+\bibitem{DBLP:journals/tse/KatcherAS93}
+D.~I. Katcher, H.~Arakawa, and J.~K. Strosnider, ``Engineering and analysis of
+  fixed priority schedulers,'' \emph{{IEEE} Trans. Softw. Eng.}, vol.~19,
+  \href{http://dx.doi.org/10.1109/32.241774}{DOI 10.1109/32.241774}, no.~9, pp.
+  920--934, 1993.
+
+\bibitem{DBLP:journals/tse/Holzmann97}
+G.~J. Holzmann, ``The model checker {SPIN},'' \emph{{IEEE} Trans. Softw. Eng.},
+  vol.~23, \href{http://dx.doi.org/10.1109/32.588521}{DOI 10.1109/32.588521},
+  no.~5, pp. 279--295, 1997.
+
+\bibitem{DBLP:conf/icfem/HanDW12}
+M.~Han, Z.~Duan, and X.~Wang, ``Time constraints with temporal logic
+  programming,'' in \emph{Formal Methods and Software Engineering - 14th
+  International Conference on Formal Engineering Methods, {ICFEM} 2012.
+  Proceedings}, ser. Lecture Notes in Computer Science, vol. 7635,
+  \href{http://dx.doi.org/10.1007/978-3-642-34281-3\_20}{DOI
+  10.1007/978-3-642-34281-3\_20}, 2012, pp. 266--282.
+
+\end{thebibliography}\
 

### 2016-11-09 RMS/final-version/TXT_15-TIE-3480.tex
finished TXT.tex

@@
-%\documentclass[onecolumn]{IEEEtranTIE}
-\documentclass[journal]{IEEEtranTIE}
+\documentclass[12pt,onecolumn]{IEEEtranTIE}
+%%\documentclass[journal]{IEEEtranTIE}
 \usepackage{graphicx}
@@
   propositions} are defined as terms of sort \verb|Prop|. Their
-semantics is defined by conditional equations of the form $\texttt{ceq
+semantics is defined by conditional equations of the form\\ $\texttt{ceq
 } \mathit{statePattern} \texttt{ |= } \mathit{prop} \texttt{ = } b
@@
 Given $\mathit{ID}$ of sort \verb|MaybeNat| and $L$ of sort
-\verb|TaskList|, $\mteTask{\mathit{ID}}{\deltaTask{\mathit{ID}}{L}{r}}
+\verb|TaskList|,\\ $\mteTask{\mathit{ID}}{\deltaTask{\mathit{ID}}{L}{r}}
 = \mteTask{\mathit{ID}}{L}\; \verb|monus|\;r$ for all
@@
 If $\mathit{ID}=\verb|none|$, the case is trivial. By definition,
-$\mteTask{\texttt{none}}{\deltaTask{\texttt{none}}{L}{r}} =
+$\mteTask{\texttt{none}}{\deltaTask{\texttt{none}}{L}{r}}\\ =
 \mteTask{\texttt{none}}{L} = \verb|INF| =
-\mteTask{\texttt{none}}{L}\\ \verb|monus|\; r$. Otherwise,
+\mteTask{\texttt{none}}{L}\; \verb|monus|\; r$. Otherwise,
 $\mathit{ID}= \verb|some|~N$ with $N$ of sort \verb|Nat|. Assume that
@@
 \verb|[|$r_e$\verb|/|$C$\verb|]|. Then by definition,
-$\deltaTask{\mathit{ID}}{L}{r}=L'$, where the
+$\deltaTask{\mathit{ID}}{L}{r}\\ = L'$, where the
 $N$th task in $L'$ has \verb|cnt| value being
@@
 $\mteIS{\deltaIS{\mathit{ISRC}}{r}} = \mteIS{\mathit{ISRC}}\;
-\verb|monus|\\ r$ for all $r\le\mteIS{\mathit{ISRC}}$.
+\verb|monus|\; r$ for all $r\le\mteIS{\mathit{ISRC}}$.
 \end{lemma}
@@
 Given $\mathit{HW}$ of sort \verb|Hardware|, for all
-$r\le\mteIr{\mathit{HW}}$, $\mteIr{\mathit{HW}} =
+$r\le\mteIr{\mathit{HW}}$,\\ $\mteIr{\mathit{HW}} =
 \mteIr{\mathit{HW}}\; \verb|monus|\; r$.
@@
 
-Condition~(iii). We must prove $\deltaS{\deltaS{s}{r}}{r'}\\ =
+Condition~(iii). We must prove $\deltaS{\deltaS{s}{r}}{r'} =
 \deltaS{s}{r+r'}$ for all $r+r'\le\mteS{s}$, with $s$ being a system
@@
 of $+$, while
-$\deltaIS{\deltaIS{\mathit{ISRC}}{r}}{r'}\!=\!\deltaIS{\mathit{ISRC}}{r+r'}$
-holds since $(v\; \verb|monus|\; r)\; \verb|monus|\; r'\\ = v\;
+$\deltaIS{\deltaIS{\mathit{ISRC}}{r}}{r'}=\deltaIS{\mathit{ISRC}}{r+r'}$
+holds since $(v\; \verb|monus|\; r)\; \verb|monus|\; r' = v\;
 \verb|monus|\; (r+r')$ with $v$ of sort \verb|Time|. Thus (iii) holds.
@@
 
-\vspace{-5mm}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{AUTHOR_MIN_ZHOU.jpeg}}]%
@@
 
-\vspace{-5mm}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{AUTHOR_XIAOYU_SONG.jpeg}}]%
@@
 
-\vspace{-5mm}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{AUTHOR_MING_GU.jpeg}}]%
@@
 
-\vspace{-5mm}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{AUTHOR_JIAGUANG_SUN.jpeg}}]%

### 2016-11-11 RMS/TIE/Final-version/ALL_15-TIE-3480.tex
rename the final-version dir
add months info to bibs

--- 2016-11-08 RMS/final-version/ALL_15-TIE-3480.tex
@@
 schedulability test conditions for the algorithm and its
-extensions~\cite{DBLP:conf/rtss/LehoczkySD89,DBLP:conf/rtss/KuoM91,DBLP:journals/tc/BiniBB03,DBLP:journals/rts/LopezGDG03,DBLP:journals/tc/BaruahG03,gardner1999}. The
+extensions~\cite{DBLP:conf/rtss/LehoczkySD89,DBLP:conf/rtss/KuoM91,DBLP:journals/tc/BiniBB03,DBLP:journals/rts/LopezGDG03,DBLP:journals/tc/BaruahG03}. The
 RMS algorithm is no doubt of practical importance.

### 2016-11-11 RMS/TIE/Final-version/TXT_15-TIE-3480.tex
modify TXT.tex

--- 2016-11-09 RMS/final-version/TXT_15-TIE-3480.tex
@@
   \href{http://dx.doi.org/10.1145/321738.321743}{DOI 10.1145/321738.321743},
-  no.~1, pp. 46--61, 1973.
+  no.~1, pp. 46--61, Jan. 1973.
 
@@
 J.~P. Lehoczky, L.~Sha, and J.~K. Strosnider, ``Enhanced aperiodic
-  responsiveness in hard real-time environments,'' in \emph{Proceedings of the
-  8th {IEEE} Real-Time Systems Symposium {(RTSS} '87)}, 1987, pp. 261--270.
+  responsiveness in hard real-time environments,'' in \emph{Proc. Real-Time
+  Systems Symposium ({RTSS} '87)}, Dec. 1987, pp. 261--270.
 
@@
   \href{http://dx.doi.org/10.1007/BF02341920}{DOI 10.1007/BF02341920}, no.~1,
-  pp. 27--60, 1989.
+  pp. 27--60, Jun. 1989.
 
@@
 J.~P. Lehoczky and S.~Ramos{-}Thuel, ``An optimal algorithm for scheduling
-  soft-aperiodic tasks in fixed-priority preemptive systems,'' in
-  \emph{Proceedings of the Real-Time Systems Symposium},
+  soft-aperiodic tasks in fixed-priority preemptive systems,'' in \emph{Proc.
+  Real-Time Systems Symposium ({RTSS} '92)},
   \href{http://dx.doi.org/10.1109/REAL.1992.242671}{DOI
-  10.1109/REAL.1992.242671}, 1992, pp. 110--123.
+  10.1109/REAL.1992.242671}, Dec. 1992, pp. 110--123.
 
@@
   \href{http://dx.doi.org/10.1109/12.368008}{DOI 10.1109/12.368008}, no.~1, pp.
-  73--91, 1995.
+  73--91, Jan. 1995.
 
@@
   \href{http://dx.doi.org/10.1016/0166-5316(82)90024-4}{DOI
-  10.1016/0166-5316(82)90024-4}, no.~4, pp. 237--250, 1982.
+  10.1016/0166-5316(82)90024-4}, no.~4, pp. 237--250, Dec. 1982.
 
 \bibitem{audsley1993deadline}
-N.~Audsley, A.~Burns, and A.~Wellings, ``Deadline monotonic scheduling theory
-  and application,'' \emph{Control Engineering Practice}, vol.~1, no.~1, pp.
-  71--78, 1993.
+N.~C. Audsley, A.~Burns, and A.~J. Wellings, ``Deadline monotonic scheduling
+  theory and application,'' \emph{Control Engineering Practice}, vol.~1, no.~1,
+  pp. 71--78, Feb. 1993.
 
@@
   vol.~39, \href{http://dx.doi.org/10.1109/12.57058}{DOI 10.1109/12.57058},
-  no.~9, pp. 1175--1185, 1990.
+  no.~9, pp. 1175--1185, Sep. 1990.
 
 \bibitem{dhall1978real}
-S.~K. Dhall and C.~Liu, ``On a real-time scheduling problem,'' \emph{Operations
-  Research}, vol.~26, no.~1, pp. 127--140, 1978.
+S.~K. Dhall and C.~L. Liu, ``On a real-time scheduling problem,''
+  \emph{Operations Research}, vol.~26, no.~1, pp. 127--140, Feb. 1978.
 
@@
   \href{http://dx.doi.org/10.1023/A:1021749005009}{DOI
-  10.1023/A:1021749005009}, no.~1, pp. 5--28, 2003.
+  10.1023/A:1021749005009}, no.~1, pp. 5--28, Jan. 2003.
 
@@
   \href{http://dx.doi.org/10.1109/TPDS.2004.25}{DOI 10.1109/TPDS.2004.25},
-  no.~7, pp. 642--653, 2004.
+  no.~7, pp. 642--653, Jul. 2004.
 
@@
   \href{http://dx.doi.org/10.1109/TC.2003.1214344}{DOI
-  10.1109/TC.2003.1214344}, no.~7, pp. 966--970, 2003.
+  10.1109/TC.2003.1214344}, no.~7, pp. 966--970, Jul. 2003.
 
@@
   \href{http://dx.doi.org/10.1007/BF01088524}{DOI 10.1007/BF01088524}, no.~3,
-  pp. 315--329, 1994.
+  pp. 315--329, Nov. 1994.
 
@@
   \href{http://dx.doi.org/10.1023/A:1008046012844}{DOI
-  10.1023/A:1008046012844}, no.~2, pp. 149--181, 1998.
+  10.1023/A:1008046012844}, no.~2, pp. 149--181, Sep. 1998.
 
@@
   \href{http://dx.doi.org/10.1109/71.798317}{DOI 10.1109/71.798317}, no.~9, pp.
-  934--945, 1999.
+  934--945, Sep. 1999.
 
@@
 J.~P. Lehoczky, L.~Sha, and Y.~Ding, ``The rate monotonic scheduling algorithm:
-  Exact characterization and average case behavior,'' in \emph{Proceedings of
-  the Real-Time Systems Symposium},
+  Exact characterization and average case behavior,'' in \emph{Proc. Real-Time
+  Systems Symposium ({RTSS} '89)},
   \href{http://dx.doi.org/10.1109/REAL.1989.63567}{DOI
-  10.1109/REAL.1989.63567}, 1989, pp. 166--171.
+  10.1109/REAL.1989.63567}, Dec. 1989, pp. 166--171.
 
@@
 T.~Kuo and A.~K. Mok, ``Load adjustment in adaptive real-time systems,'' in
-  \emph{Proceedings of the Real-Time Systems Symposium},
+  \emph{Proc. Real-Time Systems Symposium ({RTSS} '91)},
   \href{http://dx.doi.org/10.1109/REAL.1991.160369}{DOI
-  10.1109/REAL.1991.160369}, 1991, pp. 160--170.
+  10.1109/REAL.1991.160369}, Dec. 1991, pp. 160--170.
 
@@
   \href{http://dx.doi.org/10.1109/TC.2003.1214341}{DOI
-  10.1109/TC.2003.1214341}, no.~7, pp. 933--942, 2003.
-
-\bibitem{gardner1999}
-M.~K. Gardner, ``Probabilistic analysis and scheduling of critical soft
-  real-time systems,'' Ph.D. dissertation, University of Illinois at
-  Urbana-Champaign, 1999.
+  10.1109/TC.2003.1214341}, no.~7, pp. 933--942, Jul. 2003.
 
@@
   \href{http://dx.doi.org/10.1109/TIE.2014.2316234}{DOI
-  10.1109/TIE.2014.2316234}, no.~2, pp. 1270--1278, 2015.
+  10.1109/TIE.2014.2316234}, no.~2, pp. 1270--1278, Feb. 2015.
 
@@
   \href{http://dx.doi.org/10.1016/j.ic.2013.08.004}{DOI
-  10.1016/j.ic.2013.08.004}, pp. 38--69, 2013.
+  10.1016/j.ic.2013.08.004}, pp. 38--69, Oct. 2013.
 
@@
   {ACM}}, vol.~52, \href{http://dx.doi.org/10.1145/1538788.1538814}{DOI
-  10.1145/1538788.1538814}, no.~7, pp. 107--115, 2009.
+  10.1145/1538788.1538814}, no.~7, pp. 107--115, Jul. 2009.
 
@@
   D.~Elkaduwe, K.~Engelhardt, R.~Kolanski, M.~Norrish, T.~Sewell, H.~Tuch, and
-  S.~Winwood, ``sel4: formal verification of an {OS} kernel,'' in
-  \emph{Proceedings of the 22nd {ACM} Symposium on Operating Systems Principles
-  2009}, \href{http://dx.doi.org/10.1145/1629575.1629596}{DOI
-  10.1145/1629575.1629596}, 2009, pp. 207--220.
+  S.~Winwood, ``sel4: formal verification of an {OS} kernel,'' in \emph{Proc.
+  {ACM} Symposium on Operating Systems Principles ({SOSP} '09)},
+  \href{http://dx.doi.org/10.1145/1629575.1629596}{DOI
+  10.1145/1629575.1629596}, Oct. 2009, pp. 207--220.
 
@@
   on propositional projection temporal logic,'' \emph{Journal of Software},
-  vol.~22, no.~2, pp. 211--221, 2011, in {Chinese}.
+  vol.~22, \href{http://dx.doi.org/10.3724/SP.J.1001.2011.03729}{DOI
+  10.3724/SP.J.1001.2011.03729}, no.~2, pp. 211--221, Feb. 2011, in {Chinese}.
 
@@
 J.~Cui, Z.~Duan, and C.~Tian, ``Model checking rate-monotonic scheduler with
-  {TMSVL},'' in \emph{19th International Conference on Engineering of Complex
-  Computer Systems}, \href{http://dx.doi.org/10.1109/ICECCS.2014.37}{DOI
-  10.1109/ICECCS.2014.37}, 2014, pp. 202--205.
+  {TMSVL},'' in \emph{Proc. International Conference on Engineering of Complex
+  Computer Systems ({ICECCS} '14)},
+  \href{http://dx.doi.org/10.1109/ICECCS.2014.37}{DOI 10.1109/ICECCS.2014.37},
+  Aug. 2014, pp. 202--205.
 
@@
   \href{http://dx.doi.org/10.1007/s10990-007-9001-5}{DOI
-  10.1007/s10990-007-9001-5}, no. 1-2, pp. 161--196, 2007.
+  10.1007/s10990-007-9001-5}, no.~1, pp. 161--196, Jun. 2007.
 
@@
   \href{http://dx.doi.org/10.1016/S0304-3975(01)00359-0}{DOI
-  10.1016/S0304-3975(01)00359-0}, no.~2, pp. 187--243, 2002.
+  10.1016/S0304-3975(01)00359-0}, no.~2, pp. 187--243, Aug. 2002.
 
@@
   Program.}, vol.~81, \href{http://dx.doi.org/10.1016/j.jlap.2012.06.003}{DOI
-  10.1016/j.jlap.2012.06.003}, no. 7-8, pp. 721--781, 2012.
+  10.1016/j.jlap.2012.06.003}, no.~7, pp. 721--781, Oct. 2012.
 
@@
   \href{http://dx.doi.org/10.1016/j.entcs.2007.06.005}{DOI
-  10.1016/j.entcs.2007.06.005}, no.~4, pp. 5--27, 2007.
+  10.1016/j.entcs.2007.06.005}, no.~4, pp. 5--27, Jul. 2007.
 
@@
   \href{http://dx.doi.org/10.1109/32.241774}{DOI 10.1109/32.241774}, no.~9, pp.
-  920--934, 1993.
+  920--934, Sep. 1993.
 
@@
   vol.~23, \href{http://dx.doi.org/10.1109/32.588521}{DOI 10.1109/32.588521},
-  no.~5, pp. 279--295, 1997.
+  no.~5, pp. 279--295, May. 1997.
 
@@
 M.~Han, Z.~Duan, and X.~Wang, ``Time constraints with temporal logic
-  programming,'' in \emph{Formal Methods and Software Engineering - 14th
-  International Conference on Formal Engineering Methods, {ICFEM} 2012.
-  Proceedings}, ser. Lecture Notes in Computer Science, vol. 7635,
+  programming,'' in \emph{Formal Methods and Software Engineering - Proc.
+  International Conference on Formal Engineering Methods ({ICFEM} '12)}, ser.
+  Lecture Notes in Computer Science, vol. 7635,
   \href{http://dx.doi.org/10.1007/978-3-642-34281-3\_20}{DOI
-  10.1007/978-3-642-34281-3\_20}, 2012, pp. 266--282.
+  10.1007/978-3-642-34281-3\_20}, Nov. 2012, pp. 266--282.
 

### 2016-12-19 RMS/TIE/Proof-check/corrections_v1_20161210.tex
backup the 1st version of proof check for TIE

%\documentclass[a4paper]{article}
\documentclass[12pt,onecolumn]{IEEEtranTIE}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[10pt,journal,compsoc]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
% \ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
%   \usepackage[nocompress,noadjust]{cite}
% \else
  % normal IEEE
%  \usepackage[noadjust]{cite}
%\fi
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.
%
% Note that some packages require special options to format as the Computer
% Society requires. In particular, Computer Society  papers do not use
% compressed citation ranges as is done in typical IEEE papers
% (e.g., [1]-[4]). Instead, they list every citation separately in order
% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
% package with the nocompress option which is supported by cite.sty v4.0
% and later. Note also the use of a CLASSOPTION conditional provided by
% IEEEtran.cls V1.7 and later.

% *** GRAPHICS RELATED PACKAGES ***
%
%\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
%\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
%\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

\usepackage{algpseudocode}

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%% \ifCLASSOPTIONcompsoc
%%   \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
%% \else
%%   \usepackage[caption=false,font=footnotesize]{subfig}
%% \fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a sans serif font rather
% than the serif font used in traditional IEEE formatting and thus the need
% to invoke different subfig.sty package options depending on whether
% compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Do not use the stfloats baselinefloat ability as IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
\usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

\usepackage{alltt}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{multicol}
\newcommand{\hide}[1]{\ignorespaces}
\newcommand{\jx}[1]{{\textbf{Jiaxiang: }}#1{ \textbf{ End}}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newcommand{\ANSWER}{\medskip\noindent\textbf{RESPONSE: }}
\newcommand{\COMMENT}{\medskip\noindent\textbf{COMMENT: }}

% Define the fontsize in environment {verbatim}
%% \makeatletter
%% \def\verbatim{\small\@verbatim \frenchspacing\@vobeyspaces \@xverbatim}
%% %\def\verbatim@font{\small\ttfamily}
%% \makeatother

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

\title{Review to the Article Proof}
\date{}

\maketitle
\vspace{-30pt}
\begin{center}
  \begin{tabular}{r l}
    \hline\hline
    & \\
    Article Number: & 15-TIE-3480\\
    Article Title: & Formal Modeling and Verification of a \\
    & Rate-Monotonic Scheduling Implementation \\
    & with Real-Time Maude \\
    Submitted to: & Transactions on Industrial Electronics \\
    DOI: & 10.1109/TIE.2016.2633476 \\
    & \\
    \hline\hline
  \end{tabular}
  \bigskip
\end{center}

\newcommand{\by}{$\rightarrow$ }

\section{Responses to the Queries}

\bigskip
Q1. Author: Please check whether the first footnote is ok as set.

Response: The first footnote is OK.

\bigskip
Q2. Author: Please check whether the affiliations for all the authors
are ok as set.

Response: They are OK.

\bigskip
Q3. Author: Please provide the subject in which ``Xiaoyu Song'' received
his Ph.D. degree.

Response: Xiaoyu Song received his Ph.D.\ degree in computer
engineering.

\section{List of Corrections}

\medskip
The positions, which need to be corrected, are highlighted in the file
\verb|annotated_proof.pdf|. Here we list all the corrections
corresponding to the highlighted positions in
\verb|annotated_proof.pdf|. The file \verb|example.pdf| is typeset by
the authors, and it may be useful for the corrections. (The
corresponding positions are also highlighted.)

\medskip
Here are the detailed list of corrections:

\medskip
\begin{itemize}\setlength{\itemsep}{10pt}

\item Page 1, line 3: ``With'' \by ``with''.

We guess the first letter of a preposition need not be capitalized.

\item Page 1, line 65: ``few attempt [23], [24]'' \by ``few [23], [24] attempt''

\item Page 1, line 68: ``\emph{real-time Maude}'' \by ``\emph{Real-Time Maude}''.

It is the name of the tool.

\item Page 1, line 76: ``Section'' and ``II''. Please do not break
  ``Section II'' into two lines.

\item Page 2, line 78: ``real-time Maude'' \by ``Real-Time Maude''

\item Page 2, line 80: ``real-time Maude'' \by ``Real-Time Maude''

\item Page 2, line 110: ``Real-time Maude'' \by ``Real-Time Maude''

\item Page 2, line 113: ``Real-time Maude'' \by ``Real-Time Maude''

\item Page 2, line 127: ``$IR$'' \by ``$\mathit{IR}$''. Please use the
  macro \verb|\mathit{}|.

\item Page 2, line 134: ``$TR$'' \by ``$\mathit{TR}$''. Please use the
  macro \verb|\mathit{}|.

\item Page 2, line 138: ``$IR$'' \by ``$\mathit{IR}$''. Please use the
  macro \verb|\mathit{}|.

\item Page 2, line 138: ``$TR$'' \by ``$\mathit{TR}$''. Please use the
  macro \verb|\mathit{}|.

\item Page 2, line 139: ``nondeterministically'' \by
  ``non-deterministically''.

\item Page 2, line 141: ``nondeterministic'' \by
  ``non-deterministic''.

\item Page 2, line 142: ``real-time Maude'' \by ``Real-Time Maude''

\item Page 2, line 143: ``Real-time Maude'' \by ``Real-Time Maude''

\item Page 2, line 144: ``\verb|class ...|'' \by ``$\texttt{class
}C\texttt{ |
}att_1\texttt{:}s_1\texttt{,}\ldots\texttt{,}att_n\texttt{:}s_n$''.

All things should be put in \verb|\verb| mode except ``$C$''
``$att_1$'' ``$s_1$'' ``$\ldots$'' ``$att_n$'' and ``$s_n$'', which
should be in math mode.

\item Page 2, line 147: ``\verb|< ... >|'' \by ``$\texttt{< }
  O\texttt{:} C \texttt{ | } att_1\texttt{:}val_1\texttt{,} \ldots
  \texttt{,}att_n\texttt{:}val_n\texttt{ >}$''.

All things should be put in \verb|\verb| mode except ``$O$'' ``$C$''
``$att_1$'' ``$val_1$'' ``$\ldots$'' ``$att_n$'' and ``$val_n$'',
which should be in math mode.

\item Page 2, line 152: ``Real-time Maude'' \by ``Real-Time Maude''

\item Page 2, line 159: ``real-time Maude'' \by ``Real-Time Maude''

\item Page 2, line 164: ``\verb|ceq ...|'' \by ``$\texttt{ceq }
  \mathit{statePattern} \texttt{ |= } \mathit{prop} \texttt{ = } b
  \texttt{ if } cond$''.

All things should be put in \verb|\verb| mode except
``$\mathit{statePattern}$'' ``$\mathit{prop}$'' ``$b$'' and
``$cond$'', which should be in math mode. And ``$\mathit{statePattern}$''
and ``$\mathit{prop}$'' are better to use the macro \verb|\mathit{}|.

\item Page 2, line 165: ``$prop$'' \by ``$\mathit{prop}$''. Please use the
  macro \verb|\mathit{}|.

\item Page 2, line 166: ``$statePattern$'' \by
  ``$\mathit{statePattern}$''. Please use the macro \verb|\mathit{}|.

\item Page 2, line 167: ``$prop$'' \by ``$\mathit{prop}$''. Please use the
  macro \verb|\mathit{}|.

\item Page 2, line 168: ``$s~|= prop$'' \by ``$s \texttt{ |= }
  \mathit{prop}$''.

All things should be put in \verb|\verb| mode except ``$s$'' and
``$\mathit{prop}$'', which should be in math mode. And please use the
macro \verb|\mathit{}| for ``$\mathit{prop}$''.

\item Page 2, line 170: ``(negation)'' \by ``\verb|~|(negation)''. The
  tilde ``\verb|~|'' should be in \verb|\verb| mode.

\item Page 2, line 170: ``$\backslash$\verb|/|'' \by ``\verb|\/|''. All
  things should be put in \verb|\verb| mode.

\item Page 2, line 171: ``Real-time Maude'' \by ``Real-Time Maude''

\item Page 2, line between 172 and 173: ``(mc ... )'' \by
  ``\verb|(mc |$s$\verb+ |=u +$\Phi$\verb| .)|''.

All things should be put in \verb|\verb| mode except ``$s$'' and
``$\Phi$'', which should be in math mode.

\item Page 3, line 210--217:

For the \verb|\enumerate| environment, is it possible to reduce the
indentation right after the number, such that for each item, the first
word of the first line is aligned with those of the other lines? For
example, reduce the space between ``1)'' and ``the'' at line 210, such
that this ``the'' is aligned with ``possibly'' at line 211 and ``is''
at line 212.

\item Page 3, line 218: ``Switching''.

Please remove the indentation before ``Switching'', this is not a new
paragraph.

\item Page 3, line 222--227:

For the \verb|\enumerate| environment, is it possible to reduce the
indentation right after the number, such that for each item, the first
word of the first line is aligned with those of the other lines?

\item Page 3, line 258: ``Sections IV-C''. Please do not break
  ``Sections IV-C'' into two lines.

\item Page 3, line 259: ``Section IV-F''. Please do not break
  ``Section IV-F'' into two lines.

\item Page 4, lines 293--294:

Please make sure that this kind of code throughout the article is put
in \verb|\verb| mode. (We are not sure whether it is true because
``\verb+|+'' look a bit higher and ``\verb|>|'' look a bit wider than
what they should be.)

\item Page 4, lines 300--302: it should be
\begin{verbatim}
  class PTask | priority : Nat, 
                period : Nat, 
                status : Status .
\end{verbatim}

Please make sure that ``\verb|priority|'' ``\verb|period|'' and
``\verb|status|'' are aligned with each other.

\item Page 4, line 304: ``\verb|RUN-NING|'' \by ``\verb|RUNNING|''.

Please use \verb|\verb| mode and do not break the word into two parts.

\item Page 4, lines 320--321: it should be
\begin{verbatim}
  class Regs | pc : TaskID, 
               mask : Bool, ir : Bool .
\end{verbatim}

Please make sure that ``\verb|pc|'' is aligned with ``\verb|mask|''.

\item Page 4, lines 331--332: it should be
\begin{verbatim}
  class IntSrc | val : Time, 
                 cycle : Time .
\end{verbatim}

Please make sure that ``\verb|val|'' is aligned with ``\verb|cycle|''.

\item Page 4, lines 335--337: it should be
\begin{verbatim}
  op _____ : TaskList Timer SysTasks 
             Hardware Object 
             ~> System [ctor] .
\end{verbatim}

Please make sure that ``\verb|TaskList|'' ``\verb|Hardware|'' and
``\verb|~>|'' are aligned with each other.

\item Page 4, lines 338--339: it should be
\begin{verbatim}
  mb (L T STS HW < O : IntSrc |>) 
     : System .
\end{verbatim}

Please make sure that ``\verb|(|'' is aligned with ``\verb|:|''.

\item Page 4, line 340: ``\verb| ~>|'' \by ``\verb|~>|''. Please
  remove the space before ``\verb|~|''.

\item Page 4, line 342: ``\verb|Sys-Tasks|'' \by ``\verb|SysTasks|''.

Please use \verb|\verb| mode and do not break the word into two parts.

\item Page 5, lines 362--363: it should be
\begin{verbatim}
  op updateStatus_with_ : TaskList Timer 
                            -> TaskList . 
\end{verbatim}

Please make sure that ``\verb|->|'' is aligned with the first
``\verb|s|'' in ``\verb|TaskList|'' at line 362.

\item Page 5, lines 366--367: it should be
\begin{verbatim}
  op update_with_ : Object Timer 
                      ~> Object .
\end{verbatim}

Please make sure that ``\verb|~>|'' is aligned with the ``\verb|j|''
in ``\verb|Object|'' at line 366.

\item Page 5, lines 371--374: it should be
\begin{verbatim}
      = if ST == DORMANT 
        then < O : PTask | status : READY >
        else error fi
      if TIMER rem T == 0 .
\end{verbatim}

Please make sure that ``\verb|if|'' at 371, ``\verb|then|'' at 372 and
``\verb|else|'' at 373 are aligned with each other. And make sure that
``\verb|=|'' at 371 is aligned with ``\verb|if|'' at 374.

\item Page 5, lines 377--381: it should be
\begin{verbatim}
     = if ST == RUNNING 
       then < O : PTask 
              | status : INTERRUPT >
       else < O : PTask |> fi 
     [otherwise] .
\end{verbatim}

Please make sure that ``\verb|if|'' at 377, ``\verb|then|'' at 378 and
``\verb|else|'' at 380 are aligned with each other. Make sure that
``\verb+|+'' at 379 is aligned with ``\verb|O|'' at 378. Make sure
that ``\verb|[otherwise]|'' at 381 is aligned with ``\verb|=|'' at
377.

\item Page 5, lines 400--403: it should be
\begin{verbatim}
  crl [interrupt-handle] :
    SYSTEM =>  
    ((SYSTEM).interrupt).startScheduling
    if (SYSTEM).existInt .
\end{verbatim}

Please make sure that ``\verb|SYSTEM|'' at 401, ``\verb|((|'' at 402
and ``\verb|if|'' at 403 are aligned with each other.

\item Page 5, line 407--413:

For the \verb|\enumerate| environment, is it possible to reduce the
indentation right after the number, such that for each item, the first
word of the first line is aligned with those of the other lines?

\item Page 5, lines 426--427: it should be
\begin{verbatim}
  op _.startScheduling : System 
                           -> System .
\end{verbatim}

Please make sure that ``\verb|->|'' at 427 is aligned with the second
``\verb|s|'' in ``\verb|System|'' at 426.

\item Page 5, lines 429--430: it should be
\begin{verbatim}
     = ((updateStatus L with T) 
        inc(T) STS HW ISRC) .
\end{verbatim}

Please make sure that ``\verb|inc|'' at 430 is aligned with the second
``\verb|(|'' at 429.

\item Page 5, lines 435--436: it should be
\begin{verbatim}
  op _.finishScheduling : System 
                            -> System .
\end{verbatim}

Please make sure that ``\verb|->|'' at 436 is aligned with the second
``\verb|s|'' in ``\verb|System|'' at 435.

\item Page 5, lines 438--439: it should be
\begin{verbatim}
     = (L T (finish scheduling in STS) 
        HW ISRC).run1stTask .
\end{verbatim}

Please make sure that ``\verb|HW|'' at 439 is aligned with
``\verb|L|'' at 438.

\item Page 5, line 450: ``\verb|/|$\backslash$'' \by
  ``\verb|/\|''. All things should be put in \verb|\verb| mode.

\item Page 5, line 451: ``\verb|/|$\backslash$'' \by
  ``\verb|/\|''. All things should be put in \verb|\verb| mode.

\item Page 6, footnote 3: ``real-time Maude'' \by ``Real-Time Maude''

\item Page 6, footnote 4: ``Real-time Maude'' \by ``Real-Time Maude''

\item Page 6, line 478: ``$ID$'' \by ``$\mathit{ID}$''. Please use the
  macro \verb|\mathit{}|.

\item Page 6, lines 482--485: it should be
\begin{verbatim}
      = (deltaTask(ID, L, R) 
         T STS HW (deltaIS(ISRC, R)))
      if ID := (HW).getPc 
         /\ ID :: MaybeNat .
\end{verbatim}

Please make sure that ``\verb|deltaTask|'' at 482 is aligned with
``\verb|T|'' at 483. Make sure that ``\verb|=|'' at 482 is aligned
with ``\verb|if|'' at 484. And make sure that ``\verb|/\|'' at 485 is
aligned with ``\verb|ID|'' at 484.

\item Page 6, lines 495--498: it should be
\begin{verbatim}
      = minimum(mteTask(ID, L),
                mteIS(ISRC), mteIr(HW))
      if ID := (HW).getPc 
         /\ ID :: MaybeNat .
\end{verbatim}

Please make sure that ``\verb|mteTask|'' at 495 is aligned with
``\verb|mteIS|'' at 496. Make sure that ``\verb|=|'' at 495 is aligned
with ``\verb|if|'' at 497. And make sure that ``\verb|/\|'' at 498 is
aligned with ``\verb|ID|'' at 497.

\item Page 6, line 524: ``\verb|[]( taskTimeout)|'' \by
  ``\verb|[](~taskTimeout)|''.

All things should be put in \verb|\verb| mode.

\item Page 6, line 530: ``\verb|( taskTimeout)|'' \by
  ``\verb|(~taskTimeout)|''.

All things should be put in \verb|\verb| mode.

\item Page 6, lines 537--540: it should be
\begin{verbatim}
      = if ID :: MaybeNat 
        then shouldRun(ID, L)
        else true fi
      if ID := (HW).getPc .
\end{verbatim}

Please make sure that ``\verb|if|'' at 537, ``\verb|then|'' at 538 and
``\verb|else|'' at 539 are aligned with each other.  And make sure
that ``\verb|=|'' at 537 is aligned with ``\verb|if|'' at 540.

\item Page 6, lines 546--547: ``\verb|(...)\/(...)|'' \by
  ``\verb|([]correct)\/(correct U taskTimeout)|''.

Please put the formula in \verb|\verb| mode, and do not break it into
two lines.

\item Page 6, lines 551--552: it should be
\begin{verbatim}
  (mc init |=u ([]correct) 
               \/ (correct U taskTimeout) .)
\end{verbatim}

Please make sure that ``\verb|\/|'' at 552 is aligned with
``\verb|([]correct)|'' at 551.

Or if it is too wide to fit the column, it can be
\begin{verbatim}
  (mc init |=u ([]correct) \/ 
               (correct U taskTimeout) .)
\end{verbatim}

Please make sure that ``\verb|(|'' at 552 is aligned with the second
``\verb|(|'' at 551.

\item Page 6, lines 556--559:

If possible, we prefer an \verb|\itemize| (unnumbered) environment
instead of an \verb|\enumerate| (numbered) enviroment here.

\item Page 6, line 556: ``5 ms''. The space seems larger than others,
  please correct it.

\item Page 6, line 557: ``38 $\mu$s'' and ``20 $\mu$s''. The space
  seems larger than others, please correct it.

\item Page 7, lines 564--573:

If possible, we prefer an \verb|\itemize| (unnumbered) environment
instead of an \verb|\enumerate| (numbered) enviroment here.

\item Page 7, lines 564--573:

Along these lines, the spaces between the numbers and their units seem
larger than the normal value, please correct them.

\item Page 7, line 574: ``real-time Maude'' \by ``Real-Time Maude''

\item Page 7, footnote 5: ``time robustness'' \by ``time-robustness''

\item Page 7, footnote 5: ``tick invariance'' \by ``tick-invariance''

\item Page 7, line 635: ``time robust'' \by ``time-robust''

\item Page 7, line 637: ``tick invariant'' \by ``tick-invariant''

\item Page 7, line 665: ``nondeterminism'' \by ``non-determinism''

\item Page 8, line 672: ``nondeterminism'' \by ``non-determinism''

\item Page 8, line 697: ``such as'' \by ``similar to''

\item Page 8, line 700: ``real-time Maude'' \by ``Real-Time Maude''

\item Page 8, line 704: ``real-time Maude'' \by ``Real-Time Maude''

\item Page 8, line 706: ``real-time Maude'' \by ``Real-Time Maude''

\item Page 8, line 724: ``time robustness'' \by ``time-robustness''

\item Page 8, line 725: ``time robustness'' \by ``time-robustness''

\item Page 8, line 729: ``time robust'' \by ``time-robust''

\item Page 8, lines 731--738.

Please use ``(i)'' ``(ii)'' instead of ``1)'' ``2)'' for the numbers,
because they correspond to the \emph{Proof of Theorem 2}.

On the other hand, the indentation of this list is much larger than
others, please fix it.

\item Page 8, line 731: ``\verb|mte(...)|$=$\verb|mte(...)|'' \by
  ``\verb|mte(delta(|$t$\verb|,|$r$\verb|))| $=$
  \verb|mte(|$t$\verb|)|''

\item Page 8, line 732: ``$r\le$\verb|mte(|$t$\verb|)|'' \by ``$r\le$
  \verb|mte(|$t$\verb|)|''

\item Page 8, line 734: ``\verb|delta(|$t$ \verb|,|$0$\verb|)|'' \by
  ``\verb|delta(|$t$\verb|,|$0$\verb|)|''

\item Page 8, line 735:

``\verb|delta(delta(|$t$ \verb|,|$r$ \verb|),|$r'$ \verb|)|
  $=$\verb|delta(|$t$\verb|,|$r+r'$\verb|)|''

\by

``\verb|delta(delta(|$t$\verb|,|$r$\verb|),|$r'$\verb|)| $=$
\verb|delta(|$t$\verb|,|$r+r'$\verb|)|''

\item Page 8, line 736: ``$r+r'\le$\verb|mte(|$t$\verb|)|'' \by
  ``$r+r'\le$ \verb|mte(|$t$\verb|)|''

\item Page 8, line 737: ``\verb|mte(|$\sigma(l)$ \verb|)|'' \by
  ``\verb|mte(|$\sigma(l)$\verb|)|''

\item Page 8, line 739: ``tick invariance'' \by ``tick-invariance''

\item Page 9, lines 743--748:

If possible, we prefer an \verb|\itemize| (unnumbered) environment
instead of an \verb|\enumerate| (numbered) enviroment here.

\item Page 9, line 747: ``\emph{nonmaximal}'' \by
  ``\emph{non-maximal}''

\item Page 9, line 749: ``\emph{tick invariant}'' \by
  ``\emph{tick-invariant}''

\item Page 9, line 751: ``nonmaximal'' \by ``non-maximal''

\item Page 9, line 752: ``tick invariance'' \by ``tick-invariance''

\item Page 9, line 757: ``tick invariant'' \by ``tick-invariant''

\item Page 9, line 758: ``$\{t\} \simeq_P
  \{$\verb|delta(|$t$\verb|,|$r$\verb|)|$\}$'' \by
  ``\verb|{|$t$\verb|}| $\simeq_P$
  \verb|{delta(|$t$\verb|,|$r$\verb|)}|''.

The braces ``\verb|{}|'' should be put in \verb|\verb| mode.

\item Page 9, line 759: ``$r<$\verb|mte(|$t$\verb|)|'' \by ``$r<$
  \verb|mte(|$t$\verb|)|''

\item Page 9, lines 761--771: ``$ID$'' \by ``$\mathit{ID}$''. Please
  use the macro \verb|\mathit{}|.

\item Page 9, line 763: ``monus'' \by ``\verb|monus|''. It should be
  put in \verb|\verb| mode.

\item Page 9, line 764: ``none'' \by ``\verb|none|''. It should be put
  in \verb|\verb| mode.

\item Page 9, lines 765--766: ``$=$\verb|mteTask(none,|$L$\verb|)|''
  \by ``$=$ \verb|mteTask(none,|$L$\verb|)|''.

On one hand, ``$=$'' should be followed by a little space.

On the other hand, ``\verb|mteTask(none,|$L$\verb|)|'' should not be
broken into two lines.

\item Page 9, line 766: ``INF'' \by ``\verb|INF|''. It should be put
  in \verb|\verb| mode.

\item Page 9, line 766: ``monus'' \by ``\verb|monus|''. It should be
  put in \verb|\verb| mode.

\item Page 9, line 767: ``some$N$'' \by ``\verb|some|
  $N$''. ``\verb|some|'' should be put in \verb|\verb| mode.

\item Page 9, lines between 770 and 771: ``monus'' \by ``\verb|monus|''.

``\verb|monus|'' should be put in \verb|\verb| mode and there should
  be spaces before and after ``\verb|monus|''.

\item Page 9, lines 771--777: ``$ISRC$'' \by
  ``$\mathit{ISRC}$''. Please use the macro \verb|\mathit{}|.

\item Page 9, lines between 774 and 777: ``monus'' \by ``\verb|monus|''.

``\verb|monus|'' should be put in \verb|\verb| mode and there should
  be spaces before and after ``\verb|monus|''.

\item Page 9, lines 775--776: ``$<O...>$'' \by
  ``\verb|<|$O$\verb+:IntSrc|val:+$v$\verb|,cycle:|$T$\verb|>|''.

All things should be put in \verb|\verb| mode except ``$O$'' ``$v$''
and ``$T$'', which should be in math mode.

\item Page 9, lines 778--779. Please do not break the line 778.

\item Page 9, line 779: ``monus'' \by ``\verb|monus|''.

\item Page 9, line 783: ``time robustness'' \by ``time-robustness''

\item Page 9, line 784: ``Lemma 3'' \by ``Lemma A.1''

\item Page 9, line 788: ``Lemma 3'' \by ``Lemma A.1''

\item Page 9, lines 790--791: ``\verb|mte(|$s$\verb|)|''. Please do
  not break it into two lines.

\item Page 9, line 791: ``$r\le$\verb|mte(|$s$\verb|)|'' \by ``$r\le$
  \verb|mte(|$s$\verb|)|''

\item Page 9, lines 792--793: ``$(LTSTSHW ISRC)$'' \by
  ``$(L~T~\mathit{STS}~\mathit{HW}~\mathit{ISRC})$.

Please use the macro \verb|\mathit{}| for ``$\mathit{STS}$'' and
``$\mathit{ISRC}$''. And please do not break this into two lines.

\item Page 9, line 793: ``$ID$'' \by ``$\mathit{ID}$''. Please use the
  macro \verb|\mathit{}|.

\item Page 9, line 793: ``$(HW)$.getPc'' \by
  ``\verb|(|$HW$\verb|).getPc|''.

All things should be put in \verb|\verb| mode except ``$HW$'', which
should be in math mode.

\item Page 9, line 794: ``$ID$'' \by ``$\mathit{ID}$''. Please use the
  macro \verb|\mathit{}|.

\newcommand{\mteTask}[2]{\texttt{mteTask(}#1\texttt{,}#2\texttt{)}}
\newcommand{\deltaTask}[3]{\texttt{deltaTask(}#1\texttt{,}#2\texttt{,}#3\texttt{)}}
\newcommand{\mteIS}[1]{\texttt{mteIS(}#1\texttt{)}}
\newcommand{\deltaIS}[2]{\texttt{deltaIS(}#1\texttt{,}#2\texttt{)}}
\newcommand{\IntSrc}[3]{\texttt{<}#1\texttt{:IntSrc|val:}#2\texttt{,cycle:}#3\texttt{>}}
\newcommand{\mteIr}[1]{\texttt{mteIr(}#1\texttt{)}}
\newcommand{\mteS}[1]{\texttt{mte(}#1\texttt{)}}
\newcommand{\deltaS}[2]{\texttt{delta(}#1\texttt{,}#2\texttt{)}}

\item Page 9, equations between lines 795 and 796: it should be 
\begin{IEEEeqnarray*}{Cl}
  & \mteS{\deltaS{s}{r}}
\\  
= & \mteS{\deltaTask{\mathit{ID}}{L}{r}
\\
  & \;\;\;\;\;\;\;\;\;T~\mathit{STS}~\mathit{HW}~\deltaIS{\mathit{ISRC}}{r}}
\\
= & \verb|minimum(|\mteTask{\mathit{ID}}{\deltaTask{\mathit{ID}}{L}{r}}\verb|,|
\\
  & \verb|        |\mteIS{\deltaIS{\mathit{ISRC}}{r}}\verb|,|
\\
  & \verb|        |\mteIr{\mathit{HW}}\verb|)|\;.
\end{IEEEeqnarray*}

Note:

-- All things should be put in \verb|\verb| mode except ``$s$''
``$r$'' ``$\mathit{ID}$'' ``$L$'' ``$T$'' ``$\mathit{STS}$''
``$\mathit{HW}$'' and ``$\mathit{ISRC}$'', which should be in math
mode.

-- Please use the macro \verb|\mathit{}| for ``$\mathit{ID}$''
``$\mathit{STS}$'' and ``$\mathit{ISRC}$''.

-- After the first ``$=$'', ``\verb|deltaTask|'' should be aligned with
``$T$''.

-- After the second ``$=$'', ``\verb|mteTask|'' ``\verb|mteIS|'' and
``\verb|mteIr|'' should be aligned with each other.

\item Page 9, line 796: ``Lemmas 7, 8, and 9'' \by ``Lemmas A.5, A.6,
  and A.7''

\item Page 9, equations between lines 796 and 797: it should be 
\begin{IEEEeqnarray*}{Cl}
  & \mteS{\deltaS{s}{r}}
\\  
= & \verb|minimum(|\mteTask{\mathit{ID}}{L}~\verb|monus|~r~\verb|,|
\\
  & \verb|        |\mteIS{\mathit{ISRC}}~\verb|monus|~r~\verb|,|
\\
  & \verb|        |\mteIr{\mathit{HW}}~\verb|monus|~r~\verb|)|
\\
= & \verb|minimum(|\mteTask{\mathit{ID}}{L}\verb|,|
\\
  & \verb|        |\mteIS{\mathit{ISRC}}\verb|,|
\\
  & \verb|        |\mteIr{\mathit{HW}}\verb|)|~\verb|monus|~r
\\
= & \mteS{s}~\verb|monus|~r\;.
\end{IEEEeqnarray*}

Note:

-- All things should be put in \verb|\verb| mode except ``$s$''
``$r$'' ``$\mathit{ID}$'' ``$L$'' ``$\mathit{HW}$'' and
``$\mathit{ISRC}$'', which should be in math mode.

-- Please use the macro \verb|\mathit{}| for ``$\mathit{ID}$'' and
``$\mathit{ISRC}$''.

-- ``\verb|mteTask|'' ``\verb|mteIS|'' and ``\verb|mteIr|'' should be
aligned with each other.

-- There should be spaces before and after ``\verb|monus|''.

\item Page 9, line 798: ``$r$monus$0$'' \by ``$r~\verb|monus|~0$''

\item Page 9, line 802: ``$ID$'' \by ``$\mathit{ID}$''. Please use the
  macro \verb|\mathit{}|.

\item Page 9, equations between lines 803 and 804: it should be 
\begin{IEEEeqnarray*}{Cl}
  & \deltaS{\deltaS{s}{r}}{r'}
\\  
= & \verb|(|\deltaTask{\mathit{ID}}{\deltaTask{\mathit{ID}}{L}{r}}{r'}
\\
  & \verb| |~T~\mathit{STS}~\mathit{HW}~\deltaIS{\deltaIS{\mathit{ISRC}}{r}}{r'}\verb|)|~\mbox{,}
\end{IEEEeqnarray*}

Note:

-- All things should be put in \verb|\verb| mode except ``$s$''
``$r$'' ``$r'$'' ``$\mathit{ID}$'' ``$L$'' ``$T$'' ``$\mathit{STS}$''
``$\mathit{HW}$'' and ``$\mathit{ISRC}$'', which should be in math
mode.

-- Please use the macro \verb|\mathit{}| for ``$\mathit{ID}$''
``$\mathit{STS}$'' and ``$\mathit{ISRC}$''.

-- The last comma should be in text mode.

\item Page 9, equations between lines 804 and 805: it should be 
\begin{IEEEeqnarray*}{Cl}
  & \deltaS{s}{r+r'}
\\  
= & \verb|(|\deltaTask{\mathit{ID}}{L}{r+r'}
\\
  & \verb| |~T~\mathit{STS}~\mathit{HW}~\deltaIS{\mathit{ISRC}}{r+r'}\verb|)|~\mbox{.}
\end{IEEEeqnarray*}

Note:

-- All things should be put in \verb|\verb| mode except ``$s$''
``$r+r'$'' ``$\mathit{ID}$'' ``$L$'' ``$T$'' ``$\mathit{STS}$''
``$\mathit{HW}$'' and ``$\mathit{ISRC}$'', which should be in math
mode.

-- Please use the macro \verb|\mathit{}| for ``$\mathit{ID}$''
``$\mathit{STS}$'' and ``$\mathit{ISRC}$''.

-- The last period should be in text mode.

\item Page 9, line 805: ``$ID$'' \by ``$\mathit{ID}$''. Please use the
  macro \verb|\mathit{}|.

\item Page 9, lines 805--806:
  ``$=$\verb|delta-Task|$(ID$\verb|,|$L$\verb|,|$r+r'$\verb|)|'' \by
  ``$=\deltaTask{\mathit{ID}}{L}{r+r'}$''.

All things should be put in \verb|\verb| mode except ``$=$''
``$\mathit{ID}$'' ``$L$'' and ``$r+r'$'', which should be in math
mode. Please use the macro \verb|\mathit{}| for
``$\mathit{ID}$''.

\item Page 9, line 807: ``\verb|delta|$IS(...$\verb|)|'' \by
  ``$\deltaIS{\deltaIS{\mathit{ISRC}}{r}}{r'}$''.

All things should be put in \verb|\verb| mode except
``$\mathit{ISRC}$'' ``$r$'' and ``$r'$'', which should be in math
mode. Please use the macro \verb|\mathit{}| for ``$\mathit{ISRC}$''.

\item Page 9, line 808: ``$ISRC$'' \by ``$\mathit{ISRC}$''. Please use
  the macro \verb|\mathit{}|.

\item Page 9, lines 808--809: ``monus'' \by ``\verb|monus|''.

``\verb|monus|'' should be put in \verb|\verb| mode and there should
  be spaces before and after ``\verb|monus|''.

\item Page 10, line 813: ``$ISRC$'' \by ``$\mathit{ISRC}$''. Please use
  the macro \verb|\mathit{}|.

\item Page 10, equations between lines 814 and 815: it should be 
\begin{IEEEeqnarray*}{Cl}
  & \mteS{L~T~\mathit{STS}~\mathit{HW}~\mathit{ISRC}}
\\  
= & \verb|minimum(|\mteTask{\mathit{ID}}{L}\verb|,|
\\
  & \verb|        |\mteIS{\mathit{ISRC}}\verb|,| \mteIr{\mathit{HW}}\verb|)|
\\
= & \verb|minimum(|\mteTask{\mathit{ID}}{L}\verb|,|~0~\verb|,| \mteIr{\mathit{HW}}\verb|)|
\\
= & 0~\mbox{.}
\end{IEEEeqnarray*}

Note:

-- All things should be put in \verb|\verb| mode except ``$L$''
``$T$'' ``$\mathit{STS}$'' ``$HW$'' ``$\mathit{ISRC}$''
``$\mathit{ID}$'' and ``$0$'', which should be in math mode.

-- Please use the macro \verb|\mathit{}| for ``$\mathit{STS}$''
``$\mathit{ISRC}$'' and ``$\mathit{ID}$''.

-- ``\verb|mteTask|'' and ``\verb|mteIS|'' should be aligned with each
other.

-- The last period should be in text mode.

\item Page 10, line 816: ``Lemma 3'' \by ``Lemma A.1''

\item Page 10, line 817: ``tick invariance'' \by ``tick-invariance''

\item Page 10, lines 818--819: ``\verb|cor-rect|'' \by
  ``\verb|correct|''.  Please do not break it into two parts.

\item Page 10, line 819: ``Lemma 6'' \by ``Lemma A.4''

\item Page 10, line 819:
  ``$\mbox{s}\simeq_P\deltaS{\mbox{s}}{\mbox{r}}$'' \by
  ``$\verb|{|s\verb|}|\simeq_P\verb|{|\deltaS{s}{r}\verb|}|$''.

All things should be put in \verb|\verb| mode except ``$s$''
``$\simeq_P$'' and ``$r$''.

\item Page 10, line 822: ``$(L T STS HW ISRC)$'' \by
  ``$(L~T~\mathit{STS}~\mathit{HW}~\mathit{ISRC})$''.

Please use the macro \verb|\mathit{}| for ``$\mathit{STS}$'' and
``$\mathit{ISRC}$''.

\item Page 10, line 822: ``$(HW)$.getPc'' \by
  ``\verb|(|$HW$\verb|).getPc|''.

All things should be put in \verb|\verb| mode except ``$HW$'', which
should be in math mode.

\item Page 10, line 823: ``$ID$'' \by ``$\mathit{ID}$''. Please use
  the macro \verb|\mathit{}|.

\item Page 10, line 828: ``tick invariant'' \by ``tick-invariant''

\item Page 10, lines 828--829: ``\verb|taskTime-out|'' \by
  ``\verb|taskTimeout|''.

Please do not break it into two parts.

\item Page 10, line 830: ``$ID$'' \by ``$\mathit{ID}$''. Please use
  the macro \verb|\mathit{}|.

\item Page 10, line 831: ``$ID$'' \by ``$\mathit{ID}$''. Please use
  the macro \verb|\mathit{}|.

\item Page 10, line 834: ``tick invariance'' \by ``tick-invariance''

\item Page 10, line 910: ``German'' \by ``Chinese''

\item Page 10, lines 915--916: ``real-time Maude'' \by ``Real-Time
  Maude''

\item Page 10, lines 923--924: ``real-time Maude'' \by ``Real-Time
  Maude''

\end{itemize}

\end{document}
